### 2025-05-30 docs/paper/appendix.tex
initial commit

\begin{appendices}
    \section{Proofs}
    We have collected a series of proofs of the claims we made in the main text.

    \section{Benchmarks}
    \label{app:benchmarks}
    Complete list of results for the benchmarks presented in \autoref{sec:benchmarks}.
    The legend is as follows:
    \textit{Output} indicates the result produced by the solver (i.e., optimal, unbounded, infeasible or unspecified),
    \textit{Prec} indicates the number of bits used in the last floating-point number representation,
    \textit{Ref} indicates the number of refinements,
    and \textit{time} is the time in seconds.

\end{appendices}

### 2025-05-30 docs/paper/glossary.tex
initial commit

\newglossaryentry{oop}{
    name={Object-Oriented Programming},
    first={Object-Oriented Programming (OOP)},
    text={OOP},
    description={
            Object-Oriented Programming is a programming paradigm based on the concept of objects, which can hold a state in the form of fields, and methods, in the form of function with access to the object's state.
        }
}
\newglossaryentry{api}{
    name = {Application Programming Interface},
    first = {Application Programming Interface (API)},
    text = {API},
    plural={APIs},
    firstplural={Application Programming Interfaces (APIs)},
    description = {
            An application programming interface (API) defines a way for two software components to communicate with each other.
        }
}
\newglossaryentry{smt}
{
    name={Satisfiability Modulo Theories},
    first={Satisfiability Modulo Theories (SMT)},
    text={SMT},
    description={
            A decision problem for logical formulas with respect to combinations of background theories
            expressed in classical first-order logic with equality.
        }
}
\newglossaryentry{fol}{
    name={First-order logic},
    first={first-order logic (FOL)},
    text={fol},
    description={
            Expressive formal system that allows the following statements:
            \begin{itemize}
                \item Constants ($x, y$)
                \item Functions ($f(x)$)
                \item Relationships ($x > y$)
                \item Connectives ($\land, \lor, \lnot, \implies, \iff$)
                \item Quantifiers ($\forall, \exists$)
            \end{itemize}
        }
}
\newglossaryentry{smtp}{
    name={SMT problem},
    text={SMT problem},
    plural={SMT problems},
    description={
            Decision problems that are true or false depending on whether a given \gls{fol} formula
            is true or false in respect to a given background theory. \\
            In the context of computer science, the background theories are usually include
            arithmetic, bitvectors, arrays, etc.
        }
}
\newglossaryentry{sat}{
    first={Satisfiability (SAT)},
    name={Satisfiability},
    text={SAT},
    description={
            A formula is satisfiable if it is possible to find a set of values for its variables
            that makes the formula true.
            On the other hand, a formula is unsatisfiable if such set does not exists.
            \begin{multline*}
                \text{Example} \\
                (a \lor c) \land (b \lor c) \land (\neg a \lor \neg c) \\
                \text{is satisfiable with the assignment } a = 1, b = 1, c = 0 \\
            \end{multline*}
        }
}
\newglossaryentry{convopt}{
    name={Convex optimization},
    text={convex optimization},
    description={
            A convex optimization problem is a problem where the objective function and the constraints
            are convex functions. \\
            A convex function is a function whose domain is a convex set and that satisfies the following
            property:
            \begin{equation*}
                f(\lambda x + (1 - \lambda)y) \leq \lambda f(x) + (1 - \lambda)f(y)
            \end{equation*}
            for all $x, y \in \text{dom}(f)$ and $\lambda \in [0, 1]$.
        }
}
\newglossaryentry{cnf}{
    first={Conjunctive Normal Form (CNF)},
    name={Conjunctive Normal Form},
    text={CNF},
    description={
            A formula is in \gls{cnf} if it is a conjunction of clauses, where a clause is a
            disjunction of literals. \\
            A literal can be a boolean variable or its negation. \\
            \\
            \begin{equation*}
                \bigwedge_{i=1}^n \bigvee_{j=1}^{m_i} l_{ij}
            \end{equation*}
        }
}
\newglossaryentry{lp}{
    first={Linear Programming (LP)},
    name={Linear Programming},
    text={LP},
    description={
            A Linear Programming problem is an optimization problem where the objective function and the constraints
            are linear functions. \\
            A typical Linear Programming problem has the following form:
            \begin{equation*}
                \begin{aligned}
                     & \text{maximize}   & c^T x      \\
                     & \text{subject to} & A x \leq b \\
                     &                   & x \geq 0
                \end{aligned}
            \end{equation*}
            where $x \in \mathbb{R}^d$ is the vector of variables to be determined, $c \in \mathbb{R}^d$ and $b \in \mathbb{R}^n$ are vectors of coefficients, and $A \in \mathbb{R}^{n \times d}$ is a matrix of coefficients.
        }
}
\newglossaryentry{qf-lia}{
    name={QF\_LIA},
    text={QF\_LIA},
    description={
            Quantifier-free linear integer arithmetic. In essence, Boolean combinations of inequations between linear polynomials over integer variables.
        }
}
\newglossaryentry{qf-lra}{
    name={QF\_LRA},
    text={QF\_LRA},
    description={
            Quantifier-free linear real arithmetic. In essence, Boolean combinations of inequations between linear polynomials over real variables.
        }
}
\newglossaryentry{nnf}{
    name={Negation Normal Form},
    text={NNF},
    first={Negation Normal Form (NNF)},
    description={
            A formula where the negation operator $\neg$ is only applied to variables. \\
            $\neg a$ is a NNF formula, while $\neg (a \lor b)$ is not.
        }
}
\newglossaryentry{dpll}{
    name={DPLL algorithm},
    text={DPLL},
    first={Davis-Putnam-Logemann-Loveland (DPLL)},
    description={
            A complete \gls{sat} backtracking algorithm for deciding the satisfiability of propositional logic formulae in \gls{cnf}.
        }
}
\newglossaryentry{dp}{
    name={DP algorithm},
    text={DP},
    first={Davis-Putnam (DP)},
    description={
            A complete \gls{sat} algorithms that uses the resolution inference rule to decide the satisfiability of propositional logic formulae in \gls{cnf}.
        }
}
\newglossaryentry{mps}{
    name={Mathematical Programming System},
    text={MPS},
    first={Mathematical Programming System (MPS)},
    description={
            A common file format for representing \gls{lp} problems.
            Developed by IBM, it is supported by most commercial \gls{lp} solvers.
        }
}
\newglossaryentry{soi}{
    name={Sum of Infeasibilities},
    text={SoI},
    first={Sum of Infeasibilities (SoI)},
    description={
            A metric used to evaluate the quality of an \gls{lp} relaxation.
            It is the sum of the infeasibilities of the constraints that are violated by the solution.
        }
}
\newglossaryentry{onnx}{
    name={Open Neural Network Exchange},
    text={ONNX},
    first={Open Neural Network Exchange (ONNX)},
    description={
            An open-source format for representing deep learning models.
            It is supported by a wide range of tools and libraries.
        }
}
\newglossaryentry{cdlc}{
    name={Conflict Driven Learning Clause},
    text={CDLC},
    first={Conflict Driven Learning Clause (CDLC)},
    description={
            A clause that is added to the \gls{cnf} formula after a conflict is detected during the \gls{sat} solving process.
            It is used to prevent the solver from exploring the same path that led to the conflict.
        }
}

### 2025-05-30 docs/paper/main.tex
initial commit

\documentclass{article}

\input{setup.tex}

\begin{document}

\title{Delta-Complete Linear Programming}

\author{Oliver Sch\"{o}n \and
Ernesto Casablanca \and
Sadegh Soudjani \and
Paolo Zuliani
}

\begin{comment}
\institute{O. Sh\"{o}n,E. Casablanca \at Newcastle University, Newcastle upon Tyne, United Kingdgom \\ \email{e.casablanca2@newcastle.ac.uk}, \email{o.schoen2@newcastle.ac.uk}
\and
S. Soudjani \at Max Planck Institute for Software Systems, Kaiserslautern, Germany \\ \email{sadegh@mpi-sws.org}
\and
P. Zuliani \at Universit\`{a} di Roma ``La Sapienza'', Rome, Italy\\ \email{zuliani@di.uniroma1.it}
}
\end{comment}

\maketitle

\begin{abstract}
  Ensuring the safety of AI-enabled systems, particularly in high-stakes domains like autonomous driving and healthcare, has become increasingly critical.
  Traditional formal verification tools fall short when faced with the opaque, black-box nature of AI components and the sheer scale of modern applications.
  To address these challenges, we introduce Lucid, a new tool designed specifically for the safety verification and synthesis of black-box systems governed by discrete-time stochastic dynamics.

  Lucid employs a data-driven methodology rooted in control barrier certificates, which are learned directly from system trajectory data to ensure formal safety guarantees.
  We use conditional mean embeddings to embed data into a reproducing kernel Hilbert space (RKHS), where it constructs an RKHS ambiguity set that can be inflated to robustify the result to out-of-distribution behavior.
  To generalize beyond safety, we provide theoretical foundations for applying Lucid to broader classes of temporal logic specifications.

  A key innovation within Lucid is its use of a finite Fourier expansion to reformulate a semi-infinite non-linear optimization problem into a tractable linear program.
  The resulting spectral barrier allows us to leverage the fast Fourier transform to generate the relaxed problem efficiently, offering a scalable yet distributionally robust framework for verifying safety.
  Lucid thus offers a robust and efficient verification framework, able to handle the complexities of modern black-box systems while providing formal guarantees of safety.
\end{abstract}

\section{Introduction}
\label{sec:intro}

Lucid is in implemented in C++ and it is meant to be used as a library.
It provides a set of interfaces that allow users to have an high level of control and flexibility over the verification process.
We also provide a Python wrapper, called PyLucid, to facilitate the integration of the tool into existing workflows and effortlessly leverage well-established libraries such as NumPy~\cite{numpy} and SciPy~\cite{scipy}.
Lucid is available as an open-source project on GitHub at \url{https://github.com/TendTo/lucid}.
More technical details about the implementation can be found in the documentation at \url{https://tendto.github.io/lucid/}.

\section{Problem Statement}
\label{sec:problem-statement}

\subsection{Notation}
\label{sec:notation}

% Spaces and numbers
We denote the sets of positive integers and non-negative reals as $\N_{>0}$ and $\R_{\geq 0}$, respectively.
% Probability theory
Consider a Polish sample space $\X$ \cite{bogachev2007measure}.
Let $(\X,\borel{\X},\P)$ be the underlying probability space equipped with a Borel $\sigma$-algebra $\borel{\X}$ defined over $\X$, i.e., the smallest $\sigma$-algebra containing open subsets of $\X$, and a probability measure $\P$.
For a random variable $X$, let $p_X$ be the pushforward probability measure of $\P$ under $X$ such that $X\sim p_X(\cdotx)$.

The expected value of a function $f(X)$ on $\X$ is written as $\E_{p_X}[f(X)]$. If it is clear from the context, we abbreviate and write $\E[f(X)]$.
We denote the set of all probability measures for a given measurable space $(\X,\borel{\X})$ as $\mathcal{P}(\X)$.

The $n$-dimensional Gaussian measure with mean $\mu\in\mathbb{R}^n$ and covariance matrix $\Sigma\in\mathbb{R}^{n\times n}$ is given by
\begin{equation*}
  \mathcal N(dx|\mu, \Sigma) := \frac{dx}{ \sqrt{(2\pi)^n \left|\Sigma\right| }}\exp\left[-\frac{1}{2}(x-\mu)\T\Sigma^{-1\!}(x-\mu)\right],
\end{equation*}
where $|\Sigma|$ is the determinant of $\Sigma$.
The Dirac delta measure $\delta_a:\borel{\X}\rightarrow [0,1]$ concentrated at a point $a\in\X$ is defined as $\delta_a(A)=1$ if $a\in A$ and $\delta_a(A)=0$ otherwise, for any measurable set $A\in\borel{\X}$.
We denote the uniform distribution over $\X$ as $\mathcal{U}_\X$ with realizations $x\sim\mathcal{U}_\X(\cdotx)$.

For two measurable spaces $(\X,\borel{\X})$ and $(\Y,\borel{\Y})$, a \emph{probability kernel} is a mapping $\p: \X \times \borel{\Y}\rightarrow  [0,1]$ such that $\p(X=x,\cdotx):\borel{\Y}\rightarrow[0,1]$ is a probability measure for all $x\in\X$, and $\p(\cdotx, B): \X\rightarrow [0,1]$ is measurable for all  $B\in\borel{\Y}$.
A probability kernel associates to each point $x\in\X$ a measure denoted by $\p(\cdotx|X=x)$.

% Linear algebra
The transpose of a vector or matrix $A$ is indicated as $A\T$.
Let the $N\times N$ dimensional identity matrix be given by $I_N$.
Let $X_N:=[x_i]_{i=1}^N$ be a column vector with $x_i\in\X$.
We denote the element-wise evaluation of a function $f:\X\rightarrow\R$ on $X_N$ as $f(X_N):=[f(x_i)]_{i=1}^N$.
Similarly, we may write $A = [a_{ij}]_{i,j=1}^N$ to denote a matrix with its elements.

\subsection{Discrete-Time Stochastic Systems}
In this work, we consider systems expressible as Markov decision processes over continuous state and input spaces, formally defined as follows.
\begin{definition}[Markov decision process (MDP)]
  An MDP is a tuple $\M=(\X,\X_0,\U,\Tr)$, comprising a state space $\X\subset\R^n$ with states $x\in\X$; initial states $x_0\in \X_0\subset\X$; an input space $\U$ with inputs $u\in\U$; and a probability kernel $\Tr:\X\times\U\times\borel{\X}\rightarrow[0,1]$.
\end{definition}

In every execution, given a current state $x\in\X$ and control input $u\in\U$, the MDP evolves to a consecutive state $x_{+}\in\X$, which is obtained as a realization $x_{+}\sim\Tr(\,\cdot\,|X=x,U=u)$.
As a notable class of systems that can be captured using MDPs, we may consider black-box systems with Markovian discrete-time stochastic dynamics, namely
\begin{equation}
  \label{eq:model}
  \M: \left\{ \begin{array}{ll}
    x_{t+1} & = f(x_t,u_t,w_t),\quad w_t\sim p_w(\cdotx), \\
    y_t     & = x_t,
  \end{array} \right.
\end{equation}
where the system state, control input, and observation at the $t^{\text{th}}$ time-step are denoted by $x_t$, $u_t$, and $y_t$, respectively.
The state evolution of the system, described by the function $f:\X\times\U\times\mathbb{W}\rightarrow\X$,
is subject to {independent, identically distributed (i.i.d.) noise} $w_t\sim p_w(\cdotx)$ supported on a set $\mathbb{W}$.

\paragraph{Implementation}

When using \lucid, the user needs to provide a set of sampled trajectories from the system.
This is often achieved by defining a function that takes as input the current state and control input and returns the next state, adding an i.i.d. noise sampled from an appropriate distribution, or it may be collected from a simulator or a real-world system.
The sampled trajectories are then fed into \lucid, either programmatically or through a file \todo{CSV, HDF5, other?}.
\todo{Allow a simple way to define the system model? Maybe latex2sympy?}
\todo{Graphical interface?}

\subsection{System Safety}
In this paper, we wish to synthesize a controller $\pi$ such that the closed-loop system $\pi\times\M$ is safe.
Particularly, we restrict our attention to \emph{stationary} policies of the form $\pi:\X\rightarrow\U$, as for MDPs there always exists a stationary policy that is optimal.
For an MDP $\M$, we characterize \emph{safety} as a property of its state. More precisely, a system $\pi\times\M$ is said to be safe if for any initial state $x_0\in \X_0$ the system does not enter an \emph{unsafe set} of states $\X_u\subset\X$.
Note that general stochastic systems do not admit a binary notion of safety.
Thus, we quantify the \emph{probability} of reaching $\X_u$ in a given finite horizon $T\in\N_{>0}$ and compute its complement.
A (finite-horizon) \emph{safety specification} $\psi_{\text{safe}:=(\X_u,T)}$ is hence fully characterized by an unsafe set $\X_u$ and a time horizon $T$.
The system $\pi\times\M$ satisfies $\psi_{\text{safe}}$ with probability at least $p\in(0,1)$ if the probability of its trajectories starting in $\X_0$ and avoiding $\X_u$ within horizon $T$ is at least $p$. This is denoted by $P^\pi_{\text{safe}}(\M):=\P(\pi\times\M\satisfies\psi_{\text{safe}})\geq p$~\cite{BK08}.

\paragraph{Implementation}

\lucid understands \texttt{RectSet}s and \texttt{Multiset}s \todo{PolytopeSet?}.
\todo{Set definition from file?}.
These are used to indicate the initial $\X_0$ set and unsafe set $\X_u$ when defining the safety specification $\psi_{\text{safe}}$.
Once the system is fully defined, the time horizon $T$ is set as a parameter of the verification process.
\todo{Support other kinds of properties other than safety (e.g., reachability)?}

\subsection{Control Barrier Certificates}
\label{sec:cbc}
Whilst certifying the safety of a stochastic system is generally challenging, \emph{control barrier certificates} (CBCs) and \emph{control barrier functions} (CBFs) leverage the concept of set invariance to arrive at an abstraction-free formulation. This has made CBCs/CBFs popular tools for safety verification and synthesis~\cite{prajna2006barrier,cosner2023generative}.
We briefly recall the definition of a CBC.
\begin{definition}[Control barrier certificate (CBC)]\label{def:cbc}
  A function $\B:\X\rightarrow\R_{\geq 0}$ is called a CBC of an MDP $\M=(\X,\X_0,\U,\Tr)$ with reference to an unsafe set $\X_u$, if we have
  \begin{itemize}
    \item[(a)] $\forall x_0\in \X_0\!:\,\B(x_0)\leq\eta$;
    \item[(b)] $\forall x_u\in \X_u\!:\,\B(x_u)\geq\gamma$; and
    \item[(c)] $\forall x\in\X,\exists u\in\U\!:\,\E_{\Tr}[\,\B(X^+)\mid X=x,\,U=u\,] -\B(x) \leq  c;$
  \end{itemize}
  for some constants $\gamma>\eta\geq0$ and $c\geq 0$.
\end{definition}
If one can find a CBC for a system $\M$, then, a lower bound on the probability of $\M$ being safe is given by the following proposition due to \cite{kushner1967stochastic}.
\begin{proposition}[Finite-horizon safety]
  \label{prop:reach}
  Consider an MDP $\M=(\X,\X_0,\U,\Tr)$ and a safety specification $\psi_{\text{safe}}=(\X_u,T)$. Suppose there exists a CBC $B$ w.r.t. $\X_u$ (Definition~\autoref{def:cbc}) with constants $\eta$, $\gamma$, and $c$. Then, there exists a stationary policy $\pi$ such that
  $$P^\pi_{\text{safe}}(\M)\geq 1- \frac{\eta + cT}{\gamma}.$$
\end{proposition}

\paragraph{Implementation}

When verifying the safety of a system, \lucid will search for a CBC $\B$ that satisfies the conditions in Definition~\ref{def:cbc}.
If it finds it, it will return the constants $\eta$, $\gamma$, and $c$, as well as the CBC $\B$ itself, which becomes a certificate of safety for the system $\M$.
The template of the barrier function is explored later in section~\ref{sec:benchmarks}.

\subsection{Kernel Mean Embeddings}

\subsection{Data-Driven Barrier Formulation}
\label{sec:data-driven-barrier-formulation}
Compared to the typical spatial form \eqref{eq:representer-form} based on spatial support vectors $\bar{x}_1,\bar{x}_2,\ldots\in\X$, the spectral form \eqref{eq:representer-form-spectral} is a much more efficient representation for higher-dimensional systems.
The number of spatial support vectors needed to construct adequately expressive barriers grows exponentially in the dimensionality of the system. We avoid this.

Apart from the memory efficiency of the spectral barrier form, we can apply the same idea to collapse the complex CME term in \eqref{eq:semiinf-prog-kushner} via the \emph{fast Fourier transform} (FFT). That is we obtain spectral coefficients $H\in\R^{(2M+1)\times (2M+1)}$ s.t.
\begin{equation}
    k^N_{\hat{X}}(x)\T\left[ K^N_{\hat{X}}+N\lambda I_N\right]^{-1\!} (\Phi_{M, \hat{X}^{+\!}}^{N})\T b \approx \phi_M(x)\T H b,\label{eq:cme-term-spectral-approx}
\end{equation}
where $\Phi_{M, \hat{X}^{+\!}}^{N} := [\phi_M(\hat{x}^+_1),\ldots,\phi_M(\hat{x}^+_N)]$.
Whilst projection onto a truncated Fourier basis introduces an approximation error, the error decreases exponentially with the cardinality of wavenumbers in the basis \cite{rahimi2007random}. 
% Our numerical results suggest that the empirical error is negligible.

Substituting the barrier $B\in\Hilbert_M$ of the form \eqref{eq:representer-form-spectral} and the approximation of the CME term in \eqref{eq:cme-term-spectral-approx} into the SIP \eqref{eq:semiinf-prog}, we obtain the \emph{semi-infinite linear program} (SILP)
\begin{subequations}
\begin{align}
    \min_{b, c, \eta, \gamma} \; &\frac{\eta + cT}{\gamma},\label{eq:semiinfLP-prog-objective}\\
    \text{s.t.}\quad
    &\forall x_0\in\X_0:\,\phi_M(x_0)\T b\leq\eta,\label{eq:semiinfLP-prog-initial}\\
    &\forall x_u\in\X_u:\,\phi_M(x_u)\T b\geq\gamma,\label{eq:semiinfLP-prog-unsafe}\\
    &\forall x\in\X: \, \phi_M(x)\T (H b - b) \leq c - \varepsilon\bar{B}\kappa,\label{eq:semiinfLP-prog-kushner}\\
    & \forall x\in\X:\,\phi_M(x)\T b\geq 0,\label{eq:semiinfLP-prog-positive}\\
    &c\geq 0,\,\gamma>\eta\geq 0,\,b\in\R^{2M+1},\nonumber
\end{align}\label{eq:semiinfLP-prog}%
\end{subequations}
with coefficients $\kappa\geq\sigma_f$ and $\bar{B}\geq\norm{b}_2$.

\subsection{Finite-Constraint Relaxation}\label{sec:finite-constraint-relaxation}
There exist results that establish deterministic sampling-based bounds for multivariate trigonometric polynomials \cite{cifuentes2017sampling,pfister2018bounding} that can be applied to the bandlimited spectral barrier in \eqref{eq:representer-form-spectral}. This allows us to relax the SILP \eqref{eq:semiinfLP-prog} to a \emph{linear program} (LP) with finitely many constraints by sampling a finite set
$X_{\hat{N}} \subset\X$ of cardinality $\hat{N}$.
By choosing $\hat{N}=Q^n$ equidistant points that form a discrete lattice of points to cover the (state) space, the corresponding constraints can be efficiently evaluated in $\mathcal{O}(Q\log(Q))$ operations using the inverse FFT.
Note that this also substantially reduces the number of evaluations of the computationally expensive CME term in \eqref{eq:semiinf-prog-kushner}, which requires $\mathcal{O}(N^2)$ operations per evaluation. Refer to the Petersen-Middleton theorem \cite{petersen1962sampling}, which generalizes the Nyquist-Shannon sampling theorem to higher-dimensional Euclidean spaces, for further details.

We use the following result by \cite{pfister2018bounding}.
\begin{lemma}[Trigonometric bounds]\label{lem:trig-bound}
    Consider a real-valued trigonometric polynomial $f:[0,1]^n\rightarrow\R$ (cf. \eqref{eq:representer-form-spectral}) with maximum degree $d\in\N_{\geq 0}$ and a sampling lattice $\Theta_Q:=\{\frac{2\pi l}{Q},\, l=0,\ldots,Q-1\}$ with $Q\geq 2d+1$.
    Let $\bar{f}_{Q^n}:=\max_{z\in\Theta^n_Q} f(z)$ and $\underbar{f}_{Q^n}:=\min_{z\in\Theta^n_Q} f(z)$. Then, we have that
    \begin{equation*}
        \frac{1}{2}\big(\bar{f}_{Q^n} + \underbar{f}_{Q^n} - C_{Q^n}\left(\bar{f}_{Q^n}-\underbar{f}_{Q^n}\right)\big)
        \leq
        f(z)
        \leq
        \frac{1}{2}\big(\bar{f}_{Q^n} + \underbar{f}_{Q^n} + C_{Q^n}\left(\bar{f}_{Q^n}-\underbar{f}_{Q^n}\right)\big),
    \end{equation*}
    with a coefficient given by
    \setlength{\belowdisplayskip}{3pt}
    \begin{equation*}
        C_{Q^n} := \left(1-\frac{2d}{Q}\right)^{-\frac{n}{2}}.
    \end{equation*}
\end{lemma}
% \Oliver{The paper \cite{pfister2018bounding} provides a more complex expression for $C_{Q^n}$ that I put as [...]. They also provide the upper bound I use so far.}

Via Lemma~\ref{lem:trig-bound}, we obtain a finite-constraint relaxation of the SIP \eqref{eq:semiinf-prog} based on the constraint-tightening reasoning
\begin{equation*}
    \frac{1}{2}\big(\mathrm{max}_{\hat{N}}^\X + \mathrm{min}_{\hat{N}}^\X - C_{\hat{N}}\left(\mathrm{max}_{\hat{N}}^\X-\mathrm{min}_{\hat{N}}^\X\right)\big)\geq \mathrm{lb}
    \quad\Longrightarrow\quad
    \forall x\in\X: f(x) \geq \mathrm{lb},
\end{equation*}
where $\mathrm{max}_{\hat{N}}^\X:=\max_{x\in X_{\hat{N}}} \left\lbrace\phi_M(x)\T b\right\rbrace$ and $\mathrm{min}_{\hat{N}}^\X:=\min_{x\in X_{\hat{N}}} \left\lbrace\phi_M(x)\T b\right\rbrace$ for some desired lower bound $\mathrm{lb}\in\R$.
Thus, we obtain strengthened constraints of the form 
\begin{align*}
    &\frac{1}{2}\big(\mathrm{max}_{\hat{N}}^\X + \mathrm{min}_{\hat{N}}^\X - C_{\hat{N}}\left(\mathrm{max}_{\hat{N}}^\X-\mathrm{min}_{\hat{N}}^\X\right)\big) \geq \mathrm{lb},\\
    \Leftrightarrow\hspace{10pt} &
    \mathrm{min}_{\hat{N}}^\X \geq \frac{2}{C_{\hat{N}}+1}\mathrm{lb} + \frac{C_{\hat{N}}-1}{C_{\hat{N}}+1}\mathrm{max}_{\hat{N}}^\X.
\end{align*}
For an upper bound $\forall x\in\X: f(x) \leq \mathrm{ub}$, we obtain analogous constraints of the form
\begin{equation*}
    \mathrm{max}_{\hat{N}}^\X \geq \frac{2}{C_{\hat{N}}+1}\mathrm{ub} + \frac{C_{\hat{N}}-1}{C_{\hat{N}}+1}\mathrm{min}_{\hat{N}}^\X.
\end{equation*}

\vfill

\section{Benchmarks}
\label{sec:benchmarks}

\section*{Acknowledgements}
The authors thank \dots.

\bibliographystyle{ieeetr}
\bibliography{resources}

\newpage
\input{appendix.tex}

\end{document}

### 2025-06-09 bindings/pylucid/plot.py
feat: include plots for estimator and feature map

@@ -1,5 +1,9 @@
-from ._pylucid import RectSet, MultiSet, FeatureMap, Estimator, LucidNotSupportedException, log_warn
+from typing import TYPE_CHECKING
+from ._pylucid import RectSet, MultiSet, FeatureMap, Estimator, LucidNotSupportedException, log_warn, Set
 import numpy as np
+
+if TYPE_CHECKING:
+    from typing import Callable
 
 try:
     import matplotlib.pyplot as plt
@@ -169,6 +173,176 @@ def plot_solution_2d(
     ax.set_zlabel("Barrier value")
     ax.legend()
     plt.show()
+
+
+def plot_estimator_1d(
+    estimator: "Estimator",
+    x_samples: "np.typing.NDArray[np.float64]",
+    xp_samples: "np.typing.NDArray[np.float64]",
+    X_bounds: "RectSet | None" = None,
+    X_init: "Set | None" = None,
+    X_unsafe: "Set | None" = None,
+):
+    """Plot the estimator's predictions against the true system dynamics in 2D.
+
+    Args:
+        estimator: The estimator to be evaluated
+        x_samples: Sample points in the state space
+        xp_samples: Sample points at the next time step
+        X_init: Initial set of states
+        X_unsafe: Unsafe set of states
+    """
+    if X_bounds is not None:
+        plt.xlim(X_bounds.lower_bound[0], X_bounds.upper_bound[0])
+
+    if X_init is not None:
+        plot_set_1d(X_init, label="Initial Set", color="green")
+    if X_unsafe is not None:
+        plot_set_1d(X_unsafe, label="Unsafe Set", color="red")
+
+    xp_pred = estimator.predict(x_samples)
+
+    # Plot the true vs predicted next states
+    plt.scatter(x_samples, xp_samples, label="Ground truth", color="blue", marker="o")
+    plt.scatter(x_samples, xp_pred, label="Estimator prediction", color="orange", marker="x")
+    plt.title("Estimator Predictions vs True Dynamics")
+    plt.xlabel("State")
+    plt.ylabel("Next State")
+    plt.legend()
+    plt.show()
+
+
+def plot_estimator_2d(
+    estimator: "Estimator",
+    x_samples: "np.typing.NDArray[np.float64]",
+    xp_samples: "np.typing.NDArray[np.float64]",
+    X_bounds: "RectSet | None" = None,
+    X_init: "Set | None" = None,
+    X_unsafe: "Set | None" = None,
+):
[…]

### 2025-06-09 bindings/pylucid/dreal.py
feat: better support for numpy functions in dreal proofs

@@ -1,4 +1,5 @@
 import numpy as np
+import math
 from typing import Callable
 from ._pylucid import (
     RectSet,
@@ -16,6 +17,14 @@ try:
 except ImportError as e:
     log_warn("Could not import dreal. Make sure it is installed with 'pip install dreal'")
     raise e
+
+Real.cos = lambda self: Cosine(self)
+Real.sin = lambda self: Sine(self)
+
+math_original_cos = math.cos
+math_original_sin = math.sin
+math.cos = lambda x: Cosine(x) if isinstance(x, Real) else math_original_cos(x)
+math.sin = lambda x: Sine(x) if isinstance(x, Real) else math_original_sin(x)
 
 
 def build_set_constraint(xs: "list", X_set: "RectSet | MultiSet"):
@@ -136,8 +145,10 @@ def verify_barrier_certificate(
         True if the barrier certificate is verified, False otherwise.
     """
     # Create symbolic variables for the input dimensions
-    xs = [Real(f"x{i}") for i in range(X_bounds.dimension)]
-    xsp = [f_det(x) for x in xs]
+    xs = np.array([Real(f"x{i}") for i in range(X_bounds.dimension)])[np.newaxis, :]
+    xsp = f_det(xs)
+    xs = xs[0].tolist()  # Convert to a list for further processing
+    xsp = xsp[0].tolist()  # Convert to a list for further processing
     barrier = build_barrier_expression(xs=xs, X_bounds=X_bounds, tffm=tffm, sigma_f=sigma_f, sol=sol)
     barrier_p = build_barrier_expression(xs=xsp, X_bounds=X_bounds, tffm=tffm, sigma_f=sigma_f, sol=sol)
 
@@ -160,7 +171,6 @@ def verify_barrier_certificate(
             ),
         ),
     )
-    # print(constraints, file=sys.stderr)
     res = CheckSatisfiability(constraints, 1e-8)
     if res is None:
         log_info("The barrier has been verified via dReal")
@@ -168,7 +178,7 @@ def verify_barrier_certificate(
 
     log_error("Found counter example")
     log_error(f"Model: {res}")
-    point = np.array([res[xs[0]].lb()])
+    point = np.array([[res[x].lb() for x in xs]])
     pointp = f_det(point)
     log_error(f"X: {point}, barrier value: {tffm(point) @ sol.T}")
     log_error(f"Xp: {pointp}, barrier value: {tffm(pointp) @ sol.T}")

### 2025-06-09 bindings/pylucid/pipeline.py

@@ -120,7 +120,7 @@ def pipeline(
     if f_det is not None:
         # Sample some other points (half of the x_samples) to evaluate the regressor against overfitting
         x_evaluation = X_bounds.sample(x_samples.shape[0] // 2)
-        f_xp_evaluation = feature_map(f_det(x_evaluation.T).T)
+        f_xp_evaluation = feature_map(f_det(x_evaluation))
         log_debug(f"RMSE on f_det_evaluated {rmse(estimator(x_evaluation), f_xp_evaluation)}")
         log_debug(f"Score on f_det_evaluated {estimator.score(x_evaluation, f_xp_evaluation)}")
 

### 2025-06-09 tests/bindings/pylucid/CaseStudyTemplate.py
chore: simplify tests

@@ -19,7 +19,7 @@ def scenario_config() -> "ScenarioConfig":
     f_det = lambda x: 1 / 2 * x
     # Add process noise
     np.random.seed(seed)  # For reproducibility
-    f = lambda x: f_det(x) + np.random.normal(scale=0.8)
+    f = lambda x: f_det(x) + np.random.normal(scale=0.4)
 
     # %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% #
     # Safety specification
@@ -41,7 +41,7 @@ def scenario_config() -> "ScenarioConfig":
 
     N = 1000
     x_samples = X_bounds.sample(N)
-    xp_samples = f(x_samples.T).T
+    xp_samples = f(x_samples)
 
     # Initial estimator hyperparameters. Can be tuned later
     regularization_constant = 1e-3

### 2025-06-09 tests/bindings/pylucid/TestBarrier3.py

@@ -5,6 +5,9 @@ from pylucid.pipeline import pipeline, rmse
 
 
 def scenario_config() -> "ScenarioConfig":
+    """Benchmark scenario taken from
+    https://github.com/oxford-oxcav/fossil/blob/10f1f071784d16b2a5ee5da2f51ff2a81d753e2e/experiments/benchmarks/models.py#L350C1-L360C1
+    """
     # %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% #
     # Script configuration
     # ---------------------------------- #
@@ -15,7 +18,7 @@ def scenario_config() -> "ScenarioConfig":
     # System dynamics
     # ---------------------------------- #
 
-    f_det = None  # lambda x: x
+    f_det = lambda x: np.array([x[:, 1], -x[:, 0] - x[:, 1] + 1 / 3 * x[:, 0] ** 3]).T  # lambda x: x
     # Add process noise
     np.random.seed(seed)  # For reproducibility
     f = lambda x: f_det(x) + (np.random.standard_normal())
@@ -42,7 +45,7 @@ def scenario_config() -> "ScenarioConfig":
     # ---------------------------------- #
 
     x_samples = read_matrix("tests/bindings/pylucid/x_samples.matrix")
-    xp_samples = read_matrix("tests/bindings/pylucid/xp_samples.matrix")
+    xp_samples = f(x_samples)
 
     # Initial estimator hyperparameters. Can be tuned later
     regularization_constant = 1e-6

### 2025-06-09 docs/paper/main.tex
feat: add tuning

@@
 The $n$-dimensional Gaussian measure with mean $\mu\in\mathbb{R}^n$ and covariance matrix $\Sigma\in\mathbb{R}^{n\times n}$ is given by
-\begin{equation*}
+\begin{equation}
+  \label{eq:gaussian-kernel}
   \mathcal N(dx|\mu, \Sigma) := \frac{dx}{ \sqrt{(2\pi)^n \left|\Sigma\right| }}\exp\left[-\frac{1}{2}(x-\mu)\T\Sigma^{-1\!}(x-\mu)\right],
-\end{equation*}
+\end{equation}
 where $|\Sigma|$ is the determinant of $\Sigma$.
@@
 
+A symmetric function $k_\X:\X\times\X\rightarrow\R$ is called a (positive definite) \emph{kernel} (note the distinction from \emph{probability kernels}) if for all $N\in\N_{>0}$ we have $\sum_{i=1}^{N}\sum_{j=1}^{N}a_i a_j\allowbreak k_\X(x_i,x_j) \geq 0$ for $x_1,\ldots,x_N\in\X\subset{\R^n}$ and $a_1,\ldots,a_N\in\R$.
+A prominent example is the \emph{squared exponential} (SQExp) kernel \cite{Rasmussen2005GP,Kanagawa2018GPvsKernel}:
+\begin{equation}
+  \label{eq:gaussian-kernel}
+  k_\X(x,x') := \sigma_f^2 \exp\left( -\frac{1}{2} (x-x')\T \Sigma\, (x-x') \right),\quad \Sigma:=\diag(\sigma_l)^{-2},
+\end{equation}
+with amplitude $\sigma_f^2\geq0$ and lengthscale coefficients $\sigma_l\in\R^n$.
+%In the following, we refer to a positive definite kernel as \emph{kernel}, for simplicity.
+For this work, we assume that all kernels are bounded on their domain, i.e., $\E_{}[k_\X(x,x)]<\infty$, $x\in\X$.
+Given a kernel $k_\X$ on a non-empty set $\X$, there exists a unique corresponding \emph{reproducing kernel Hilbert space} (RKHS) $\Hilbert_{k_\X}$ of functions $f:\X\rightarrow\R$ equipped with an inner product $\innerH{\cdotx}{\cdotx}{\Hilbert_{k_\X}}$ possessing the \emph{reproducing property} such that for any function $f\in\Hilbert_{k_\X}$ and $x\in\X$ we have $f(x)=\innerH{f}{k_\X(\cdotx,x)}{\Hilbert_{k_\X}}$.
+Note that $k_\X(\cdotx,x):\X\rightarrow\Hilbert_{k_\X}$ is a real-valued function,
+\new{which is} also called an implicit \emph{canonical} \emph{embedding} or \emph{feature map} $\phi_\X$
+such that $k_\X(x,x')=\innerH{\phi_\X(x)}{\phi_\X(x')}{\Hilbert_{k_\X}}$ for all $x,x'\in\X$.
+For an RKHS $\Hilbert_{k_\X}$, we use the associated feature map $\phi_\X$ and kernel $k_\X$ interchangeably for ease of notation and comprehensibility.
+%We will call the kernel associated to an RKHS $\Hilbert_{k_\X}$ the \emph{characteristic} kernel of $\Hilbert_{k_\X}$ and use $\phi_\X$ and $k_\X$ interchangeably for ease of notation and comprehensibility.
+%and an implicit \emph{canonical} \emph{embedding} or \emph{feature map} $\phi_\X:\X\rightarrow\Hilbert_{k_\X}$ with an inner product on $\Hilbert_{k_\X}$, i.e., $k_\X(x,x')=\innerH{\phi_\X(x)}{\phi_\X(x')}{\Hilbert_{k_\X}}$,
+%Furthermore, 
+The inner product induces the norm $\norm{f}_{\Hilbert_{k_\X}}\!\!\!\!:=\!\!\sqrt{\smash[b]{\innerH{f}{f}{\Hilbert_{k_\X}}}}$ of the RKHS.
+%Note that $\Hilbert_{k_\X}$ is a space of functions $f:\X\rightarrow\R$. 
+%It is equipped with the infamous \emph{reproducing property} such that for any function $f\in\Hilbert_{k_\X}$ and $x\in\X$ we have $f(x)=\innerH{f}{\phi_\X(x)}{\Hilbert_{k_\X}}$.
+%Furthermore, the norm associated with the RKHS $\Hilbert_{k_\X}$ is defined as $\norm{f}_{\Hilbert_{k_\X}}:=\sqrt{\innerH{f}{f}{\Hilbert_{k_\X}}}$.
+%We refer the interested reader to XX for a comprehensive dissemination on RKHS.
+Throughout this paper, we assume that all RKHSs are \emph{separable}.
+Given $N$ i.i.d. samples $\hat X_N:=[\hat{x}_i]_{i=1}^N$ with $\hat{x}_i\in\X$, the
+\emph{Gram matrix} of $k_\X$ is given by
+$K_{\hat{X}}^N:=[k_\X(\hat{x}_i,\hat{x}_j)]_{i,j=1}^N.$
+Furthermore, we define the vector-valued function
+$k_{\hat{X}}^N(x)  := [k_\X(x,\hat{x}_i)]_{i=1}^N.$
+
 \subsection{Data-Driven Barrier Formulation}
@@
   \begin{align}
-    \min_{b, c, \eta, \gamma} \; &\frac{\eta + cT}{\gamma},\label{eq:semiinfLP-prog-objective}\\
+    \min_{b, c, \eta, \gamma} \; & \frac{\eta + cT}{\gamma},\label{eq:semiinfLP-prog-objective}                                                 \\
     \text{s.t.}\quad
-    &\forall x_0\in\X_0:\,\phi_M(x_0)\T b\leq\eta,\label{eq:semiinfLP-prog-initial}\\
-    &\forall x_u\in\X_u:\,\phi_M(x_u)\T b\geq\gamma,\label{eq:semiinfLP-prog-unsafe}\\
-    &\forall x\in\X: \, \phi_M(x)\T (H b - b) \leq c - \varepsilon\bar{B}\kappa,\label{eq:semiinfLP-prog-kushner}\\
-    & \forall x\in\X:\,\phi_M(x)\T b\geq 0,\label{eq:semiinfLP-prog-positive}\\
-    &c\geq 0,\,\gamma>\eta\geq 0,\,b\in\R^{2M+1},\nonumber
+                                 & \forall x_0\in\X_0:\,\phi_M(x_0)\T b\leq\eta,\label{eq:semiinfLP-prog-initial}                               \\
+                                 & \forall x_u\in\X_u:\,\phi_M(x_u)\T b\geq\gamma,\label{eq:semiinfLP-prog-unsafe}                              \\
+                                 & \forall x\in\X: \, \phi_M(x)\T (H b - b) \leq c - \varepsilon\bar{B}\kappa,\label{eq:semiinfLP-prog-kushner} \\
+                                 & \forall x\in\X:\,\phi_M(x)\T b\geq 0,\label{eq:semiinfLP-prog-positive}                                      \\
+                                 & c\geq 0,\,\gamma>\eta\geq 0,\,b\in\R^{2M+1},\nonumber
   \end{align}\label{eq:semiinfLP-prog}%
@@
 \begin{align*}
-    &\frac{1}{2}\big(\mathrm{max}_{\hat{N}}^\X + \mathrm{min}_{\hat{N}}^\X - C_{\hat{N}}\left(\mathrm{max}_{\hat{N}}^\X-\mathrm{min}_{\hat{N}}^\X\right)\big) \geq \mathrm{lb},\\
+                               & \frac{1}{2}\big(\mathrm{max}_{\hat{N}}^\X + \mathrm{min}_{\hat{N}}^\X - C_{\hat{N}}\left(\mathrm{max}_{\hat{N}}^\X-\mathrm{min}_{\hat{N}}^\X\right)\big) \geq \mathrm{lb}, \\
   \Leftrightarrow\hspace{10pt} &
@@
 
-\vfill
+\subsection{Tuning the Hyperparameters}
+\label{sec:tuning-hyperparameters}
+
+Kernel methods do not require the expensive learning process of other machine learning methods, such as neural networks.
+However, they still depend on a number of \hp, such as the kernel bandwidth $\sigma_f$ and the number of Fourier coefficients $M$.
+Changes in their values can have a significant impact on the estimator's efficiency and accuracy.
+The process of finding good values for these \hp is known as \emph{hyperparameter tuning}, and it is problem-dependent.
+
+There are several approaches to find the optimal \hp for a given problem.
+A cheap option which can be used as a starting point when working with a Gaussian Kernels as in~\eqref{eq:gaussian-kernel} is to use the \emph{median heuristic} \cite{garreau2018largesampleanalysismedian}.
+We choose $\sigma_l^2$ to be the median of the squared distances between all pairs of points in the training set, i.e.,
+\begin{equation}
+  \sigma_l^2 = \mathrm{median}_{1 \leq i < j \leq N}\left(\|\hat{x}_i-\hat{x}_j\|^2\right),
+\end{equation}
+where $\hat{x}_1,\ldots,\hat{x}_N$ are the $N$ training samples.
+If $N(N-1)/2$ is even, the median is the average of the two middle values in the sorted list of distances.
+Better results can be obtained via \emph{grid search}, which consists of evaluating the performance of the estimator for all combinations of \hp in a predefined grid.
+This approach is simple to implement and can be very effective for small problems, but it can become computationally expensive for larger problems.
+Borrowing a technique from Gaussian processes, we can also try to optimize the \hp to maximize the \emph{log marginal likelihood}, defined as
+\begin{equation}
+  \log p(\hat{X^+}_N | \hat{X}_N) = - \frac{1}{2}\hat{X^+}_N\T (K_{\hat{X}}^N + N\lambda I_N)^{-1} \hat{X^+}_N -\frac{1}{2}\log |K_{\hat{X}}^N + N\lambda I_N| - \frac{N}{2}\log(2\pi).
+\end{equation}
+
+\paragraph{Implementation}
+
+While it is possible to tune the \hp with any method and then set them manually in the estimator, \lucid provides a set of classes, which specialize the \texttt{Tuner} interface, to automate the process.
+The \texttt{GridSearchTuner} class implements the grid search method, while the \texttt{MedianHeuristicTuner} class implements the median heuristic.
+If the user wants to optimize the log marginal likelihood, they can use the \texttt{LBGSTuner} class, which runs the L-BFGS or L-BFGS-B quasi-Newton optimization algorithms~\cite{book:nonlinear-programming} over the log marginal likelihood function.
+Internally, \lucid uses the \texttt{LBFGS++} library~\footnote{https://github.com/yixuan/LBFGSpp} to perform the optimization.
 

### 2025-06-16 docs/paper/fig/architecture.tex
feat: add case studies

\begin{figure}
    \centering
    \begin{tikzpicture}[node distance=1.2cm and 1.8cm,
            input-block/.style={rectangle, draw, fill=red!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
            output-block/.style={rectangle, draw, fill=green!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
            block/.style={rectangle, draw, fill=blue!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
            arrow/.style={thick,->,>=Stealth},
            tool/.style={rectangle, draw, fill=magenta!10, text width=3cm, minimum height=0.8cm, align=center, rounded corners},
            inv/.style={}
        ]

        % Input block
        \node[input-block] (input) {Config File};

        % Lucid blocks
        \node[block, right=of input] (estimator) {Estimator};
        \node[block, right=of estimator] (feature) {Feature map / Barrier template};
        \node[block, below=of feature] (optimizer) {Optimizer};
        \node[block, left=of optimizer] (verifier) {Verifier};
        \node[draw, dashed, inner sep=0.3cm, rounded corners,
        fit=(estimator)(feature)(optimizer)(verifier), label=above:{\textbf{Lucid}}] {};

        % Output block
        \node[output-block, left=of verifier] (output) {Barrier certificate};

        % Smt solvers
        \node[inv, below=2.5cm of verifier.north, anchor=north] (smtInv) {};
        \node[tool, left=0.3cm of smtInv] (dreal) {dReal};
        \node[tool, right=0.3cm of smtInv] (cvc5) {CVC5};
        \node[draw, dashed, inner sep=0.3cm, rounded corners,
        fit=(dreal)(cvc5), label=left:{\textbf{SMT Solver}}] {};

        % Arrows
        \draw[arrow] (input) -- (estimator);
        \draw[arrow] (estimator) -- (feature);
        \draw[arrow] (feature) -- (optimizer);
        \draw[arrow] (optimizer) -- (verifier);
        \draw[arrow] (verifier) -- (output);

        \draw[arrow] (cvc5.north) -- (verifier.south);
        \draw[arrow] (dreal.north) -- (verifier.south);

    \end{tikzpicture}
    \caption{General architecture of Lucid. \todo{Only dReal is supported at the moment}}
    \label{fig:architecture}
\end{figure}

### 2025-06-16 docs/paper/main.tex
feat: add case studies

@@
 
-\title{Delta-Complete Linear Programming}
+\title{Lucid: Lifting-based Uncertain Control Invariant Dynamics}
 
@@
 
-Lucid is in implemented in C++ and it is meant to be used as a library.
+\paragraph{Motivation.}
+
+We present a software tool, called \lucid, able to address the challenges of verifying the safety of black-box noisy systems.
+A description that, for better or for worse, fits many modern AI-enabled systems, such as autonomous vehicles, robotics, and healthcare applications.
+To ensure their safety, we use \glspl{cbc}~\cite{prajna2006barrier,cosner2023generative}, which are a powerful tools that provides formal guarantees and a verifiable witness.
+The peculiar function template we chose for the \glspl{cbc} makes it easier for the model to be learned from limited data collected from the system, without the need for an explicit dynamical model.
+Note that the current version of the tool does not deal with external control inputs, which we plan to address in future work.
+
+\paragraph{Tool.}
+
+\lucid is implemented in C++ and it is meant to be used as a library.
 It provides a set of interfaces that allow users to have an high level of control and flexibility over the verification process.
 We also provide a Python wrapper, called PyLucid, to facilitate the integration of the tool into existing workflows and effortlessly leverage well-established libraries such as NumPy~\cite{numpy} and SciPy~\cite{scipy}.
-Lucid is available as an open-source project on GitHub at \url{https://github.com/TendTo/lucid}.
-More technical details about the implementation can be found in the documentation at \url{https://tendto.github.io/lucid/}.
+\lucid is available as an open-source project on GitHub at \url{https://github.com/TendTo/lucid}.
+More technical details about the implementation can be found in the online documentation at \url{https://tendto.github.io/lucid/}, but at an high level, the architecture of \lucid is illustrated in~\autoref{fig:architecture}.
+
+\input{fig/architecture}
+
+\paragraph{Literature Background.}
+\todo{Add relevant literature citations and background information here.}
+
+% \input{fig/architecture.tex}
 
@@
 \label{sec:problem-statement}
-
-\subsection{Notation}
-\label{sec:notation}
 
@@
 This has made CBCs/CBFs popular tools for safety verification and synthesis~\cite{prajna2006barrier,cosner2023generative}.
-We briefly recall the definition of a CBC.
+We briefly recall the definition of a \gls{cbc}.
 \begin{definition}[Control barrier certificate (CBC)]\label{def:cbc}
-  A function $\B:\X\rightarrow\R_{\geq 0}$ is called a CBC of an MDP $\M=(\X,\X_0,\U,\Tr)$ with reference to an unsafe set $\X_u$, if we have
+  A function $\B:\X\rightarrow\R_{\geq 0}$ is called a \gls{cbc} of an MDP $\M=(\X,\X_0,\U,\Tr)$ with reference to an unsafe set $\X_u$, if we have
   \begin{itemize}
@@
 \end{definition}
-If one can find a CBC for a system $\M$, then, a lower bound on the probability of $\M$ being safe is given by the following proposition due to \cite{kushner1967stochastic}.
+If one can find a \gls{cbc} for a system $\M$, then, a lower bound on the probability of $\M$ being safe is given by the following proposition due to \cite{kushner1967stochastic}.
 \begin{proposition}[Finite-horizon safety]
@@
 
-When verifying the safety of a system, \lucid will search for a CBC $\B$ that satisfies the conditions in Definition~\ref{def:cbc}.
+When verifying the safety of a system, \lucid will search for a \gls{cbc} $\B$ that satisfies the conditions in Definition~\ref{def:cbc}.
 If it finds it, it will return the constants $\eta$, $\gamma$, and $c$, as well as the CBC $\B$ itself, which becomes a certificate of safety for the system $\M$.
@@
 \begin{align*}
-                               & \frac{1}{2}\big(\mathrm{max}_{\hat{N}}^\X + \mathrm{min}_{\hat{N}}^\X - C_{\hat{N}}\left(\mathrm{max}_{\hat{N}}^\X-\mathrm{min}_{\hat{N}}^\X\right)\big) \geq \mathrm{lb}, \\
-  \Leftrightarrow\hspace{10pt} &
   \mathrm{min}_{\hat{N}}^\X \geq \frac{2}{C_{\hat{N}}+1}\mathrm{lb} + \frac{C_{\hat{N}}-1}{C_{\hat{N}}+1}\mathrm{max}_{\hat{N}}^\X.
 \end{align*}
-For an upper bound $\forall x\in\X: f(x) \leq \mathrm{ub}$, we obtain analogous constraints of the form
-\begin{equation*}
-  \mathrm{max}_{\hat{N}}^\X \geq \frac{2}{C_{\hat{N}}+1}\mathrm{ub} + \frac{C_{\hat{N}}-1}{C_{\hat{N}}+1}\mathrm{min}_{\hat{N}}^\X.
-\end{equation*}
+We obtain an analogous constraints for an upper bound $\forall x\in\X: f(x) \leq \mathrm{ub}$.
+
+\paragraph{Implementation}
+
+The finite-constraint relaxation of the SIP \eqref{eq:semiinf-prog} is what \lucid uses to synthesize the \gls{cbc} $\B$.
+More precisely, we follow the steps outlined in~\autoref{fig:steps}.
+While the theory gives us precise indication on how to construct the \gls{lp} which would yield a correct-by-design solution,
+in practice the problem may become too conservative.
+To mitigate this, we can either increase the number of lattice points $Q$, worsening the computational efficiency, 
+or we may choose to adjust the coefficient $C_{\hat{N}}$, improving performance at the cost of loosening the guarantees, 
+which can still be checked with the verifier, provided we have access to the system's model.
+
+\input{fig/steps}
 
@@
 
-\section{Benchmarks}
-\label{sec:benchmarks}
+\section{Tool Evaluation}
+\label{sec:evaluation}
+
+We evaluate \lucid on a set of benchmarks, which are described in detail in the documentation.
+
+\paragraph{Linear System}
+
+To showcase the basic functionality of \lucid, we consider a simple linear system with the dynamics
+
+\begin{equation*}
+  \begin{bmatrix}
+    {x}_{1, t+1}
+  \end{bmatrix}
+  = \begin{bmatrix}
+    0.5
+  \end{bmatrix}
+  \begin{bmatrix}
+    {x}_{1, t}
+  \end{bmatrix} + w_t,
+\end{equation*}
+where $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I)$ is a one-dimensional Gaussian noise.
+We restrict the state space to the interval $\X=[-1,1]$ and define the initial set $\X_0=[-0.5,0.5]$ and the unsafe set $\X_u=[-1,-0.9]\cup[0.9,1]$.
+Translating the system into the \lucid format, we obtain the following configuration file:
+\lstinputlisting[language=Python,caption={\texttt{linear.py} configuration file.}]{code/linear.py}
+It can then be run with the command
+\begin{lstlisting}[language=bash]
+python -m pylucid tests/bindings/pylucid/MinScenarioConfig.py --seed 42 --gamma 1.0 \
+  --time_horizon 5 --num_samples 1000 --lambda 1e-3 --sigma_f 15.0 \ 
+  --sigma_l 1.75555556 --num_frequencies 4 --plot --verify --oversample_factor 32.0
+\end{lstlisting}
+to produce the results shown in~\autoref{fig:linear}.
+By including the \texttt{--verify} flag, also get formal guarantees that the barrier is indeed a valid \gls{cbc} for the system.
+\begin{lstlisting}[language=bash]
+# ...
+[info] [thread 1] [-] The barrier has been verified via dReal
+# ...
+\end{lstlisting}
+
+\begin{figure}[ht]
+  \import{fig}{linear.pgf}
+  \caption{\gls{cbc} synthesis for the linear system benchmark.
+    The blue regions represent the initial set $\X_0$, while the red regions represent the unsafe set $\X_u$.
+    The pink surface indicates the value of $\gamma$.
+  }
+  \label{fig:linear}
+\end{figure}
+
+\paragraph{Barrier 3}
+
+The first benchmark is inspired by the example \barr from \cite{abate2021fossil}, which we extend by adding stochastic noise $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$ to arrive at the two-dimensional nonlinear stochastic dynamics
+\begin{equation*}
+  \begin{bmatrix}
+    {x}_{1, t+1} \\
+    {x}_{2, t+1}
+  \end{bmatrix}
+  = \begin{bmatrix}
+    {x}_{2, t} \\
+    \frac{1}{3} {x}^3_{1, t} - {x}_{1,t} - {x}_{2,t}
+  \end{bmatrix} + w_t.
+\end{equation*}
+We illustrate the setup in Figure~\ref{fig:CSBarr3}.
+
+The goal is to compute the probability that the system initialized in $[{x}_{1,0},{x}_{2,0}]\T\in \X_0$ (blue regions) does not enter the unsafe regions $\X_u$ (in red) within $T=10$ time steps.
+
+\begin{figure}[ht]
+  \import{fig}{barrier3.pgf}
+  \caption{\gls{cbc} synthesis for the \barr benchmark.
+    The blue regions represent the initial set $\X_0$, while the red regions represent the unsafe set $\X_u$.
+    The pink surface indicates the value of $\gamma$.
+  }
+  \label{fig:CSBarr3}
+\end{figure}
 

### 2025-06-16 docs/paper/code/linear.py

@@ -1,0 +1,39 @@
+# linear.py
+from pylucid import *
+
+
+def scenario_config(args: CLIArgs):
+    # Model
+    f_det = lambda x: 0.5 * x
+    f = lambda x: f_det(x) + np.random.normal(scale=0.01)
+
+    # Sets
+    X_bounds = RectSet([(-1, 1)], seed=args.seed)
+    X_init = RectSet([(-0.5, 0.5)])
+    X_unsafe = MultiSet(RectSet([(-1, -0.9)]), RectSet([(0.9, 1)]))
+
+    # Sampling
+    x_samples = X_bounds.sample(args.num_samples)
+    xp_samples = f(x_samples)
+
+    # Estimator
+    estimator = KernelRidgeRegressor(
+        kernel=GaussianKernel(sigma_f=args.sigma_f, sigma_l=args.sigma_l),
+        regularization_constant=args.lambda_,
+    )
+
+    # Lucid configuration
+    return ScenarioConfig(
+        x_samples=x_samples,
+        xp_samples=xp_samples,
+        X_bounds=X_bounds,
+        X_init=X_init,
+        X_unsafe=X_unsafe,
+        T=args.time_horizon,
+        gamma=args.gamma,
+        num_freq_per_dim=args.num_frequencies,
+        f_det=f_det,
+        estimator=estimator,
+        sigma_f=args.sigma_f,
+        oversample_factor=args.oversample_factor,
+    )

### 2025-07-10 bindings/pylucid/interrupt.cpp
chore: add include check for python interrupt

@@ -4,6 +4,10 @@
  * @copyright 2025 lucid
  * @licence BSD 3-Clause License
  */
+#ifndef LUCID_PYTHON_BUILD
+#error LUCID_PYTHON_BUILD is not defined. Ensure you are building with the option '--config=py'
+#endif
+
 #include <Python.h>
 #include <pybind11/pybind11.h>
 

### 2025-07-10 bindings/pylucid/interrupt.h

@@ -7,6 +7,10 @@
  */
 #pragma once
 
+#ifndef LUCID_PYTHON_BUILD
+#error LUCID_PYTHON_BUILD is not defined. Ensure you are building with the option '--config=py'
+#endif
+
 namespace lucid {
 
 /**

### 2025-07-10 bindings/pylucid/pylucid.h

@@ -5,6 +5,8 @@
  * @file
  * pylucid main module.
  */
+#pragma once
+
 #ifndef LUCID_PYTHON_BUILD
 #error LUCID_PYTHON_BUILD is not defined. Ensure you are building with the option '--config=py'
 #endif

### 2025-07-10 lucid/util/matplotlib.h

@@ -9,6 +9,7 @@
  * Inspired by Benno Evers' matplotlib-cpp
  */
 #pragma once
+
 #ifndef LUCID_MATPLOTLIB_BUILD
 #error "This file should not be included without LUCID_LUCID_MATPLOTLIB_BUILD"
 #endif

### 2025-07-10 docs/paper/main.tex
chore: oliver setup

@@
 
-\author{Oliver Sch\"{o}n \and
-Ernesto Casablanca \and
-Sadegh Soudjani \and
-Paolo Zuliani
+\begin{comment}
+\author{Ernesto Casablanca \and
+Oliver Sch\"{o}n \and
+Paolo Zuliani \and
+Sadegh Soudjani
 }
 
-\begin{comment}
 \institute{O. Sh\"{o}n,E. Casablanca \at Newcastle University, Newcastle upon Tyne, United Kingdgom \\ \email{e.casablanca2@newcastle.ac.uk}, \email{o.schoen2@newcastle.ac.uk}
 \and
+P. Zuliani \at Universit\`{a} di Roma ``La Sapienza'', Rome, Italy\\ \email{zuliani@di.uniroma1.it}
+\and
 S. Soudjani \at Max Planck Institute for Software Systems, Kaiserslautern, Germany \\ \email{sadegh@mpi-sws.org}
-\and
-P. Zuliani \at Universit\`{a} di Roma ``La Sapienza'', Rome, Italy\\ \email{zuliani@di.uniroma1.it}
 }
@@
 To ensure their safety, we use \glspl{cbc}~\cite{prajna2006barrier,cosner2023generative}, which are a powerful tools that provides formal guarantees and a verifiable witness.
-The peculiar function template we chose for the \glspl{cbc} makes it easier for the model to be learned from limited data collected from the system, without the need for an explicit dynamical model.
+The particular function template we chose for the \glspl{cbc} makes it easier for the model to be learned from limited data collected from the system, without the need for an explicit dynamical model.
 Note that the current version of the tool does not deal with external control inputs, which we plan to address in future work.
@@
 The \texttt{GridSearchTuner} class implements the grid search method, while the \texttt{MedianHeuristicTuner} class implements the median heuristic.
-If the user wants to optimize the log marginal likelihood, they can use the \texttt{LBGSTuner} class, which runs the L-BFGS or L-BFGS-B quasi-Newton optimization algorithms~\cite{book:nonlinear-programming} over the log marginal likelihood function.
+If the user wants to optimize the log marginal likelihood, they can use the \texttt{LBFGSTuner} class, which runs the L-BFGS or L-BFGS-B quasi-Newton optimization algorithms~\cite{book:nonlinear-programming} over the log marginal likelihood function.
 Internally, \lucid uses the \texttt{LBFGS++} library~\footnote{https://github.com/yixuan/LBFGSpp} to perform the optimization.
@@
 
+\begin{table}
+    \centering
+    \begin{tabular}{cccc}
+        \toprule
+        \textbf{Benchmark} & \textbf{Dim} & \textbf{Runtime} & \textbf{Safety Prob.} \\
+         & & [m:ss] & [\%] \\ % Units
+        \midrule
+        Barr3 & 2 & X:XX & XX \\
+        name1 & 3 & X:XX & XX \\
+        name2 & 7 & X:XX & XX \\
+        \bottomrule
+    \end{tabular}
+    \caption{Computational benchmarks: ...}
+    \label{tbl:benchmarks}
+\end{table}
+
 \section*{Acknowledgements}

### 2025-07-10 tests/integration/TestLinear.cpp
chore: update integration due to feature map changes

@@ -81,13 +81,13 @@ TYPED_TEST(TestLinear, TestLinear) {
   ASSERT_EQ(n_per_dim, 288);
 
   estimator.fit(x_samples, f_xp_samples);
-  ASSERT_DOUBLE_EQ(scorer::rmse_score(estimator, x_samples, f_xp_samples), -0.4711612131628251);
-  ASSERT_DOUBLE_EQ(estimator.score(x_samples, f_xp_samples), 0.9903926538293206);
+  ASSERT_DOUBLE_EQ(scorer::rmse_score(estimator, x_samples, f_xp_samples), -0.55940545363305361);
+  ASSERT_DOUBLE_EQ(estimator.score(x_samples, f_xp_samples), 0.9901976271473962);
 
   const Matrix x_evaluation = X_bounds.sample(x_samples.rows() / 2);
   const Matrix f_xp_evaluation = feature_map(this->f_det(x_evaluation));
-  ASSERT_DOUBLE_EQ(scorer::rmse_score(estimator, x_evaluation, f_xp_evaluation), -0.44500887787023974);
-  ASSERT_DOUBLE_EQ(estimator.score(x_evaluation, f_xp_evaluation), 0.991434699768147);
+  ASSERT_DOUBLE_EQ(scorer::rmse_score(estimator, x_evaluation, f_xp_evaluation), -0.5265806387684655);
+  ASSERT_DOUBLE_EQ(estimator.score(x_evaluation, f_xp_evaluation), 0.9913180698330606);
 
   const Matrix x_lattice = X_bounds.lattice(n_per_dim, true);
   const Matrix u_f_x_lattice = feature_map(x_lattice);
@@ -106,11 +106,11 @@ TYPED_TEST(TestLinear, TestLinear) {
                      [[maybe_unused]] const float eta, [[maybe_unused]] const float c,
                      [[maybe_unused]] const float norm) {
     ASSERT_TRUE(success);
-    ASSERT_NEAR(obj_val, 0.09592434763, tolerance);
-    ASSERT_NEAR(eta, 0.0583335943, tolerance);
+    ASSERT_NEAR(obj_val, 0.0959243, tolerance);
+    ASSERT_NEAR(eta, 0.05833359, tolerance);
     ASSERT_NEAR(c, 0.007518151, tolerance);
-    ASSERT_NEAR(norm, 0.09005303722312392, tolerance);
[…]

### 2025-07-10 lucid/verification/GurobiOptimiser.cpp
feat: add interrupt check for python bindings and avoid setting names if not needed

@@ -16,16 +16,38 @@
 #include "lucid/util/error.h"
 #include "lucid/util/logging.h"
 
+#ifdef LUCID_PYTHON_BUILD
+#include "bindings/pylucid/interrupt.h"
+#endif
+
 #ifndef NLOG
-#define LUCID_MODEL_ADD_CONSTRAINT(model, expr, op, rhs, name) \
-  model.addConstr(expr, op, rhs).set(GRB_StringAttr_ConstrName, name)
+#define LUCID_MODEL_ADD_CONSTRAINT(model, expr, op, rhs, name, should_log)   \
+  do {                                                                       \
+    if (should_log) {                                                        \
+      (model).addConstr(expr, op, rhs).set(GRB_StringAttr_ConstrName, name); \
+    } else {                                                                 \
+      (model).addConstr(expr, op, rhs);                                      \
+    }                                                                        \
+  } while (0)
 #else
-#define LUCID_MODEL_ADD_CONSTRAINT(model, expr, op, rhs, name) model.addConstr(expr, op, rhs)
+#define LUCID_MODEL_ADD_CONSTRAINT(model, expr, op, rhs, name, should_log) model.addConstr(expr, op, rhs)
 #endif
 
 namespace lucid {
 
 #ifdef LUCID_GUROBI_BUILD
+
+namespace {
+
+#ifdef LUCID_PYTHON_BUILD
+class PyInterruptCallback final : public GRBCallback {
+ public:
+  void callback() override { py_check_signals(); }
+};
+#endif
+
+}  // namespace
+
 bool GurobiOptimiser::solve(ConstMatrixRef f0_lattice, ConstMatrixRef fu_lattice, ConstMatrixRef phi_mat,
                             ConstMatrixRef w_mat, const Dimension rkhs_dim, const Dimension num_frequencies_per_dim,
                             const Dimension num_frequency_samples_per_dim, const Dimension original_dim,
[…]

### 2025-07-10 lucid/verification/HighsOptimiser.cpp

@@ -15,11 +15,14 @@
 #include "lucid/lib/highs.h"
 #include "lucid/util/error.h"
 
+#ifdef LUCID_PYTHON_BUILD
+#include "bindings/pylucid/interrupt.h"
+#endif
+
 #ifndef NLOG
-#define LUCID_FORMAT_NAME(str, ...) fmt::format(str, __VA_ARGS__)
+#define LUCID_FORMAT_NAME(should_log, str, ...) (should_log) ? fmt::format(str, __VA_ARGS__) : ""
 #else
-const char* emtpy_string = "";
-#define LUCID_FORMAT_NAME(str, ...) emtpy_string
+#define LUCID_FORMAT_NAME(should_log, str, ...) ""
 #endif
 
 namespace lucid {
@@ -27,13 +30,19 @@ namespace lucid {
 #ifdef LUCID_HIGHS_BUILD
 namespace {
 
+#ifdef LUCID_PYTHON_BUILD
+void interrupt_callback(const int, const char*, const HighsCallbackDataOut*, HighsCallbackDataIn*, void*) {
+  py_check_signals();
+}
+#endif
+
 constexpr double infinity = std::numeric_limits<double>::infinity();
 constexpr double neg_infinity = -std::numeric_limits<double>::infinity();
 
 class HighsLpProblem {
  public:
-  explicit HighsLpProblem(const Dimension num_vars, const Dimension num_constraints)
-      : triplets_{}, A_{num_constraints, num_vars}, model_{} {
+  explicit HighsLpProblem(const Dimension num_vars, const Dimension num_constraints, const bool should_log)
+      : triplets_{}, A_{num_constraints, num_vars}, model_{}, should_log_{should_log} {
     LUCID_ASSERT(num_vars > 0, "Number of variables must be greater than 0.");
     LUCID_ASSERT(num_constraints > 0, "Number of constraints must be greater than 0.");
 
@@ -49,9 +58,12 @@ class HighsLpProblem {
     triplets_.reserve(num_vars * num_constraints);
 
 #ifndef NLOG
-    model_.lp_.row_names_.reserve(num_constraints);
-    model_.lp_.col_names_.resize(num_vars);
-    for (Dimension i = 0; i < num_vars; i++) model_.lp_.col_names_[i] = fmt::format("b[{}]", i);
+    if (should_log_) {
+      model_.lp_.row_names_.reserve(num_constraints);
[…]

### 2025-07-10 lucid/verification/Optimiser.h

@@ -68,6 +68,10 @@ class Optimiser {
   [[nodiscard]] double sigma_f() const { return sigma_f_; }
   /** @getter{C coefficient, solver} */
   [[nodiscard]] double C_coeff() const { return C_coeff_; }
+  /** @checker{configured to log the lp problem, solver} */
+  [[nodiscard]] bool should_log_problem() const { return !problem_log_file_.empty(); }
+  /** @checker{configured to log the iis, solver} */
+  [[nodiscard]] bool should_log_iis() const { return !iis_log_file_.empty(); }
 
  protected:
   const int T_;                   ///< Time horizon

### 2025-07-10 bindings/pylucid/cli.py
docs: update pylucid documentation

@@ -155,8 +155,8 @@ class ConfigAction(Action):
         # Validate the configuration dictionary against the schema
         self.validate(config, verbosity=namespace.verbose)
 
-        # Convert the dictionary to CLIArgs and update the namespace
-        self.dict_to_cliargs(config, namespace)
+        # Convert the dictionary to configuration and update the namespace
+        self.dict_to_configuration(config, namespace)
 
     def validate(self, config_dict: dict, verbosity: int = log.LOG_INFO):
         """Validate the configuration dictionary against the schema."""
@@ -177,15 +177,15 @@ class ConfigAction(Action):
                 e if verbosity >= log.LOG_DEBUG else None
             )
 
-    def dict_to_cliargs(self, config_dict: dict, args: Configuration) -> Configuration:
+    def dict_to_configuration(self, config_dict: dict, args: Configuration) -> Configuration:
         """
-        Convert a dictionary parsed from a YAML or JSON file to a CLIArgs object.
+        Convert a dictionary parsed from a YAML or JSON file to a Configuration object.
 
         Args:
             config_dict: Dictionary parsed from a configuration file
 
         Returns:
-            CLIArgs object with the configuration values
+            Configuration object with the configuration values
         """
         # Process basic parameters
         args.input = Path()

### 2025-07-10 bindings/pylucid/gui.py

@@ -64,7 +64,7 @@ def get_args(config_dict: "dict | None" = None) -> Configuration:
         args: Configuration = Configuration()
         config_action = ConfigAction(option_strings=None, dest="")
         config_action.validate(config_dict)
-        config_action.dict_to_cliargs(config_dict, args)
+        config_action.dict_to_configuration(config_dict, args)
         # Just to ensure the system dynamics function is compatible with the initial state
         if args.system_dynamics is None and len(args.xp_samples) == 0:
             return {

### 2025-07-10 docs/filters/markdown.sh

@@ -29,7 +29,7 @@ readonly regex_match_tabbed_end='\[\/\/\]: # "@end-tabbed"'
 readonly regex_substitute_tabbed_end='<\/ul><\/div>'
 
 readonly regex_match_tab='\d16[^#]+#+ *([^\n]*)\n([^\d17]+)\d17'
-readonly regex_substitute_tab='<li><b class="tab-title">\1<\/b>\n\2\n<\/li>'
+readonly regex_substitute_tab='<li><b id="\1" class="tab-title">\1<\/b>\n\2\n<\/li>'
 
 readonly regex_match_mermaid='\d30mermaid\n([^\d30]*)\n\d30'
 readonly regex_substitute_mermaid="<pre class='mermaid'>\n\1<\/pre>"

### 2025-07-10 tests/bindings/pylucid/CaseStudyTemplate.py

@@ -9,7 +9,7 @@ from pylucid.pipeline import pipeline
 
 
 def scenario_config(
-    args: CLIArgs = CLIArgs(
+    args: Configuration = Configuration(
         seed=42,
         gamma=1,
         time_horizon=5,

### 2025-07-10 docs/paper/figures/steps.tex
chore: rename figs into figures

\begin{figure}
    \centering
    \begin{tikzpicture}[node distance=1.2cm and 1.8cm,
            input-block/.style={rectangle, draw, fill=red!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
            output-block/.style={rectangle, draw, fill=green!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
            block/.style={rectangle, draw, fill=blue!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
            arrow/.style={thick,->,>=Stealth},
            tool/.style={rectangle, draw, fill=green!20, text width=3cm, minimum height=0.8cm, align=center, rounded corners},
            inv/.style={}
        ]

        % Input block
        \node[input-block] (input) {Collect samples $\{(x_i, x^+_i)\}_{i=1}^N$};

        % Lucid blocks
        \node[block, right=of input] (feature) {Construct the feature map $\phi: \X \to \mathbb{R}^M$};
        \node[block, right=of feature] (estimator) {Fit the estimator $\hat{f}: \X \to \mathbb{R}^M$};
        \node[block, below=of estimator] (lattice) {Construct lattices on $\X, \X_0, \X_u$};
        \node[block, below=of lattice] (apply-lattice) {Apply the feature map to the lattices points};
        \node[block, left=of apply-lattice] (optimizer) {Optimize the LP};
        \node[draw, dashed, inner sep=0.3cm, rounded corners,
        fit=(estimator)(feature)(lattice)(apply-lattice)(optimizer), label=above:{\textbf{Lucid}}] {};

        % Output block
        \node[output-block, left=of optimizer] (output) {Barrier coefficients};

        % Arrows
        \draw[arrow] (input) -- (feature);
        \draw[arrow] (feature) -- (estimator);
        \draw[arrow] (estimator) -- (lattice);
        \draw[arrow] (lattice) -- (apply-lattice);
        \draw[arrow] (apply-lattice) -- (optimizer);
        \draw[arrow] (optimizer) -- (output);

    \end{tikzpicture}
    \caption{Sequence of steps \lucid goes through to generate a barrier certificate.}
    \label{fig:steps}
\end{figure}

### 2025-07-12 docs/paper/figures/architecture.tex
chore: rename figs into figures
chore: port content to new format

--- 2025-06-16 docs/paper/fig/architecture.tex
@@
     \centering
-    \begin{tikzpicture}[node distance=1.2cm and 1.8cm,
-            input-block/.style={rectangle, draw, fill=red!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
-            output-block/.style={rectangle, draw, fill=green!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
-            block/.style={rectangle, draw, fill=blue!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
+    \begin{tikzpicture}[node distance=0.6cm and 0.6cm,
+            input-block/.style={rectangle, draw, fill=red!10, text width=2.5cm, minimum height=1.2cm, align=center, rounded corners},
+            output-block/.style={rectangle, draw, fill=green!10, text width=2.5cm, minimum height=1.2cm, align=center, rounded corners},
+            block/.style={rectangle, draw, fill=blue!10, text width=2.0cm, minimum height=1.2cm, align=center, rounded corners},
             arrow/.style={thick,->,>=Stealth},
@@
         % Input block
-        \node[input-block] (input) {Config File};
+        \node[input-block] (input) {Configuration};
 
         % Lucid blocks
-        \node[block, right=of input] (estimator) {Estimator};
-        \node[block, right=of estimator] (feature) {Feature map / Barrier template};
-        \node[block, below=of feature] (optimizer) {Optimizer};
-        \node[block, left=of optimizer] (verifier) {Verifier};
+        \node[block, below=of input] (estimator) {Estimator};
+        \node[block, right=of estimator] (tuner) {Tuner};
+        \node[block, left=of estimator] (sets) {Sets};
+        \node[block, below=of estimator] (feature) {Feature map / Barrier template};
+        \node[block, left=of feature] (optimizer) {Optimizer};
+        % \node[block, below=of optimizer] (verifier) {Verifier};
         \node[draw, dashed, inner sep=0.3cm, rounded corners,
-        fit=(estimator)(feature)(optimizer)(verifier), label=above:{\textbf{Lucid}}] {};
+        % fit=(estimator)(feature)(optimizer)(verifier), label=above:{\textbf{Lucid}}] {};
+        fit=(estimator)(feature)(optimizer)(sets)(tuner), label=below:{\textbf{Lucid}}] {};
 
         % Output block
-        \node[output-block, left=of verifier] (output) {Barrier certificate};
+        % \node[output-block, left=of verifier] (output) {Barrier certificate};
+        \node[output-block, below=of optimizer] (output) {Barrier certificate};
 
         % Smt solvers
-        \node[inv, below=2.5cm of verifier.north, anchor=north] (smtInv) {};
-        \node[tool, left=0.3cm of smtInv] (dreal) {dReal};
-        \node[tool, right=0.3cm of smtInv] (cvc5) {CVC5};
-        \node[draw, dashed, inner sep=0.3cm, rounded corners,
-        fit=(dreal)(cvc5), label=left:{\textbf{SMT Solver}}] {};
+        % \node[inv, below=2.5cm of verifier.north, anchor=north] (smtInv) {};
+        % \node[tool, left=0.3cm of smtInv] (dreal) {dReal};
+        % \node[tool, right=0.3cm of smtInv] (cvc5) {CVC5};
+        % \node[draw, dashed, inner sep=0.3cm, rounded corners,
+        % fit=(dreal)(cvc5), label=left:{\textbf{SMT Solver}}] {};
 
@@
         \draw[arrow] (input) -- (estimator);
+        \draw[arrow] (input) -- (tuner);
+        \draw[arrow] (input) -- (sets);
+        \draw[arrow] (sets) -- (optimizer);
+        \draw[arrow] (tuner) -- (estimator);
         \draw[arrow] (estimator) -- (feature);
         \draw[arrow] (feature) -- (optimizer);
-        \draw[arrow] (optimizer) -- (verifier);
-        \draw[arrow] (verifier) -- (output);
+        % \draw[arrow] (optimizer) -- (verifier);
+        % \draw[arrow] (verifier) -- (output);
+        \draw[arrow] (optimizer) -- (output);
 
-        \draw[arrow] (cvc5.north) -- (verifier.south);
-        \draw[arrow] (dreal.north) -- (verifier.south);
+        % \draw[arrow] (cvc5.north) -- (verifier.south);
+        % \draw[arrow] (dreal.north) -- (verifier.south);
 
     \end{tikzpicture}
-    \caption{General architecture of Lucid. \todo{Only dReal is supported at the moment}}
+    \caption{General architecture of Lucid, highlighting its core components and their connections.}
     \label{fig:architecture}

### 2025-07-12 docs/paper/figures/steps.tex
chore: port content to new format

@@
-\begin{figure}
+\begin{figure}[ht]
     \centering
-    \begin{tikzpicture}[node distance=1.2cm and 1.8cm,
-            input-block/.style={rectangle, draw, fill=red!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
-            output-block/.style={rectangle, draw, fill=green!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
-            block/.style={rectangle, draw, fill=blue!10, text width=3.5cm, minimum height=1.2cm, align=center, rounded corners},
+    \begin{tikzpicture}[node distance=0.6cm and 0.9cm,
+            input-block/.style={rectangle, draw, fill=red!10, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners},
+            output-block/.style={rectangle, draw, fill=green!10, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners},
+            block/.style={rectangle, draw, fill=blue!10, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners},
             arrow/.style={thick,->,>=Stealth},
-            tool/.style={rectangle, draw, fill=green!20, text width=3cm, minimum height=0.8cm, align=center, rounded corners},
+            tool/.style={rectangle, draw, fill=green!20, text width=2cm, minimum height=0.8cm, align=center, rounded corners},
             inv/.style={}
@@
         % Lucid blocks
-        \node[block, right=of input] (feature) {Construct the feature map $\phi: \X \to \mathbb{R}^M$};
-        \node[block, right=of feature] (estimator) {Fit the estimator $\hat{f}: \X \to \mathbb{R}^M$};
-        \node[block, below=of estimator] (lattice) {Construct lattices on $\X, \X_0, \X_u$};
+        \node[block, right=of input] (estimator) {Fit the estimator $\hat{f}: \X \to \mathbb{R}^M$};
+        \node[block, below=of estimator] (feature) {Construct the feature map $\phi: \X \to \mathbb{R}^M$};
+        \node[block, below=of feature] (lattice) {Construct lattices on $\X, \X_0, \X_u$};
         \node[block, below=of lattice] (apply-lattice) {Apply the feature map to the lattices points};
-        \node[block, left=of apply-lattice] (optimizer) {Optimize the LP};
+        \node[block, below=of apply-lattice] (optimizer) {Optimize the LP};
         \node[draw, dashed, inner sep=0.3cm, rounded corners,
@@
         % Output block
-        \node[output-block, left=of optimizer] (output) {Barrier coefficients};
+        \node[output-block, left=of optimizer] (output) {Barrier certificate};
 
         % Arrows
-        \draw[arrow] (input) -- (feature);
-        \draw[arrow] (feature) -- (estimator);
-        \draw[arrow] (estimator) -- (lattice);
+        \draw[arrow] (input) -- (estimator);
+        \draw[arrow] (estimator) -- (feature);
+        \draw[arrow] (feature) -- (lattice);
         \draw[arrow] (lattice) -- (apply-lattice);

### 2025-07-26 bindings/pylucid/ext.py
chore: support params in ModelEstimator

@@ -1,6 +1,6 @@
 from typing import TYPE_CHECKING
 
-from ._pylucid import Estimator
+from ._pylucid import Estimator, Parameter
 
 if TYPE_CHECKING:
     from typing import Callable
@@ -16,11 +16,14 @@ class ModelEstimator(Estimator):
 
     Args:
         f: A callable that takes a numpy array as input and returns a numpy array as output.
+        params: A dictionary of parameters that can be used to configure the model.
+            This is not used in this case, but may be required to match the interface of the expected Estimator class.
     """
 
-    def __init__(self, f: "Callable[[NMatrix], NMatrix]"):
+    def __init__(self, f: "Callable[[NMatrix], NMatrix]", params: "dict[str, int | float | NVector] | None" = None):
         super().__init__()
         self._f = f
+        self._params = params or {}
 
     def predict(self, x: "NMatrix") -> "NMatrix":
         """Predict the next state given the current state by applying the model function."""
@@ -44,6 +47,10 @@ class ModelEstimator(Estimator):
         Since we are using the model directly, we can return a fixed score.
         """
         return 1.0
+
+    def get(self, param: Parameter) -> "dict[str, int | float | NVector]":
+        """Get the parameters of the model."""
+        return self._params[param]
 
     def clone(self) -> "ModelEstimator":
         """Clone the estimator."""

### 2025-07-26 bindings/pylucid/cli.py
chore: improve serialisation

@@ -110,12 +110,14 @@ class Configuration(Namespace):
         for k, v in config_dict.items():
             if isinstance(v, np.ndarray):
                 config_dict[k] = v.tolist()
-            if isinstance(v, type):
+            elif isinstance(v, type):
                 config_dict[k] = v.__name__
-            if isinstance(v, Path):
+            elif isinstance(v, Path):
                 config_dict[k] = str(v)
-            if isinstance(v, Set):
+            elif isinstance(v, Set):
                 config_dict[k] = str(v)
+            elif isinstance(v, (Estimator, Kernel, FeatureMap, Optimiser)):
+                config_dict[k] = v.__class__.__name__
         return config_dict
 
     def to_yaml(self, path: "str | Path | None" = None) -> str:

### 2025-07-26 docs/paper/appendix.tex
feat: add theory

@@
-\begin{appendices}
-    \section{Proofs}
-    We have collected a series of proofs of the claims we made in the main text.
+% !TEX root =  main.tex
+\appendix
 
-    \section{Benchmarks}
-    \label{app:benchmarks}
-    Complete list of results for the benchmarks presented in \autoref{sec:benchmarks}.
-    The legend is as follows:
-    \textit{Output} indicates the result produced by the solver (i.e., optimal, unbounded, infeasible or unspecified),
-    \textit{Prec} indicates the number of bits used in the last floating-point number representation,
-    \textit{Ref} indicates the number of refinements,
-    and \textit{time} is the time in seconds.
+\section{Additional Theoretical Details}
+\paragraph{RKHS basics.}
+A symmetric function $k_\X:\X\times\X\rightarrow\R$ is called a (positive definite) \emph{kernel} (note the distinction from \emph{probability kernels}) if for all $N\in\N_{>0}$ we have $\sum_{i=1}^{N}\sum_{j=1}^{N}a_i a_j\allowbreak k_\X(x_i,x_j) \geq 0$ for $x_1,\ldots,x_N\in\X\subset{\R^n}$ and $a_1,\ldots,a_N\in\R$.
+A prominent example is the \emph{squared exponential} (SQExp) kernel \shortcite{Rasmussen2005GP,Kanagawa2018GPvsKernel}:
+\begin{equation}
+    k_\X(x,x') := \sigma_f^2 \exp\left( -\frac{1}{2} (x-x')\T \Sigma\, (x-x') \right),\quad \Sigma:=\mathrm{diag}(\sigma_l)^{-2},\label{eq:sqexp_kernel}
+\end{equation}
+with amplitude $\sigma_f^2\geq0$ and lengthscale coefficients $\sigma_l\in\R^n$.
+\new{For this work,} we assume that all kernels are bounded on their domain, i.e., $\E_{}[k_\X(x,x)]<\infty$, $x\in\X$.
+Given a kernel $k_\X$ on a non-empty set $\X$, there exists a unique corresponding
+\emph{reproducing kernel Hilbert space} (RKHS) $\Hilbert_{k_\X}$
+of functions $f:\X\rightarrow\R$ equipped with an inner product $\innerH{\cdotx}{\cdotx}{\Hilbert_{k_\X}}$
+with the celebrated \emph{reproducing property} such that for any function $f\in\Hilbert_{k_\X}$ and $x\in\X$ we have $f(x)=\innerH{f}{k_\X(\cdotx,x)}{\Hilbert_{k_\X}}$.
+Note that $k_\X(\cdotx,x):\X\rightarrow\Hilbert_{k_\X}$ is a real-valued function,
+which is also called an implicit \emph{canonical} \emph{embedding} or \emph{feature map} $\phi_\X$
+such that $k_\X(x,x')=\innerH{\phi_\X(x)}{\phi_\X(x')}{\Hilbert_{k_\X}}$ for all $x,x'\in\X$.
+For an RKHS $\Hilbert_{k_\X}$, we use the associated feature map $\phi_\X$ and kernel $k_\X$ interchangeably for ease of notation and comprehensibility.
+The inner product induces the norm $\norm{f}_{\Hilbert_{k_\X}}\!\!\!\!:=\!\!\sqrt{\smash[b]{\innerH{f}{f}{\Hilbert_{k_\X}}}}$ of the RKHS. 
+Throughout this paper, we assume that all RKHSs are \emph{separable}.
+Refer to the monograph by \citet{Berlinet2004RKHSProbStat} for a comprehensive study on RKHSs.
+Given $N$ i.i.d. samples $\hat X_N:=[\hat{x}_i]_{i=1}^N$ with $\hat{x}_i\in\X$, the
+\emph{Gram matrix} of $k_\X$ is given by
+$\new{K_{\hat{X}}^N}:=[k_\X(\hat{x}_i,\hat{x}_j)]_{i,j=1}^N.$
+Furthermore, we define the vector-valued function 
+$\new{k_{\hat{X}}^N}(x)  := [k_\X(x,\hat{x}_i)]_{i=1}^N.$
 
-\end{appendices}
+\begin{definition}[Conditional Mean Embedding (CME)]\label{def:condMeanEmbed}
+    Given two RKHSs $\Hilbert_{k_\X}$ and $\Hilbert_{k_\Y}$ with the associated kernels $k_\X\colon\X\times\X\to\R$ and $k_\Y\colon\X\times\X\to\R$, the \emph{CME} of a probability kernel $\Tr\colon\X\times\borel{\Y}\rightarrow[0,1]$ is an $X$-measurable random variable taking values in $\Hilbert_{k_\Y}$, given by
+    \begin{equation*}
+        \cme_{k_\Y|k_\X}(\Tr)(\cdotx) := \E_{\Tr}[\phi_\Y(Y)\mid X=\cdotx].
+    \end{equation*}
+\end{definition}
+
+    % \section{Proofs}
+    % We have collected a series of proofs of the claims we made in the main text.
+
+    % \section{Benchmarks}
+    % \label{app:benchmarks}
+    % Complete list of results for the benchmarks presented in \autoref{sec:benchmarks}.
+    % The legend is as follows:
+    % \textit{Output} indicates the result produced by the solver (i.e., optimal, unbounded, infeasible or unspecified),
+    % \textit{Prec} indicates the number of bits used in the last floating-point number representation,
+    % \textit{Ref} indicates the number of refinements,
+    % and \textit{time} is the time in seconds.

### 2025-07-26 docs/paper/figures/architecture.tex
feat: add theory

@@
     \begin{tikzpicture}[node distance=0.6cm and 0.6cm,
-            input-block/.style={rectangle, draw, fill=red!10, text width=2.5cm, minimum height=1.2cm, align=center, rounded corners},
-            output-block/.style={rectangle, draw, fill=green!10, text width=2.5cm, minimum height=1.2cm, align=center, rounded corners},
-            block/.style={rectangle, draw, fill=blue!10, text width=2.0cm, minimum height=1.2cm, align=center, rounded corners},
-            arrow/.style={thick,->,>=Stealth},
-            tool/.style={rectangle, draw, fill=magenta!10, text width=3cm, minimum height=0.8cm, align=center, rounded corners},
+            input-block/.style={rectangle, draw, fill=red!10, text width=2.5cm, minimum height=0.8cm, align=center, rounded corners},
+            output-block/.style={rectangle, draw, fill=green!20, text width=2.6cm, minimum height=0.8cm, align=center, rounded corners},
+            block/.style={rectangle, draw, fill=accent!20, text width=2.0cm, minimum height=0.8cm, align=center, rounded corners},
+            arrow/.style={thick,->,>=latex},
+            % tool/.style={rectangle, draw, fill=magenta!10, text width=3cm, minimum height=0.8cm, align=center, rounded corners},
             inv/.style={}
@@
         % Input block
-        \node[input-block] (input) {Configuration};
+        \node[doc] (input) {Config\\(.yaml?)};
 
         % Lucid blocks
-        \node[block, below=of input] (estimator) {Estimator};
-        \node[block, right=of estimator] (tuner) {Tuner};
-        \node[block, left=of estimator] (sets) {Sets};
-        \node[block, below=of estimator] (feature) {Feature map / Barrier template};
-        \node[block, left=of feature] (optimizer) {Optimizer};
+        \node[block, below=1cm of input] (estimator) {\Circled{2} Estimator};
+        \node[block, right=of estimator] (tuner) {\Circled{3} Tuner};
+        \node[block, left=of estimator] (sets) {\Circled{1} Safety Specification};
+        \node[block, below=of estimator] (feature) {\Circled{4} Feature Map}; % / Barrier template
+        \node[block, left=of feature] (optimizer) {\Circled{5} Solver};
         % \node[block, below=of optimizer] (verifier) {Verifier};
-        \node[draw, dashed, inner sep=0.3cm, rounded corners,
+        \node[draw, dashed, inner sep=0.25cm, rounded corners,
         % fit=(estimator)(feature)(optimizer)(verifier), label=above:{\textbf{Lucid}}] {};
-        fit=(estimator)(feature)(optimizer)(sets)(tuner), label=below:{\textbf{Lucid}}] {};
+        fit=(estimator)(feature)(optimizer)(sets)(tuner), label=below:{\textbf{\lucid}}] {};
 
@@
         % \node[output-block, left=of verifier] (output) {Barrier certificate};
-        \node[output-block, below=of optimizer] (output) {Barrier certificate};
+        \node[output-block, below=of optimizer] (output) {Barrier Certificate};
+        \node[output-block, below=.5cm of output] (prob) {Safety Probability};
+        \node[] at ($(output)!0.5!(prob)$) (plus) {$+$};
 
@@
         \draw[arrow] (input) -- (estimator);
-        \draw[arrow] (input) -- (tuner);
-        \draw[arrow] (input) -- (sets);
+        \draw[arrow] ($(input.south)+(0.0,-0.3)$) -| (tuner);
+        \draw[arrow] ($(input.south)+(0.0,-0.3)$) -| (sets);
         \draw[arrow] (sets) -- (optimizer);
@@
     \end{tikzpicture}
-    \caption{General architecture of Lucid, highlighting its core components and their connections.}
+    \caption{General architecture of \lucid, highlighting its core components and their connections.}
     \label{fig:architecture}

### 2025-07-26 docs/paper/figures/steps.tex
feat: add theory

@@
         % Input block
-        \node[input-block] (input) {Collect samples $\{(x_i, x^+_i)\}_{i=1}^N$};
+        \node[input-block] (input) {Collect samples $\{(x^i,a^i, x_+^i)\}_{i=1}^N$};
 
         % Lucid blocks
-        \node[block, right=of input] (estimator) {Fit the estimator $\hat{f}: \X \to \mathbb{R}^M$};
-        \node[block, below=of estimator] (feature) {Construct the feature map $\phi: \X \to \mathbb{R}^M$};
+        \node[block, right=of input] (estimator) {Fit the estimator $\hat{f}\colon \X\times\A \to \X$};
+        \node[block, below=of estimator] (feature) {Construct the feature map $\phi_M\colon \X\times\A \to \mathbb{R}^M$};
         \node[block, below=of feature] (lattice) {Construct lattices on $\X, \X_0, \X_u$};
-        \node[block, below=of lattice] (apply-lattice) {Apply the feature map to the lattices points};
-        \node[block, below=of apply-lattice] (optimizer) {Optimize the LP};
+        \node[block, below=of lattice] (apply-lattice) {Apply the feature map to the lattice points};
+        \node[block, below=of apply-lattice] (optimizer) {Solve the LP};
         \node[draw, dashed, inner sep=0.3cm, rounded corners,
-        fit=(estimator)(feature)(lattice)(apply-lattice)(optimizer), label=above:{\textbf{Lucid}}] {};
+        fit=(estimator)(feature)(lattice)(apply-lattice)(optimizer), label=above:{\textbf{\lucid}}] {};
 
         % Output block
-        \node[output-block, left=of optimizer] (output) {Barrier certificate};
+        \node[output-block, left=of optimizer] (output) {Barrier certificate\\+\\Safety probability};
 

### 2025-07-26 docs/paper/code/example.py

@@ -1,0 +1,33 @@
+# example.py
+from pylucid import *
+import numpy as np
+
+def scenario_config() -> Configuration:
+    random.seed(42)
+    np.random.seed(42)
+    # Configuration
+    c = Configuration()
+    c.gamma = 15.0
+    c.time_horizon = 15
+    c.sigma_f = 1.0
+    c.sigma_l = [1.75555556]
+    c.num_frequencies = 5
+    c.oversample_factor = 64.0
+    # System parameters
+    c.system_dynamics = lambda x: x / 2
+    c.X_bounds = RectSet([(-1, 1)])
+    c.X_init = RectSet([(-0.5, 0.5)])
+    c.X_unsafe = MultiSet(RectSet([(-1, -0.9)]), RectSet([(0.9, 1)]))
+    # Sampling
+    c.x_samples = c.X_bounds.sample(1000)
+    c.xp_samples = c.system_dynamics(c.x_samples) + np.random.normal(scale=0.01)
+    # Estimator
+    c.estimator = KernelRidgeRegressor(
+        kernel=GaussianKernel(sigma_f=c.sigma_f, sigma_l=c.sigma_l),
+        regularization_constant=1e-6,
+    )
+    # Execution options
+    c.plot = True
+    c.verify = True
+    c.optimiser = GurobiOptimiser
+    return c

### 2025-07-26 docs/paper/code/linear.py

@@ -1,39 +1,0 @@
-# linear.py
-from pylucid import *
-
-
-def scenario_config(args: CLIArgs):
-    # Model
-    f_det = lambda x: 0.5 * x
-    f = lambda x: f_det(x) + np.random.normal(scale=0.01)
-
-    # Sets
-    X_bounds = RectSet([(-1, 1)], seed=args.seed)
-    X_init = RectSet([(-0.5, 0.5)])
-    X_unsafe = MultiSet(RectSet([(-1, -0.9)]), RectSet([(0.9, 1)]))
-
-    # Sampling
-    x_samples = X_bounds.sample(args.num_samples)
-    xp_samples = f(x_samples)
-
-    # Estimator
-    estimator = KernelRidgeRegressor(
-        kernel=GaussianKernel(sigma_f=args.sigma_f, sigma_l=args.sigma_l),
-        regularization_constant=args.lambda_,
-    )
-
-    # Lucid configuration
-    return ScenarioConfig(
-        x_samples=x_samples,
-        xp_samples=xp_samples,
-        X_bounds=X_bounds,
-        X_init=X_init,
-        X_unsafe=X_unsafe,
-        T=args.time_horizon,
-        gamma=args.gamma,
-        num_freq_per_dim=args.num_frequencies,
-        f_det=f_det,
-        estimator=estimator,
-        sigma_f=args.sigma_f,
-        oversample_factor=args.oversample_factor,
-    )

### 2025-07-26 public/Kernel_8h.js
Update documentation

@@ -1,0 +1,4 @@
+var Kernel_8h =
+[
+    [ "lucid::Kernel", "classlucid_1_1Kernel.html", "classlucid_1_1Kernel" ]
+];

### 2025-07-26 public/LbfgsTuner_8h.js

@@ -1,0 +1,5 @@
+var LbfgsTuner_8h =
+[
+    [ "lucid::LbgsParameters", "structlucid_1_1LbgsParameters.html", "structlucid_1_1LbgsParameters" ],
+    [ "lucid::LbfgsTuner", "classlucid_1_1LbfgsTuner.html", "classlucid_1_1LbfgsTuner" ]
+];

### 2025-07-26 public/MultiSet_8h.js

@@ -1,0 +1,4 @@
+var MultiSet_8h =
+[
+    [ "lucid::MultiSet", "classlucid_1_1MultiSet.html", "classlucid_1_1MultiSet" ]
+];

### 2025-07-26 public/ParameterValue_8h.js

@@ -1,0 +1,4 @@
+var ParameterValue_8h =
+[
+    [ "lucid::ParameterValue", "classlucid_1_1ParameterValue.html", "classlucid_1_1ParameterValue" ]
+];

### 2025-07-26 public/TensorIterator_8h.js

@@ -1,0 +1,4 @@
+var TensorIterator_8h =
+[
+    [ "lucid::TensorIterator< T >", "classlucid_1_1TensorIterator.html", "classlucid_1_1TensorIterator" ]
+];

### 2025-07-26 public/classlucid_1_1ParameterValues.js

@@ -1,0 +1,14 @@
+var classlucid_1_1ParameterValues =
+[
+    [ "ParameterValues", "classlucid_1_1ParameterValues.html#aa8f9610a369a647588bdf003b4122a66", null ],
+    [ "ParameterValues", "classlucid_1_1ParameterValues.html#a555f81b9bf9ebd3889d7fd838aafe6e0", null ],
+    [ "ParameterValues", "classlucid_1_1ParameterValues.html#a935d534639cbaf6f31f9f2e7d0fb54d0", null ],
+    [ "get", "classlucid_1_1ParameterValues.html#ace1b1a0e916c51e47d0b4a6a0b779b7e", null ],
+    [ "operator==", "classlucid_1_1ParameterValues.html#aade677c3cdb56b4eeeed35e028e29c1a", null ],
+    [ "parameter", "classlucid_1_1ParameterValues.html#adc0ad5792df06268a38b75f10929c457", null ],
+    [ "size", "classlucid_1_1ParameterValues.html#aa39280c957d6647b4a7055268d134603", null ],
+    [ "values", "classlucid_1_1ParameterValues.html#a15ce50d6c4133e81454a88b5b52cb8a1", null ],
+    [ "parameter_", "classlucid_1_1ParameterValues.html#a433e67302cf71abf35ea03b4c316ed07", null ],
+    [ "size_", "classlucid_1_1ParameterValues.html#a9351957697eee7f5f2e6b3283f255a0e", null ],
+    [ "values_", "classlucid_1_1ParameterValues.html#a77a79905d7152fad1b2c4bd9c7822708", null ]
+];

### 2025-07-26 public/dir_0185b220c667a4ac70a5cda9c2cc673f.js

@@ -1,0 +1,12 @@
+var dir_0185b220c667a4ac70a5cda9c2cc673f =
+[
+    [ "alglib.cpp", "alglib_8cpp.html", null ],
+    [ "alglib.h", "alglib_8h.html", null ],
+    [ "eigen.cpp", "eigen_8cpp.html", "eigen_8cpp" ],
+    [ "eigen.h", "eigen_8h.html", "eigen_8h" ],
+    [ "eigen_extension.h", "eigen__extension_8h.html", "eigen__extension_8h" ],
+    [ "eigen_matrix_base_plugin.h", "eigen__matrix__base__plugin_8h.html", "eigen__matrix__base__plugin_8h" ],
+    [ "gurobi.h", "gurobi_8h.html", null ],
+    [ "highs.h", "highs_8h.html", null ],
+    [ "pocketfft.h", "pocketfft_8h.html", null ]
+];

### 2025-07-26 public/files_dup.js

@@ -1,0 +1,4 @@
+var files_dup =
+[
+    [ "lucid", "dir_7dd98ebc1faa69ba9fd53f2d897504fc.html", "dir_7dd98ebc1faa69ba9fd53f2d897504fc" ]
+];

### 2025-07-26 public/namespaces_dup.js

@@ -1,0 +1,4 @@
+var namespaces_dup =
+[
+    [ "lucid", "namespacelucid.html", "namespacelucid" ]
+];

### 2025-07-26 public/navtreeindex0.js

@@ -1,0 +1,253 @@
+var NAVTREEINDEX0 =
+{
+"AlglibOptimiser_8cpp.html":[15,0,0,3,0],
+"AlglibOptimiser_8h.html":[15,0,0,3,1],
+"ConstantTruncatedFourierFeatureMap_8cpp.html":[15,0,0,1,0],
+"ConstantTruncatedFourierFeatureMap_8h.html":[15,0,0,1,1],
+"Estimator_8cpp.html":[15,0,0,1,2],
+"Estimator_8h.html":[15,0,0,1,3],
+"FeatureMap_8cpp.html":[15,0,0,1,4],
+"FeatureMap_8h.html":[15,0,0,1,5],
+"GaussianKernel_8cpp.html":[15,0,0,1,6],
+"GaussianKernel_8h.html":[15,0,0,1,7],
+"GradientOptimizable_8cpp.html":[15,0,0,1,8],
+"GradientOptimizable_8h.html":[15,0,0,1,9],
+"GramMatrix_8cpp.html":[15,0,0,1,10],
+"GramMatrix_8h.html":[15,0,0,1,11],
+"GridSearchTuner_8cpp.html":[15,0,0,1,12],
+"GridSearchTuner_8h.html":[15,0,0,1,13],
+"GurobiOptimiser_8cpp.html":[15,0,0,3,2],
+"GurobiOptimiser_8h.html":[15,0,0,3,3],
+"HighsOptimiser_8cpp.html":[15,0,0,3,4],
+"HighsOptimiser_8h.html":[15,0,0,3,5],
+"IndexIterator_8cpp.html":[15,0,0,2,5],
+"IndexIterator_8h.html":[15,0,0,2,6],
+"InverseGramMatrix_8cpp.html":[15,0,0,1,14],
+"InverseGramMatrix_8h.html":[15,0,0,1,15],
+"KernelRidgeRegressor_8cpp.html":[15,0,0,1,18],
+"KernelRidgeRegressor_8h.html":[15,0,0,1,19],
+"Kernel_8cpp.html":[15,0,0,1,16],
+"Kernel_8h.html":[15,0,0,1,17],
+"LbfgsTuner_8cpp.html":[15,0,0,1,20],
+"LbfgsTuner_8h.html":[15,0,0,1,21],
+"LinearTruncatedFourierFeatureMap_8cpp.html":[15,0,0,1,22],
[…]

### 2025-07-26 public/search/all_4.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['4_0',['4',['../md_docs_2Todo.html#activity-4',1,'Activity 4'],['../md_docs_2Todo.html#extension-4',1,'Extension 4']]]
+];

### 2025-07-26 public/search/enums_0.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['loggertype_0',['LoggerType',['../namespacelucid_1_1log.html#abdb89e7c48b6f30be5e3e5f8eb57ab80',1,'lucid::log']]]
+];

### 2025-07-26 public/search/enumvalues_4.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['regularization_5fconstant_0',['REGULARIZATION_CONSTANT',['../namespacelucid.html#af391319051f1a656ecaf252ddfd84d84a563dc7650b3dee61cf6cb2711af2bcc6',1,'lucid']]]
+];

### 2025-07-26 public/search/files_a.js

@@ -1,0 +1,12 @@
+var searchData=
+[
+  ['main_2ecpp_0',['main.cpp',['../main_8cpp.html',1,'']]],
+  ['math_2eh_1',['math.h',['../math_8h.html',1,'']]],
+  ['matplotlib_2ecpp_2',['matplotlib.cpp',['../matplotlib_8cpp.html',1,'']]],
+  ['matplotlib_2eh_3',['matplotlib.h',['../matplotlib_8h.html',1,'']]],
+  ['medianheuristictuner_2ecpp_4',['MedianHeuristicTuner.cpp',['../MedianHeuristicTuner_8cpp.html',1,'']]],
+  ['medianheuristictuner_2eh_5',['MedianHeuristicTuner.h',['../MedianHeuristicTuner_8h.html',1,'']]],
+  ['model_2eh_6',['model.h',['../model_8h.html',1,'']]],
+  ['multiset_2ecpp_7',['MultiSet.cpp',['../MultiSet_8cpp.html',1,'']]],
+  ['multiset_2eh_8',['MultiSet.h',['../MultiSet_8h.html',1,'']]]
+];

### 2025-07-26 public/search/functions_7.js

@@ -1,0 +1,6 @@
+var searchData=
+[
+  ['has_0',['has',['../classlucid_1_1Parametrizable.html#aa9aeaa85d55e01638aa10f9ce1b091e7',1,'lucid::Parametrizable']]],
+  ['has_5fiis_5flog_5ffile_1',['has_iis_log_file',['../classlucid_1_1Optimiser.html#a6af72ba8b0581902ce716f1a5c1c89f5',1,'lucid::Optimiser']]],
+  ['has_5fproblem_5flog_5ffile_2',['has_problem_log_file',['../classlucid_1_1Optimiser.html#ad32725ac2c215d43b5cce6616aaaa183',1,'lucid::Optimiser']]]
+];

### 2025-07-26 public/search/pages_3.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['features_0',['Features',['../md_docs_2Features.html',1,'']]]
+];

### 2025-07-26 public/search/searchdata.js

@@ -1,0 +1,48 @@
+var indexSectionsWithContent =
+{
+  0: "012348_abcdefghiklmnopqrstuvwxyz—",
+  1: "acefghiklmoprst",
+  2: "l",
+  3: "acdefghiklmoprstuv",
+  4: "abcdefghiklmnoprstuvwxy",
+  5: "abcdefghiklmnoprstuvwxz",
+  6: "hoprs",
+  7: "lpr",
+  8: "_dgors",
+  9: "l",
+  10: "bcdfilptu—",
+  11: "aimnst"
+};
+
+var indexSectionNames =
+{
+  0: "all",
+  1: "classes",
+  2: "namespaces",
+  3: "files",
+  4: "functions",
+  5: "variables",
+  6: "typedefs",
+  7: "enums",
+  8: "enumvalues",
+  9: "defines",
+  10: "pages",
+  11: "concepts"
+};
+
+var indexSectionLabels =
+{
+  0: "All",
+  1: "Classes",
+  2: "Namespaces",
+  3: "Files",
+  4: "Functions",
+  5: "Variables",
+  6: "Typedefs",
+  7: "Enumerations",
+  8: "Enumerator",
+  9: "Macros",
+  10: "Pages",
+  11: "Concepts"
+};
+

### 2025-07-26 public/search/variables_f.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['regularization_5fconstant_5f_0',['regularization_constant_',['../classlucid_1_1KernelRidgeRegressor.html#ae95cc0f5dcfb51b98e2f304bf43e3d0c',1,'lucid::KernelRidgeRegressor']]],
+  ['rstride_1',['rstride',['../structlucid_1_1plt_1_1PlotSurfaceKwargs.html#a763e295b472cd8718c9ee95c6afabd24',1,'lucid::plt::PlotSurfaceKwargs::rstride'],['../structlucid_1_1plt_1_1PlotWireframeKwargs.html#ab82cd3a5a17b4abb13578ec7a908f0d6',1,'lucid::plt::PlotWireframeKwargs::rstride']]]
+];

### 2025-07-26 public/structlucid_1_1plt_1_1PlotWireframeKwargs.js

@@ -1,0 +1,7 @@
+var structlucid_1_1plt_1_1PlotWireframeKwargs =
+[
+    [ "cmap", "structlucid_1_1plt_1_1PlotWireframeKwargs.html#a601db5a6098a9ecbc2807dec7746131c", null ],
+    [ "cstride", "structlucid_1_1plt_1_1PlotWireframeKwargs.html#a2d4cfb39bc75d3cc8605a4a8871f92b1", null ],
+    [ "fig_number", "structlucid_1_1plt_1_1PlotWireframeKwargs.html#acbdfad1d9a7d62f75110497879f8883d", null ],
+    [ "rstride", "structlucid_1_1plt_1_1PlotWireframeKwargs.html#ab82cd3a5a17b4abb13578ec7a908f0d6", null ]
+];

### 2025-07-26 public/structlucid_1_1plt_1_1ScatterKwargs.js

@@ -1,0 +1,8 @@
+var structlucid_1_1plt_1_1ScatterKwargs =
+[
+    [ "c", "structlucid_1_1plt_1_1ScatterKwargs.html#acd4461a79cf5b06adcda8028b9775b44", null ],
+    [ "fig_number", "structlucid_1_1plt_1_1ScatterKwargs.html#a4f9499760de4ab7af53c0ad2fe82d2fa", null ],
+    [ "marker", "structlucid_1_1plt_1_1ScatterKwargs.html#a022862690f44d7217278732e0a1ef3a7", null ],
+    [ "s", "structlucid_1_1plt_1_1ScatterKwargs.html#ac1408a587e7e1f384735ed7fc1313c07", null ],
+    [ "zdir", "structlucid_1_1plt_1_1ScatterKwargs.html#ab97e2ba202697e2796cbe091b5a6151a", null ]
+];

### 2025-07-28 docs/paper/figures/architecture.tex
feat: update paper

@@
     \begin{tikzpicture}[node distance=0.6cm and 0.6cm,
-            input-block/.style={rectangle, draw, fill=red!10, text width=2.5cm, minimum height=0.8cm, align=center, rounded corners},
-            output-block/.style={rectangle, draw, fill=green!20, text width=2.6cm, minimum height=0.8cm, align=center, rounded corners},
-            block/.style={rectangle, draw, fill=accent!20, text width=2.0cm, minimum height=0.8cm, align=center, rounded corners},
+            input-block/.style={rectangle, draw, fill=red!10!white, text width=2.5cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
+            output-block/.style={rectangle, draw, fill=green!20!white, text width=2.6cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
+            block/.style={rectangle, draw, fill=accent!20!white, text width=2.0cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
             arrow/.style={thick,->,>=latex},
@@
         % Input block
-        \node[doc] (input) {Config\\(.yaml?)};
+        \node[doc] (input) {Configuration\\[.2em]\textit{.yaml/.json}};
 

### 2025-07-28 docs/paper/figures/steps.tex
feat: update paper

@@
     \begin{tikzpicture}[node distance=0.6cm and 0.9cm,
-            input-block/.style={rectangle, draw, fill=red!10, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners},
-            output-block/.style={rectangle, draw, fill=green!10, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners},
-            block/.style={rectangle, draw, fill=blue!10, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners},
+            input-block/.style={rectangle, draw, fill=white, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
+            output-block/.style={rectangle, draw, fill=green!20, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
+            block/.style={rectangle, draw, fill=accent!20, text width=3.7cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
             arrow/.style={thick,->,>=Stealth},
-            tool/.style={rectangle, draw, fill=green!20, text width=2cm, minimum height=0.8cm, align=center, rounded corners},
-            inv/.style={}
+            tool/.style={rectangle, draw, fill=green!20, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
+            inv/.style={}, 
+            arrow/.style={thick,->,>=latex}
         ]
@@
         % Input block
-        \node[input-block] (input) {Collect samples $\{(x^i,a^i, x_+^i)\}_{i=1}^N$};
+        \node[input-block] (samples) {Collect samples $\{(x^i,a^i, x_+^i)\}_{i=1}^N$};
 
         % Lucid blocks
-        \node[block, right=of input] (estimator) {Fit the estimator $\hat{f}\colon \X\times\A \to \X$};
-        \node[block, below=of estimator] (feature) {Construct the feature map $\phi_M\colon \X\times\A \to \mathbb{R}^M$};
+        \node[block, right=of samples] (estimator) {Fit the estimator 
+        $\E[f(X_+)\!\mid\! X=x,A=a]$
+        % $\hat{f}\colon \X\times\A \to \X$
+        };
+        \node[block, below=of estimator] (feature) {Construct the feature map $\phi_M\colon \X \to \mathbb{R}^{2M+1}$};
         \node[block, below=of feature] (lattice) {Construct lattices on $\X, \X_0, \X_u$};
@@
 
+        \node[input-block, left=of lattice] (specification) {Specify $\X, \X_0, \X_u$};
+
         % Output block
-        \node[output-block, left=of optimizer] (output) {Barrier certificate\\+\\Safety probability};
+        \node[output-block, left=of optimizer, yshift=.75cm] (output) {Barrier certificate};
+        \node[output-block, left=of optimizer, yshift=-.75cm] (output2) {Safety probability};
 
         % Arrows
-        \draw[arrow] (input) -- (estimator);
+        \draw[arrow] (samples) -- (estimator);
+        \draw[arrow] (specification) -- (lattice);
         \draw[arrow] (estimator) -- (feature);
@@
         \draw[arrow] (apply-lattice) -- (optimizer);
-        \draw[arrow] (optimizer) -- (output);
+        \draw[arrow] (optimizer.170) -- (output.east);
+        \draw[arrow] (optimizer.190) -- (output2.east);
 

### 2025-07-28 benchmarks/integration/benchmark.py
fix: aligh benchmarks with pipeline

@@ -133,8 +133,6 @@ class TimeLogger:
 
 
 def benchmark_pipeline(config: Configuration):
-    tick = datetime.now()
-
     with TimeLogger("setup"):
         config_dict = config.to_safe_dict()
         mlflow.log_dict(config_dict, "config.yaml")
@@ -216,13 +214,35 @@ def benchmark_pipeline(config: Configuration):
         # We are fixing the zero frequency to the constant value we computed in the feature map
         # If we don't, the regressor has a hard time learning it on the extreme left and right points, because it tends to 0
         u_f_xp_lattice_via_regressor[:, 0] = feature_map.weights[0] * config.sigma_f
+        mlflow.log_metric("x_lattice.shape.0", x_lattice.shape[0])
+        mlflow.log_metric("u_f_x_lattice.shape.1", u_f_x_lattice.shape[1])
 
-        x0_lattice = config.X_init.lattice(num_oversample, True)
+        if config.constant_lattice_points:
+            x0_lattice = config.X_init.lattice(num_oversample, True)
+            xu_lattice = config.X_unsafe.lattice(num_oversample, True)
+        else:
+            # TODO: implement this more efficiently in lucid (C++)
+            count = 0
+            x0_lattice = np.empty_like(x_lattice)
+            for point in x_lattice:
+                if point in config.X_init:
+                    x0_lattice[count] = point
+                    count += 1
+            x0_lattice.resize((count, config.X_bounds.dimension))
+            count = 0
+            xu_lattice = np.empty_like(x_lattice)
+            for point in x_lattice:
+                if point in config.X_unsafe:
+                    xu_lattice[count] = point
+                    count += 1
+            xu_lattice.resize((count, config.X_bounds.dimension))
+        mlflow.log_metric("x0_lattice.shape.0", x0_lattice.shape[0])
+        mlflow.log_metric("xu_lattice.shape.0", xu_lattice.shape[0])
+
         f_x0_lattice = feature_map(x0_lattice)
-
-        xu_lattice = config.X_unsafe.lattice(num_oversample, True)
         f_xu_lattice = feature_map(xu_lattice)
 
+    with TimeLogger("solve"):
         return config.optimiser(
             config.time_horizon,
             config.gamma,
@@ -262,7 +282,7 @@ def check_cb_factory(config: Configuration, num_oversample: int, feature_map: Fe
         )
         if success:
             mlflow.log_table({"solution": sol.tolist()}, "solution.json")
[…]

### 2025-07-28 bindings/pylucid/pipeline.py
fix: manually add extreme points in the lattice

@@ -155,21 +155,30 @@ def pipeline(
     # We are fixing the zero frequency to the constant value we computed in the feature map
     # If we don't, the regressor has a hard time learning it on the extreme left and right points, because it tends to 0
     u_f_xp_lattice_via_regressor[:, 0] = feature_map.weights[0] * args.sigma_f
+    log.debug(f"x_lattice: {x_lattice.shape}, u_f_x_lattice: {u_f_x_lattice.shape}")
+
 
     if args.constant_lattice_points:
         x0_lattice = args.X_init.lattice(num_oversample, True)
         xu_lattice = args.X_unsafe.lattice(num_oversample, True)
     else:
         # TODO: implement this more efficiently in lucid (C++)
-        count = 0
-        x0_lattice = np.empty_like(x_lattice)
+        # Extreme points are always included in the lattice,
+        # to make sure gamma and eta conditions are satisfied on the boundaries
+        x0_extreme_points = args.X_init.lattice(2, True)
+        x0_lattice = np.concatenate([x0_extreme_points, np.empty_like(x_lattice)], axis=0)
+        count = x0_extreme_points.shape[0]
         for point in x_lattice:
             if point in args.X_init:
                 x0_lattice[count] = point
                 count += 1
         x0_lattice.resize((count, args.X_bounds.dimension))
-        count = 0
-        xu_lattice = np.empty_like(x_lattice)
+
+        # Extreme points are always included in the lattice,
+        # to make sure gamma and eta conditions are satisfied on the boundaries
+        xu_extreme_points = args.X_unsafe.lattice(2, True)
+        xu_lattice = np.concatenate([xu_extreme_points, np.empty_like(x_lattice)], axis=0)
+        count = xu_extreme_points.shape[0]
         for point in x_lattice:
             if point in args.X_unsafe:
                 xu_lattice[count] = point
@@ -190,7 +199,7 @@ def pipeline(
             log.info("Optimization succeeded")
             log.debug(f"{obj_val = }, {eta = }, {c = }, {norm = }")
             log.debug(f"{sol = }")
-        if args.plot:
+        if args.plot and args.X_bounds.dimension <= 2:
             result["fig"] = plot_solution(
                 X_bounds=args.X_bounds,
                 X_init=args.X_init,

### 2025-07-28 bindings/pylucid/dreal.py
feat: add relative tolerance and improve error report

@@ -179,11 +179,11 @@ def verify_barrier_certificate(
                 # Non-negativity of the barrier function (-tolerance)
                 barrier >= -tolerance,
                 # First condition
-                Implies(build_set_constraint(xs, X_init), barrier <= eta),
+                Implies(build_set_constraint(xs, X_init), barrier <= eta + tolerance * eta),
                 # Second condition
-                Implies(build_set_constraint(xs, X_unsafe), barrier >= gamma),
+                Implies(build_set_constraint(xs, X_unsafe), barrier >= gamma - tolerance * gamma),
                 # Third condition
-                barrier_p - barrier <= c + tolerance,
+                barrier_p - barrier <= c + tolerance * c,
             ),
         ),
     )
@@ -197,9 +197,20 @@ def verify_barrier_certificate(
     log.error(f"Model: {model}")
     point = np.array([list(model.values())], dtype=np.float64)
     pointp = f_det(point)
-    log.error(f"X: {point}, barrier value: {tffm(point) @ sol.T}")
-    log.error(f"Xp: {pointp}, barrier value: {tffm(pointp) @ sol.T}")
-    log.error(f"Xp: estimated, barrier value: {estimator(point) @ sol.T}")
+    true_barrier = tffm(point) @ sol.T
+    true_barrier_p = tffm(pointp) @ sol.T
+    estimated_barrier = estimator(point) @ sol.T
+    log.error(f"X: {point}, barrier value: {true_barrier}")
+    log.error(f"Xp: {pointp}, barrier value: {true_barrier_p}")
+    log.error(f"Xp: estimated, barrier value: {estimated_barrier}")
     log.error(f"Barrier at Xp {tffm(pointp)[0]}")
     log.error(f"Estimated barrier at Xp {estimator(point)[0]}")
+    if (true_barrier < -tolerance).any():
+        log.error("Violated barrier condition: B >= 0.")
+    if point in X_unsafe and (true_barrier < gamma - tolerance * gamma).any():
+        log.error("Violated barrier condition: B >= gamma.")
+    if point in X_init and (true_barrier > eta + tolerance * eta).any():
+        log.error("Violated barrier condition: B <= eta.")
+    if (true_barrier_p - true_barrier > c + tolerance * c).any():
+        log.error("Violated barrier condition: Bp - B <= c.")
     return False

### 2025-07-28 frontend/src/utils/constants.ts
fix: linear example in frontend

@@ -54,23 +54,16 @@ const Linear: Partial<Configuration> = {
   xp_samples: [],
   X_bounds: [{ RectSet: [[-1, 1]] }],
   X_init: [{ RectSet: [[-0.5, 0.5]] }],
-  X_unsafe: [
-    {
-      RectSet: [[-1, -0.9]],
-    },
-    {
-      RectSet: [[0.9, 1]],
-    },
-  ],
+  X_unsafe: [{ RectSet: [[-1, -0.9]] }, { RectSet: [[0.9, 1]] }],
   gamma: 1,
   c_coefficient: 1,
-  lambda: 0.001,
+  lambda: 0.00001,
   num_samples: 1000,
-  time_horizon: 5,
-  sigma_f: 15.0,
-  sigma_l: 1.75555556,
-  num_frequencies: 8,
-  oversample_factor: 128.0,
+  time_horizon: 15,
+  sigma_f: 18,
+  sigma_l: 0.034,
+  num_frequencies: 5,
+  oversample_factor: 64,
   num_oversample: -1,
   noise_scale: 0.01,
   plot: true,

### 2025-07-28 bindings/pylucid/plot.py
chore: shorten label

@@ -249,7 +249,7 @@ def plot_solution_1d(
                 y=est_values.flatten(),
                 mode="lines",
                 line=dict(color="purple"),
-                name="B(xp) via regression",
+                name="B(xp) est.",
             )
 
         # Lattice points
@@ -280,8 +280,17 @@ def plot_solution_1d(
                 y=est_lattice_values.flatten(),
                 mode="markers",
                 marker=dict(color="purple"),
-                name="B(xp) via regression (lattice)",
+                name="B(xp) est. (lattice)",
             )
+
+    # Mainly for the presentation
+    # fig.update_layout(margin=dict(l=0, r=0, t=40, b=10))
+    # fig.update_layout(legend=dict(
+    #     yanchor="middle",
+    #     y=0.5,
+    #     xanchor="center",
+    #     x=0.5
+    # ))
 
     fig.update_layout(title="Barrier certificate", xaxis_title="State space", showlegend=True)
 
@@ -441,7 +450,7 @@ def plot_solution_2d(
                 z=Z_est,
                 colorscale=[[0, "purple"], [1, "purple"]],
                 opacity=0.3,
-                name="B(xp) via regression",
+                name="B(xp) est.",
                 showscale=False,
                 showlegend=True,
             )

### 2025-07-28 benchmarks/integration/benchmark.py
fix: align benchmarks with pipeline

@@ -222,15 +222,22 @@ def benchmark_pipeline(config: Configuration):
             xu_lattice = config.X_unsafe.lattice(num_oversample, True)
         else:
             # TODO: implement this more efficiently in lucid (C++)
-            count = 0
-            x0_lattice = np.empty_like(x_lattice)
+            # Extreme points are always included in the lattice,
+            # to make sure gamma and eta conditions are satisfied on the boundaries
+            x0_extreme_points = config.X_init.lattice(2, True)
+            x0_lattice = np.concatenate([x0_extreme_points, np.empty_like(x_lattice)], axis=0)
+            count = x0_extreme_points.shape[0]
             for point in x_lattice:
                 if point in config.X_init:
                     x0_lattice[count] = point
                     count += 1
             x0_lattice.resize((count, config.X_bounds.dimension))
-            count = 0
-            xu_lattice = np.empty_like(x_lattice)
+
+            # Extreme points are always included in the lattice,
+            # to make sure gamma and eta conditions are satisfied on the boundaries
+            xu_extreme_points = config.X_unsafe.lattice(2, True)
+            xu_lattice = np.concatenate([xu_extreme_points, np.empty_like(x_lattice)], axis=0)
+            count = xu_extreme_points.shape[0]
             for point in x_lattice:
                 if point in config.X_unsafe:
                     xu_lattice[count] = point

### 2025-07-28 docs/paper/figures/architecture.tex
chore: add benchmark template

--- 2025-07-26 docs/paper/figures/architecture.tex
@@
     \begin{tikzpicture}[node distance=0.6cm and 0.6cm,
-            input-block/.style={rectangle, draw, fill=red!10, text width=2.5cm, minimum height=0.8cm, align=center, rounded corners},
-            output-block/.style={rectangle, draw, fill=green!20, text width=2.6cm, minimum height=0.8cm, align=center, rounded corners},
-            block/.style={rectangle, draw, fill=accent!20, text width=2.0cm, minimum height=0.8cm, align=center, rounded corners},
+            input-block/.style={rectangle, draw, fill=red!10!white, text width=2.5cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
+            output-block/.style={rectangle, draw, fill=green!20!white, text width=2.6cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
+            block/.style={rectangle, draw, fill=accent!20!white, text width=2.0cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
             arrow/.style={thick,->,>=latex},
+            doc/.style={draw,thick,align=center,color=black,shape=document,minimum width=20mm-6mm,minimum height=24.2mm-10mm,shape=document,inner sep=1ex,fill=white,drop shadow=gray!50},
             % tool/.style={rectangle, draw, fill=magenta!10, text width=3cm, minimum height=0.8cm, align=center, rounded corners},
@@
         % Input block
-        \node[doc] (input) {Config\\(.yaml?)};
+        \node[doc] (input) {Configuration\\[.2em]\textit{.yaml/.json/.py}};
 

### 2025-07-28 docs/paper/glossary.tex
feat: add case studies
chore: port content to new format
feat: add theory
feat: fast comment address
chore: add benchmark template

@@
 \newglossaryentry{lp}{
-    first={Linear Programming (LP)},
-    name={Linear Programming},
+    first={Linear Program (LP)},
+    name={Linear Program},
     text={LP},
     description={
-            A Linear Programming problem is an optimization problem where the objective function and the constraints
+            A Linear Program is an optimization problem where the objective function and the constraints
             are linear functions. \\
-            A typical Linear Programming problem has the following form:
+            A typical Linear Program has the following form:
             \begin{equation*}
@@
 }
+\newglossaryentry{rkhs}{
+    name={Reproducing Kernel Hilbert Space},
+    text={RKHS},
+    first={Reproducing Kernel Hilbert Space (RKHS)},
+    firstplural={Reproducing Kernel Hilbert Spaces (RKHS)},
+    description={}
+}
+\newglossaryentry{cbc}{
+    name={Control Barrier Certificate},
+    text={CBC},
+    plural={CBCs},
+    first={\emph{Control Barrier Certificate} (CBC)},
+    firstplural={\emph{Control Barrier Certificates} (CBCs)},
+    description={}
+}
+\newglossaryentry{cbf}{
+    name={Control Barrier Certificate},
+    text={CBF},
+    plural={CBFs},
+    first={\emph{Control Barrier Function} (CBF)},
+    firstplural={\emph{Control Barrier Functions} (CBFs)},
+    description={}
+}
+\newglossaryentry{gui}{
+    name={Graphical User Interface},
+    text={GUI},
+    first={\emph{Graphical User Interface} (GUI)},
+    description={}
+}
+\newglossaryentry{cli}{
+    name={Command Line Interface},
+    text={CLI},
+    first={\emph{Command Line Interface} (CLI)},
+    description={}
+}
+\newglossaryentry{nn}{
+    name={Neural Network},
+    text={NN},
+    first={\emph{Neural Network} (NN)},
+    description={}
+}
+\newglossaryentry{cme}{
+    name={Conditional Mean Embedding},
+    text={CME},
+    plural={CMEs},
+    first={\emph{Conditional Mean Embedding} (CME)},
+    firstplural={\emph{Conditional Mean Embeddings} (CMEs)},
+    description={}
+}

### 2025-07-30 benchmarks/integration/Barrier2.py
chore: improve experiment and tuning parameters

@@ -8,7 +8,6 @@ from benchmark import single_benchmark
 
 from pylucid import *
 from pylucid import __version__
-from pylucid.plot import plot_function, plot_data
 
 
 def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) -> Configuration:
@@ -37,22 +36,6 @@ def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) ->
     config.x_samples = config.X_bounds.sample(config.num_samples)
     config.xp_samples = f(config.x_samples)
 
-    plot_function(
-        f=config.system_dynamics,
-        X_bounds=config.X_bounds,
-        X_init=config.X_init,
-        X_unsafe=config.X_unsafe,
-    )
-
-    plot_data(
-        config.x_samples,
-        config.xp_samples,
-        X_bounds=config.X_bounds,
-        X_init=config.X_init,
-        X_unsafe=config.X_unsafe,
-    )
-    return
-
     # feature_map = config.feature_map(
     #     num_frequencies=config.num_frequencies,
     #     sigma_l=config.sigma_l,
@@ -71,16 +54,10 @@ def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) ->
     # ################################## #
     # Running the pipeline
     # ################################## #
-
-    if config.num_frequencies >= 12 and config.oversample_factor > 20.0:
-        log.warn("The number of frequencies and oversampling factor too high.")
-        return
-
     single_benchmark(
-        name="Barrier3",
+        name="Barrier2",
         config=config,
     )
-
 
 if __name__ == "__main__":
     # ################################## #
@@ -91,12 +68,12 @@ if __name__ == "__main__":
 
     grid = {
         # "num_frequencies": [9, 12, 13, 16, 17],
-        # "num_frequencies": [9, 12, 13],
+        "num_frequencies": [15],
         # "num_frequencies": [4],
         "c_coefficient": [1.0],
         "time_horizon": [5],
         # "oversample_factor": [10.0, 20.0, 30.0],
-        "num_oversample": [250.0],
+        "num_oversample": [250, 300, 350],
         # "oversample_factor": [10.0],
     }
 

### 2025-07-30 benchmarks/integration/Barrier3.py

@@ -33,7 +33,7 @@ def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) ->
     # ################################## #
     # Data
     # ################################## #
-    f = lambda x: config.system_dynamics(x)  # + (np.random.normal(scale=config.noise_scale))
+    f = lambda x: config.system_dynamics(x) + (np.random.normal(scale=config.noise_scale))
     config.x_samples = config.X_bounds.sample(config.num_samples)
     config.xp_samples = f(config.x_samples)
 
@@ -74,12 +74,12 @@ if __name__ == "__main__":
 
     grid = {
         # "num_frequencies": [9, 12, 13, 16, 17],
-        "num_frequencies": [9, 12, 13],
+        "num_frequencies": [13],
         # "num_frequencies": [4],
         "c_coefficient": [1.0],
         "time_horizon": [5],
-        # "oversample_factor": [10.0, 20.0, 30.0],
-        "num_oversample": [250.0],
+        "oversample_factor": [20.0, 25.0],
+        # "num_oversample": [250, 300, 350, 400],
         # "oversample_factor": [10.0],
     }
 

### 2025-07-30 benchmarks/integration/DcMotor.py

@@ -4,11 +4,11 @@ import multiprocessing
 import time
 
 import numpy as np
-from benchmark import grid_to_config, single_benchmark
+from benchmark import single_benchmark
 
 from pylucid import *
 from pylucid import __version__
-from pylucid.plot import plot_function, plot_data
+from pylucid.plot import plot_data
 from pylucid.cli import ConfigAction
 
 

### 2025-07-30 benchmarks/integration/TuneBarrier.py

@@ -1,87 +1,0 @@
-#!/usr/bin/env python3
-import time
-
-import numpy as np
-
-from pylucid import *
-from pylucid import __version__
-from pylucid.pipeline import pipeline
-
-try:
-    from pylucid.plot import plot_function
-except ImportError:
-
-    def plot_function(*args, **kwargs):
-        pass
-
-
-"""
-KernelRidgeRegressor( kernel( GaussianKernel( sigma_l( 10  7  5 ) sigma_f( 7 ) isotropic( 0 ) ) ) regularization_constant( 1e-05 ) )                 => 0.999265720310824
-KernelRidgeRegressor( kernel( GaussianKernel( sigma_l( 3.57182 3.12249 1.10899 ) sigma_f( 7 ) isotropic( 0 ) ) ) regularization_constant( 1e-05 ) )  => 0.9999970679186748
-KernelRidgeRegressor( kernel( GaussianKernel( sigma_l( 3.59381 0.278256 3.59381 ) sigma_f( 7 ) isotropic( 0 ) ) ) regularization_constant( 1e-05 ) ) => 0.9999999635706251
-"""
-import itertools
-
-def scenario_config(config: Configuration):
-    # Add process noise
-    if config.seed >= 0:
-        np.random.seed(config.seed)  # For reproducibility
-        random.seed(config.seed)
-
-    if config.system_dynamics:
-        f = lambda x: config.system_dynamics(x) + (np.random.normal(scale=config.noise_scale))
-        config.x_samples = config.X_bounds.sample(config.num_samples)
-        config.xp_samples = f(config.x_samples)
-
-    val = [v for v in np.logspace(-3, 2, num=10, endpoint=True, dtype=float)]
-    tuner = GridSearchTuner(
-        parameters={
-            Parameter.REGULARIZATION_CONSTANT: [1e-8, 1e-9, 1e-10, 1e-11],
-            Parameter.SIGMA_F: [1.0],
-            Parameter.SIGMA_L: [np.array(vs) for vs in itertools.product(val, val)],
-        },
-    )
-    estimator = KernelRidgeRegressor(
-        kernel=GaussianKernel(sigma_l=config.sigma_l, sigma_f=config.sigma_f),
-        regularization_constant=config.lambda_,
-    )
-    feature_map = LinearTruncatedFourierFeatureMap(
-        num_frequencies=config.num_frequencies,
-        sigma_l=config.sigma_l,
-        sigma_f=config.sigma_f,
-        x_limits=config.X_bounds,
-    )
-
[…]

### 2025-07-30 benchmarks/integration/TuneBarrier3.py

@@ -10,7 +10,7 @@ if __name__ == "__main__":
     grid = {
         Parameter.REGULARIZATION_CONSTANT: [1.0e-6],
         Parameter.SIGMA_F: [1.0],
-        Parameter.SIGMA_L: [np.array(x) for x in itertools.product(val, val, val)],
+        Parameter.SIGMA_L: [np.array(x) for x in itertools.product(val, val)],
     }
 
-    scenario_tuner("benchmarks/integration/overtaking.yaml", grid)
+    scenario_tuner("benchmarks/integration/barrier3.yaml", grid)

### 2025-07-30 docs/paper/appendix.tex
feat: update paper

--- 2025-05-30 docs/paper/appendix.tex
@@
-\begin{appendices}
-    \section{Proofs}
-    We have collected a series of proofs of the claims we made in the main text.
+% !TEX root =  main.tex
+\appendix
 
-    \section{Benchmarks}
-    \label{app:benchmarks}
-    Complete list of results for the benchmarks presented in \autoref{sec:benchmarks}.
-    The legend is as follows:
-    \textit{Output} indicates the result produced by the solver (i.e., optimal, unbounded, infeasible or unspecified),
-    \textit{Prec} indicates the number of bits used in the last floating-point number representation,
-    \textit{Ref} indicates the number of refinements,
-    and \textit{time} is the time in seconds.
+% \section{Additional Theoretical Details}
+% \paragraph{RKHS basics.}
+% A symmetric function $k_\X:\X\times\X\rightarrow\R$ is called a (positive definite) \emph{kernel} (note the distinction from \emph{probability kernels}) if for all $N\in\N_{>0}$ we have $\sum_{i=1}^{N}\sum_{j=1}^{N}a_i a_j\allowbreak k_\X(x_i,x_j) \geq 0$ for $x_1,\ldots,x_N\in\X\subset{\R^n}$ and $a_1,\ldots,a_N\in\R$.
+% A prominent example is the \emph{squared exponential} (SQExp) kernel \shortcite{Rasmussen2005GP,Kanagawa2018GPvsKernel}:
+% \begin{equation}
+%     k_\X(x,x') := \sigma_f^2 \exp\left( -\frac{1}{2} (x-x')\T \Sigma\, (x-x') \right),\quad \Sigma:=\mathrm{diag}(\sigma_l)^{-2},\label{eq:sqexp_kernel}
+% \end{equation}
+% with amplitude $\sigma_f^2\geq0$ and lengthscale coefficients $\sigma_l\in\R^n$.
+% \new{For this work,} we assume that all kernels are bounded on their domain, i.e., $\E_{}[k_\X(x,x)]<\infty$, $x\in\X$.
+% Given a kernel $k_\X$ on a non-empty set $\X$, there exists a unique corresponding
+% \emph{reproducing kernel Hilbert space} (RKHS) $\Hilbert_{k_\X}$
+% of functions $f:\X\rightarrow\R$ equipped with an inner product $\innerH{\cdotx}{\cdotx}{\Hilbert_{k_\X}}$
+% with the celebrated \emph{reproducing property} such that for any function $f\in\Hilbert_{k_\X}$ and $x\in\X$ we have $f(x)=\innerH{f}{k_\X(\cdotx,x)}{\Hilbert_{k_\X}}$.
+% Note that $k_\X(\cdotx,x):\X\rightarrow\Hilbert_{k_\X}$ is a real-valued function,
+% which is also called an implicit \emph{canonical} \emph{embedding} or \emph{feature map} $\phi_\X$
+% such that $k_\X(x,x')=\innerH{\phi_\X(x)}{\phi_\X(x')}{\Hilbert_{k_\X}}$ for all $x,x'\in\X$.
+% For an RKHS $\Hilbert_{k_\X}$, we use the associated feature map $\phi_\X$ and kernel $k_\X$ interchangeably for ease of notation and comprehensibility.
+% The inner product induces the norm $\norm{f}_{\Hilbert_{k_\X}}\!\!\!\!:=\!\!\sqrt{\smash[b]{\innerH{f}{f}{\Hilbert_{k_\X}}}}$ of the RKHS. 
+% Throughout this paper, we assume that all RKHSs are \emph{separable}.
+% Refer to the monograph by \citet{Berlinet2004RKHSProbStat} for a comprehensive study on RKHSs.
+% Given $N$ i.i.d. samples $\hat X_N:=[\hat{x}_i]_{i=1}^N$ with $\hat{x}_i\in\X$, the
+% \emph{Gram matrix} of $k_\X$ is given by
+% $\new{K_{\hat{X}}^N}:=[k_\X(\hat{x}_i,\hat{x}_j)]_{i,j=1}^N.$
+% Furthermore, we define the vector-valued function 
+% $\new{k_{\hat{X}}^N}(x)  := [k_\X(x,\hat{x}_i)]_{i=1}^N.$
 
-\end{appendices}
+% \begin{definition}[Conditional Mean Embedding (CME)]\label{def:condMeanEmbed}
+%     Given two RKHSs $\Hilbert_{k_\X}$ and $\Hilbert_{k_\Y}$ with the associated kernels $k_\X\colon\X\times\X\to\R$ and $k_\Y\colon\X\times\X\to\R$, the \emph{CME} of a probability kernel $\Tr\colon\X\times\borel{\Y}\rightarrow[0,1]$ is an $X$-measurable random variable taking values in $\Hilbert_{k_\Y}$, given by
+%     \begin{equation*}
+%         \cme_{k_\Y|k_\X}(\Tr)(\cdotx) := \E_{\Tr}[\phi_\Y(Y)\mid X=\cdotx].
+%     \end{equation*}
+% \end{definition}
+
+\section{Linear Program}
+The finitely-constrained LP discussed in Section~\ref{sec:ddbarriers} is presented.
+For this, the lattices $X_{{N}}\subset\X$, $\smash{\{ x_0^{1}, \ldots, x_0^{{N}_0} \}} \subset \X_0$, and $\smash{\{ x_u^{1}, \ldots, x_u^{{N}_u} \}} \subset \X_u$ of cardinality ${N}_0\in\N$ and ${N}_u\in\N$, respectively, are formed.
+%
+For given values of $\overline{\B}$, $\gamma$, and robustness radius $\mathcal{R}\geq0$, the following LP is obtained:
+    \begin{equation*}
+        \begin{alignedat}{3}
+                  & \min_{\stackrel{b, c, \eta}{\Bmin_{{N}}^{\X_0}, \Bmax_{{N}}^{\X_u},\Bmax_{{N}}^\X,\Bmin_\Delta}}\hspace{-1.5em}  &                                            & \eta + cT,                                          &                       &
+            %\label{eq:blackbox:linear_prog_objective}
+            \\
+                  & \text{subject to}
+                  &                                                                                                                                & \phi_M(x_0^{i})\T b\leq\hat{\eta}, \quad &                                                     & i=1,\ldots,{N}_0,
+            %\label{eq:blackbox:linear_prog_initial}
+            \\
+                  &                                                                                                                                &                                            & \phi_M(x_u^{i})\T b\geq\hat{\gamma},
+            \quad &                                                                                                                                & i=1,\ldots,{N}_u,
+            %\label{eq:blackbox:linear_prog_unsafe}
+            \\
+                  &                                                                                                                                &                                            & \phi_M(x^{i})\T(Hb - b) \leq \hat{\Delta},
+            \quad &                                                                                                                                & i=1,\ldots,{N},
+            %\label{eq:blackbox:linear_prog_kushner}
+            \\
+                  &                                                                                                                                &                                            & \phi_M(x^{i})\T b\geq \hat{\xi},
+            \quad &                                                                                                                                & i=1,\ldots,{N},
+            %\label{eq:blackbox:linear_prog_positive}
+            \\
+                  &                                                                                                                                &                                            & \Bmin_{{N}}^{\X_0}\leq\phi_M(x_0^{i})\T b,
+            \quad &                                                                                                                                & i=1,\ldots,{N}_0,                                                                                                      \\
+                  &                                                                                                                                &                                            & \Bmax_{{N}}^{\X_u}\geq\phi_M(x_u^{i})\T b,
+            \quad &                                                                                                                                & i=1,\ldots,{N}_u,                                                                                                      \\
+                  &                                                                                                                                &                                            & \Bmax_{{N}}^\X\geq\phi_M(x^{i})\T b,
+            \quad &                                                                                                                                & i=1,\ldots,{N},                                                                                                        \\
+                  &                                                                                                                                &                                            & \Bmin_\Delta\leq\phi_M(x^{i})\T (Hb - b),
+            \quad &                                                                                                                                & i=1,\ldots,{N},                                                                                                        \\
+                  &                                                                                                                                &                                            & c\geq 0,\,\gamma>\eta\geq 0,\, b\in\R^{2M+1},       &                       &
+            \label{eq:blackbox:linear_prog}%
+        \end{alignedat}
+    \end{equation*}
+with $\overline{\kappa}\geq\sigma_f$, $\overline{\B}\geq\norm{b}_2$, and constraint-tightening coefficients
+    \begin{align*}
+        \hat{\eta}   & := \frac{2}{C_{{N}}+1}\eta + \frac{C_{{N}}-1}{C_{{N}}+1}\Bmin_{{N}}^{\X_0},
+                     \\                                                                                                                                    & \hat{\gamma} := \frac{2}{C_{{N}}+1}\gamma + \frac{C_{{N}}-1}{C_{{N}}+1}\Bmax_{{N}}^{\X_u}, \\
+        \hat{\Delta} & := \frac{2}{C_{{N}}+1}\left(c - \mathcal{R}\overline{\B}\overline{\kappa}\right) + \frac{C_{{N}}-1}{C_{{N}}+1}\Bmin_\Delta,
+                     \\                                                                                                                                     & \hat{\xi} := \frac{C_{{N}}-1}{C_{{N}}+1}\Bmax_{{N}}^\X.
+    \end{align*}
+
+    % \section{Proofs}
+    % We have collected a series of proofs of the claims we made in the main text.
+
+    % \section{Benchmarks}
+    % \label{app:benchmarks}
+    % Complete list of results for the benchmarks presented in \autoref{sec:benchmarks}.
+    % The legend is as follows:
+    % \textit{Output} indicates the result produced by the solver (i.e., optimal, unbounded, infeasible or unspecified),
+    % \textit{Prec} indicates the number of bits used in the last floating-point number representation,
+    % \textit{Ref} indicates the number of refinements,
+    % and \textit{time} is the time in seconds.

### 2025-07-30 docs/paper/main.tex
feat: update paper

--- 2025-06-09 docs/paper/main.tex
@@
-\documentclass{article}
+%File: anonymous-submission-latex-2025.tex
+\documentclass[letterpaper]{article} % DO NOT CHANGE THIS
 
@@
 
+% Title
+
+% Your title must be in mixed case, not sentence case.
+% That means all verbs (including short verbs like be, is, using,and go),
+% nouns, adverbs, adjectives should be capitalized, including both words in hyphenated terms, while
+% articles, conjunctions, and prepositions are lower case unless they
+% directly follow a colon or long dash
+\title{LUCID: Learning-Enabled Uncertainty-Aware Certification of Stochastic Dynamical Systems}
+%\title{LUCID -- ???}
+% Black-Box Verification Engine for Embodied AI Systems?
+% \author {
+%     % Authors
+    % Ernesto Casablanca\textsuperscript{\rm 1},
+    % Oliver Sch\"on\textsuperscript{\rm 1}%,
+    % Third Author Name\textsuperscript{\rm 2}
+% }
+% \affiliations {
+    % Affiliations
+    % \textsuperscript{\rm 1}Newcastle University, United Kingdom\\
+    % \textsuperscript{\rm 2}Affiliation 2\\
+    % e.casablanca2@ncl.ac.uk, o.schoen2@ncl.ac.uk%, thirdAuthor@affiliation1.com
+% }
+
+% REMOVE THIS: bibentry
+% This is only needed to show inline citations in the guidelines document. You should not need it and can safely delete it.
+\usepackage{bibentry}
+% END REMOVE bibentry
+
 \begin{document}
-
-\title{Delta-Complete Linear Programming}
-
-\author{Oliver Sch\"{o}n \and
-Ernesto Casablanca \and
-Sadegh Soudjani \and
-Paolo Zuliani
-}
-
-\begin{comment}
-\institute{O. Sh\"{o}n,E. Casablanca \at Newcastle University, Newcastle upon Tyne, United Kingdgom \\ \email{e.casablanca2@newcastle.ac.uk}, \email{o.schoen2@newcastle.ac.uk}
-\and
-S. Soudjani \at Max Planck Institute for Software Systems, Kaiserslautern, Germany \\ \email{sadegh@mpi-sws.org}
-\and
-P. Zuliani \at Universit\`{a} di Roma ``La Sapienza'', Rome, Italy\\ \email{zuliani@di.uniroma1.it}
-}
-\end{comment}
 
@@
 \begin{abstract}
-  Ensuring the safety of AI-enabled systems, particularly in high-stakes domains like autonomous driving and healthcare, has become increasingly critical.
-  Traditional formal verification tools fall short when faced with the opaque, black-box nature of AI components and the sheer scale of modern applications.
-  To address these challenges, we introduce Lucid, a new tool designed specifically for the safety verification and synthesis of black-box systems governed by discrete-time stochastic dynamics.
+    Ensuring the safety of AI-enabled systems, particularly in high-stakes domains such as autonomous driving and healthcare, has become increasingly critical.
+    Traditional formal verification tools fall short when faced with systems that embed both opaque, black-box AI components and complex stochastic dynamics.
+    To address these challenges, we introduce \lucid (Learning-enabled Uncertainty-aware Certification of stochastIc Dynamical systems), a verification engine for certifying safety of black-box stochastic dynamical systems from a finite dataset of random state transitions.
+    As such, \lucid is the first known tool capable of establishing quantified safety guarantees for such systems.
+    Thanks to its modular architecture and extensive documentation, \lucid is designed for easy extensibility.
 
-  Lucid employs a data-driven methodology rooted in control barrier certificates, which are learned directly from system trajectory data to ensure formal safety guarantees.
-  We use conditional mean embeddings to embed data into a reproducing kernel Hilbert space (RKHS), where it constructs an RKHS ambiguity set that can be inflated to robustify the result to out-of-distribution behavior.
-  To generalize beyond safety, we provide theoretical foundations for applying Lucid to broader classes of temporal logic specifications.
+    \lucid employs a data-driven methodology rooted in control barrier certificates, which are learned directly from system transition data, to ensure formal safety guarantees.
+    We use conditional mean embeddings to embed data into a reproducing kernel Hilbert space (RKHS), where an RKHS ambiguity set is constructed that can be inflated to robustify the result to out-of-distribution behavior.
 
-  A key innovation within Lucid is its use of a finite Fourier expansion to reformulate a semi-infinite non-linear optimization problem into a tractable linear program.
+    A key innovation within \lucid is its use of a finite Fourier kernel expansion to reformulate a semi-infinite non-convex optimization problem into a tractable linear program.
     The resulting spectral barrier allows us to leverage the fast Fourier transform to generate the relaxed problem efficiently, offering a scalable yet distributionally robust framework for verifying safety.
-  Lucid thus offers a robust and efficient verification framework, able to handle the complexities of modern black-box systems while providing formal guarantees of safety.
+    \lucid thus offers a robust and efficient verification framework, able to handle the complexities of modern black-box systems while providing formal guarantees of safety.
+    These unique capabilities are demonstrated on challenging benchmarks.
 \end{abstract}
 
+% Uncomment the following to link to your code, datasets, an extended version or similar.
+%
+\begin{links}
+    \link{Source Code}{https://gitlab.com/lucidtoolsource/lucid}
+    \link{Documentation}{https://lucidtoolsource.gitlab.io/lucid/}
+    % \link{Datasets}{https://aaai.org/example/datasets}
+    % \link{Extended version}{https://aaai.org/example/extended-version}
+\end{links}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Introduction}
-\label{sec:intro}
+Embodied forms of AI are on the rise, including applications such as autonomous vehicles, robotics, personalized healthcare, and smart infrastructure.
+Their core functionality is build around the advances of deep learning, enabling systems to understand and reason in complex and human-like ways to produce a desired behavior.
+Whilst the black-box nature of AI components has been a crucial contributor to the widespread success of deep learning, in response to a rapidly evolving legal scrutinization~\cite{veale2021demystifying}, the resulting lack of traceability and certifiability has put a premature halt to its deployment in safety-critical applications.
 
-Lucid is in implemented in C++ and it is meant to be used as a library.
-It provides a set of interfaces that allow users to have an high level of control and flexibility over the verification process.
-We also provide a Python wrapper, called PyLucid, to facilitate the integration of the tool into existing workflows and effortlessly leverage well-established libraries such as NumPy~\cite{numpy} and SciPy~\cite{scipy}.
-Lucid is available as an open-source project on GitHub at \url{https://github.com/TendTo/lucid}.
-More technical details about the implementation can be found in the documentation at \url{https://tendto.github.io/lucid/}.
+As deep learning agents are left to choose their actions autonomously in closed-loop interaction with the physical world, they are confronted with a world riddled with randomness and uncertainty. 
+Efforts to establishing trust in their safe operation have been largely focused on developing tools to verify the input--output behavior of neural networks (NNs) embedded in the systems~\cite{liu2021algorithms}.
+Unfortunately, there do not exist any tools that could take these results and certify the safety of the entire system, as uncertainty-aware models of closed-loop systems are rarely available and simulators are often too complicated and opaque to perform verification directly~\cite{wongpiromsarn2023formal}.
+This motivates a holistic black-box treatment~\cite{corso2021survey}, where safety guarantees are to be established from behavioral data and in account of the unknown uncertainty.
 
-\section{Problem Statement}
-\label{sec:problem-statement}
+There exist no tools capable of solving this problem with quantified guarantees.
+%
+For the setting where a model of the closed-loop system is available, \npinterval by \citet{harapanahalli2023forward} verifies safety of nonlinear systems with non-deterministic disturbance based on existing NN verification tools.
+See the references therein and the annual friendly competition by \citet{abate2024arch} for adjacent work.
+%
+Few data-driven approaches for stochastic systems exist. 
+\omnisafe is a comprehensive platform for the development of safe reinforcement learning (RL) algorithms~\citet{ji2024omnisafe}.
+However, safe RL does generally only \emph{encourage} safer behavior, without providing any rigorous or quantified guarantees on the probability of the absence of unsafe behavior.
+As a popular working principle for certifying safety, control barrier certificates (CBCs)~\cite{prajna2006barrier} are at the basis of tools such as \trust~\cite{gardner2025trust} (supports only polynomial dynamics) and \fossil~\cite{edwards2024fossil} (model-based), which are restricted to deterministic systems.
 
-\subsection{Notation}
-\label{sec:notation}
+To close this gap (see Table~\ref{tab:qualitative_comparison}), we introduce \lucid, the first verification engine for black-box stochastic dynamical systems with quantified guarantees.
+\begin{table}
+    \centering
+    \begin{tabular}{ccccccc}
+        \toprule
+        \textbf{Tool}                                    & \multicolumn{6}{c}{\textbf{Supported Features}}                                                                                                                                                             \\[.4em]
+                                                         & \rotatebox{90}{Guarantees}                      & \rotatebox{90}{Data Driven} & \rotatebox{90}{Stochastic D.} & \rotatebox{90}{Non-Poly.
+D.} & \rotatebox{90}{Stat.
+Correct.} & \rotatebox{90}{Closed Loop} \\
+        \midrule
+        \textbf{\lucid}                                  & \cmark                                          & \cmark                      & \cmark                        & \cmark                       & \cmark                         & \cmark                      \\
+        \trust~\shortcite{gardner2025trust}              & \cmark                                          & \cmark                      & \xmarkred                     & \xmarkred                    & \cmark\footnotemark[1]            & \cmark                      \\
+        \fossil~\shortcite{edwards2024fossil}            & \cmark                                          & \xmarkred                   & \xmarkred                     & \cmark                       & NA                             & \cmark                      \\
+        \omnisafe~\shortcite{ji2024omnisafe}             & \xmarkred                                       & \cmark                      & \cmark                        & \cmark                       & \xmarkred                      & \cmark                      \\
+        \npinterval~\shortcite{harapanahalli2023forward} & \cmark                                          & \xmarkred                   & \cmark/\xmarkred\footnotemark[2] & \cmark                            & NA                             & \cmark                      \\
+        % \deepsplit~\shortcite{henriksen2021deepsplit} & \xmarkred & \xmarkred & \cmark & \xmarkred& \xmarkred \\
+        % \reluplex~\shortcite{katz2017reluplex} & \xmarkred & \xmarkred & \cmark & \xmarkred & \xmarkred \\
+        % tool6                                            &                                                 &                             &                               &                                                                                             \\
+        \bottomrule
+    \end{tabular}
+    \caption{Qualitative comparison with existing tools based on their supported features: quantified safety guarantees, data driven, stochastic dynamics, non-polynomial dynamics, statistical correctness guarantees of the learned model (only applicable if data driven), and support for closed-loop systems.}
+    \label{tab:qualitative_comparison}
+\end{table}
+\footnotetext[1]{Assuming the data satisfies persistence of excitation.} % TRUST
+\footnotetext[2]{Accepts non-deterministic bounded disturbances.} % npinterval
+At its core, it learns CBCs for unknown systems based solely on data, by constructing an uncertainty-aware estimator of the expected system behavior based on \emph{conditional mean embeddings} (CMEs)~\cite{muandet2017kernel}.
+Crucially, the underlying learning framework establishes quantified safety probabilities with distributionally robust guarantees for arbitrary smooth dynamics, thus relaxing the need for restrictive structural assumptions common to related approaches.
+For instance, \citet{schoen2024distributionally} learn CBCs for systems with polynomial dynamics and \citet{chen2025distributionally} assume systems with known deterministic component.
+%
+Alternative approaches often leave the statistical correctness with respect to the underlying data-generating process unaddressed: \citet{kazemi2020fullLTL} use model-free reinforcement learning, relying on known Lipschitz constants; \citet{lew2021sampling} compute reachable sets for stochastic systems using a sampling-based scheme, which yields only asymptotic guarantees; and \citet{salamati2024data} use a scenario-based method, based on Lipschitz constants and exponentially large datasets.
+For data-driven safety verification of stochastic systems via conformal prediction~\cite{lindemann2024formal}, no tools are available.
 
-% Spaces and numbers
-We denote the sets of positive integers and non-negative reals as $\N_{>0}$ and $\R_{\geq 0}$, respectively.
-% Probability theory
-Consider a Polish sample space $\X$ \cite{bogachev2007measure}.
-Let $(\X,\borel{\X},\P)$ be the underlying probability space equipped with a Borel $\sigma$-algebra $\borel{\X}$ defined over $\X$, i.e., the smallest $\sigma$-algebra containing open subsets of $\X$, and a probability measure $\P$.
-For a random variable $X$, let $p_X$ be the pushforward probability measure of $\P$ under $X$ such that $X\sim p_X(\cdotx)$.
+We summarize the main contributions of this work:
+\begin{itemize}
+    \item We introduce \lucid, a novel verification engine that learns control barrier certificates from data using kernel-based CMEs.
+\lucid uses a tractable reformulation of the verification problem via a finite Fourier expansion, enabling efficient barrier synthesis based on a linear program.
+    \item A robust and extensible software implementation, with both C++ and Python interfaces, supporting configuration via YAML, JSON, or Python scripts, and offering both a \gls{cli} and a \gls{gui}.
+    \item Numerical evaluation on a suite of benchmarks, demonstrating \lucid{}’s unique capabilities, robustness, and practical utility.
+\end{itemize}
 
-The expected value of a function $f(X)$ on $\X$ is written as $\E_{p_X}[f(X)]$. If it is clear from the context, we abbreviate and write $\E[f(X)]$.
-We denote the set of all probability measures for a given measurable space $(\X,\borel{\X})$ as $\mathcal{P}(\X)$.
+\paragraph{Organization}
+The paper is organized as follows:
+Section~\ref{sec:theory} provides the theoretical foundations of \lucid, including the safety of black-box dynamical systems, control barrier certificates, conditional mean embeddings, and derivation of the relaxed linear program.
+Section~\ref{sec:tool} describes the architecture and functionalities of \lucid alongside a running example, presenting \lucid's components and how they interact.
+% Section~\ref{sec:example} presents a simple example use case, demonstrating how to use \lucid to certify the safety of a simple linear system.
+Section~\ref{sec:experiments} evaluates \lucid on a suite of benchmarks. Finally, Sections~\ref{sec:future_extensions} and \ref{sec:conclusion} provide future extensions and a conclusion.
 
-The $n$-dimensional Gaussian measure with mean $\mu\in\mathbb{R}^n$ and covariance matrix $\Sigma\in\mathbb{R}^{n\times n}$ is given by
-\begin{equation}
-  \label{eq:gaussian-kernel}
-  \mathcal N(dx|\mu, \Sigma) := \frac{dx}{ \sqrt{(2\pi)^n \left|\Sigma\right| }}\exp\left[-\frac{1}{2}(x-\mu)\T\Sigma^{-1\!}(x-\mu)\right],
-\end{equation}
-where $|\Sigma|$ is the determinant of $\Sigma$.
-The Dirac delta measure $\delta_a:\borel{\X}\rightarrow [0,1]$ concentrated at a point $a\in\X$ is defined as $\delta_a(A)=1$ if $a\in A$ and $\delta_a(A)=0$ otherwise, for any measurable set $A\in\borel{\X}$.
-We denote the uniform distribution over $\X$ as $\mathcal{U}_\X$ with realizations $x\sim\mathcal{U}_\X(\cdotx)$.
+\section{Theoretical Working Principles}\label{sec:theory}
+\subsection{Safety of Black-Box Dynamical Systems}
 
-For two measurable spaces $(\X,\borel{\X})$ and $(\Y,\borel{\Y})$, a \emph{probability kernel} is a mapping $\p: \X \times \borel{\Y}\rightarrow  [0,1]$ such that $\p(X=x,\cdotx):\borel{\Y}\rightarrow[0,1]$ is a probability measure for all $x\in\X$, and $\p(\cdotx, B): \X\rightarrow [0,1]$ is measurable for all  $B\in\borel{\Y}$.
-A probability kernel associates to each point $x\in\X$ a measure denoted by $\p(\cdotx|X=x)$.
-
-% Linear algebra
-The transpose of a vector or matrix $A$ is indicated as $A\T$.
-Let the $N\times N$ dimensional identity matrix be given by $I_N$.
-Let $X_N:=[x_i]_{i=1}^N$ be a column vector with $x_i\in\X$.
-We denote the element-wise evaluation of a function $f:\X\rightarrow\R$ on $X_N$ as $f(X_N):=[f(x_i)]_{i=1}^N$.
-Similarly, we may write $A = [a_{ij}]_{i,j=1}^N$ to denote a matrix with its elements.
-
-\subsection{Discrete-Time Stochastic Systems}
-In this work, we consider systems expressible as Markov decision processes over continuous state and input spaces, formally defined as follows.
-\begin{definition}[Markov decision process (MDP)]
-  An MDP is a tuple $\M=(\X,\X_0,\U,\Tr)$, comprising a state space $\X\subset\R^n$ with states $x\in\X$; initial states $x_0\in \X_0\subset\X$; an input space $\U$ with inputs $u\in\U$; and a probability kernel $\Tr:\X\times\U\times\borel{\X}\rightarrow[0,1]$.
-\end{definition}
-
-In every execution, given a current state $x\in\X$ and control input $u\in\U$, the MDP evolves to a consecutive state $x_{+}\in\X$, which is obtained as a realization $x_{+}\sim\Tr(\,\cdot\,|X=x,U=u)$.
-As a notable class of systems that can be captured using MDPs, we may consider black-box systems with Markovian discrete-time stochastic dynamics, namely
+\paragraph{System Description}
+Many AI-driven systems exhibit complex, nonlinear, and stochastic behavior that can be modeled as discrete-time stochastic processes with Markovian dynamics:
 \begin{equation}
     \label{eq:model}
-  \M: \left\{ \begin{array}{ll}
-    x_{t+1} & = f(x_t,u_t,w_t),\quad w_t\sim p_w(\cdotx), \\
-    y_t     & = x_t,
-  \end{array} \right.
+    \S\colon\quad x_{t+1}  = f(x_t,a_t,w_t),\quad w_t\sim p_w,
 \end{equation}
-where the system state, control input, and observation at the $t^{\text{th}}$ time-step are denoted by $x_t$, $u_t$, and $y_t$, respectively.
-The state evolution of the system, described by the function $f:\X\times\U\times\mathbb{W}\rightarrow\X$,
-is subject to {independent, identically distributed (i.i.d.) noise} $w_t\sim p_w(\cdotx)$ supported on a set $\mathbb{W}$.
+where $f\colon\X\times\A\times\W\rightarrow\X$ is a continuous vector field describing the evolution of the system state $x_t\in\X\subset\R^n$ over time $t\in\N_{\geq0}$, driven by control actions $a_t\in\A\subset\R^m$ and process noise $w_t\in\W\subset\R^l$.
+The noise is assumed to be drawn from a stochastic distribution $p_w$ in an independent and identically distributed (i.i.d.) manner.
+%
+This general formulation subsumes a wide range of systems, including discrete-time Markov decision processes (MDPs).
 
-\paragraph{Implementation}
+\paragraph{Black-Box Policies}
+Here, the focus is on systems $\S$ driven by black-box control policies of the form $\pi\colon\R^n\rightarrow\R^m$, i.e., at every time step $t=0,1,2,\ldots$ a continuous action $a_t\in\A$ is selected based on the current state $x_t$.
+Such policies could be, for example, neural networks trained via RL, or any other black-box function generating actions in $\R^m$ (see Figure~\ref{fig:closed_loop_system}).
+The resulting closed-loop system is denoted as $\S^\pi$.
+\begin{figure}
+    \centering
+    \begin{tikzpicture}
+        \foreach \i in {4, ..., 1}{
+                \node[name=xa\i] at (\i/4*9,0) {$x_\i$};
+            }
+        \foreach \i in {4, ..., 1}{
+                \node[name=aa\i] at (\i/4*9+.5,0) {$u_{\i}$};
+            }
+        \foreach \i in {4, ..., 1}{
+                \path[draw,->] (xa\i) -- +(0,.5)-| node[left,above,xshift = -0.3cm]{\footnotesize$\pi$} (aa\i);
+            }
+        \foreach \i in {3, ..., 1}{
+                \pgfmathtruncatemacro{\j}{\i + 1}
+                \path[draw,->] (aa\i)-- node[above]{\footnotesize$\S$} (xa\j);
+            }
+    \end{tikzpicture}
+    \caption{Evolution of the closed-loop system.}
+    \label{fig:closed_loop_system}
+\end{figure}
 
-When using \lucid, the user needs to provide a set of sampled trajectories from the system.
-This is often achieved by defining a function that takes as input the current state and control input and returns the next state, adding an i.i.d.
-noise sampled from an appropriate distribution, or it may be collected from a simulator or a real-world system.
-The sampled trajectories are then fed into \lucid, either programmatically or through a file \todo{CSV, HDF5, other?}.
-\todo{Allow a simple way to define the system model? Maybe latex2sympy?}
-\todo{Graphical interface?}
+\paragraph{Dataset}
+Due to their complexity and opacity, such systems must often be treated as black boxes in their entirety, assuming only access to a finite amount, $N$, of system observations
+\begin{equation}
+    \data_N\colon \quad \{x^i,a^i,x^i_+\}_{i=1}^N,\label{eq:data}
+\end{equation}
+where every sample transition from $x^i\in\X$ to a successor $x^i_+\in\X$ is generated as a realization
+\begin{equation*}
+    (x^i,a^i,x_+^i)\sim\int \delta_{f(x^i,a^i,w)}\,p_w(dw)\,\mathcal{U}_\X(dx^i)\,\mathcal{U}_\A(da^i),
+\end{equation*}
+with $\mathcal{U}_\X,\mathcal{U}_\A$ uniform distributions on $\X$ and $\A$, respectively.
 
-\subsection{System Safety}
-In this paper, we wish to synthesize a controller $\pi$ such that the closed-loop system $\pi\times\M$ is safe.
-Particularly, we restrict our attention to \emph{stationary} policies of the form $\pi:\X\rightarrow\U$, as for MDPs there always exists a stationary policy that is optimal.
-For an MDP $\M$, we characterize \emph{safety} as a property of its state.
-More precisely, a system $\pi\times\M$ is said to be safe if for any initial state $x_0\in \X_0$ the system does not enter an \emph{unsafe set} of states $\X_u\subset\X$.
-Note that general stochastic systems do not admit a binary notion of safety.
-Thus, we quantify the \emph{probability} of reaching $\X_u$ in a given finite horizon $T\in\N_{>0}$ and compute its complement.
-A (finite-horizon) \emph{safety specification} $\psi_{\text{safe}:=(\X_u,T)}$ is hence fully characterized by an unsafe set $\X_u$ and a time horizon $T$.
-The system $\pi\times\M$ satisfies $\psi_{\text{safe}}$ with probability at least $p\in(0,1)$ if the probability of its trajectories starting in $\X_0$ and avoiding $\X_u$ within horizon $T$ is at least $p$.
-This is denoted by $P^\pi_{\text{safe}}(\M):=\P(\pi\times\M\satisfies\psi_{\text{safe}})\geq p$~\cite{BK08}.
+\input{figures/steps}
 
-\paragraph{Implementation}
+\paragraph{Safety Problem}
+A question that often arises when designing a policy $\pi$ for a system $\S$, especially in engineering contexts, is if the closed-loop system $\S^\pi$ elicits safe behavior.
+That is, when operating in some operating domain $\X_{0}\subset\X$ under a policy $\pi$, the system $\S^\pi$ shall avoid unsafe regions $\X_U\subset\X$ (such as obstacles) for at least some predefined control horizon $T\in\N\cup\{\infty\}$.
 
-\lucid understands \texttt{RectSet}s and \texttt{Multiset}s \todo{PolytopeSet?}.
-\todo{Set definition from file?}.
-These are used to indicate the initial $\X_0$ set and unsafe set $\X_u$ when defining the safety specification $\psi_{\text{safe}}$.
-Once the system is fully defined, the time horizon $T$ is set as a parameter of the verification process.
-\todo{Support other kinds of properties other than safety (e.g., reachability)?}
+Such safety problems are tricky and even for the case where an explicit model \eqref{eq:model} is given, certifying safety of a discrete-time stochastic system over an uncountable state space does generally not admit an analytical solution and is extremely challenging, especially for complex dynamics~\cite{abate2008probabilistic}.
+Even more, for unbounded stochasticity $w_t\sim p_w$, there is generally no deterministic answer to safe or not, but a safety probability $P_{\text{safe}}(\S^\pi)\in[0,1)$.
+Thus the goal is generally to estimate a \emph{lower bound} on the true safety probability $P_{\text{safe}}(\S^\pi)$.
 
-\subsection{Control Barrier Certificates}
-\label{sec:cbc}
-Whilst certifying the safety of a stochastic system is generally challenging, \emph{control barrier certificates} (CBCs) and \emph{control barrier functions} (CBFs) leverage the concept of set invariance to arrive at an abstraction-free formulation.
-This has made CBCs/CBFs popular tools for safety verification and synthesis~\cite{prajna2006barrier,cosner2023generative}.
-We briefly recall the definition of a CBC.
-\begin{definition}[Control barrier certificate (CBC)]\label{def:cbc}
-  A function $\B:\X\rightarrow\R_{\geq 0}$ is called a CBC of an MDP $\M=(\X,\X_0,\U,\Tr)$ with reference to an unsafe set $\X_u$, if we have
+\paragraph{Problem Statement}
+Assuming access to a finite dataset $\data_N$ from the black-box system $\S$ in \eqref{eq:model}, quantify a certifiable lower bound on the probability of the black-box system $\S^\pi$ being safe with respect to a safety specification given by $(\X_0,\X_U,T)$.
+
+\medskip
+
+\lucid provides a solution to this problem by automating the steps in Figure~\ref{fig:steps}, outlined in the next sections.
+
+\subsection{Control Barrier Certificates}\label{sec:cbc}
+\glspl{cbc}\footnote[3]{\glspl{cbc} and discrete-time \glspl{cbf} \cite{cosner2023generative} are equivalent.} leverage the concept of set invariance to arrive at an abstraction-free numerical solution to finding a lower bound on $P_{\text{safe}}(\S^\pi)$.
+This has made them popular tools for safety verification and controller synthesis~\cite{prajna2006barrier}.
+
+A non-negative function $\B\colon\X\rightarrow\R_{\geq 0}$ is a \gls{cbc} of a system $\S$ with reference to an unsafe set $\X_U$, if it satisfies
 \begin{itemize}
-    \item[(a)] $\forall x_0\in \X_0\!:\,\B(x_0)\leq\eta$;
-    \item[(b)] $\forall x_u\in \X_u\!:\,\B(x_u)\geq\gamma$; and
-    \item[(c)] $\forall x\in\X,\exists u\in\U\!:\,\E_{\Tr}[\,\B(X^+)\mid X=x,\,U=u\,] -\B(x) \leq  c;$
+    \item[(a)] $\forall x_0\in \X_0\colon\,\B(x_0)\leq\eta$;
+    \item[(b)] $\forall x_U\in \X_U\colon\,\B(x_u)\geq\gamma$; and
+    \item[(c)] $\forall x\in\X,\,\exists a\in\A\colon\,\E[\B(X_+) \mid X=x,\,A=a] -\B(x) \leq  c;$
 \end{itemize}
-  for some constants $\gamma>\eta\geq0$ and $c\geq 0$.
-\end{definition}
-If one can find a CBC for a system $\M$, then, a lower bound on the probability of $\M$ being safe is given by the following proposition due to \cite{kushner1967stochastic}.
-\begin{proposition}[Finite-horizon safety]
-  \label{prop:reach}
-  Consider an MDP $\M=(\X,\X_0,\U,\Tr)$ and a safety specification $\psi_{\text{safe}}=(\X_u,T)$.
-Suppose there exists a CBC $B$ w.r.t.
-$\X_u$ (Definition~\autoref{def:cbc}) with constants $\eta$, $\gamma$, and $c$.
-Then, there exists a stationary policy $\pi$ such that
-  $$P^\pi_{\text{safe}}(\M)\geq 1- \frac{\eta + cT}{\gamma}.$$
-\end{proposition}
+for some constants $\gamma>\eta\geq0$ and $c\geq 0$. Here, upper case $X_+$, $X$, and $A$ denote the random variables underlying concrete realizations $(x_t,a_t,x_{t+1})$ elicited by $\S$.
+%
+Intuitively, if one can find a \gls{cbc} for a system $\S$, then, a lower bound on the probability of $\S$ being safe can be quantified based on the distance between the two level sets $\gamma$ and $\eta$~\cite{kushner1967stochastic}:
+\begin{equation}
+    P_{\text{safe}}(\S^\pi)\geq 1- \frac{\eta + cT}{\gamma},\label{eq:safety_prob_lb}
+\end{equation}
+where $T$ is the desired control horizon.
+Notably, the system dynamics only enter the barrier conditions through the conditional expectation in (c), and a \gls{cbc} thus only depends on the \emph{expected} system behavior, with no need to consider its concrete stochastic law.
 
-\paragraph{Implementation}
+Whilst \eqref{eq:safety_prob_lb} can provide a robust assessment of a systems safety, in practice, the bound can be overly conservative and thus several improved variants of the original barrier constraints exist~\cite{mahathi2022kinductive}.
+As these conditions in essence all rely on the computation of chance constraint with respect to the expected behavior of the system, they are basically interchangeable.
 
-When verifying the safety of a system, \lucid will search for a CBC $\B$ that satisfies the conditions in Definition~\ref{def:cbc}.
-If it finds it, it will return the constants $\eta$, $\gamma$, and $c$, as well as the CBC $\B$ itself, which becomes a certificate of safety for the system $\M$.
-The template of the barrier function is explored later in section~\ref{sec:benchmarks}.
+Although there exist model-\emph{based} efficient solutions to this problem for linear and control affine systems, especially for complex systems this is generally a semi-infinite problem, demanding a data-driven solution.
+Furthermore, for the data-driven case, establishing constraint (c) rigorously without relying on impractical assumptions is extremely challenging.
 
-\subsection{Kernel Mean Embeddings}
+\subsection{Data-Driven Dynamics Estimation via Conditional Mean Embeddings}
+To reason about the expected value of a random variable, embedding the variable into a (higher dimensional) space and forming a data-driven estimate is a well-established concept in machine learning \cite{scholkopf2002learning,Steinwart2008SVM}.
+Following the same reasoning, the \emph{kernel mean embedding} represents the projection of a probability measure into a \gls{rkhs} via a feature map $\phi$ associated with a positive definite kernel $k$~\cite{Smola2007EmbedDistrb,muandet2017kernel}.
+For conditional probability distributions a similar concept exists: \glspl{cme} can be used to model the expected value of any RKHS function $f\colon\X\rightarrow\R$ under a stochastic process such as $\S$~\cite{park2020measuretheoretic,muandet2017kernel}.
+For the Gaussian kernel,
+\begin{equation}
+    k(x,x') := \sigma_f^2 \exp\left( -\tfrac{1}{2} (x-x')\T \Sigma\, (x-x') \right),\label{eq:gaussian_kernel}
+\end{equation}
+where $\Sigma:=\diag(\sigma_l)^{-2}$, with hyperparameters $\sigma_f,\sigma_l\in\R$, this encompasses all smooth functions $f$.
+A data-driven estimate can then be obtained in closed form from a finite amount of data $\data_N$:
+\begin{align}
+    \begin{split}
+         & \E[f(X_+)\mid X=x,\,A=a] \approx                                                  \\
+        % \innerH{f}{\hat{\Psi}^N_{X^+|X}(x)}{\Hilbert_{k}} = 
+         & \hspace{5em} k_{XA}^N(x,a)\T\left[ K_{XU}^N+N \lambda I_N\right]^{-1}\! f(X_+^N),
+    \end{split}\label{eq:empiricalEstimate}
+\end{align}
+with column vector $k_{XA}^N(x,a):=[k((x^i,a^i),(x,a))]_{i=1}^N$, Gram matrix $K_{XA}^N:=[k((x^i,a^i),(x^j,a^j))]_{i,j=1}^N$, regularization factor $\lambda\geq0$, identity matrix $I_N$, and $f(X_+^N):=[f(x^i_+)]_{i=1}^N$.
+The empirical estimator in \eqref{eq:empiricalEstimate} converges in expectation to the true \gls{cme} for $N\rightarrow\infty$~\cite{park2020measuretheoretic}.
 
-A symmetric function $k_\X:\X\times\X\rightarrow\R$ is called a (positive definite) \emph{kernel} (note the distinction from \emph{probability kernels}) if for all $N\in\N_{>0}$ we have $\sum_{i=1}^{N}\sum_{j=1}^{N}a_i a_j\allowbreak k_\X(x_i,x_j) \geq 0$ for $x_1,\ldots,x_N\in\X\subset{\R^n}$ and $a_1,\ldots,a_N\in\R$.
-A prominent example is the \emph{squared exponential} (SQExp) kernel \cite{Rasmussen2005GP,Kanagawa2018GPvsKernel}:
+It is common practice to robustify empirical estimates such as \eqref{eq:empiricalEstimate} to out-of-sample behavior by constructing an RKHS ambiguity set centered at the empirical \gls{cme}.
+The result is a distributionally robust estimator with an adjustable robustness radius.
+The details are omitted here for brevity, but the interested reader is referred to~\citet{kuhn2025distributionally,li2022optimal}.
+
+\subsection{Data-Driven Spectral Barriers}\label{sec:ddbarriers}
+Based on the data-driven estimator in \eqref{eq:empiricalEstimate}, the problem of computing \glspl{cbc} based on data can be formulated as a nonconvex semi-infinite program, which for general classes of systems and barriers is extremely difficult to solve.
+To arrive at a tractable solution, \lucid conducts two additional steps:
+\paragraph{1. Spectral Abstraction} Inspired by the popular random Fourier features approach by \citet{rahimi2007random}, the Gaussian kernel \eqref{eq:gaussian_kernel} admits a Fourier expansion
+\begin{align}
+    k(x, x') \equiv \sigma_f^2 \int_{\R^{n}}\!\! \mathcal{N}(d\omega\mid0,\Sigma)\; e^{\mathbf{i}\omega\T (P(x)-P(x'))},\label{eq:sqexp_kernel_fourier}
+\end{align}
+with the zero-mean Gaussian distribution $\smash{\mathcal{N}(d\omega\mid0,\Sigma)}$ with covariance $\Sigma$, the imaginary unit $\mathbf{i}:=\smash{\sqrt{-1}}$, and where the projection $x \mapsto P(x)$ maps the domain $\X$ into the unit hypercube $[0,1]^{n}$.
+Partitioning the space of spatial frequencies $\omega\in\R^n$ into a set of discrete frequency bands (see Figure~\ref{fig:spectral_barrier}) yields a spectral abstraction of the associated RKHS, i.e., characterizing learnable functions $B$ in the form of Fourier series.
+By truncating the series to a finite number, $M$, of fixed frequency bands $\omega_j\in\R^{n}$, $j\in\{0,\ldots,M\}$, the resulting barriers are of the form
+\begin{align*}
+    \B(x) = \alpha_0 +\sum_{i=1}^{M} \alpha_i \cos\left(\omega_i\T P(x)\right) + \beta_i \sin\left(\omega_i\T P(x)\right).%\label{eq:blackbox:representer_form_spectral}
+\end{align*}
+Notably, $\B$ admits the linear form $B(x)=b\T\phi_M(x)$, with a truncated Fourier feature map $\phi_M\colon\X\rightarrow\R^{2M+1}$, parametrized by learnable spectral amplitudes
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{fourier_series.pdf}
+    \caption{Spectral barrier certificate $B(x)=b\T\phi_M(x)$}
+    \label{fig:spectral_barrier}
+\end{figure}
+\begin{align*}
+    b\!=\!\begin{bmatrix}
+              \frac{\alpha_0}{\sigma_f^2w_0^2}\!
+& \frac{\alpha_1}{2\sigma_f^2w_1^2}\!\!
+& \frac{\beta_1}{2\sigma_f^2w_1^2}\!\!
+& \ldots\!\!
+& \frac{\alpha_{M}}{2\sigma_f^2w_{M}^2}\!\!
+& \frac{\beta_{M}}{2\sigma_f^2w_{M}^2}
+          \end{bmatrix}\T\!\!\!\!\in\R^{2M+1}\!\!,
+\end{align*}
+where the weights $w_0,\ldots,w_{M}\in\R_{\geq 0}$ associated with each frequency band are determined efficiently from the kernel's Gaussian spectral measure via the multivariate CDF (see Figure~\ref{fig:spectral_measure_abstraction}).
+The \gls{cme}-based estimator \eqref{eq:empiricalEstimate} is approximated in the same finite basis, with an approximation error decreasing exponentially with $M$~\cite{rahimi2007random}.
+This simplifies the barrier problem to a semi-infinite linear program.
+% \OS{Importantly, the closed-form estimator in \eqref{eq:empiricalEstimate} does not depend on the choice of features and only through the spectral abstraction is the feature map introduced directly.}
+\begin{figure}
+    \centering
+    % GAUSSIANs: 68-95-99 rule
+    \begin{tikzpicture}
+        \def\N{50} % number of sample points
+        \def\B{0};
+        \def\Bs{3.0};
+        \def\var{1.3}
+        \def\xmax{\B+3.5*\Bs};
+        \def\ymin{{-0.1*gauss(\B,\B,\Bs)}};
+        \def\h{0.08*gauss(\B,\B,\Bs)};
+
+        \begin{axis}[every axis plot post/.append style={
+            mark=none,domain={-(\xmax)}:{1.0*\xmax},samples=\N,smooth},
+            xmin={-(\xmax)}, xmax=\xmax,
+            axis/.style={>=latex},
+            ymin=\ymin, ymax={1.1*gauss(\B,\B,\Bs)},
+            axis lines=middle,
+            axis line style=thick,
+            enlarge x limits, % extend the axes a bit
+            ticks=none,
+            xlabel=$\omega$,
+            every axis x label/.style={at={(current axis.right of origin)},anchor=north},
+            width=1.1\linewidth, height=0.55*\linewidth,
+            y=700pt,
+            clip=false,
+            axis line style={-latex}
+            ]
+
+            % PLOTS
+            \addplot[accent,thick,name path=B] {gauss(x,\B,\var*\Bs)};
+
+            % FILL
+            \path[name path=xaxis]
+            (\B-\pgfkeysvalueof{/pgfplots/xmax},0) -- (\B+\pgfkeysvalueof{/pgfplots/xmax},0); %\pgfkeysvalueof{/pgfplots/xmin}
+            \addplot[accent!3.75] fill between[of=xaxis and B, soft clip={domain={\B-3.5*\Bs}:{\B+3.5*\Bs}}];
+            \addplot[accent!7.5] fill between[of=xaxis and B, soft clip={domain={\B-2.5*\Bs}:{\B+2.5*\Bs}}];
+            \addplot[accent!15] fill between[of=xaxis and B, soft clip={domain={\B-1.5*\Bs}:{\B+1.5*\Bs}}];
+            \addplot[accent!30] fill between[of=xaxis and B, soft clip={domain={\B-.5*\Bs}:{\B+.5*\Bs}}];
+
+            % LINES
+            \addplot[black,dashdotted,thin]
+            coordinates {({\B-3*\Bs},{20*gauss(\B-3*\Bs,\B,\Bs)}) ({\B-3*\Bs},{-\h})}
+            node[below=-3pt,scale=1.0] {\strut$\omega_3$};
+            \addplot[black,dashdotted,thin]
+            coordinates {({\B-2*\Bs},{4*gauss(\B-2*\Bs,\B,\Bs)}) ({\B-2*\Bs},{-\h})}
+            node[below=-3pt,scale=1.0] {\strut$\omega_2$};
+            \addplot[black,dashdotted,thin]
+            coordinates {({\B-1*\Bs},{1.3*gauss(\B-\Bs,\B,\Bs)}) ({\B-1*\Bs},{-\h})}
+            node[below=-3pt,scale=1.0] at ({\B-\Bs},{-\h}) {\strut$\omega_1$};
+            \addplot[black,dashdotted,thin]
+            coordinates {(\B,{1.05*gauss(\B,\B,\Bs)}) (\B,{-\h})}
+            node[below=-3pt,scale=1.0] {\strut$\omega_0$};
+            \node[scale=1.0] (w0)
+            at ({\B+.5*\Bs},{.125}) {$w_0^2$};
+            \node (b0) at ({\B+.25*\Bs},{.08}) {};
+            \draw[->] (w0) to (b0.center);
+            % \addplot[white,dashed,thin]
+            % coordinates {({\B+.5*\Bs},{gauss(\B+.5*\Bs,\B,\Bs)}) ({\B+.5*\Bs},0)};
+            \addplot[black,dashdotted,thin]
+            coordinates {({\B+1*\Bs},{1.3*gauss(\B+\Bs,\B,\Bs)}) ({\B+1*\Bs},{-\h})}
+            node[below=-3pt,scale=1.0] at ({\B+\Bs},{-\h}) {\strut$\omega_1$};
+            \node[scale=1.0] (w1)
+            at ({\B+1.5*\Bs},{.085}) {$\frac{w_1^2}{2}$};
+            \node (b1) at ({\B+1.25*\Bs},{.04}) {};
+            \draw[->] (w1) to (b1.center);
+            \addplot[black,dashdotted,thin]
+            coordinates {({\B+2*\Bs},{4*gauss(\B+2*\Bs,\B,\Bs)}) ({\B+2*\Bs},{-\h})}
+            node[below=-3pt,scale=1.0] at ({\B+2*\Bs},{-\h}) {\strut$\omega_2$};
+            \node[scale=1.0] (w2)
+            at ({\B+2.5*\Bs},{.055}) {$\frac{w_2^2}{2}$};
+            \node (b2) at ({\B+2.25*\Bs},{.01}) {};
+            \draw[->] (w2) to (b2.center);
+            \addplot[black,dashdotted,thin]
+            coordinates {({\B+3*\Bs},{20*gauss(\B+3*\Bs,\B,\Bs)}) ({\B+3*\Bs},{-\h})}
+            node[below=-3pt,scale=1.0] at ({\B+3*\Bs},{-\h}) {\strut$\omega_3$};
+            \node[scale=1.0] (w3)
+            at ({\B+3.5*\Bs},{.046}) {$\frac{w_3^2}{2}$};
+            \node (b3) at ({\B+3.25*\Bs},{.001}) {};
+            \draw[->] (w3) to (b3.center);
+
+            % Hyperparameters
+            \addplot[<->,accent]
+            coordinates {({\B-2*\var*\Bs},{gauss(\B+2*\var*\Bs,\B,\var*\Bs)}) ({\B+2*\var*\Bs},{gauss(\B+2*\var*\Bs,\B,\var*\Bs)})};
+            \node[accent,fill=accent!30,inner xsep=3,inner ysep=2,scale=.8] at (\B,{gauss(\B+2*\var*\Bs,\B,\var*\Bs)}) {$\pm 2\sigma_l$};
+            \addplot[<->,accent]
+            coordinates {({\B-3*\var*\Bs},{gauss(0,0,\var*\Bs)}) ({\B-3*\var*\Bs},{0})};
+            \addplot[dashed,thin,accent]
+            coordinates {({\B-3*\var*\Bs},{gauss(0,0,\var*\Bs)}) ({0},{gauss(0,0,\var*\Bs)})};
+            \node[accent,fill=white,inner xsep=3,inner ysep=2,scale=.8] at (\B-3*\var*\Bs,{.5*gauss(0,0,\var*\Bs)}) {$\sigma_f^2$};
+
+        \end{axis}
+    \end{tikzpicture}
+    % \includegraphics[width=\linewidth]{figures/spectral_measure_abstraction.png}
+    \caption{Abstraction of a 1-dim. Gaussian spectral measure of the Gaussian kernel, shown in \eqref{eq:sqexp_kernel_fourier}.}
+    \label{fig:spectral_measure_abstraction}
+\end{figure}
+% Naturally, barriers of the form \eqref{eq:blackbox:representer_form_spectral} will be referred to as \emph{Fourier control barrier certificates}.
+
+\paragraph{2.
+Finite-Constraint Relaxation} To obtain a program with \emph{finitely} many constraints, trigonometric bounding results \cite{pfister2018bounding} are used to obtain a relaxed linear program by sampling spatial lattices on $\X$, $\X_0$, and $\X_U$.
+For example, to enforce barrier constraint (a) in Section~\ref{sec:cbc}, it suffices to construct a lattice $\{x_0^i\}_{i=1}^{N_0}\subset\X_0$ and impose the constraints $b\T\phi_M(x_0^i)\leq\eta$ for $i=1,\ldots,N_0$.
+Selecting lattices with a sampling density meeting the Nyquist-Shannon sampling theorem with respect to the highest frequency $\omega_M$ appearing in the barrier and truncated estimator, the relaxation retains all guarantees.
+As a result, the semi-infinite problem is relaxed to a finitely-constrained \gls{lp}, provided in full in {\color{red}the appendix}.
+Recall that given an appropriate robustness radius, the barriers produced by \lucid based on data $\data_N$ are statistically correct with respect to the unknown true system $\S$.
+
+\section{Tool Structure and Functionalities}
+\label{sec:tool}
+\lucid implements the previously outlined functionality, written in C++ and designed to be used as a library or standalone executable.
+The choice of a low level language gives us plenty of freedom and fine-grained control over the execution of the software.
+We expose a set of interfaces allowing users to highly customize the verification process.
+A high-level visualization of \lucid's architecture is illustrated in Figure~\ref{fig:architecture}, while a more technical description can be found in the online documentation at
+\begin{center}
+    \url{https://lucidtoolsource.gitlab.io/lucid/}.
+\end{center}
+% \lucid's source code is hosted at \url{https://gitlab.com/lucidtoolsource/lucid}.
+
+We also provide a Python wrapper, called \pylucid, to facilitate the integration of the tool into existing workflows and effortlessly leverage well-established libraries such as NumPy~\cite{numpy} and SciPy~\cite{scipy}.
+Moreover, \pylucid can be extensively configured in a variety of ways (e.g., Python scripts, YAML files, GUI), making it the recommended way to operate \lucid.
+Hence, for the rest of the paper, we will focus on \pylucid when describing the user interfaces.
+
+\paragraph{Installation}
+Provided \texttt{Python>=3.8} is already present, \pylucid can be installed with the command
+\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
+pip install pylucid[gui,plot] --index-url \
+  https://gitlab.com/api/v4/projects/71977529/packages/pypi/simple
+\end{lstlisting}
+% \EC{The command is long, but at the moment it cannot be shortened (we would need to host the package on PyPI).}
+
+\paragraph{Configuration}
+% The system and the specification \lucid will check against shall be provided as a configuration to the program.
+To certify safety of a system, \lucid accepts a configuration comprising data from the system and the safety specification.
+We suggest defining it as a \yaml or equivalent \json file.%
+\footnote[4]{The Json schema for \yaml and \json files can be found at \url{https://lucidtoolsource.gitlab.io/lucid/configuration_schema.json}}
+% \OS{I would personally avoid the word "scenario", as it could be misunderstood with an actual run of the system.}
+If more flexibility is needed, a Python script generating a configuration can be used instead,
+with the only requirement being that it must contain a function named \lstinline|scenario_config| returning a \texttt{Configuration} object.
+Regardless of their format, configuration files can be loaded with the command \lstinline|pylucid <config file>| to start the tool's verification pipeline.
+The same configuration values can also be given directly as command line arguments.
+For a list of all available options, run \lstinline|pylucid --help|.
+
+In its current form, \lucid implements all functionality needed to certify safety of closed-loop system with a given control policy $\pi$.
+Future releases will expand this core functionality to synthesize controllers that render the system safe as well.
+Due to its modular architecture, \lucid can be easily extended in multiple directions, as outlined in Section~\ref{sec:future_extensions}.
+
+\subsection{Configuring and Running the Tool}
+% \todo{Map the theoretical modules from Section~\ref{sec:theory} to components/modules of the code.}
+
+\lucid is built with a modular architecture where each component is responsible for a specific task in the certification process.
+Moreover, since they extend from a common interface, they can be easily replaced or extended to suit the user's needs or in future versions of the tool.
+An overview of the core components and how they interact is shown in Figure~\ref{fig:architecture}.
+Classes and interfaces available in \pylucid are written in \texttt{monospace font}.
+
+To make the explanation more intuitive, we will use as a running example the one-dimensional linear system
 \begin{equation}
-  \label{eq:gaussian-kernel}
-  k_\X(x,x') := \sigma_f^2 \exp\left( -\frac{1}{2} (x-x')\T \Sigma\, (x-x') \right),\quad \Sigma:=\diag(\sigma_l)^{-2},
+    \label{eq:linear-system}
+    \S\colon%\begin{bmatrix}
+    \quad
+    {x}_{t+1}
+    %\end{bmatrix}
+    = %\begin{bmatrix}
+    0.5
+        %\end{bmatrix}
+        %\begin{bmatrix}
+        {x}_{t}
+    %\end{bmatrix} 
+    + w_t,
+    \quad w_t \sim \mathcal{N}(\cdotx | 0, 0.01),
 \end{equation}
-with amplitude $\sigma_f^2\geq0$ and lengthscale coefficients $\sigma_l\in\R^n$.
-%In the following, we refer to a positive definite kernel as \emph{kernel}, for simplicity.
-For this work, we assume that all kernels are bounded on their domain, i.e., $\E_{}[k_\X(x,x)]<\infty$, $x\in\X$.
-Given a kernel $k_\X$ on a non-empty set $\X$, there exists a unique corresponding \emph{reproducing kernel Hilbert space} (RKHS) $\Hilbert_{k_\X}$ of functions $f:\X\rightarrow\R$ equipped with an inner product $\innerH{\cdotx}{\cdotx}{\Hilbert_{k_\X}}$ possessing the \emph{reproducing property} such that for any function $f\in\Hilbert_{k_\X}$ and $x\in\X$ we have $f(x)=\innerH{f}{k_\X(\cdotx,x)}{\Hilbert_{k_\X}}$.
-Note that $k_\X(\cdotx,x):\X\rightarrow\Hilbert_{k_\X}$ is a real-valued function,
-\new{which is} also called an implicit \emph{canonical} \emph{embedding} or \emph{feature map} $\phi_\X$
-such that $k_\X(x,x')=\innerH{\phi_\X(x)}{\phi_\X(x')}{\Hilbert_{k_\X}}$ for all $x,x'\in\X$.
-For an RKHS $\Hilbert_{k_\X}$, we use the associated feature map $\phi_\X$ and kernel $k_\X$ interchangeably for ease of notation and comprehensibility.
-%We will call the kernel associated to an RKHS $\Hilbert_{k_\X}$ the \emph{characteristic} kernel of $\Hilbert_{k_\X}$ and use $\phi_\X$ and $k_\X$ interchangeably for ease of notation and comprehensibility.
-%and an implicit \emph{canonical} \emph{embedding} or \emph{feature map} $\phi_\X:\X\rightarrow\Hilbert_{k_\X}$ with an inner product on $\Hilbert_{k_\X}$, i.e., $k_\X(x,x')=\innerH{\phi_\X(x)}{\phi_\X(x')}{\Hilbert_{k_\X}}$,
-%Furthermore, 
-The inner product induces the norm $\norm{f}_{\Hilbert_{k_\X}}\!\!\!\!:=\!\!\sqrt{\smash[b]{\innerH{f}{f}{\Hilbert_{k_\X}}}}$ of the RKHS.
-%Note that $\Hilbert_{k_\X}$ is a space of functions $f:\X\rightarrow\R$. 
-%It is equipped with the infamous \emph{reproducing property} such that for any function $f\in\Hilbert_{k_\X}$ and $x\in\X$ we have $f(x)=\innerH{f}{\phi_\X(x)}{\Hilbert_{k_\X}}$.
-%Furthermore, the norm associated with the RKHS $\Hilbert_{k_\X}$ is defined as $\norm{f}_{\Hilbert_{k_\X}}:=\sqrt{\innerH{f}{f}{\Hilbert_{k_\X}}}$.
-%We refer the interested reader to XX for a comprehensive dissemination on RKHS.
-Throughout this paper, we assume that all RKHSs are \emph{separable}.
-Given $N$ i.i.d. samples $\hat X_N:=[\hat{x}_i]_{i=1}^N$ with $\hat{x}_i\in\X$, the
-\emph{Gram matrix} of $k_\X$ is given by
-$K_{\hat{X}}^N:=[k_\X(\hat{x}_i,\hat{x}_j)]_{i,j=1}^N.$
-Furthermore, we define the vector-valued function
-$k_{\hat{X}}^N(x)  := [k_\X(x,\hat{x}_i)]_{i=1}^N.$
+% where $x_t$ is the state at time $t$ and $w_t$ is Gaussian noise.
+% Given the
+with
+state space $\X = [-1, 1]$, initial set $\X_0 = [-0.5, 0.5]$, and unsafe regions $\X_u = [-1, -0.9] \cup [0.9, 1]$.
+While going over each component of \lucid, we will show how they can be configured within a \yaml configuration file to capture the system~\eqref{eq:linear-system} and its safety specification.
 
-\subsection{Data-Driven Barrier Formulation}
-\label{sec:data-driven-barrier-formulation}
-Compared to the typical spatial form \eqref{eq:representer-form} based on spatial support vectors $\bar{x}_1,\bar{x}_2,\ldots\in\X$, the spectral form \eqref{eq:representer-form-spectral} is a much more efficient representation for higher-dimensional systems.
-The number of spatial support vectors needed to construct adequately expressive barriers grows exponentially in the dimensionality of the system. We avoid this.
+\paragraph{Dataset}
+% \todo{Should this be considered a component? It is more about the data loader} \Sadegh{This is good to have as a separate component.}
+Due to its data-driven nature, all that \lucid needs to operate, is a set of sampled transitions $\data_N$ from the system, as shown in \eqref{eq:data}, and the safety specification itself.
+% Data can be obtained by defining a function that takes as input the current state and control input and returns the next state, adding i.i.d.
+noise sampled from an appropriate distribution, or it may be collected from an external simulator or real-world system.
+The samples can be specified directly in the configuration file:
+\begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
+x_samples: [[5.930e-01], ..., [-1.937e-01]]
+xp_samples: [[3.015e-01], ..., [-1.018e-01]]
+\end{lstlisting}
+Alternatively, the samples can either be generated programmatically in the user-provided Python configuration script, or be stored in a separate file.
+\pylucid natively supports common formats such as \texttt{.csv}, \texttt{.mat}, \texttt{.npy}, and \texttt{.npz}.
+% Refer to the documentation for more details.
+\begin{comment}
+\begin{lstlisting}[language=iPython]
+    def scenario_config():
+    # ...
+    # Sampling
+    f = lambda x: x / 2
+    c.x_samples = c.X_bounds.sample(1000)
+    c.xp_samples = f(c.x_samples) + np.random.normal(scale=0.01)
+    # ...
+    return c
+\end{lstlisting}
+\end{comment}
 
-Apart from the memory efficiency of the spectral barrier form, we can apply the same idea to collapse the complex CME term in \eqref{eq:semiinf-prog-kushner} via the \emph{fast Fourier transform} (FFT).
-That is we obtain spectral coefficients $H\in\R^{(2M+1)\times (2M+1)}$ s.t.
-\begin{equation}
-  k^N_{\hat{X}}(x)\T\left[ K^N_{\hat{X}}+N\lambda I_N\right]^{-1\!} (\Phi_{M, \hat{X}^{+\!}}^{N})\T b \approx \phi_M(x)\T H b,\label{eq:cme-term-spectral-approx}
-\end{equation}
-where $\Phi_{M, \hat{X}^{+\!}}^{N} := [\phi_M(\hat{x}^+_1),\ldots,\phi_M(\hat{x}^+_N)]$.
-Whilst projection onto a truncated Fourier basis introduces an approximation error, the error decreases exponentially with the cardinality of wavenumbers in the basis \cite{rahimi2007random}.
-% Our numerical results suggest that the empirical error is negligible.
+\input{figures/architecture}
 
-Substituting the barrier $B\in\Hilbert_M$ of the form \eqref{eq:representer-form-spectral} and the approximation of the CME term in \eqref{eq:cme-term-spectral-approx} into the SIP \eqref{eq:semiinf-prog}, we obtain the \emph{semi-infinite linear program} (SILP)
-\begin{subequations}
-  \begin{align}
-    \min_{b, c, \eta, \gamma} \; & \frac{\eta + cT}{\gamma},\label{eq:semiinfLP-prog-objective}                                                 \\
-    \text{s.t.}\quad
-                                 & \forall x_0\in\X_0:\,\phi_M(x_0)\T b\leq\eta,\label{eq:semiinfLP-prog-initial}                               \\
-                                 & \forall x_u\in\X_u:\,\phi_M(x_u)\T b\geq\gamma,\label{eq:semiinfLP-prog-unsafe}                              \\
-                                 & \forall x\in\X: \, \phi_M(x)\T (H b - b) \leq c - \varepsilon\bar{B}\kappa,\label{eq:semiinfLP-prog-kushner} \\
-                                 & \forall x\in\X:\,\phi_M(x)\T b\geq 0,\label{eq:semiinfLP-prog-positive}                                      \\
-                                 & c\geq 0,\,\gamma>\eta\geq 0,\,b\in\R^{2M+1},\nonumber
-  \end{align}\label{eq:semiinfLP-prog}%
-\end{subequations}
-with coefficients $\kappa\geq\sigma_f$ and $\bar{B}\geq\norm{b}_2$.
+\paragraph{\Circled{1}~Safety Specification}
+\lucid understands sets $\X,\X_0,\X_U$ specified as \texttt{RectSet}, \texttt{SphereSet}, or \texttt{Multiset} objects (collections of sets from the first two categories).
+% Sets are mainly used to indicate the bounds of the whole state space $\X$, the initial set $\X_0$ and the unsafe set $\X_U$ in the context of defining the safety specification to verify.
+They can be included in the configuration as shown below:
+\begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
+X_bounds: "RectSet([-1], [1])"
+X_init: "RectSet([-0.5], [0.5])"
+X_unsafe: 
+  - "RectSet([-1], [-0.9])"
+  - "RectSet([0.9], [1])"
+\end{lstlisting}
+% \OS{So is the \lstinline{X_unsafe} here a Multiset?}
 
-\subsection{Finite-Constraint Relaxation}\label{sec:finite-constraint-relaxation}
-There exist results that establish deterministic sampling-based bounds for multivariate trigonometric polynomials \cite{cifuentes2017sampling,pfister2018bounding} that can be applied to the bandlimited spectral barrier in \eqref{eq:representer-form-spectral}.
-This allows us to relax the SILP \eqref{eq:semiinfLP-prog} to a \emph{linear program} (LP) with finitely many constraints by sampling a finite set
-$X_{\hat{N}} \subset\X$ of cardinality $\hat{N}$.
-By choosing $\hat{N}=Q^n$ equidistant points that form a discrete lattice of points to cover the (state) space, the corresponding constraints can be efficiently evaluated in $\mathcal{O}(Q\log(Q))$ operations using the inverse FFT.
-Note that this also substantially reduces the number of evaluations of the computationally expensive CME term in \eqref{eq:semiinf-prog-kushner}, which requires $\mathcal{O}(N^2)$ operations per evaluation.
-Refer to the Petersen-Middleton theorem \cite{petersen1962sampling}, which generalizes the Nyquist-Shannon sampling theorem to higher-dimensional Euclidean spaces, for further details.
+\paragraph{\mbox{\Circled{2}\hspace{.4em}Estimator}}
+The core of \lucid is its \estimator, namely the \texttt{KernelRidgeRegressor}, which uses the \texttt{GaussianKernel} to learn the underlying system dynamics by estimating the \gls{cme} from the samples.
+Its predictions of the expected next state $x_+$ are used
+% of all the lattice points we need from $\X$, necessary 
+to determine the constraints for the \gls{cbc} \gls{lp}.
+% The \hp of the \texttt{KernelRidgeRegressor} can be set explicitly in the configuration file:
+% We provide the \hp values for the kernel, namely the bandwidth $\sigma_f = 1$, the length scale $\sigma_l = 1.75555556$, values obtained from a previous tuning process, 
+% and the regularization constant $\lambda = 0.00001$.
+The setup is configured as follows:
+\begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
+kernel: "GaussianKernel"
+estimator: "KernelRidgeRegressor"
+\end{lstlisting}
 
-We use the following result by \cite{pfister2018bounding}.
-\begin{lemma}[Trigonometric bounds]\label{lem:trig-bound}
-  Consider a real-valued trigonometric polynomial $f:[0,1]^n\rightarrow\R$ (cf.
-\eqref{eq:representer-form-spectral}) with maximum degree $d\in\N_{\geq 0}$ and a sampling lattice $\Theta_Q:=\{\frac{2\pi l}{Q},\, l=0,\ldots,Q-1\}$ with $Q\geq 2d+1$.
-  Let $\bar{f}_{Q^n}:=\max_{z\in\Theta^n_Q} f(z)$ and $\underbar{f}_{Q^n}:=\min_{z\in\Theta^n_Q} f(z)$. Then, we have that
+\paragraph{\Circled{3}~Tuner}
+Being parameter-free approaches, kernel methods do not require the expensive learning processes of other machine learning methods, such as neural networks.
+However, they still depend on a number of \hp, such as the kernel bandwidth $\sigma_f$, the lengthscale $\sigma_l$, and the regularization constant $\lambda$.
+Changes in their values can have a significant impact on the \estimator's efficiency and accuracy.
+The process of finding good values for these \hp is known as \emph{hyperparameter tuning}, with the optimal parameters being problem dependent.
+\lucid provides a set of utilities, which specialize the \texttt{Tuner} interface, to aid in this task:
+\begin{itemize}
+    \item \texttt{MedianHeuristicTuner} uses the \emph{median heuristic} \cite{garreau2018largesampleanalysismedian} to produce rule-of-thumb-type estimates for the hyperparameters $\sigma_f$ and $\sigma_l$ of, e.g., the Gaussian kernel \eqref{eq:gaussian_kernel}, via closed-form expressions.
+          This can offer a cheap starting point for successive fine-tuning.
+    \item \texttt{LbfgsTuner} finds the \hp that maximize the \emph{log marginal likelihood}~\cite{rasmussen2006gaussian}, defined as
           \begin{equation*}
-    \frac{1}{2}\big(\bar{f}_{Q^n} + \underbar{f}_{Q^n} - C_{Q^n}\left(\bar{f}_{Q^n}-\underbar{f}_{Q^n}\right)\big)
-    \leq
-    f(z)
-    \leq
-    \frac{1}{2}\big(\bar{f}_{Q^n} + \underbar{f}_{Q^n} + C_{Q^n}\left(\bar{f}_{Q^n}-\underbar{f}_{Q^n}\right)\big),
+              \begin{split}
+                   & \log p(X^+_N | X_N,\theta) =  - \frac{1}{2}X^+_N{}\T (K_{X}^N + N\lambda I_N)^{-1} X^+_N \\
+                   & \hspace{40pt} -\frac{1}{2}\log |K_{X}^N + N\lambda I_N| - \frac{N}{2}\log(2\pi),
+              \end{split}
           \end{equation*}
-  with a coefficient given by
-  \setlength{\belowdisplayskip}{3pt}
-  \begin{equation*}
-    C_{Q^n} := \left(1-\frac{2d}{Q}\right)^{-\frac{n}{2}}.
-  \end{equation*}
-\end{lemma}
-% \Oliver{The paper \cite{pfister2018bounding} provides a more complex expression for $C_{Q^n}$ that I put as [...]. They also provide the upper bound I use so far.}
+          where $\theta:=(\sigma_f,\sigma_l,\lambda)$ is the hyperparameter being optimized.
+          The \texttt{LbfgsTuner} uses the L-BFGS or L-BFGS-B quasi-Newton optimization algorithms~\cite{book:nonlinear-programming},
+          implemented in the \texttt{LBFGS++} library\footnote{https://github.com/yixuan/LBFGSpp}.
+    \item \texttt{GridSearchTuner} implements the grid search method, exploring the space of possible \hp values to find the one that maximizes the \estimator's $R^2$ score, defined as $R^2 = 1 - (\sum_{i=1}^M (y_i - \hat{y}_i)^2/\sum_{i=1}^M (y_i - \bar{y})^2)$.
+\end{itemize}
+Tuners open a wide range of possibilities to the user.
+We recommend using them within a Python script generating a configuration to automate the tuning process before finalizing the \estimator's hyperparameter values:
+\begin{lstlisting}[language=iPython,style=nonumbers]
+def scenario_config(c: Configuration):
+    ...
+    t = LbfgsTuner(lb=[1e-5], ub=[1e5])
+    c.estimator = KernelRidgeRegressor(
+        kernel=GaussianKernel(),
+    )
+    c.estimator.fit(c.x_samples, c.xp_samples, tuner=t)
+    return c
+\end{lstlisting}
+For the running example, we set the hyperparameters explicitly:
+\begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
+sigma_f: 15
+sigma_l: [1.76]
+lambda: 1.0e-5
+\end{lstlisting}
 
-Via Lemma~\ref{lem:trig-bound}, we obtain a finite-constraint relaxation of the SIP \eqref{eq:semiinf-prog} based on the constraint-tightening reasoning
-\begin{equation*}
-  \frac{1}{2}\big(\mathrm{max}_{\hat{N}}^\X + \mathrm{min}_{\hat{N}}^\X - C_{\hat{N}}\left(\mathrm{max}_{\hat{N}}^\X-\mathrm{min}_{\hat{N}}^\X\right)\big)\geq \mathrm{lb}
-  \quad\Longrightarrow\quad
-  \forall x\in\X: f(x) \geq \mathrm{lb},
-\end{equation*}
-where $\mathrm{max}_{\hat{N}}^\X:=\max_{x\in X_{\hat{N}}} \left\lbrace\phi_M(x)\T b\right\rbrace$ and $\mathrm{min}_{\hat{N}}^\X:=\min_{x\in X_{\hat{N}}} \left\lbrace\phi_M(x)\T b\right\rbrace$ for some desired lower bound $\mathrm{lb}\in\R$.
-Thus, we obtain strengthened constraints of the form
-\begin{align*}
-                               & \frac{1}{2}\big(\mathrm{max}_{\hat{N}}^\X + \mathrm{min}_{\hat{N}}^\X - C_{\hat{N}}\left(\mathrm{max}_{\hat{N}}^\X-\mathrm{min}_{\hat{N}}^\X\right)\big) \geq \mathrm{lb}, \\
-  \Leftrightarrow\hspace{10pt} &
-  \mathrm{min}_{\hat{N}}^\X \geq \frac{2}{C_{\hat{N}}+1}\mathrm{lb} + \frac{C_{\hat{N}}-1}{C_{\hat{N}}+1}\mathrm{max}_{\hat{N}}^\X.
-\end{align*}
-For an upper bound $\forall x\in\X: f(x) \leq \mathrm{ub}$, we obtain analogous constraints of the form
-\begin{equation*}
-  \mathrm{max}_{\hat{N}}^\X \geq \frac{2}{C_{\hat{N}}+1}\mathrm{ub} + \frac{C_{\hat{N}}-1}{C_{\hat{N}}+1}\mathrm{min}_{\hat{N}}^\X.
-\end{equation*}
-
-\subsection{Tuning the Hyperparameters}
-\label{sec:tuning-hyperparameters}
-
-Kernel methods do not require the expensive learning process of other machine learning methods, such as neural networks.
-However, they still depend on a number of \hp, such as the kernel bandwidth $\sigma_f$ and the number of Fourier coefficients $M$.
-Changes in their values can have a significant impact on the estimator's efficiency and accuracy.
-The process of finding good values for these \hp is known as \emph{hyperparameter tuning}, and it is problem-dependent.
-
-There are several approaches to find the optimal \hp for a given problem.
-A cheap option which can be used as a starting point when working with a Gaussian Kernels as in~\eqref{eq:gaussian-kernel} is to use the \emph{median heuristic} \cite{garreau2018largesampleanalysismedian}.
+\begin{comment}
+A cheap starting point when working with a Gaussian kernel as in~\eqref{eq:gaussian_kernel} is to use the \emph{median heuristic} \cite{garreau2018largesampleanalysismedian}, implemented in the \texttt{MedianHeuristicTuner}.
+\OS{We can cut the following to save space. This is standard knowledge:}
+{\color{gray}
     We choose $\sigma_l^2$ to be the median of the squared distances between all pairs of points in the training set, i.e.,
@@
     where $\hat{x}_1,\ldots,\hat{x}_N$ are the $N$ training samples.
-If $N(N-1)/2$ is even, the median is the average of the two middle values in the sorted list of distances.
-Better results can be obtained via \emph{grid search}, which consists of evaluating the performance of the estimator for all combinations of \hp in a predefined grid.
-This approach is simple to implement and can be very effective for small problems, but it can become computationally expensive for larger problems.
-Borrowing a technique from Gaussian processes, we can also try to optimize the \hp to maximize the \emph{log marginal likelihood}, defined as
+    If $N(N-1)/2$ is even, the median is the average of the two middle values in the sorted list of distances.}
+The \texttt{GridSearchTuner}, on the other hand, implements the grid search method, exploring the space of possible \hp values to find the one that yields the best \estimator $R^2$ score,
+defined as $R^2 = 1 - \frac{\sum_{i=1}^n (y_i - \hat{y}_i)^2}{\sum_{i=1}^n (y_i - \bar{y})^2}$.
+This approach is simple to implement and can be very effective for small problems, but it can become computationally expensive for larger ones.
+Borrowing a technique from Gaussian processes, we can also optimize the \hp to maximize the \emph{log marginal likelihood}, defined as
 \begin{equation}
-  \log p(\hat{X^+}_N | \hat{X}_N) = - \frac{1}{2}\hat{X^+}_N\T (K_{\hat{X}}^N + N\lambda I_N)^{-1} \hat{X^+}_N -\frac{1}{2}\log |K_{\hat{X}}^N + N\lambda I_N| - \frac{N}{2}\log(2\pi).
+    \begin{split}
+         & \log p(X^+_N | X_N,\theta) =  - \frac{1}{2}X^+_N{}\T (K_{X}^N + N\lambda I_N)^{-1} X^+_N \\
+         & \hspace{40pt} -\frac{1}{2}\log |K_{X}^N + N\lambda I_N| - \frac{N}{2}\log(2\pi),
+    \end{split}
 \end{equation}
+where $\theta:=(\sigma_f,\sigma_l, M)$ \OS{Which are implemented?} contains all learnable hyperparameters (of the kernel).
+To do so, the \texttt{LbfgsTuner} uses the L-BFGS or L-BFGS-B quasi-Newton optimization algorithms~\cite{book:nonlinear-programming},
+implemented in the \texttt{LBFGS++} library\footnote{https://github.com/yixuan/LBFGSpp}.
+\end{comment}
 
-\paragraph{Implementation}
+\paragraph{\Circled{4}~Feature Map}
+We exploit the truncated spectral kernel expansion in \eqref{eq:sqexp_kernel_fourier} by building an explicit approximated feature map, composed of a linear sum of trigonometric functions with increasing frequencies (see Figure~\ref{fig:spectral_barrier}).
+The underlying kernel expansion, visualized in Figure~\ref{fig:spectral_measure_abstraction}, can be controlled to trade-off efficiency and accuracy/conserativeness.
+% The full expansion of the kernel would need a sum of infinitely many terms with diminishing impact on the overall result, which we truncate arbitrarily short, a decision based on the tradeoff we are looking for between efficiency and accuracy.
+After being defined with the same \hp $(\sigma_f,\sigma_l)$ that characterize the \texttt{KernelRidgeRegressor}, the function can be used to map any point from $\X$ to the \gls{rkhs} associated with the kernel.
+\lucid currently implements three different ways for partitioning the spectral measure in Figure~\ref{fig:spectral_measure_abstraction}:
+\begin{itemize}
+    \item \texttt{LinearTruncatedFourierFeatureMap} defines equally spaced frequency bands on the interval $[-3\sigma_l,3\sigma_l]$, capturing 99.73\% of the spectral measure.
+This partitioning is shown in Figure~\ref{fig:spectral_measure_abstraction}.
+    \item \texttt{LogTruncatedFourierFeatureMap} defines logarithmically spaced frequency bands on the interval $[-3\sigma_l,3\sigma_l]$, with each frequency band carrying an equal share of the spectral measure.
+    \item \texttt{ConstantTruncatedFourierFeatureMap} defines frequency bands with a fixed size.
+\end{itemize}
+Different feature map implementations may yield different results.
+In our example, we truncate the Fourier expansion to $5$ frequency bands, including the constant term, and use $64$ times the Nyquist frequency of lattice points to build the constraints of the optimization problem, to avoid it being too conservative.\OS{Specifying it as a multiple of the Nyquist frequency will inevitably raise questions.
+Just say we generate $X$ lattice points?
+"lattice density"}
+\begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
+feature_map: 
+    "LinearTruncatedFourierFeatureMap"
+num_frequencies: 5
+oversample_factor: 64
+\end{lstlisting}
 
-While it is possible to tune the \hp with any method and then set them manually in the estimator, \lucid provides a set of classes, which specialize the \texttt{Tuner} interface, to automate the process.
-The \texttt{GridSearchTuner} class implements the grid search method, while the \texttt{MedianHeuristicTuner} class implements the median heuristic.
-If the user wants to optimize the log marginal likelihood, they can use the \texttt{LBGSTuner} class, which runs the L-BFGS or L-BFGS-B quasi-Newton optimization algorithms~\cite{book:nonlinear-programming} over the log marginal likelihood function.
-Internally, \lucid uses the \texttt{LBFGS++} library~\footnote{https://github.com/yixuan/LBFGSpp} to perform the optimization.
+\paragraph{\Circled{5} Solver}
+% \todo{Barriers should probably be an explicit class in \lucid that hides the optimization implementation}
+Based on the components discussed above, \lucid generates and solves a finite-constraint \gls{lp} as outlined in Section~\ref{sec:ddbarriers}.
+% If successful, the output is a \glspl{cbc} and a quantified lower bound on the true safety probability $P_{safe}(\S^\pi)$.
+%
+% When verifying the safety of a system, \lucid will search for a \gls{cbc} $\B$ that satisfies the conditions in Definition~\ref{def:cbc}.
+If successful, \lucid returns a \gls{cbc}, a quantified lower bound on the true safety probability $P_{safe}(\S^\pi)$, as well as the corresponding constants $\eta$, $\gamma$, and $c$.
+% More precisely, we follow the steps outlined in Figure~\ref{fig:steps}.
 
-\section{Benchmarks}
-\label{sec:benchmarks}
+Generating the \gls{lp}, specifically choosing an appropriate lattice density, involves trading off efficiency versus conservativeness (see Section~\ref{sec:ddbarriers}), with any sampling density beyond the Nyquist frequency yielding a valid relaxation.
+In the benchmarks in Section~\ref{sec:experiments}, we showcase the relation numerically.
+%
+% While the theory gives us a precise indication on how to construct the \gls{lp} which yields a correct-by-design solution, in practice the constraints may be too conservative to find a valid solution.
+% To mitigate this, the user can either increase the number of lattice points $Q$, worsening the computational efficiency,
+% or adjust the coefficient $C_{\hat{N}}$, improving performance at the cost of loosening the guarantees.
+For solving the \gls{lp}, \lucid can interface with different linear optimizers: \gurobi, \alglib or \highs. Here, we use \gurobi:
+\begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
+optimiser: "GurobiOptimiser"
+\end{lstlisting}
 
-\section*{Acknowledgements}
-The authors thank \dots.
+\paragraph{Running the Tool}
+We have configured all the components needed to run \lucid.
+Putting it all together in a single configuration file \texttt{config.yaml} we can run the tool with the command \lstinline|pylucid config.yaml --plot|.
+\lucid will parse the configuration, synthesize a barrier certificate and plot the result.
+For the running example, we obtain the barrier certificate shown in Figure~\ref{fig:example} for a control horizon of $T = 15$ certifying safety of the system in \eqref{eq:linear-system} with a probability of at least $93.73\%$ ($\eta = 0.013, \gamma=1.0, c = 0.003$).
+%\|B\| = 1.72
 
-\bibliographystyle{ieeetr}
-\bibliography{resources}
+\begin{figure}
+    \centering
+    \resizebox{\columnwidth}{!}{\import{figures}{example.pgf}}
+    \caption{Barrier certificate for the linear system example.
+        The state space $\X$ is plotted in the X axis, while the value of the barrier $\B$ is plotted in the Y axis.
+        The green line represents the barrier value at time $t$ while the purple one represents the barrier value at time $t+1$.
+        The initial and unsafe sets are highlighted in blue and red respectively.}
+    \label{fig:example}
+\end{figure}
+
+\paragraph{Validation (optional)}
+Albeit, if \lucid finds a barrier, this is already formally sound with respect to the data-driven estimator,
+if the system dynamics are known, \lucid provides the option to formally verify the correctness of the barrier using the \dreal SMT solver~\cite{dreal}.
+Note that \dreal has to be installed separately with \lstinline|pip install dreal| and may not be available on all systems.
+
+% The resulting barrier can then be checked with the verifier, provided we have access to the system's model, to ensure its correctness.
+
+Since we know the expected behavior of the example system $\S$ from~\eqref{eq:linear-system}, we can run the formal validation by adding the following two lines to the configuration:
+\begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
+system_dynamics: ["x1 / 2"]
+verify: true
+\end{lstlisting}
+Doing so confirms that the $\B$ is indeed a valid \gls{cbc} for the system.
+
+\subsection{Graphical User Interface}
+
+\pylucid provides a \gls{gui} to guide the user in the creation of the scenario configuration and presenting the results in an intuitive way.
+Running \lstinline|pylucid-gui| will open a browser tab containing the interface shown in Figure~\ref{fig:gui}, while a local server will listen for requests coming from the \gls{gui}, computing and returning the results.
+\todo{Improve picture of the GUI}
+\begin{figure}
+    \centering
+    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
+    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
+    The left half of the screen allows the user to provide the transition samples and the safety specification to verify.
+    The results will be shown on the right half of the screen.
+    }
+    \label{fig:gui}
+\end{figure}
+
+\begin{comment}
+\subsection{Functionality}
+
+Having parsed and validated the scenario configuration, \lucid will begin the main pipeline to produce the expected result.
+If a set of sample transitions has not been provided by the user, \lucid will try to produce it itself by randomly sampling $\X$ to which apply the system dynamics function.
+The samples will be used to fit and optionally tune the \estimator so that, given an input state, it will accurately predict the value of the feature map applied to the next state.
+\lucid will then store a lattice of points from each of the set provided to which apply the feature map.
+These values will be used to define the constraints of the \gls{lp} that the chosen optimizer will solve.
+
+\Sadegh{In the following figure, when you say collect samples, it should be the dataset mentioned earlier in the paper. You also need the next state.}
+
+\section{Example Use Case}
+
+\paragraph{Configuration via Python}
+We can also define the same exact configuration in Python, allowing for more flexibility and programmatic control.
+\lstinputlisting[language=iPython,caption={Python configuration for the example.}]{code/example.py}
+Note that in this case we are building the \estimator ourself instead of just providing the type of \estimator to use.
+This gives us absolute control over how the \estimator is tuned before being used.
+\end{comment}
+
+\section{Experimental Evaluation}
+\label{sec:experiments}
+
+\todo{Platform, configuration, seed for reproducibility}
+
+To ascertain the performance of \lucid, we conducted a series of experiments, run on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, and 64 GB of RAM.
+All runs had the random seed set to $42$ to ensure reproducibility.
+
+\subsection{Barrier 3}
+
+The \barr experiment is inspired by the one from \cite{abate2021fossil}, which we extend by adding stochastic noise $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$ to arrive at the two-dimensional nonlinear stochastic dynamics
+\begin{equation*}
+    \begin{bmatrix}
+        {x}_{1, t+1} \\
+        {x}_{2, t+1}
+    \end{bmatrix}
+    = \begin{bmatrix}
+        {x}_{2, t} \\
+        \frac{1}{3} {x}^3_{1, t} - {x}_{1,t} - {x}_{2,t}
+    \end{bmatrix} + w_t.
+\end{equation*}
+Given
+\begin{align*}
+    &\X = [ -3, 2.5 ] \times [ -2 , 1 ] \\
+    &\X_0 = [ 1 , 2 ] \times [ -0.7 , 0.3 ] \cup [ -1.8 , -1.4 ] \times [ -0.1 , 0.1 ] \\
+    &\qquad \cup [-1.4, -1.2] \times [-0.5 , 0.1] \\
+    &\X_U = [ 0.4 , 0.6 ] \times [ 0.2 , 0.6 ] \cup [ 0.6 , 0.7 ] \times [ 0.2 , 0.4 ],
+\end{align*}
+we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=10$ time steps.
+\EC{we can remove all the explicit set intevals}
+This example is particularly challenging due to the closeness between the initial set and the unsafe set.
+Hence, we need a rather high number of frequencies to achieve the required expressivity in the barrier.
+The results are shown in Figure~\ref{fig:CSBarr3}.
+The kernel \hp have been selected through offline tuning to be $\sigma_f=X$ and $\sigma_l=[X, X]$.
+Using a spectral basis of $M=X^3-1$ frequencies and a lattice density of $\hat{N} = X^2$, 
+we were able to generate a \gls{cbc} with $\eta \approx X.X$, $\gamma \approx X.X$, and $c \approx X.X$ in $X$ minutes and $X$ seconds, achieving a safety probability of $P_{safe}(\S^\pi) \approx XX.X\%$.
+% Knowing the system dynamics, we were also able to formally validate the barrier.
+
+\begin{figure}[ht]
+    \resizebox{\columnwidth}{!}{\import{figures}{barrier3.pgf}}%
+    \caption{\gls{cbc} synthesis for the \barr benchmark.
+        The blue regions represent the initial set $\X_0$, while the red regions represent the unsafe set $\X_U$.
+        The pink surface indicates the value of $\gamma$.
+    }
+    \label{fig:CSBarr3}
+\end{figure}
+
+\subsection{Overtaking}
+
+We consider a scenario where an autonomous vehicle (AV) controlled by a \gls{nn} is overtaking another vehicle, as indicated in Figure~\ref{fig:safety_setup}. 
+The dynamics of the ego vehicle are given by Dubin's car model \EC{does it need a cit or is it just textbook} by adding the noise vector $w = \begin{bmatrix}w_t^1 & w_t^2 & w_t^3\end{bmatrix}$ where each component is drawn from a zero-mean Gaussian with standard deviation $0.01$, $0.01$, and $0.001$, respectively.
+The steering wheel angle is supplied by the \gls{nn} controller and we travel at a fixed velocity $v=1$.
+The goal is to certify that the controlled system remains safe by computing the probability that the system initialized in $[{x}_0,{y}_0,\phi_0]\T\in \X_0$ does not enter the unsafe region $\X_u$ within $T=50$ time steps.
+
+The \gls{lp} is generated based on a lattice of $\hat{N}=X^3$ equidistant points and a spectral basis of $M=4^3-1$ frequencies.
+The kernel \hp are selected to be $\sigma_f=X$ and $\sigma_l=[X, X, X]$.
+We obtained a barrier which certifies safety with a probability of at least $XX\%$ with $c=0$, $\gamma=X.X$ and $\eta=X.X$.
+Note that this is only certifying safety w.r.t. the empirical distribution, i.e., the \gls{cme} constructed from the observed data.
+
+% \begin{table}
+%     \centering
+%     \begin{tabular}{cccc}
+%         \toprule
+%         \textbf{Benchmark} & \textbf{Dim} & \textbf{Runtime} & \textbf{Safety Prob.} \\
+%                            &              & [m:ss]           & [\%]                  \\ % Units
+%         \midrule
+%         Barr3              & 2            & X:XX             & XX                    \\
+%         name1              & 3            & X:XX             & XX                    \\
+%         name2              & 7            & X:XX             & XX                    \\
+%         \bottomrule
+%     \end{tabular}
+%     \caption{Computational benchmarks: ...}
+%     \label{tbl:benchmarks}
+% \end{table}
+
+Overview of the experimental results in Table~\ref{tbl:benchmarks_results}.
+\begin{table}[tb]
+    \centering
+    \begin{tabular}{ccccc}
+        \toprule
+        \textbf{Benchmark} & \textbf{Dim} & \textbf{Lattice} & \textbf{Runtime} & \textbf{Safety Prob.} \\
+                           &              & \textbf{Density} & [mm:ss]          & [\%]                  \\ % Units
+        \midrule
+        Linear             & 1            & $?$              & 00:02            & 95.15                 \\
+        Barr3              & 2            & $30^2$           & XX:XX            & XX                    \\
+                           &              & $40^2$           & XX:XX            & XX                    \\
+                           &              & $?^2$            & XX:XX            & XX                    \\
+        Overtaking         & 3            & $?^3$            & XX:XX            & XX                    \\
+                           & 3            & $?^3$            & XX:XX            & XX                    \\
+                           & 3            & $?^3$            & XX:XX            & XX                    \\
+        name2              & 7            &                  & XX:XX            & XX                    \\
+        \bottomrule
+    \end{tabular}
+    \caption{Computational benchmarks: ...}
+    \label{tbl:benchmarks_results}
+\end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{placeholder.jpeg}
+    \caption{Barrier}
+    \label{fig:barr3_barrier}
+\end{figure}
+
+\Sadegh{Are we comparing with alternative approaches in the literature?
+Since we mention alternative tools and their capabilities in Table 1, this raises expectations that we provide a fair benchmarking and show how we are better than them.}
+
+\section{Future Extensions}\label{sec:future_extensions}
+The form of data \eqref{eq:data} considered here assumes access to full state measurements, as it is the case when working with simulated systems.
+Extending this to partially observed settings adds another level of complexity.
+Extending \lucid to such settings is on our agenda and builds on top of the results presented in this paper.
+
+\OS{As the GaussianKernel and KernelRidgeRegressor are the only options we currently provide, is specifying them explicitly necessary?
+Maybe we could also add a sentence about the fact that they are currently the only option, but that in the future we plan to extend this to to allow to include prior knowledge about the system dynamics (in the spirit of physics-informed approaches).}
+
+\section{Conclusion}\label{sec:conclusion}
+...
+
+\input{appendix}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{aaai25}
 
 \newpage
-\input{appendix.tex}
+\def\isChecklistMainFile{\FALSE}
+\input{reproducibility checklist/ReproducibilityChecklist}
 

### 2025-07-30 docs/paper/reproducibility checklist/ReproducibilityChecklist.tex
feat: update paper

% !TEX root =  main.tex
\makeatletter
\@ifundefined{isChecklistMainFile}{
  % We are compiling a standalone document
  \newif\ifreproStandalone
  \reproStandalonetrue
}{
  % We are being \input into the main paper
  \newif\ifreproStandalone
  \reproStandalonefalse
}
\makeatother

\ifreproStandalone
\documentclass[letterpaper]{article}
\usepackage[submission]{aaai2026}
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{xcolor}
\frenchspacing

\begin{document}
\fi
\setlength{\leftmargini}{20pt}
\makeatletter\def\@listi{\leftmargin\leftmargini \topsep .5em \parsep .5em \itemsep .5em}
\def\@listii{\leftmargin\leftmarginii \labelwidth\leftmarginii \advance\labelwidth-\labelsep \topsep .4em \parsep .4em \itemsep .4em}
\def\@listiii{\leftmargin\leftmarginiii \labelwidth\leftmarginiii \advance\labelwidth-\labelsep \topsep .4em \parsep .4em \itemsep .4em}\makeatother

\setcounter{secnumdepth}{0}
\renewcommand\thesubsection{\arabic{subsection}}
\renewcommand\labelenumi{\thesubsection.\arabic{enumi}}

\newcounter{checksubsection}
\newcounter{checkitem}[checksubsection]

\newcommand{\checksubsection}[1]{%
  \refstepcounter{checksubsection}%
  \paragraph{\arabic{checksubsection}. #1}%
  \setcounter{checkitem}{0}%
}

\newcommand{\checkitem}{%
  \refstepcounter{checkitem}%
  \item[\arabic{checksubsection}.\arabic{checkitem}.]%
}
\newcommand{\question}[2]{\normalcolor\checkitem #1 #2 \color{blue}}
\newcommand{\ifyespoints}[1]{\makebox[0pt][l]{\hspace{-15pt}\normalcolor #1}}

\section*{Reproducibility Checklist}
\begin{comment}

\vspace{1em}
\hrule
\vspace{1em}

\textbf{Instructions for Authors:}

This document outlines key aspects for assessing reproducibility. Please provide your input by editing this \texttt{.tex} file directly.

For each question (that applies), replace the ``Type your response here'' text with your answer.

\vspace{1em}
\noindent
\textbf{Example:} If a question appears as
%
\begin{center}
\noindent
\begin{minipage}{.9\linewidth}
\ttfamily\raggedright
\string\question \{Proofs of all novel claims are included\} \{(yes/partial/no)\} \\
Type your response here
\end{minipage}
\end{center}
you would change it to:
\begin{center}
\noindent
\begin{minipage}{.9\linewidth}
\ttfamily\raggedright
\string\question \{Proofs of all novel claims are included\} \{(yes/partial/no)\} \\
yes
\end{minipage}
\end{center}
%
Please make sure to:
\begin{itemize}\setlength{\itemsep}{.1em}
\item Replace ONLY the ``Type your response here'' text and nothing else.
\item Use one of the options listed for that question (e.g., \textbf{yes}, \textbf{no}, \textbf{partial}, or \textbf{NA}).
\item \textbf{Not} modify any other part of the \texttt{\string\question} command or any other lines in this document.\\
\end{itemize}

You can \texttt{\string\input} this .tex file right before \texttt{\string\end\{document\}} of your main file or compile it as a stand-alone document. Check the instructions on your conference's website to see if you will be asked to provide this checklist with your paper or separately.

\vspace{1em}
\hrule
\vspace{1em}
\end{comment}
% The questions start here

\checksubsection{General Paper Structure}
\begin{itemize}

\question{Includes a conceptual outline and/or pseudocode description of AI methods introduced}{(yes/partial/no/NA)}
Type your response here

\question{Clearly delineates statements that are opinions, hypothesis, and speculation from objective facts and results}{(yes/no)}
Type your response here

\question{Provides well-marked pedagogical references for less-familiar readers to gain background necessary to replicate the paper}{(yes/no)}
Type your response here

\end{itemize}
\checksubsection{Theoretical Contributions}
\begin{itemize}

\question{Does this paper make theoretical contributions?}{(yes/no)}
Type your response here

	\ifyespoints{\vspace{1.2em}If yes, please address the following points:}
        \begin{itemize}

	\question{All assumptions and restrictions are stated clearly and formally}{(yes/partial/no)}
	Type your response here

	\question{All novel claims are stated formally (e.g., in theorem statements)}{(yes/partial/no)}
	Type your response here

	\question{Proofs of all novel claims are included}{(yes/partial/no)}
	Type your response here

	\question{Proof sketches or intuitions are given for complex and/or novel results}{(yes/partial/no)}
	Type your response here

	\question{Appropriate citations to theoretical tools used are given}{(yes/partial/no)}
	Type your response here

	\question{All theoretical claims are demonstrated empirically to hold}{(yes/partial/no/NA)}
	Type your response here

	\question{All experimental code used to eliminate or disprove claims is included}{(yes/no/NA)}
	Type your response here

	\end{itemize}
\end{itemize}

\checksubsection{Dataset Usage}
\begin{itemize}

\question{Does this paper rely on one or more datasets?}{(yes/no)}
Type your response here

\ifyespoints{If yes, please address the following points:}
\begin{itemize}

	\question{A motivation is given for why the experiments are conducted on the selected datasets}{(yes/partial/no/NA)}
	Type your response here

	\question{All novel datasets introduced in this paper are included in a data appendix}{(yes/partial/no/NA)}
	Type your response here

	\question{All novel datasets introduced in this paper will be made publicly available upon publication of the paper with a license that allows free usage for research purposes}{(yes/partial/no/NA)}
	Type your response here

	\question{All datasets drawn from the existing literature (potentially including authors' own previously published work) are accompanied by appropriate citations}{(yes/no/NA)}
	Type your response here

	\question{All datasets drawn from the existing literature (potentially including authors' own previously published work) are publicly available}{(yes/partial/no/NA)}
	Type your response here

	\question{All datasets that are not publicly available are described in detail, with explanation why publicly available alternatives are not scientifically satisficing}{(yes/partial/no/NA)}
	Type your response here

\end{itemize}
\end{itemize}

\checksubsection{Computational Experiments}
\begin{itemize}

\question{Does this paper include computational experiments?}{(yes/no)}
Type your response here

\ifyespoints{If yes, please address the following points:}
\begin{itemize}

	\question{This paper states the number and range of values tried per (hyper-) parameter during development of the paper, along with the criterion used for selecting the final parameter setting}{(yes/partial/no/NA)}
	Type your response here

	\question{Any code required for pre-processing data is included in the appendix}{(yes/partial/no)}
	Type your response here

	\question{All source code required for conducting and analyzing the experiments is included in a code appendix}{(yes/partial/no)}
	Type your response here

	\question{All source code required for conducting and analyzing the experiments will be made publicly available upon publication of the paper with a license that allows free usage for research purposes}{(yes/partial/no)}
	Type your response here

	\question{All source code implementing new methods have comments detailing the implementation, with references to the paper where each step comes from}{(yes/partial/no)}
	Type your response here

	\question{If an algorithm depends on randomness, then the method used for setting seeds is described in a way sufficient to allow replication of results}{(yes/partial/no/NA)}
	Type your response here

	\question{This paper specifies the computing infrastructure used for running experiments (hardware and software), including GPU/CPU models; amount of memory; operating system; names and versions of relevant software libraries and frameworks}{(yes/partial/no)}
	Type your response here

	\question{This paper formally describes evaluation metrics used and explains the motivation for choosing these metrics}{(yes/partial/no)}
	Type your response here

	\question{This paper states the number of algorithm runs used to compute each reported result}{(yes/no)}
	Type your response here

	\question{Analysis of experiments goes beyond single-dimensional summaries of performance (e.g., average; median) to include measures of variation, confidence, or other distributional information}{(yes/no)}
	Type your response here

	\question{The significance of any improvement or decrease in performance is judged using appropriate statistical tests (e.g., Wilcoxon signed-rank)}{(yes/partial/no)}
	Type your response here

	\question{This paper lists all final (hyper-)parameters used for each model/algorithm in the paper’s experiments}{(yes/partial/no/NA)}
	Type your response here

\end{itemize}
\end{itemize}
\ifreproStandalone
\end{document}
\fi

### 2025-07-30 docs/paper/main.tex
feat: introduce barrier 2

@@
 
-\todo{Platform, configuration, seed for reproducibility}
-
 To ascertain the performance of \lucid, we conducted a series of experiments, run on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, and 64 GB of RAM.
@@
 
+\subsection{Barrier 2}
+
+The \barrII experiment is inspired by the one from \cite{abate2021fossil}, which we extend by adding stochastic noise $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$ to arrive at the two-dimensional nonlinear stochastic dynamics
+
+\begin{equation*}
+    \begin{bmatrix}
+        {x}_{1, t+1} \\
+        {x}_{2, t+1}
+    \end{bmatrix}
+    = \begin{bmatrix}
+        {x}_{2, t} - 1 + e^{-x_{1, t}} \\
+        -\sin^2(x_{1, t})
+    \end{bmatrix} + w_t.
+\end{equation*}
+Given
+\begin{align*}
+    &\X = [ -2, 2 ] \times [ -2 , 2 ] \\
+    &\X_0 = \{ [x_1, x_2] : (x_1 + 0.5)^2 + (x_2 - 0.5)^2 \leq 0.4 \} \\
+    &\X_u = \{ [x_1, x_2] : (x_1 - 0.7)^2 + (x_2 + 0.7)^2 \leq 0.3 \}
+\end{align*}
+we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=5$ time steps.
+\EC{we can remove all the explicit set intevals}
+The results are shown in Figure~\ref{fig:CSBarr2}.
+The kernel \hp have been selected through offline tuning to be $\sigma_f=X$ and $\sigma_l=[X, X]$.
+Using a spectral basis of $M=X^3-1$ frequencies and a lattice density of $\hat{N} = X^2$, 
+we were able to generate a \gls{cbc} with $\eta \approx X.X$, $\gamma \approx X.X$, and $c \approx X.X$ in $X$ minutes and $X$ seconds, achieving a safety probability of $P_{safe}(\S^\pi) \approx XX.X\%$.
+% Knowing the system dynamics, we were also able to formally validate the barrier.
+
+\begin{figure}[ht]
+    \resizebox{\columnwidth}{!}{\import{figures}{barrier3.pgf}}%
+    \caption{\gls{cbc} synthesis for the \barrIII benchmark.
+        The blue regions represent the initial set $\X_0$, while the red regions represent the unsafe set $\X_U$.
+        The pink surface indicates the value of $\gamma$.
+    }
+    \label{fig:CSBarr2}
+\end{figure}
+
 \subsection{Barrier 3}
 
-The \barr experiment is inspired by the one from \cite{abate2021fossil}, which we extend by adding stochastic noise $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$ to arrive at the two-dimensional nonlinear stochastic dynamics
+The \barrIII experiment is inspired by the one from \cite{abate2021fossil}, which we extend by adding stochastic noise $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$ to arrive at the two-dimensional nonlinear stochastic dynamics
 \begin{equation*}
@@
     \resizebox{\columnwidth}{!}{\import{figures}{barrier3.pgf}}%
-    \caption{\gls{cbc} synthesis for the \barr benchmark.
+    \caption{\gls{cbc} synthesis for the \barrIII benchmark.
         The blue regions represent the initial set $\X_0$, while the red regions represent the unsafe set $\X_U$.

### 2025-07-30 docs/paper/main.tex
feat: add barrier2

@@
     \lucid employs a data-driven methodology rooted in control barrier certificates, which are learned directly from system transition data, to ensure formal safety guarantees.
-    We use conditional mean embeddings to embed data into a reproducing kernel Hilbert space (RKHS), where an RKHS ambiguity set is constructed that can be inflated to robustify the result to out-of-distribution behavior.
+    We use conditional mean embeddings to embed data into a \gls{rkhs}, where an \gls{rkhs} ambiguity set is constructed that can be inflated to robustify the result to out-of-distribution behavior.
 
@@
 As deep learning agents are left to choose their actions autonomously in closed-loop interaction with the physical world, they are confronted with a world riddled with randomness and uncertainty. 
-Efforts to establishing trust in their safe operation have been largely focused on developing tools to verify the input--output behavior of neural networks (NNs) embedded in the systems~\cite{liu2021algorithms}.
+Efforts to establishing trust in their safe operation have been largely focused on developing tools to verify the input--output behavior of \glspl{nn} embedded in the systems~\cite{liu2021algorithms}.
 Unfortunately, there do not exist any tools that could take these results and certify the safety of the entire system, as uncertainty-aware models of closed-loop systems are rarely available and simulators are often too complicated and opaque to perform verification directly~\cite{wongpiromsarn2023formal}.
@@
 
-There exist no tools capable of solving this problem with quantified guarantees.
+There exist no tools capable of quantifying safety guarantees for complex stochastic closed-loop systems from data.
 %
-For the setting where a model of the closed-loop system is available, \npinterval by \citet{harapanahalli2023forward} verifies safety of nonlinear systems with non-deterministic disturbance based on existing NN verification tools.
+For the setting where a model of the closed-loop system is available, \npinterval by \citet{harapanahalli2023forward} verifies safety of nonlinear systems with non-deterministic disturbance based on existing \gls{nn} verification tools.
 See the references therein and the annual friendly competition by \citet{abate2024arch} for adjacent work.
@@
 Few data-driven approaches for stochastic systems exist. 
-\omnisafe is a comprehensive platform for the development of safe reinforcement learning (RL) algorithms~\citet{ji2024omnisafe}.
-However, safe RL does generally only \emph{encourage} safer behavior, without providing any rigorous or quantified guarantees on the probability of the absence of unsafe behavior.
-As a popular working principle for certifying safety, control barrier certificates (CBCs)~\cite{prajna2006barrier} are at the basis of tools such as \trust~\cite{gardner2025trust} (supports only polynomial dynamics) and \fossil~\cite{edwards2024fossil} (model-based), which are restricted to deterministic systems.
+\omnisafe is a comprehensive platform for the development of safe \gls{rl} algorithms~\citet{ji2024omnisafe}.
+However, safe \gls{rl} does generally only \emph{encourage} safer behavior, without providing any rigorous or quantified guarantees on the probability of the absence of unsafe behavior.
+As a popular working principle for certifying safety, \glspl{cbc}~\cite{prajna2006barrier} are at the basis of tools such as \trust~\cite{gardner2025trust} (supports only polynomial dynamics) and \fossil~\cite{edwards2024fossil} (model-based), which are restricted to deterministic systems.
 
@@
 \footnotetext[2]{Accepts non-deterministic bounded disturbances.} % npinterval
-At its core, it learns CBCs for unknown systems based solely on data, by constructing an uncertainty-aware estimator of the expected system behavior based on \emph{conditional mean embeddings} (CMEs)~\cite{muandet2017kernel}.
+At its core, it learns \glspl{cbc} for unknown systems based solely on data, by constructing an uncertainty-aware estimator of the expected system behavior based on \glspl{cme}~\cite{muandet2017kernel}.
 Crucially, the underlying learning framework establishes quantified safety probabilities with distributionally robust guarantees for arbitrary smooth dynamics, thus relaxing the need for restrictive structural assumptions common to related approaches.
-For instance, \citet{schoen2024distributionally} learn CBCs for systems with polynomial dynamics and \citet{chen2025distributionally} assume systems with known deterministic component.
+For instance, \citet{schoen2024distributionally} learn \glspl{cbc} for systems with polynomial dynamics and \citet{chen2025distributionally} assume systems with known deterministic component.
 %
@@
 \begin{itemize}
-    \item We introduce \lucid, a novel verification engine that learns control barrier certificates from data using kernel-based CMEs.
+    \item We introduce \lucid, a novel verification engine that learns control barrier certificates from data using kernel-based \glspl{cme}.
 \lucid uses a tractable reformulation of the verification problem via a finite Fourier expansion, enabling efficient barrier synthesis based on a linear program.
@@
 %
-This general formulation subsumes a wide range of systems, including discrete-time Markov decision processes (MDPs).
+This general formulation subsumes a wide range of systems, including discrete-time \glspl{mdp}.
 
@@
 Here, the focus is on systems $\S$ driven by black-box control policies of the form $\pi\colon\R^n\rightarrow\R^m$, i.e., at every time step $t=0,1,2,\ldots$ a continuous action $a_t\in\A$ is selected based on the current state $x_t$.
-Such policies could be, for example, neural networks trained via RL, or any other black-box function generating actions in $\R^m$ (see Figure~\ref{fig:closed_loop_system}).
+Such policies could be, for example, neural networks trained via \gls{rl}, or any other black-box function generating actions in $\R^m$ (see Figure~\ref{fig:closed_loop_system}).
 The resulting closed-loop system is denoted as $\S^\pi$.
@@
 
-Such safety problems are tricky and even for the case where an explicit model \eqref{eq:model} is given, certifying safety of a discrete-time stochastic system over an uncountable state space does generally not admit an analytical solution and is extremely challenging, especially for complex dynamics~\cite{abate2008probabilistic}.
-Even more, for unbounded stochasticity $w_t\sim p_w$, there is generally no deterministic answer to safe or not, but a safety probability $P_{\text{safe}}(\S^\pi)\in[0,1)$.
+Such safety problems are tricky and even for the case where an explicit model \eqref{eq:model} is given, certifying safety of a discrete-time stochastic system over an uncountable state space does not generally admit an analytical solution and is extremely challenging, especially for complex dynamics~\cite{abate2008probabilistic}.
+Even more, for unbounded stochasticity $w_t\sim p_w$, there is generally no deterministic answer (safe or not), but a safety probability $P_{\text{safe}}(\S^\pi)\in[0,1)$.
 Thus the goal is generally to estimate a \emph{lower bound} on the true safety probability $P_{\text{safe}}(\S^\pi)$.
@@
     \item[(a)] $\forall x_0\in \X_0\colon\,\B(x_0)\leq\eta$;
-    \item[(b)] $\forall x_U\in \X_U\colon\,\B(x_u)\geq\gamma$; and
+    \item[(b)] $\forall x_U\in \X_U\colon\,\B(x_U)\geq\gamma$; and
     \item[(c)] $\forall x\in\X,\,\exists a\in\A\colon\,\E[\B(X_+) \mid X=x,\,A=a] -\B(x) \leq  c;$
@@
 where $T$ is the desired control horizon.
-Notably, the system dynamics only enter the barrier conditions through the conditional expectation in (c), and a \gls{cbc} thus only depends on the \emph{expected} system behavior, with no need to consider its concrete stochastic law.
+Notably, the system dynamics only enters the barrier conditions through the conditional expectation in (c), and a \gls{cbc} thus only depends on the \emph{expected} system behavior, with no need to consider its concrete stochastic law.
 
-Whilst \eqref{eq:safety_prob_lb} can provide a robust assessment of a systems safety, in practice, the bound can be overly conservative and thus several improved variants of the original barrier constraints exist~\cite{mahathi2022kinductive}.
+Whilst \eqref{eq:safety_prob_lb} can provide a robust assessment of a system's safety, in practice, the bound can be overly conservative and thus several improved variants of the original barrier constraints exist~\cite{mahathi2022kinductive}.
 As these conditions in essence all rely on the computation of chance constraint with respect to the expected behavior of the system, they are basically interchangeable.
@@
 Following the same reasoning, the \emph{kernel mean embedding} represents the projection of a probability measure into a \gls{rkhs} via a feature map $\phi$ associated with a positive definite kernel $k$~\cite{Smola2007EmbedDistrb,muandet2017kernel}.
-For conditional probability distributions a similar concept exists: \glspl{cme} can be used to model the expected value of any RKHS function $f\colon\X\rightarrow\R$ under a stochastic process such as $\S$~\cite{park2020measuretheoretic,muandet2017kernel}.
+For conditional probability distributions a similar concept exists: \glspl{cme} can be used to model the expected value of any \gls{rkhs} function $f\colon\X\rightarrow\R$ under a stochastic process such as $\S$~\cite{park2020measuretheoretic,muandet2017kernel}.
 For the Gaussian kernel,
@@
 
-It is common practice to robustify empirical estimates such as \eqref{eq:empiricalEstimate} to out-of-sample behavior by constructing an RKHS ambiguity set centered at the empirical \gls{cme}.
+It is common practice to robustify empirical estimates such as \eqref{eq:empiricalEstimate} to out-of-sample behavior by constructing an \gls{rkhs} ambiguity set centered at the empirical \gls{cme}.
 The result is a distributionally robust estimator with an adjustable robustness radius.
@@
 with the zero-mean Gaussian distribution $\smash{\mathcal{N}(d\omega\mid0,\Sigma)}$ with covariance $\Sigma$, the imaginary unit $\mathbf{i}:=\smash{\sqrt{-1}}$, and where the projection $x \mapsto P(x)$ maps the domain $\X$ into the unit hypercube $[0,1]^{n}$.
-Partitioning the space of spatial frequencies $\omega\in\R^n$ into a set of discrete frequency bands (see Figure~\ref{fig:spectral_barrier}) yields a spectral abstraction of the associated RKHS, i.e., characterizing learnable functions $B$ in the form of Fourier series.
+Partitioning the space of spatial frequencies $\omega\in\R^n$ into a set of discrete frequency bands (see Figure~\ref{fig:spectral_barrier}) yields a spectral abstraction of the associated \gls{rkhs}, i.e., characterizing learnable functions $B$ in the form of Fourier series.
 By truncating the series to a finite number, $M$, of fixed frequency bands $\omega_j\in\R^{n}$, $j\in\{0,\ldots,M\}$, the resulting barriers are of the form
@@
 where the weights $w_0,\ldots,w_{M}\in\R_{\geq 0}$ associated with each frequency band are determined efficiently from the kernel's Gaussian spectral measure via the multivariate CDF (see Figure~\ref{fig:spectral_measure_abstraction}).
-The \gls{cme}-based estimator \eqref{eq:empiricalEstimate} is approximated in the same finite basis, with an approximation error decreasing exponentially with $M$~\cite{rahimi2007random}.
-This simplifies the barrier problem to a semi-infinite linear program.
+The \gls{cme}-based estimator \eqref{eq:empiricalEstimate} is approximated in the same finite basis via $H\in\R^{(2M+1)\times (2M+1)}$ such that
+\begin{equation*}
+    k_{XA}^N(x,a)\T\left[ K_{XU}^N+N \lambda I_N\right]^{-1}\! \Phi_{M,+}^N
+    \approx
+    \phi_M{\color{red}(x,a)}\T H,
+\end{equation*}
+where $\Phi_{M,+}^N:=[\phi_M(x_+^i)\T]_{i=1}^N$,
+with an approximation error decreasing exponentially with $M$~\cite{rahimi2007random}.
+This reduces the barrier synthesis problem
+% This simplifies the barrier problem 
+to a semi-infinite linear program, with barrier conditions linear in $b$:
+\begin{itemize}
+    \item[(a)] $\forall x_0\in \X_0\colon\,\phi_M(x_0)\T b\leq\eta$;
+    \item[(b)] $\forall x_U\in \X_U\colon\,\phi_M(x_U)\T b\geq\gamma$; and
+    \item[(c)] $\forall x\in\X,\,\exists a\in\A\colon\,\phi_M{\color{red}(x,a)}\T (Hb -b) \leq  c.$
+\end{itemize}
 % \OS{Importantly, the closed-form estimator in \eqref{eq:empiricalEstimate} does not depend on the choice of features and only through the spectral abstraction is the feature map introduced directly.}
@@
 As a result, the semi-infinite problem is relaxed to a finitely-constrained \gls{lp}, provided in full in {\color{red}the appendix}.
-Recall that given an appropriate robustness radius, the barriers produced by \lucid based on data $\data_N$ are statistically correct with respect to the unknown true system $\S$.
+Recall that given an appropriate robustness radius, the barriers produced by \lucid based on data $\data_N$ are statistically correct with respect to the unknown true system $\S$, and a lower bound for the safety probability is computed according to \eqref{eq:safety_prob_lb}.
 
@@
 Hence, for the rest of the paper, we will focus on \pylucid when describing the user interfaces.
-
-\paragraph{Installation}
-Provided \texttt{Python>=3.8} is already present, \pylucid can be installed with the command
-\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
-pip install pylucid[gui,plot] --index-url \
-  https://gitlab.com/api/v4/projects/71977529/packages/pypi/simple
-\end{lstlisting}
-% \EC{The command is long, but at the moment it cannot be shortened (we would need to host the package on PyPI).}
+{\color{red}Instructions for installing \lucid are deferred to the appendix.}
 
@@
 
-In its current form, \lucid implements all functionality needed to certify safety of closed-loop system with a given control policy $\pi$.
-Future releases will expand this core functionality to synthesize controllers that render the system safe as well.
+In its current form, \lucid implements all the functionalities needed to certify safety of a closed-loop system with a given control policy $\pi$.
+Future releases will expand this core functionality to 
+safe controller synthesis as well.
 Due to its modular architecture, \lucid can be easily extended in multiple directions, as outlined in Section~\ref{sec:future_extensions}.
@@
 \lucid is built with a modular architecture where each component is responsible for a specific task in the certification process.
-Moreover, since they extend from a common interface, they can be easily replaced or extended to suit the user's needs or in future versions of the tool.
+Moreover, since they extend from a common interface, they can be easily replaced or extended.
 An overview of the core components and how they interact is shown in Figure~\ref{fig:architecture}.
@@
 with
-state space $\X = [-1, 1]$, initial set $\X_0 = [-0.5, 0.5]$, and unsafe regions $\X_u = [-1, -0.9] \cup [0.9, 1]$.
+state space $\X = [-1, 1]$, initial set $\X_0 = [-0.5, 0.5]$, and unsafe regions $\X_U = [-1, -0.9] \cup [0.9, 1]$.
 While going over each component of \lucid, we will show how they can be configured within a \yaml configuration file to capture the system~\eqref{eq:linear-system} and its safety specification.
@@
     &\X_0 = \{ [x_1, x_2] : (x_1 + 0.5)^2 + (x_2 - 0.5)^2 \leq 0.4 \} \\
-    &\X_u = \{ [x_1, x_2] : (x_1 - 0.7)^2 + (x_2 + 0.7)^2 \leq 0.3 \}
+    &\X_U = \{ [x_1, x_2] : (x_1 - 0.7)^2 + (x_2 + 0.7)^2 \leq 0.3 \}
 \end{align*}
 we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=5$ time steps.
-\EC{we can remove all the explicit set intevals}
+\EC{we can remove all the explicit set intervals}
 The results are shown in Figure~\ref{fig:CSBarr2}.
-The kernel \hp have been selected through offline tuning to be $\sigma_f=X$ and $\sigma_l=[X, X]$.
-Using a spectral basis of $M=X^3-1$ frequencies and a lattice density of $\hat{N} = X^2$, 
-we were able to generate a \gls{cbc} with $\eta \approx X.X$, $\gamma \approx X.X$, and $c \approx X.X$ in $X$ minutes and $X$ seconds, achieving a safety probability of $P_{safe}(\S^\pi) \approx XX.X\%$.
+The kernel \hp have been selected through offline tuning to be $\sigma_f=1$ and $\sigma_l=[1.0, 5.39334]$.
+Using a spectral basis of $M=15^2-1$ frequencies and a lattice density of $\hat{N} = 350^2$, 
+we were able to generate a \gls{cbc} with $\eta \approx 5.032$, $\gamma = 100$, and $c \approx 3.926$ in $14.7$ minutes, achieving a lower bound on the safety probability of $P_{\text{safe}}(\S^\pi) \geq 75.34\%$.
 % Knowing the system dynamics, we were also able to formally validate the barrier.
@@
 \begin{figure}[ht]
-    \resizebox{\columnwidth}{!}{\import{figures}{barrier3.pgf}}%
-    \caption{\gls{cbc} synthesis for the \barrIII benchmark.
-        The blue regions represent the initial set $\X_0$, while the red regions represent the unsafe set $\X_U$.
-        The pink surface indicates the value of $\gamma$.
+    %\resizebox{\columnwidth}{!}{\import{figures}{barrier2.pdf}}%
+    \includegraphics[trim={5cm 3cm 2cm 4cm},clip,width=\linewidth]{barrier2.pdf}
+    \caption{\gls{cbc} synthesis for the \barrII benchmark.
+        The blue circle represents the initial set $\X_0$, while the red one represents the unsafe set $\X_U$.
     }
@@
 
-The \barrIII experiment is inspired by the one from \cite{abate2021fossil}, which we extend by adding stochastic noise $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$ to arrive at the two-dimensional nonlinear stochastic dynamics
+Similarly, we also tested \lucid on the \barrIII benchmark adapted from \cite{abate2021fossil} with added stochastic noise.
+The resulting nonlinear stochastic dynamics are
 \begin{equation*}
@@
 The steering wheel angle is supplied by the \gls{nn} controller and we travel at a fixed velocity $v=1$.
-The goal is to certify that the controlled system remains safe by computing the probability that the system initialized in $[{x}_0,{y}_0,\phi_0]\T\in \X_0$ does not enter the unsafe region $\X_u$ within $T=50$ time steps.
+The goal is to certify that the controlled system remains safe by computing the probability that the system initialized in $[{x}_0,{y}_0,\phi_0]\T\in \X_0$ does not enter the unsafe region $\X_U$ within $T=50$ time steps.
 

### 2025-07-30 benchmarks/integration/Barrier3.py
feat: update benchmarks

@@ -74,12 +74,12 @@ if __name__ == "__main__":
 
     grid = {
         # "num_frequencies": [9, 12, 13, 16, 17],
-        "num_frequencies": [13],
+        "num_frequencies": [18],
         # "num_frequencies": [4],
         "c_coefficient": [1.0],
         "time_horizon": [5],
-        "oversample_factor": [20.0, 25.0],
-        # "num_oversample": [250, 300, 350, 400],
+        # "oversample_factor": [1.0],
+        "num_oversample": [350],
         # "oversample_factor": [10.0],
     }
 

### 2025-07-30 benchmarks/integration/benchmark.py

@@ -63,7 +63,11 @@ def benchmark(name: str, config: Configuration, grid: dict[str, list[Any]]):
 def single_benchmark(name: str, config: Configuration):
     """Run the benchmark scenario."""
     logs: list[str] = []
-    log.set_sink(logs.append)
+    def handle_log(message: str):
+        logs.append(message)
+        if "C:" in message:
+            print(message)
+    log.set_sink(handle_log)
     log.set_verbosity(log.LOG_DEBUG)
 
     mlflow.set_experiment(experiment_name=name)

### 2025-07-30 benchmarks/integration/TuneOvertaking.py
chore: rename file

@@ -1,6 +1,6 @@
 #!/usr/bin/env python3
 from pylucid import *
-from ScenarioTuner import scenario_tuner
+from hp_tuning import hp_tuning
 import itertools
 
 

### 2025-07-30 benchmarks/integration/hp_tuning.py

@@ -49,7 +49,7 @@ def grid_search_tuner(config: Configuration, grid: "dict[Parameter, ParameterVal
     score_estimator(config)
 
 
-def scenario_tuner(file_path: str, grid: "dict[Parameter, ParameterValuesType]"):
+def hp_tuning(file_path: str, grid: "dict[Parameter, ParameterValuesType]"):
     action = ConfigAction(option_strings=None, dest="input")
     config = Configuration()
     action(None, config, Path(file_path), None)

### 2025-07-30 docs/paper/appendix.tex
feat: add barrier2
feat: add appendix

@@
 
-    % \section{Benchmarks}
-    % \label{app:benchmarks}
-    % Complete list of results for the benchmarks presented in \autoref{sec:benchmarks}.
-    % The legend is as follows:
-    % \textit{Output} indicates the result produced by the solver (i.e., optimal, unbounded, infeasible or unspecified),
-    % \textit{Prec} indicates the number of bits used in the last floating-point number representation,
-    % \textit{Ref} indicates the number of refinements,
-    % and \textit{time} is the time in seconds.
+\section{Installation}
+Provided \texttt{Python>=3.8} is already present, \pylucid can be installed with the command
+\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
+pip install pylucid[gui,plot] --index-url \
+  https://gitlab.com/api/v4/projects/71977529/packages/pypi/simple
+\end{lstlisting}
+There are a few limitation some of the dependencies introduce, which may preclude the ability of using certain features on not supported platforms.
+Formal verification of the barrier requires the \dreal SMT solver, which can only be installed on Linux and non-ARM macOS.
+Support for \highs \gls{lp} is not available on Windows at the moment.
+The \gurobi solver must be installed beforehand, and requires a license for commercial use, but is free for academic purposes.
+
+For more details on the installation process, please refer to the online documentation at \url{https://lucidtoolsource.gitlab.io/lucid/md_docs_2Pylucid.html}.
+
+\section{Benchmarks}
+\label{app:benchmarks}
+Complete list of results for the benchmarks presented in Section~\ref{sec:experiments}.
+The legend is as follows:
+\textit{Output} indicates the result produced by the solver (i.e., optimal, unbounded, infeasible or unspecified),
+\textit{Prec} indicates the number of bits used in the last floating-point number representation,
+\textit{Ref} indicates the number of refinements,
+and \textit{time} is the time in seconds.
+
+All benchmarks were run on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, and 64 GB of RAM, and all runs had the random seed set to $42$ to ensure reproducibility.
+The scripts responsible for running the benchmarks and \hp tuning are available in the \texttt{benchmarks/integration} folder of the repository.
+Note that a version of \texttt{Python>=3.9} is required to run the scripts, as some dependencies used to track the benchmarks' metrics across multiple runs are not compatible with \texttt{Python 3.8}.
+The \hp tuning of the \estimator was performed with the \texttt{LbfgsTuner}, bounding the value of $\sigma_l$ between $[10^{-5}, 10^5]$, and refined with the \texttt{GridSearchTuner}.
+The implementation can be found in the \texttt{benchmarks/integration/hp\_tuning.py} script. 
+Note that we used the \gurobi optimiser.
+Other optimizers, such as \alglib or \highs, can be used instead, but may yield different results, especially in terms of performance.
+
+\subsection{Linear}
+
+We consider the following system:
+\begin{equation*}
+    \begin{bmatrix}
+        {x}_{t+1}
+    \end{bmatrix}
+    = \begin{bmatrix}
+        0.5 {x}_{t}
+    \end{bmatrix} + w_t,
+\end{equation*}
+where $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_1)$.
+Given
+\begin{align*}
+    &\X = [-1, 1] \\
+    &\X_0 = [-0.5, 0.5] \\
+    &\X_U = [-1, -0.9] \cup [0.9, 1],
+\end{align*}
+we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=15$ time steps.
+The complete configuration for the linear example benchmark is shown in Listing~\ref{lst:linear}.
+\lstinputlisting[language=yaml,caption={Configuration for linear example},captionpos=b,label={lst:linear}]{code/linear.yaml}
+
+\subsection{Barrier 2}
+
+We consider the following system:
+\begin{equation*}
+    \begin{bmatrix}
+        {x}_{1, t+1} \\
+        {x}_{2, t+1}
+    \end{bmatrix}
+    = \begin{bmatrix}
+        {x}_{2, t} - 1 + e^{-x_{1, t}} \\
+        -\sin^2(x_{1, t})
+    \end{bmatrix} + w_t,
+\end{equation*}
+where $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$.
+Given
+\begin{align*}
+    &\X = [ -2, 2 ] \times [ -2 , 2 ] \\
+    &\X_0 = \{ [x_1, x_2] : (x_1 + 0.5)^2 + (x_2 - 0.5)^2 \leq 0.4 \} \\
+    &\X_U = \{ [x_1, x_2] : (x_1 - 0.7)^2 + (x_2 + 0.7)^2 \leq 0.3 \},
+\end{align*}
+we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=5$ time steps.
+The complete configuration for the \barrII benchmark is shown in Listing~\ref{lst:barrier2}.
+\lstinputlisting[language=yaml,caption={Configuration for \barrII},captionpos=b,label={lst:barrier2}]{code/barrier2.yaml}
+
+\subsection{Barrier 3}
+
+We consider the following system:
+\begin{equation*}
+    \begin{bmatrix}
+        {x}_{1, t+1} \\
+        {x}_{2, t+1}
+    \end{bmatrix}
+    = \begin{bmatrix}
+        {x}_{2, t} \\
+        \frac{1}{3} {x}^3_{1, t} - {x}_{1,t} - {x}_{2,t}
+    \end{bmatrix} + w_t,
+\end{equation*}
+where $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$.
+Given
+\begin{align*}
+    &\X = [ -3, 2.5 ] \times [ -2 , 1 ] \\
+    &\X_0 = [ 1 , 2 ] \times [ -0.7 , 0.3 ] \cup [ -1.8 , -1.4 ] \times [ -0.1 , 0.1 ] \\
+    &\qquad \cup [-1.4, -1.2] \times [-0.5 , 0.1] \\
+    &\X_U = [ 0.4 , 0.6 ] \times [ 0.2 , 0.6 ] \cup [ 0.6 , 0.7 ] \times [ 0.2 , 0.4 ],
+\end{align*}
+we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=5$ time steps.
+The complete configuration for the \barrIII benchmark is shown in Listing~\ref{lst:barrier3}.
+\lstinputlisting[language=yaml,caption={Configuration for \barrIII},captionpos=b,label={lst:barrier3}]{code/barrier3.yaml}
+
+\subsection{Overtaking}
+
+We consider a scenario where an autonomous vehicle (AV) controlled by a \gls{nn} is overtaking another vehicle.
+The dynamics of the ego vehicle are given by Dubin's car model \EC{does it need a cit or is it just textbook} by adding the noise vector $w = \begin{bmatrix}w_t^1 & w_t^2 & w_t^3\end{bmatrix}$ where each component is drawn from a zero-mean Gaussian with standard deviation $0.01$, $0.01$, and $0.001$, respectively.
+The steering wheel angle is supplied by the \gls{nn} controller and we travel at a fixed velocity $v=1$.
+Given
+\todo{correct the sets}
+\begin{align*}
+    &\X = [ -3, 2.5 ] \times [ -2 , 1 ] \\
+    &\X_0 = [ 1 , 2 ] \times [ -0.7 , 0.3 ] \cup [ -1.8 , -1.4 ] \times [ -0.1 , 0.1 ] \\
+    &\qquad \cup [-1.4, -1.2] \times [-0.5 , 0.1] \\
+    &\X_U = [ 0.4 , 0.6 ] \times [ 0.2 , 0.6 ] \cup [ 0.6 , 0.7 ] \times [ 0.2 , 0.4 ],
+\end{align*}
+we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=5$ time steps.
+
+The complete configuration for the \overtaking benchmark is shown in Listing~\ref{lst:overtaking}.
+\lstinputlisting[language=yaml,caption={Configuration for \overtaking},captionpos=b,label={lst:overtaking}]{code/overtaking.yaml}

### 2025-07-30 docs/paper/reproducibility checklist/ReproducibilityChecklist.tex
feat: add appendix

@@
 \question{Includes a conceptual outline and/or pseudocode description of AI methods introduced}{(yes/partial/no/NA)}
-Type your response here
+NA
 
 \question{Clearly delineates statements that are opinions, hypothesis, and speculation from objective facts and results}{(yes/no)}
-Type your response here
+yes
 
@@
 \question{Does this paper include computational experiments?}{(yes/no)}
-Type your response here
+yes
 
@@
 	\question{This paper states the number and range of values tried per (hyper-) parameter during development of the paper, along with the criterion used for selecting the final parameter setting}{(yes/partial/no/NA)}
-	Type your response here
+	yes
 
 	\question{Any code required for pre-processing data is included in the appendix}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{All source code required for conducting and analyzing the experiments is included in a code appendix}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{All source code required for conducting and analyzing the experiments will be made publicly available upon publication of the paper with a license that allows free usage for research purposes}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{All source code implementing new methods have comments detailing the implementation, with references to the paper where each step comes from}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{If an algorithm depends on randomness, then the method used for setting seeds is described in a way sufficient to allow replication of results}{(yes/partial/no/NA)}
-	Type your response here
+	yes
 
 	\question{This paper specifies the computing infrastructure used for running experiments (hardware and software), including GPU/CPU models; amount of memory; operating system; names and versions of relevant software libraries and frameworks}{(yes/partial/no)}
-	Type your response here
+	yes
 
@@
 	\question{This paper lists all final (hyper-)parameters used for each model/algorithm in the paper’s experiments}{(yes/partial/no/NA)}
-	Type your response here
+	yes
 

### 2025-07-30 docs/paper/appendix.tex
feat: add configuration

@@
 
-\section{Installation}
-Provided \texttt{Python>=3.8} is already present, \pylucid can be installed with the command
+\section{Tool technical details}
+
+\subsection{Installation}
+\OS{Ernesto, can we organise this in a better order?}
+The recommended way to install \pylucid is via the \texttt{pip} package manager, using one of the pre-built wheels, 
+hence avoiding the time-consuming need to compile the code from source.
+Provided \texttt{Python>=3.8} is already present, installing \pylucid requires only the command
 \begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
@@
 \end{lstlisting}
-There are a few limitation some of the dependencies introduce, which may preclude the ability of using certain features on not supported platforms.
-Formal verification of the barrier requires the \dreal SMT solver, which can only be installed on Linux and non-ARM macOS.
-Support for \highs \gls{lp} is not available on Windows at the moment.
-The \gurobi solver must be installed beforehand, and requires a license for commercial use, but is free for academic purposes.
+If the desired platform's wheel is not available, \pylucid can be installed from source by cloning the repository and running
+\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
+pip install .[gui,plot]
+\end{lstlisting}
+Note that this requires \texttt{Python>=3.8} and \texttt{Bazel>=8.0} to be installed on the system.
+For more details on the installation process, please refer to the online documentation at \url{https://lucidtoolsource.gitlab.io/lucid/md_docs_2Pylucid.html}.
 
-For more details on the installation process, please refer to the online documentation at \url{https://lucidtoolsource.gitlab.io/lucid/md_docs_2Pylucid.html}.
+\subsection{Platform support}
+Some dependencies \pylucid includes do not support all platforms, which may preclude the ability of using certain features.
+Formal verification of the barrier requires the \dreal SMT solver, which can be installed with \lstinline|pip install dreal|, but only supports Linux and non-ARM macOS.
+The \highs \gls{lp} solver cannot be used on Windows at the moment.
+The \gurobi solver must be installed separately beforehand and requires a licence.
+
+\subsection{Configuration formats}
+\pylucid provides extensive support for configuration, which can be specified as a \texttt{.yaml} file (recommended), \texttt{.json} file,
+with a \texttt{.py} file returning a \texttt{Configuration} object, or directly via command line arguments.
+Moreover, sampled transitions can be embedded in the configuration file, or be provided separately with \texttt{.csv}, \texttt{.mat}, \texttt{.npy}, or \texttt{.npz} file.
+For example, following configurations will be equivalent:
+\lstinputlisting[language=yaml,caption={Yaml configuration.},captionpos=b,label={lst:configuration.yaml}]{code/configuration.yaml}
+\lstinputlisting[language=json,caption={Json configuration.},captionpos=b,label={lst:configuration.json}]{code/configuration.json}
+\lstinputlisting[language=iPython,style={nonumbers},caption={Python configuration.},captionpos=b,label={lst:configuration.py}]{code/configuration.py}
+\lstinputlisting[language=bash,style={nonumbers},caption={Command line configuration.
+Assumes that the transition samples have been stored as \texttt{.csv} files.},captionpos=b,label={lst:configuration.sh}]{code/configuration.sh}
+
+\subsection{Graphical User Interface}
+
+\pylucid provides a \gls{gui} to guide the user in the creation of the scenario configuration and presenting the results in an intuitive way.
+Running \lstinline|pylucid-gui| will open a browser tab containing the interface shown in Figures~[\ref{fig:gui-left},\ref{fig:gui-right}], while a local server will listen for requests coming from the \gls{gui}, computing and returning the results.
+\begin{figure}
+    \centering
+    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
+    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
+    The left half of the screen allows the user to provide the transition samples and the safety specification to verify.
+    }
+    \label{fig:gui-left}
+\end{figure}
+\begin{figure}
+    \centering
+    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
+    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
+    The right half of the screen shows the results produced by \lucid, including a plot of the computed barrier function, 
+    the numerical safety guarantee and , and detailed logs of the computations.
+    }
+    \label{fig:gui-right}
+\end{figure}
 
@@
 \begin{align*}
-    &\X = [-1, 1] \\
-    &\X_0 = [-0.5, 0.5] \\
-    &\X_U = [-1, -0.9] \cup [0.9, 1],
+       & \X = [-1, 1]                     \\
+       & \X_0 = [-0.5, 0.5]               \\
+       & \X_U = [-1, -0.9] \cup [0.9, 1],
 \end{align*}
@@
 \begin{align*}
-    &\X = [ -2, 2 ] \times [ -2 , 2 ] \\
-    &\X_0 = \{ [x_1, x_2] : (x_1 + 0.5)^2 + (x_2 - 0.5)^2 \leq 0.4 \} \\
-    &\X_U = \{ [x_1, x_2] : (x_1 - 0.7)^2 + (x_2 + 0.7)^2 \leq 0.3 \},
+       & \X = [ -2, 2 ] \times [ -2 , 2 ]                                  \\
+       & \X_0 = \{ [x_1, x_2] : (x_1 + 0.5)^2 + (x_2 - 0.5)^2 \leq 0.4 \}  \\
+       & \X_U = \{ [x_1, x_2] : (x_1 - 0.7)^2 + (x_2 + 0.7)^2 \leq 0.3 \},
 \end{align*}
@@
 \begin{align*}
-    &\X = [ -3, 2.5 ] \times [ -2 , 1 ] \\
-    &\X_0 = [ 1 , 2 ] \times [ -0.7 , 0.3 ] \cup [ -1.8 , -1.4 ] \times [ -0.1 , 0.1 ] \\
-    &\qquad \cup [-1.4, -1.2] \times [-0.5 , 0.1] \\
-    &\X_U = [ 0.4 , 0.6 ] \times [ 0.2 , 0.6 ] \cup [ 0.6 , 0.7 ] \times [ 0.2 , 0.4 ],
+       & \X = [ -3, 2.5 ] \times [ -2 , 1 ]                                                 \\
+       & \X_0 = [ 1 , 2 ] \times [ -0.7 , 0.3 ] \cup [ -1.8 , -1.4 ] \times [ -0.1 , 0.1 ]  \\
+       & \qquad \cup [-1.4, -1.2] \times [-0.5 , 0.1]                                       \\
+       & \X_U = [ 0.4 , 0.6 ] \times [ 0.2 , 0.6 ] \cup [ 0.6 , 0.7 ] \times [ 0.2 , 0.4 ],
 \end{align*}
@@
 Given
-\todo{correct the sets}
 \begin{align*}
-    &\X = [ -3, 2.5 ] \times [ -2 , 1 ] \\
-    &\X_0 = [ 1 , 2 ] \times [ -0.7 , 0.3 ] \cup [ -1.8 , -1.4 ] \times [ -0.1 , 0.1 ] \\
-    &\qquad \cup [-1.4, -1.2] \times [-0.5 , 0.1] \\
-    &\X_U = [ 0.4 , 0.6 ] \times [ 0.2 , 0.6 ] \cup [ 0.6 , 0.7 ] \times [ 0.2 , 0.4 ],
+       & \X = [ 1, 90 ] \times [ -7, 19 ] \times [ -\pi, \pi ]         \\
+       & \X_0 = [ 1, 3 ] \times [ -1, 1 ] \times [ -0.5, 0.5 ]         \\
+       & \X_U = [ 1, 90 ] \times [ -7, -6 ] \times [ -\pi, \pi ]       \\
+       & \qquad \cup [ 1, 90 ] \times [ 18, 19 ] \times [ -\pi, \pi ]  \\
+       & \qquad \cup [ 40, 45 ] \times [ -6, 6 ] \times [ -\pi, \pi ],
 \end{align*}

### 2025-07-30 docs/paper/main.tex
feat: add configuration

@@
 Hence, for the rest of the paper, we will focus on \pylucid when describing the user interfaces.
-{\color{red}Instructions for installing \lucid are deferred to the appendix.}
+{\color{red}Further information about \pylucid are deferred to the appendix.}
 
@@
 noise sampled from an appropriate distribution, or it may be collected from an external simulator or real-world system.
-The samples can be specified directly in the configuration file:
+The samples can be specified directly in the configuration file, divided into $x^1,\ldots,x^N$ and $x^1_+,\ldots,x^N_+$:
 \begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
@@
 Alternatively, the samples can either be generated programmatically in the user-provided Python configuration script, or be stored in a separate file.
-\pylucid natively supports common formats such as \texttt{.csv}, \texttt{.mat}, \texttt{.npy}, and \texttt{.npz}.
 % Refer to the documentation for more details.
@@
 Being parameter-free approaches, kernel methods do not require the expensive learning processes of other machine learning methods, such as neural networks.
-However, they still depend on a number of \hp, such as the kernel bandwidth $\sigma_f$, the lengthscale $\sigma_l$, and the regularization constant $\lambda$.
+However, they still depend on a number of \hp, such as the kernel bandwidth $\sigma_f$, the lengthscale $\sigma_l$, and the regularization constant $\lambda$ (see \eqref{eq:gaussian_kernel}--\eqref{eq:empiricalEstimate}).
 Changes in their values can have a significant impact on the \estimator's efficiency and accuracy.
@@
 Just say we generate $X$ lattice points?
-"lattice density"}
+"lattice size"}
 \begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
@@
 if the system dynamics are known, \lucid provides the option to formally verify the correctness of the barrier using the \dreal SMT solver~\cite{dreal}.
-Note that \dreal has to be installed separately with \lstinline|pip install dreal| and may not be available on all systems.
 
@@
 All runs had the random seed set to $42$ to ensure reproducibility.
+The results of all experimental results are summarized in Table~\ref{tbl:benchmarks_results}.
+\begin{table}[tb]
+    \centering
+    \begin{tabular}{ccccc}
+        \toprule
+        \textbf{Benchmark} & \textbf{Dim} & \textbf{Lattice} & \textbf{Runtime} & \textbf{Safety} \\
+                           &              & \textbf{Size} & [mm:ss]          & \textbf{Probability}                  \\ % Units
+        \midrule
+        Linear             & 1            & $?$              & 00:02            & 95.15\%                 \\
+        Barr2              & 2            & $350^2$           & 14:42            & 75.34\%                    \\
+        Barr3              & 2            & $30^2$           & XX:XX            & XX\%                    \\
+                           &              & $40^2$           & XX:XX            & XX\%                    \\
+                           &              & $?^2$            & XX:XX            & XX\%                    \\
+        Overtaking         & 3            & $?^3$            & XX:XX            & XX\%                    \\
+                           & 3            & $?^3$            & XX:XX            & XX\%                    \\
+                           & 3            & $?^3$            & XX:XX            & XX\%                    \\
+        name2              & 7            &                  & XX:XX            & XX\%                    \\
+        \bottomrule
+    \end{tabular}
+    \caption{Computational benchmarks: ...}
+    \label{tbl:benchmarks_results}
+\end{table}
 
@@
 
-Overview of the experimental results in Table~\ref{tbl:benchmarks_results}.
-\begin{table}[tb]
-    \centering
-    \begin{tabular}{ccccc}
-        \toprule
-        \textbf{Benchmark} & \textbf{Dim} & \textbf{Lattice} & \textbf{Runtime} & \textbf{Safety Prob.} \\
-                           &              & \textbf{Density} & [mm:ss]          & [\%]                  \\ % Units
-        \midrule
-        Linear             & 1            & $?$              & 00:02            & 95.15                 \\
-        Barr3              & 2            & $30^2$           & XX:XX            & XX                    \\
-                           &              & $40^2$           & XX:XX            & XX                    \\
-                           &              & $?^2$            & XX:XX            & XX                    \\
-        Overtaking         & 3            & $?^3$            & XX:XX            & XX                    \\
-                           & 3            & $?^3$            & XX:XX            & XX                    \\
-                           & 3            & $?^3$            & XX:XX            & XX                    \\
-        name2              & 7            &                  & XX:XX            & XX                    \\
-        \bottomrule
-    \end{tabular}
-    \caption{Computational benchmarks: ...}
-    \label{tbl:benchmarks_results}
-\end{table}
-
 \begin{figure}

### 2025-07-30 docs/paper/code/configuration.py

@@ -1,0 +1,20 @@
+from pylucid import *
+import numpy as np
+
+def scenario_config() -> Configuration:
+    np.random.seed(42)
+    random.seed(42)
+    c = Configuration()
+    c.seed = 42
+    c.X_bounds = RectSet([(-1, 1)])
+    c.X_init = RectSet([(-0.5, 0.5)])
+    c.X_unsafe = MultiSet(RectSet([(-1, -0.9)]), RectSet([(0.9, 1)]))
+    c.x_samples = np.array([[1.0], [-1.0]])
+    c.xp_samples = np.array([[0.5], [-0.5]])
+    c.lambda_ = 1.0e-5
+    c.time_horizon = 15
+    c.sigma_f = 18.0
+    c.sigma_l = 0.034
+    c.num_frequencies = 5
+    c.oversample_factor = 64.0
+    return c

### 2025-07-30 docs/paper/code/configuration.sh

@@ -1,0 +1,13 @@
+pylucid \ 
+  --seed 42 \
+  --X_bounds "RectSet([-1], [1])" \
+  --X_init "RectSet([-0.5], [0.5])" \
+  --X_unsafe "MultiSet([RectSet([-1], [-0.9]), RectSet([0.9], [1])])" \
+  --lambda "1.0e-5" \
+  --time_horizon 15 \
+  --sigma_f 18.0 \
+  --sigma_l 0.034 \
+  --num_frequencies 5 \
+  --oversample_factor 64.0 \
+  -i x_samples.csv \
+  -o xp_samples.csv

### 2025-07-30 benchmarks/integration/TuneDcMotor.py
chore: try openmp (wip)

@@ -1,4 +1,4 @@
-from ScenarioTuner import scenario_tuner, Parameter
+from hp_tuning import hp_tuning, Parameter
 import numpy as np
 import itertools
 

### 2025-07-30 lucid/main.cpp

@@ -9,6 +9,7 @@
 
 #include <chrono>
 #include <iostream>
+#include <numbers>
 #include <span>
 #include <string>
 #include <utility>
@@ -194,6 +195,54 @@ struct CliArgs {
   Solver solver{Solver::Gurobi};
 };
 
+bool test_overtaking(const CliArgs& args) {
+  const long long start_time = std::chrono::steady_clock::now().time_since_epoch().count();
+  random::seed(args.seed);
+
+  const RectSet X_bounds{{{1, 90}, {-7, 19}, {-std::numbers::pi, std::numbers::pi}}};
+  const RectSet X_init{{{1, 2}, {-0.5, 0.5}, {-0.005, 0.005}}};
+  const MultiSet X_unsafe{RectSet{{1, 90}, {-7, -6}, {-std::numbers::pi, std::numbers::pi}},
+                          RectSet{{1, 90}, {18, 19}, {-std::numbers::pi, std::numbers::pi}},
+                          RectSet{{40, 45}, {-6, 6}, {-std::numbers::pi, std::numbers::pi}}};
+
+  const Matrix x_samples{X_bounds.sample(1000)};
+  const Matrix xp_samples{x_samples + Matrix::Constant(x_samples.rows(), x_samples.cols(), 0.1)};
+  KernelRidgeRegressor estimator{std::make_unique<GaussianKernel>(args.sigma_l, args.sigma_f), args.lambda};
+  LinearTruncatedFourierFeatureMap feature_map{args.num_frequencies, args.sigma_l, args.sigma_f, X_bounds};
+
+  const Matrix f_xp_samples{feature_map(xp_samples)};
+
+  const int n_per_dim = args.num_oversample < 0
+                            ? static_cast<int>(std::ceil((2 * args.num_frequencies + 1) * args.oversample_factor))
+                            : args.num_oversample;
+  LUCID_DEBUG_FMT("Number of samples per dimension: {}", n_per_dim);
+  LUCID_ASSERT(n_per_dim > 2 * args.num_frequencies,
+               "n_per_dim must be greater than nyquist (2 * num_freq_per_dim + 1)");
+
+  LUCID_DEBUG_FMT("Estimator pre-fit: {}", estimator);
+  estimator.fit(x_samples, f_xp_samples);
+  LUCID_INFO_FMT("Estimator post-fit: {}", estimator);
+
+  LUCID_DEBUG_FMT("Feature map: {}", feature_map);
+
[…]

### 2025-07-30 lucid/main.cpp
feat: add openMP support for Eigen speedup

@@ -205,7 +205,7 @@ bool test_overtaking(const CliArgs& args) {
                           RectSet{{1, 90}, {18, 19}, {-std::numbers::pi, std::numbers::pi}},
                           RectSet{{40, 45}, {-6, 6}, {-std::numbers::pi, std::numbers::pi}}};
 
-  const Matrix x_samples{X_bounds.sample(1000)};
+  const Matrix x_samples{X_bounds.sample(args.num_samples)};
   const Matrix xp_samples{x_samples + Matrix::Constant(x_samples.rows(), x_samples.cols(), 0.1)};
   KernelRidgeRegressor estimator{std::make_unique<GaussianKernel>(args.sigma_l, args.sigma_f), args.lambda};
   LinearTruncatedFourierFeatureMap feature_map{args.num_frequencies, args.sigma_l, args.sigma_f, X_bounds};
@@ -380,16 +380,16 @@ int main(const int argc, char* argv[]) {
       .seed = 42,
       .gamma = 1.0,
       .time_horizon = 5,
-      .num_samples = 1000,
+      .num_samples = 500,
       .lambda = 1e-3,
       .sigma_f = 15.0,
       .sigma_l = 1.75555556,
-      .num_frequencies = 4,
+      .num_frequencies = 8,
       .plot = true,
       .verify = true,
       .problem_log_file = log_file,
       .iis_log_file = "iis.ilp",
-      .oversample_factor = 32.0,
+      .oversample_factor = 2.0,
       .noise_scale = 0.01,
       .solver = solver,
   });

### 2025-07-31 benchmarks/integration/TuneBarrier2.py
chore: change system_dynamics

@@ -5,7 +5,7 @@ import itertools
 
 
 if __name__ == "__main__":
-    val = np.logspace(-3, 2, num=10, endpoint=True, dtype=float)
+    val = np.logspace(-5, 5, num=10, endpoint=True, dtype=float)
 
     grid = {
         Parameter.REGULARIZATION_CONSTANT: [1.0e-6],
@@ -13,4 +13,4 @@ if __name__ == "__main__":
         Parameter.SIGMA_L: [np.array(x) for x in itertools.product(val, val)],
     }
 
-    scenario_tuner("benchmarks/integration/barrier2.yaml", grid)
+    hp_tuning("benchmarks/integration/barrier2.yaml", grid)

### 2025-07-31 benchmarks/integration/TuneBarrier3.py

@@ -5,7 +5,7 @@ import itertools
 
 
 if __name__ == "__main__":
-    val = np.logspace(-3, 2, num=10, endpoint=True, dtype=float)
+    val = np.logspace(-35, 5, num=10, endpoint=True, dtype=float)
 
     grid = {
         Parameter.REGULARIZATION_CONSTANT: [1.0e-6],
@@ -13,4 +13,4 @@ if __name__ == "__main__":
         Parameter.SIGMA_L: [np.array(x) for x in itertools.product(val, val)],
     }
 
-    scenario_tuner("benchmarks/integration/barrier3.yaml", grid)
+    hp_tuning("benchmarks/integration/barrier3.yaml", grid)

### 2025-07-31 bindings/pylucid/plot.py

@@ -566,6 +566,7 @@ def plot_estimator_2d(
         fig.show()
     return fig
 
+
 def plot_estimator_22d(
     estimator: "Estimator",
     x_samples: "NMatrix",
@@ -617,6 +618,7 @@ def plot_estimator_22d(
     if show:
         fig.show()
     return fig
+
 
 def plot_feature_map(
     feature_map: "FeatureMap",
@@ -694,9 +696,7 @@ def plot_estimator(
             estimator, x_samples, xp_samples, X_bounds, X_init, X_unsafe, show
         )
     elif x_samples.shape[1] == 2 and xp_samples.shape[1] == 2:
-        return plot_estimator_22d(
-            estimator, x_samples, xp_samples, X_bounds, X_init, X_unsafe, show
-        )
+        return plot_estimator_22d(estimator, x_samples, xp_samples, X_bounds, X_init, X_unsafe, show)
     raise exception.LucidNotSupportedException(
         f"Plotting is not supported for {x_samples.shape[1]} => {xp_samples.shape[1]}-dimensional sets. "
         f"Only (1D or 2D) => 1D are supported."

### 2025-07-31 benchmarks/integration/Barrier2.py
chore: update benchmark configuraitons

@@ -68,12 +68,11 @@ if __name__ == "__main__":
 
     grid = {
         # "num_frequencies": [9, 12, 13, 16, 17],
-        "num_frequencies": [15],
+        "num_frequencies": [20],
         # "num_frequencies": [4],
-        "c_coefficient": [1.0],
         "time_horizon": [5],
         # "oversample_factor": [10.0, 20.0, 30.0],
-        "num_oversample": [250, 300, 350],
+        "num_oversample": [300],
         # "oversample_factor": [10.0],
     }
 

### 2025-07-31 benchmarks/integration/Barrier3.py

@@ -59,12 +59,10 @@ if __name__ == "__main__":
 
     grid = {
         # "num_frequencies": [9, 12, 13, 16, 17],
-        "num_frequencies": [30],
+        "num_frequencies": [12, 14, 16],
         # "num_frequencies": [4],
-        "c_coefficient": [1.0],
         "time_horizon": [5],
-        "oversample_factor": [5.0],
-        # "num_oversample": [350],
+        "num_oversample": [370],
         # "oversample_factor": [10.0],
     }
 

### 2025-07-31 benchmarks/integration/plot_solution.py
feat: add plot utility

@@ -1,0 +1,345 @@
+import json
+import numpy as np
+from pathlib import Path
+
+from pylucid import *
+from pylucid.dreal import verify_barrier_certificate
+from pylucid import random
+import matplotlib.pyplot as plt
+
+
+def plot_solution_matplotlib(
+    args: "argparse.Namespace",
+    X_bounds: "RectSet",
+    X_init: "Set | None" = None,
+    X_unsafe: "Set | None" = None,
+    feature_map: "FeatureMap | None" = None,
+    sol: "NVector | None" = None,
+    eta: "float | None" = None,
+    gamma: "float | None" = None,
+    estimator: "Estimator | None" = None,
+    f: "Callable[[NMatrix], NMatrix] | None" = None,
+    c: "float" = 0.0,
+    num_samples: "int | None" = None,
+    show: bool = True,
+) -> plt.Figure:
+    assert X_bounds.dimension > 0, "X_bounds must have a positive dimension."
+    plot_solution_fun = (plot_solution_1d_matplotlib, plot_solution_2d_matplotlib)
+    if X_bounds.dimension <= len(plot_solution_fun):
+        return plot_solution_fun[X_bounds.dimension - 1](
+            args, X_bounds, X_init, X_unsafe, feature_map, sol, eta, gamma, estimator, f, c, num_samples, show
+        )
+    raise exception.LucidNotSupportedException(
+        f"Plotting is not supported for {X_bounds.dimension}-dimensional sets. Only 1D and 2D are supported."
+    )
+
+
+def plot_solution_1d_matplotlib(
+    args: "argparse.Namespace",
+    X_bounds: "RectSet",
+    X_init: "Set | None" = None,
+    X_unsafe: "Set | None" = None,
+    feature_map: "FeatureMap | None" = None,
+    sol: "NVector | None" = None,
+    eta: "float | None" = None,
+    gamma: "float | None" = None,
+    estimator: "Estimator | None" = None,
+    f: "callable | None" = None,
+    c: float = 0.0,
+    num_samples: "int | None" = None,
+    show: bool = True,
+):
+    """
+    Alternative to plot_solution_1d using matplotlib instead of plotly.
+    """
+
+    # use an interactive backend if available
+
+    fig, ax = plt.subplots()
+    ax.set_xlim([X_bounds.lower_bound[0], X_bounds.upper_bound[0]])
+    # Scale the y-axis to fit the plot to make the plot shorter
[…]

### 2025-07-31 benchmarks/integration/hp_tuning.py
chore: demote log to debug

@@ -36,7 +36,6 @@ def lbfgs_tuner(config: Configuration):
 
 def grid_search_tuner(config: Configuration, grid: "dict[Parameter, ParameterValuesType]"):
     tuner = GridSearchTuner(parameters=grid)
-    log.set_verbosity(log.LOG_WARN)
     tuner.tune(
         config.estimator,
         config.x_samples,
@@ -45,7 +44,6 @@ def grid_search_tuner(config: Configuration, grid: "dict[Parameter, ParameterVal
         config.num_frequencies,
         config.X_bounds,
     )
-    log.set_verbosity(log.LOG_INFO)
     score_estimator(config)
 
 

### 2025-07-31 lucid/model/TruncatedFourierFeatureMap.cpp

@@ -41,7 +41,7 @@ TruncatedFourierFeatureMap::TruncatedFourierFeatureMap(const int num_frequencies
 
   const Vector prod{combvec(prob_dim_wise).colwise().prod()};
   if (captured_probability_ = prod.sum(); captured_probability_ > 0.94)
-    LUCID_INFO_FMT("Probability captured by Fourier expansion is {:.3f} percent", captured_probability_);
+    LUCID_DEBUG_FMT("Probability captured by Fourier expansion is {:.3f} percent", captured_probability_);
   else
     LUCID_WARN_FMT("Probability captured by Fourier expansion is only {:.3f} percent", captured_probability_);
 

### 2025-07-31 docs/paper/appendix.tex
feat: update paper

@@
 \begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
-pip install pylucid[gui,plot] --index-url \
+pip install "pylucid[gui,plot]" --index-url \
   https://gitlab.com/api/v4/projects/71977529/packages/pypi/simple
 \end{lstlisting}
-If the desired platform's wheel is not available, \pylucid can be installed from source by cloning the repository and running
+If the desired platform's wheel is not available, \pylucid can be installed from source running the following commands:
 \begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
+git clone https://gitlab.com/lucidtoolsource/lucid.git
+cd lucid
 pip install .[gui,plot]
@@
 \pylucid provides a \gls{gui} to guide the user in the creation of the scenario configuration and presenting the results in an intuitive way.
-Running \lstinline|pylucid-gui| will open a browser tab containing the interface shown in Figures~[\ref{fig:gui-left},\ref{fig:gui-right}], while a local server will listen for requests coming from the \gls{gui}, computing and returning the results.
+Running \lstinline|pylucid-gui| will open a browser tab containing the interface shown in Figures~\ref{fig:gui-left}--\ref{fig:gui-right}, while a local server will listen for requests coming from the \gls{gui}, computing and returning the results.
 \begin{figure}

### 2025-07-31 docs/paper/figures/architecture.tex
feat: update paper

@@
         \node[block, left=of estimator] (sets) {\Circled{1} Safety Specification};
-        \node[block, below=of estimator] (feature) {\Circled{4} Feature Map}; % / Barrier template
-        \node[block, left=of feature] (optimizer) {\Circled{5} Solver};
+        \node[block, below=of estimator, text width=2.4cm] (feature) {\Circled{4} Feature Map}; % / Barrier template
+        \node[block, left=.4cm of feature] (optimizer) {\Circled{5} Solver};
         % \node[block, below=of optimizer] (verifier) {Verifier};

### 2025-07-31 docs/paper/main.tex
feat: update paper

@@
 Embodied forms of AI are on the rise, including applications such as autonomous vehicles, robotics, personalized healthcare, and smart infrastructure.
-Their core functionality is build around the advances of deep learning, enabling systems to understand and reason in complex and human-like ways to produce a desired behavior.
+Their core functionality is built around the advances of deep learning, enabling systems to understand and reason in complex and human-like ways to produce a desired behavior.
 Whilst the black-box nature of AI components has been a crucial contributor to the widespread success of deep learning, in response to a rapidly evolving legal scrutinization~\cite{veale2021demystifying}, the resulting lack of traceability and certifiability has put a premature halt to its deployment in safety-critical applications.
@@
 Unfortunately, there do not exist any tools that could take these results and certify the safety of the entire system, as uncertainty-aware models of closed-loop systems are rarely available and simulators are often too complicated and opaque to perform verification directly~\cite{wongpiromsarn2023formal}.
-This motivates a holistic black-box treatment~\cite{corso2021survey}, where safety guarantees are to be established from behavioral data and in account of the unknown uncertainty.
+This motivates a holistic black-box treatment~\cite{corso2021survey}, where safety guarantees are to be established from behavioral data and in account of the unknown laws of randomness themselves.
 
@@
 Few data-driven approaches for stochastic systems exist. 
-\omnisafe is a comprehensive platform for the development of safe \gls{rl} algorithms~\citet{ji2024omnisafe}.
+\omnisafe is a comprehensive platform for the development of safe \gls{rl} algorithms~\cite{ji2024omnisafe}.
 However, safe \gls{rl} does generally only \emph{encourage} safer behavior, without providing any rigorous or quantified guarantees on the probability of the absence of unsafe behavior.
-As a popular working principle for certifying safety, \glspl{cbc}~\cite{prajna2006barrier} are at the basis of tools such as \trust~\cite{gardner2025trust} (supports only polynomial dynamics) and \fossil~\cite{edwards2024fossil} (model-based), which are restricted to deterministic systems.
+As a popular working principle for certifying safety, \glspl{cbc}~\cite{prajna2006barrier} are at the basis of tools such as \trust~\cite{gardner2025trust}, which supports only polynomial dynamics, and \fossil~\cite{edwards2024fossil}, which is model-based, and both being restricted to deterministic systems.
 
 To close this gap (see Table~\ref{tab:qualitative_comparison}), we introduce \lucid, the first verification engine for black-box stochastic dynamical systems with quantified guarantees.
+At its core, \lucid learns \glspl{cbc} for unknown systems based solely on data, by constructing an uncertainty-aware estimator of the expected system behavior based on \glspl{cme}~\cite{muandet2017kernel}.
+Crucially, the underlying learning framework establishes quantified safety probabilities with distributionally robust guarantees for arbitrary smooth dynamics, thus relaxing the need for restrictive structural assumptions common to related approaches.
+For instance, \citet{schoen2024distributionally} learn \glspl{cbc} for systems with polynomial dynamics and \citet{chen2025distributionally} assume systems with known deterministic component.
 \begin{table}
@@
         \textbf{Tool}                                    & \multicolumn{6}{c}{\textbf{Supported Features}}                                                                                                                                                             \\[.4em]
-                                                         & \rotatebox{90}{Guarantees}                      & \rotatebox{90}{Data Driven} & \rotatebox{90}{Stochastic D.} & \rotatebox{90}{Non-Poly.
-D.} & \rotatebox{90}{Stat.
+                                                         & \rotatebox{90}{Guarantees}                      & \rotatebox{90}{Data Driven} & \rotatebox{90}{Stochastic Dyn.} & \rotatebox{90}{Non-Poly.
+Dyn.} & \rotatebox{90}{Stat.
 Correct.} & \rotatebox{90}{Closed Loop} \\
@@
 \footnotetext[2]{Accepts non-deterministic bounded disturbances.} % npinterval
-At its core, it learns \glspl{cbc} for unknown systems based solely on data, by constructing an uncertainty-aware estimator of the expected system behavior based on \glspl{cme}~\cite{muandet2017kernel}.
-Crucially, the underlying learning framework establishes quantified safety probabilities with distributionally robust guarantees for arbitrary smooth dynamics, thus relaxing the need for restrictive structural assumptions common to related approaches.
-For instance, \citet{schoen2024distributionally} learn \glspl{cbc} for systems with polynomial dynamics and \citet{chen2025distributionally} assume systems with known deterministic component.
+
 %
@@
 \paragraph{Organization}
-The paper is organized as follows:
+The paper is organized as follows.
 Section~\ref{sec:theory} provides the theoretical foundations of \lucid, including the safety of black-box dynamical systems, control barrier certificates, conditional mean embeddings, and derivation of the relaxed linear program.
@@
 % Section~\ref{sec:example} presents a simple example use case, demonstrating how to use \lucid to certify the safety of a simple linear system.
-Section~\ref{sec:experiments} evaluates \lucid on a suite of benchmarks. Finally, Sections~\ref{sec:future_extensions} and \ref{sec:conclusion} provide future extensions and a conclusion.
+Section~\ref{sec:experiments} evaluates \lucid on a suite of benchmarks. Finally, Section~\ref{sec:conclusion_and_future_extensions} provides a conclusion and future extensions.
 
@@
 \begin{equation}
-    \data_N\colon \quad \{x^i,a^i,x^i_+\}_{i=1}^N,\label{eq:data}
+    \data_N\colon \quad \{(x^i,a^i,x^i_+)\}_{i=1}^N,\label{eq:data}
 \end{equation}
-where every sample transition from $x^i\in\X$ to a successor $x^i_+\in\X$ is generated as a realization
+where every sampled transition from $x^i\in\X$ to a successor $x^i_+\in\X$ is generated as a realization
 \begin{equation*}
-    (x^i,a^i,x_+^i)\sim\int \delta_{f(x^i,a^i,w)}\,p_w(dw)\,\mathcal{U}_\X(dx^i)\,\mathcal{U}_\A(da^i),
+    (x^i,a^i,x_+^i)\sim\int \delta_{f(x^i,a^i,w)}(dx_+^i)\,p_w(dw)\,\mathcal{U}_\X(dx^i)\,\mathcal{U}_\A(da^i),
 \end{equation*}
-with $\mathcal{U}_\X,\mathcal{U}_\A$ uniform distributions on $\X$ and $\A$, respectively.
+with $\mathcal{U}_\X$ and $\mathcal{U}_\A$ uniform distributions on $\X$ and $\A$, respectively, and $\delta$ indicating the Dirac delta distribution capturing the system dynamics.
 
@@
 A question that often arises when designing a policy $\pi$ for a system $\S$, especially in engineering contexts, is if the closed-loop system $\S^\pi$ elicits safe behavior.
-That is, when operating in some operating domain $\X_{0}\subset\X$ under a policy $\pi$, the system $\S^\pi$ shall avoid unsafe regions $\X_U\subset\X$ (such as obstacles) for at least some predefined control horizon $T\in\N\cup\{\infty\}$.
+That is, when starting from a domain $\X_{0}\subset\X$ under a policy $\pi$, the system $\S^\pi$ shall avoid unsafe regions $\X_U\subset\X$ (such as obstacles) for at least some predefined time horizon $T\in\N\cup\{\infty\}$.
 
-Such safety problems are tricky and even for the case where an explicit model \eqref{eq:model} is given, certifying safety of a discrete-time stochastic system over an uncountable state space does not generally admit an analytical solution and is extremely challenging, especially for complex dynamics~\cite{abate2008probabilistic}.
-Even more, for unbounded stochasticity $w_t\sim p_w$, there is generally no deterministic answer (safe or not), but a safety probability $P_{\text{safe}}(\S^\pi)\in[0,1)$.
+%Such safety problems are tricky and even for the case where an explicit model \eqref{eq:model} is given, 
+Certifying safety of a discrete-time stochastic system over an uncountable state space does not generally admit an analytical solution and is extremely challenging, especially for complex dynamics~\cite{abate2008probabilistic}.
+Furthermore, for unbounded stochasticity $w_t\sim p_w$, there is generally no yes/no answer to safety, but a safety probability $P_{\text{safe}}(\S^\pi)\in[0,1)$.
 Thus the goal is generally to estimate a \emph{lower bound} on the true safety probability $P_{\text{safe}}(\S^\pi)$.
@@
 
-A non-negative function $\B\colon\X\rightarrow\R_{\geq 0}$ is a \gls{cbc} of a system $\S$ with reference to an unsafe set $\X_U$, if it satisfies
+A non-negative function $\B\colon\X\rightarrow\R_{\geq 0}$ is a \gls{cbc} of a system $\S$ with reference to an unsafe set $\X_U$ if it satisfies
 \begin{itemize}
@@
 \end{equation}
-where $T$ is the desired control horizon.
+where $T$ is the desired time horizon.
 Notably, the system dynamics only enters the barrier conditions through the conditional expectation in (c), and a \gls{cbc} thus only depends on the \emph{expected} system behavior, with no need to consider its concrete stochastic law.
@@
 Following the same reasoning, the \emph{kernel mean embedding} represents the projection of a probability measure into a \gls{rkhs} via a feature map $\phi$ associated with a positive definite kernel $k$~\cite{Smola2007EmbedDistrb,muandet2017kernel}.
-For conditional probability distributions a similar concept exists: \glspl{cme} can be used to model the expected value of any \gls{rkhs} function $f\colon\X\rightarrow\R$ under a stochastic process such as $\S$~\cite{park2020measuretheoretic,muandet2017kernel}.
+For conditional probability distributions a similar concept exists: \glspl{cme} can be used to model the expected value of any \gls{rkhs} function $\new{g}\colon\X\rightarrow\R$ under a stochastic process such as $\S$~\cite{park2020measuretheoretic,muandet2017kernel}.
 For the Gaussian kernel,
@@
 \end{equation}
-where $\Sigma:=\diag(\sigma_l)^{-2}$, with hyperparameters $\sigma_f,\sigma_l\in\R$, this encompasses all smooth functions $f$.
+where $\Sigma:=\diag(\sigma_l)^{-2}$, with hyperparameters $\sigma_f,\sigma_l\in\R$, \new{the associated RKHS encompasses all smooth functions $g$}.
 A data-driven estimate can then be obtained in closed form from a finite amount of data $\data_N$:
@@
         % \innerH{f}{\hat{\Psi}^N_{X^+|X}(x)}{\Hilbert_{k}} = 
-         & \hspace{5em} k_{XA}^N(x,a)\T\left[ K_{XU}^N+N \lambda I_N\right]^{-1}\! f(X_+^N),
+         & \hspace{5em} k_{XA}^N(x,a)\T\left[ K_{XA}^N+N \lambda I_N\right]^{-1}\! f(X_+^N),
     \end{split}\label{eq:empiricalEstimate}
@@
 The result is a distributionally robust estimator with an adjustable robustness radius.
-The details are omitted here for brevity, but the interested reader is referred to~\citet{kuhn2025distributionally,li2022optimal}.
+The details are omitted here for brevity, but the interested reader is referred to the works by \citet{kuhn2025distributionally} and \citet{li2022optimal}.
 
 \subsection{Data-Driven Spectral Barriers}\label{sec:ddbarriers}
-Based on the data-driven estimator in \eqref{eq:empiricalEstimate}, the problem of computing \glspl{cbc} based on data can be formulated as a nonconvex semi-infinite program, which for general classes of systems and barriers is extremely difficult to solve.
+Based on the data-driven estimator in \eqref{eq:empiricalEstimate}, the problem of computing \glspl{cbc} using data can be formulated as a nonconvex semi-infinite program, which for general classes of systems and barriers is extremely difficult to solve.
 To arrive at a tractable solution, \lucid conducts two additional steps:
@@
 \end{align*}
-Notably, $\B$ admits the linear form $B(x)=b\T\phi_M(x)$, with a truncated Fourier feature map $\phi_M\colon\X\rightarrow\R^{2M+1}$, parametrized by learnable spectral amplitudes
+Notably, $\B$ admits the linear form \new{$B(x)=\phi_M(x)\T b$}, with a truncated Fourier feature map $\phi_M\colon\X\rightarrow\R^{2M+1}$, parametrized by learnable spectral amplitudes
 \begin{figure}
@@
     \includegraphics[width=\linewidth]{fourier_series.pdf}
-    \caption{Spectral barrier certificate $B(x)=b\T\phi_M(x)$}
+    \caption{Spectral barrier certificate \new{$B(x)=\phi_M(x)\T b$}.}
     \label{fig:spectral_barrier}
@@
     b\!=\!\begin{bmatrix}
-              \frac{\alpha_0}{\sigma_f^2w_0^2}\!
-& \frac{\alpha_1}{2\sigma_f^2w_1^2}\!\!
-& \frac{\beta_1}{2\sigma_f^2w_1^2}\!\!
-& \ldots\!\!
-& \frac{\alpha_{M}}{2\sigma_f^2w_{M}^2}\!\!
-& \frac{\beta_{M}}{2\sigma_f^2w_{M}^2}
+              \frac{\alpha_0}{\sigma_f^2\w_0^2}\!\!
+& \frac{\alpha_1}{2\sigma_f^2\w_1^2}\!\!\!
+& \frac{\beta_1}{2\sigma_f^2\w_1^2}\!\!\!
+& \ldots\!\!\!
+& \frac{\alpha_{M}}{2\sigma_f^2\w_{M}^2}\!\!\!
+& \frac{\beta_{M}}{2\sigma_f^2\w_{M}^2}
           \end{bmatrix}\T\!\!\!\!\in\R^{2M+1}\!\!,
 \end{align*}
-where the weights $w_0,\ldots,w_{M}\in\R_{\geq 0}$ associated with each frequency band are determined efficiently from the kernel's Gaussian spectral measure via the multivariate CDF (see Figure~\ref{fig:spectral_measure_abstraction}).
+where the weights $\w_0,\ldots,\w_{M}\in\R_{\geq 0}$ associated with each frequency band are determined efficiently from the kernel's Gaussian spectral measure via the multivariate CDF (see Figure~\ref{fig:spectral_measure_abstraction}).
 The \gls{cme}-based estimator \eqref{eq:empiricalEstimate} is approximated in the same finite basis via $H\in\R^{(2M+1)\times (2M+1)}$ such that
 \begin{equation*}
-    k_{XA}^N(x,a)\T\left[ K_{XU}^N+N \lambda I_N\right]^{-1}\! \Phi_{M,+}^N
+    k_{XA}^N(x,a)\T\left[ K_{XA}^N+N \lambda I_N\right]^{-1}\! \Phi_{M,+}^N
     \approx
-    \phi_M{\color{red}(x,a)}\T H,
+    \new{\varphi_M(x,a)}\T H,
 \end{equation*}
-where $\Phi_{M,+}^N:=[\phi_M(x_+^i)\T]_{i=1}^N$,
+where $\Phi_{M,+}^N:=[\phi_M(x_+^i)\T]_{i=1}^N$, \new{$\varphi_M(x,a)\colon\X\times\A\rightarrow\smash{\R^{2M+1}}$ a feature map augmenting $\phi_M(x)$}, and
 with an approximation error decreasing exponentially with $M$~\cite{rahimi2007random}.
@@
     \item[(b)] $\forall x_U\in \X_U\colon\,\phi_M(x_U)\T b\geq\gamma$; and
-    \item[(c)] $\forall x\in\X,\,\exists a\in\A\colon\,\phi_M{\color{red}(x,a)}\T (Hb -b) \leq  c.$
+    \item[(c)] $\forall x\in\X,\,\exists a\in\A\colon\,\new{\varphi_M(x,a)}\T (Hb -b) \leq  c.$
 \end{itemize}
+\new{For the case where $a$ is provided by a given fixed policy $\pi$, $\varphi_M(x,a)$ reduces to $\phi_M(x)$.}
 % \OS{Importantly, the closed-form estimator in \eqref{eq:empiricalEstimate} does not depend on the choice of features and only through the spectral abstraction is the feature map introduced directly.}
@@
             \node[scale=1.0] (w0)
-            at ({\B+.5*\Bs},{.125}) {$w_0^2$};
+            at ({\B+.5*\Bs},{.125}) {$\w_0^2$};
             \node (b0) at ({\B+.25*\Bs},{.08}) {};
@@
             \node[scale=1.0] (w1)
-            at ({\B+1.5*\Bs},{.085}) {$\frac{w_1^2}{2}$};
+            at ({\B+1.5*\Bs},{.085}) {$\frac{\w_1^2}{2}$};
             \node (b1) at ({\B+1.25*\Bs},{.04}) {};
@@
             \node[scale=1.0] (w2)
-            at ({\B+2.5*\Bs},{.055}) {$\frac{w_2^2}{2}$};
+            at ({\B+2.5*\Bs},{.055}) {$\frac{\w_2^2}{2}$};
             \node (b2) at ({\B+2.25*\Bs},{.01}) {};
@@
             \node[scale=1.0] (w3)
-            at ({\B+3.5*\Bs},{.046}) {$\frac{w_3^2}{2}$};
+            at ({\B+3.5*\Bs},{.046}) {$\frac{\w_3^2}{2}$};
             \node (b3) at ({\B+3.25*\Bs},{.001}) {};
@@
 Recall that given an appropriate robustness radius, the barriers produced by \lucid based on data $\data_N$ are statistically correct with respect to the unknown true system $\S$, and a lower bound for the safety probability is computed according to \eqref{eq:safety_prob_lb}.
+%\Sadegh{Just to double check: we are not making the third inequality more conservative related to CME.} \OS{Not currently implemented.}
 
@@
 For a list of all available options, run \lstinline|pylucid --help|.
+\Sadegh{space needs fixing before ".. to start ...".}
 
 In its current form, \lucid implements all the functionalities needed to certify safety of a closed-loop system with a given control policy $\pi$.
+\OS{Thus the action $a$ in the previous section is replaced with the policy $\pi(x)$.}
 Future releases will expand this core functionality to 
 safe controller synthesis as well.
-Due to its modular architecture, \lucid can be easily extended in multiple directions, as outlined in Section~\ref{sec:future_extensions}.
+Due to its modular architecture, \lucid can be easily extended in multiple directions, as outlined in Section~\ref{sec:conclusion_and_future_extensions}.
 
@@
           The \texttt{LbfgsTuner} uses the L-BFGS or L-BFGS-B quasi-Newton optimization algorithms~\cite{book:nonlinear-programming},
-          implemented in the \texttt{LBFGS++} library\footnote{https://github.com/yixuan/LBFGSpp}.
-    \item \texttt{GridSearchTuner} implements the grid search method, exploring the space of possible \hp values to find the one that maximizes the \estimator's $R^2$ score, defined as $R^2 = 1 - (\sum_{i=1}^M (y_i - \hat{y}_i)^2/\sum_{i=1}^M (y_i - \bar{y})^2)$.
+          implemented in the \texttt{LBFGS++} library.\footnote{https://github.com/yixuan/LBFGSpp}
+    \item \texttt{GridSearchTuner} implements the grid search method, exploring the space of possible \hp values to find the one that maximizes the \estimator's $R^2$ score, defined as $$R^2 = 1 - (\sum_{i=1}^M (y_i - \hat{y}_i)^2/\sum_{i=1}^M (y_i - \bar{y})^2).$$
 \end{itemize}
@@
 
-Generating the \gls{lp}, specifically choosing an appropriate lattice density, involves trading off efficiency versus conservativeness (see Section~\ref{sec:ddbarriers}), with any sampling density beyond the Nyquist frequency yielding a valid relaxation.
+Generating the \gls{lp}, specifically choosing an appropriate lattice density, involves trading off efficiency versus conservativeness, with any sampling density beyond the Nyquist frequency yielding a valid relaxation.
 In the benchmarks in Section~\ref{sec:experiments}, we showcase the relation numerically.
+% (see Section~\ref{sec:ddbarriers})
 %
@@
 \lucid will parse the configuration, synthesize a barrier certificate and plot the result.
-For the running example, we obtain the barrier certificate shown in Figure~\ref{fig:example} for a control horizon of $T = 15$ certifying safety of the system in \eqref{eq:linear-system} with a probability of at least $93.73\%$ ($\eta = 0.013, \gamma=1.0, c = 0.003$).
+For the running example, we obtain the barrier certificate shown in Figure~\ref{fig:example} for a time horizon of $T = 15$ certifying safety of the system in \eqref{eq:linear-system} with a probability of at least $93.73\%$ ($\eta = 0.013, \gamma=1.0, c = 0.003$).
 %\|B\| = 1.72
@@
     \resizebox{\columnwidth}{!}{\import{figures}{example.pgf}}
-    \caption{Barrier certificate for the linear system example.
+    \caption{Barrier certificate for the running example.
         The state space $\X$ is plotted in the X axis, while the value of the barrier $\B$ is plotted in the Y axis.
         The green line represents the barrier value at time $t$ while the purple one represents the barrier value at time $t+1$.
-        The initial and unsafe sets are highlighted in blue and red respectively.}
+        The initial and unsafe sets are highlighted in blue and red respectively. \Sadegh{Figure not very readable.}}
     \label{fig:example}
@@
 \end{lstlisting}
-Doing so confirms that the $\B$ is indeed a valid \gls{cbc} for the system.
+Doing so confirms that $\B$ is indeed a valid \gls{cbc} for the system.
 
@@
     \caption{\lucid's \gls{gui} can be accessed via any web browser. 
-    The left half of the screen allows the user to provide the transition samples and the safety specification to verify.
+    The left half of the screen, \Sadegh{as indicated in this picture,} allows the user to provide the transition samples and the safety specification to verify.
     The results will be shown on the right half of the screen.
@@
 
-To ascertain the performance of \lucid, we conducted a series of experiments, run on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, and 64 GB of RAM.
+To ascertain the performance of \lucid, we conduct a series of experiments, run on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, and 64 GB of RAM.
 All runs had the random seed set to $42$ to ensure reproducibility.
@@
                            & 3            & $?^3$            & XX:XX            & XX\%                    \\
-        name2              & 7            &                  & XX:XX            & XX\%                    \\
+        anotherSimpleOne              & X            &                  & XX:XX            & XX\%                    \\
         \bottomrule
@@
     = \begin{bmatrix}
+        {x}_{1, t} \\
+        {x}_{2, t}
+    \end{bmatrix}+ h\begin{bmatrix}
         {x}_{2, t} - 1 + e^{-x_{1, t}} \\
@@
 \end{equation*}
+with {\color{red}$h:=0.01-0.0001$}.
 Given
@@
     = \begin{bmatrix}
+        {x}_{1, t} \\
+        {x}_{2, t}
+    \end{bmatrix}+ h
+    \begin{bmatrix}
         {x}_{2, t} \\
         \frac{1}{3} {x}^3_{1, t} - {x}_{1,t} - {x}_{2,t}
-    \end{bmatrix} + w_t.
+    \end{bmatrix} + w_t
 \end{equation*}
+with {\color{red}$h:=0.01-0.0001$}.
 Given
@@
 
-\Sadegh{Are we comparing with alternative approaches in the literature?
+%\Sadegh{Are we comparing with alternative approaches in the literature?
 Since we mention alternative tools and their capabilities in Table 1, this raises expectations that we provide a fair benchmarking and show how we are better than them.}
 
-\section{Future Extensions}\label{sec:future_extensions}
+\section{Conclusion and Future Extensions}\label{sec:conclusion_and_future_extensions}
+\Sadegh{we should combine Conclusion and Future extensions into one section and keep it in the main body. We should also mention sparse CME as a way of improving scalability...}
+
+\new{This paper introduces \lucid, a novel }
+
 The form of data \eqref{eq:data} considered here assumes access to full state measurements, as it is the case when working with simulated systems.
@@
 
+\OS{Mention robustness radius}
+
 \section{Conclusion}\label{sec:conclusion}
 ...
-
-\input{appendix}
 
@@
 
+\input{appendix}
+
 \newpage
-\def\isChecklistMainFile{\FALSE}
+% \def\isChecklistMainFile{\FALSE}
 \input{reproducibility checklist/ReproducibilityChecklist}

### 2025-07-31 docs/paper/reproducibility checklist/ReproducibilityChecklist.tex
feat: update paper

--- 2025-07-30 docs/paper/reproducibility checklist/ReproducibilityChecklist.tex
@@
 % !TEX root =  main.tex
-\makeatletter
-\@ifundefined{isChecklistMainFile}{
-  % We are compiling a standalone document
-  \newif\ifreproStandalone
-  \reproStandalonetrue
-}{
-  % We are being \input into the main paper
-  \newif\ifreproStandalone
-  \reproStandalonefalse
-}
-\makeatother
 
-\ifreproStandalone
-\documentclass[letterpaper]{article}
-\usepackage[submission]{aaai2026}
-\setlength{\pdfpagewidth}{8.5in}
-\setlength{\pdfpageheight}{11in}
-\usepackage{times}
-\usepackage{helvet}
-\usepackage{courier}
-\usepackage{xcolor}
-\frenchspacing
-
-\begin{document}
-\fi
 \setlength{\leftmargini}{20pt}
@@
 \question{Includes a conceptual outline and/or pseudocode description of AI methods introduced}{(yes/partial/no/NA)}
-Type your response here
+yes
 
 \question{Clearly delineates statements that are opinions, hypothesis, and speculation from objective facts and results}{(yes/no)}
-Type your response here
+yes
 
 \question{Provides well-marked pedagogical references for less-familiar readers to gain background necessary to replicate the paper}{(yes/no)}
-Type your response here
+yes
 
@@
 \question{Does this paper make theoretical contributions?}{(yes/no)}
-Type your response here
+no
 
@@
 	\question{All assumptions and restrictions are stated clearly and formally}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{All novel claims are stated formally (e.g., in theorem statements)}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{Proofs of all novel claims are included}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{Proof sketches or intuitions are given for complex and/or novel results}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{Appropriate citations to theoretical tools used are given}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{All theoretical claims are demonstrated empirically to hold}{(yes/partial/no/NA)}
-	Type your response here
+	yes
 
 	\question{All experimental code used to eliminate or disprove claims is included}{(yes/no/NA)}
-	Type your response here
+	yes
 
@@
 \question{Does this paper rely on one or more datasets?}{(yes/no)}
-Type your response here
+no
 
@@
 	\question{A motivation is given for why the experiments are conducted on the selected datasets}{(yes/partial/no/NA)}
-	Type your response here
+	NA
 
 	\question{All novel datasets introduced in this paper are included in a data appendix}{(yes/partial/no/NA)}
-	Type your response here
+	NA
 
 	\question{All novel datasets introduced in this paper will be made publicly available upon publication of the paper with a license that allows free usage for research purposes}{(yes/partial/no/NA)}
-	Type your response here
+	NA
 
 	\question{All datasets drawn from the existing literature (potentially including authors' own previously published work) are accompanied by appropriate citations}{(yes/no/NA)}
-	Type your response here
+	NA
 
 	\question{All datasets drawn from the existing literature (potentially including authors' own previously published work) are publicly available}{(yes/partial/no/NA)}
-	Type your response here
+	NA
 
 	\question{All datasets that are not publicly available are described in detail, with explanation why publicly available alternatives are not scientifically satisficing}{(yes/partial/no/NA)}
-	Type your response here
+	NA
 
@@
 \end{itemize}
-\ifreproStandalone
-\end{document}
-\fi

### 2025-08-01 benchmarks/integration/Barrier3_orig.py
feat: add barrier3 original

@@ -8,35 +8,44 @@ from benchmark import single_benchmark
 
 from pylucid import *
 from pylucid import __version__
-from pylucid.plot import plot_data
-from pylucid.cli import ConfigAction
 
 
 def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) -> Configuration:
+    """Benchmark scenario taken from
+    https://github.com/oxford-oxcav/fossil/blob/10f1f071784d16b2a5ee5da2f51ff2a81d753e2e/experiments/benchmarks/models.py#L350C1-L360C1
+    """
     # ################################## #
     # System dynamics
     # ################################## #
     action = ConfigAction(option_strings=None, dest="input")
     config = Configuration()
-    action(None, config, Path("benchmarks/integration/dc_motor.yaml"), None)
+    action(None, config, Path("benchmarks/integration/barrier3_orig.yaml"), None)
 
     for key, value in zip(param_name, param_combinations):
         setattr(config, key, value)
 
-    plot_data(
-        config.x_samples,
-        config.xp_samples,
-        X_bounds=config.X_bounds,
-        X_init=config.X_init,
-        X_unsafe=config.X_unsafe,
-    )
+    # Add process noise
+    if config.seed >= 0:
+        np.random.seed(config.seed)  # For reproducibility
+        random.seed(config.seed)
+
+    # ################################## #
+    # Data
+    # ################################## #
+    f = lambda x: config.system_dynamics(x) + (np.random.normal(scale=config.noise_scale))
+    config.x_samples = config.X_bounds.sample(config.num_samples)
+    config.xp_samples = f(config.x_samples)
 
     # ################################## #
     # Running the pipeline
     # ################################## #
-    return
+
+    if config.num_frequencies >= 12 and config.oversample_factor > 20.0:
+        log.warn("The number of frequencies and oversampling factor too high.")
+        return
+
     single_benchmark(
-        name="DcMotor",
+        name="Barrier3_orig",
         config=config,
     )
 
@@ -49,12 +58,11 @@ if __name__ == "__main__":
     start = time.time()
 
     grid = {
-        # "num_frequencies": [9, 12, 13, 16, 17],
-        "num_frequencies": [5], # [6, 7], 
-        # "num_frequencies": [4],
         "c_coefficient": [1.0],
-        # "time_horizon": [5, 15],
[…]

### 2025-08-01 docs/paper/appendix.tex
feat: move to appendix

@@
 Running \lstinline|pylucid-gui| will open a browser tab containing the interface shown in Figures~\ref{fig:gui-left}--\ref{fig:gui-right}, while a local server will listen for requests coming from the \gls{gui}, computing and returning the results.
+Following the same numeration as the arrows in the figures, we provide a list of the main components of the \gls{gui}:
+\begin{enumerate}
+      \item Only a subsection of the configuration options is shown at any given moment. More options can be accessed by clicking on the \textit{Advanced} button.
+      \item It is easy to import or export the configuration using the Json format. The experiments discussed in this paper are also available in the \textit{Import} menu.
+      \item Clicking the \textit{Preview} button produces a visualization of the system function described by the transition samples.
+      \item The dimension of the system can be specified in the \textit{Model} tab.
+      \item You can either provide the transition samples yourself in the \textit{Data} tab, or specify a transition function in the \textit{Model} tab.
+      \item The $x^1,\ldots,x^N$ samples, stored in \texttt{csv} format.
+      \item The $x^1_+,\ldots,x^N_+$ samples, stored in \texttt{csv} format.
+      \item The bounding box of the state space.
+      \item The initial set $\X_0$.
+      \item The unsafe set $\X_U$.
+      \item Clicking the \textit{Submit} button will start the computation of the barrier function with the current configuration.
+      \item Plot of the transition function or the computed barrier function.
+      \item Numerical results of the computation.
+      \item Logs of the computation.
+\end{enumerate}
 \begin{figure}
       \centering
-    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
-    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
-    The left half of the screen allows the user to provide the transition samples and the safety specification to verify.
+      \includegraphics[trim={0 0 17cm 0},clip,width=.7\linewidth]{figures/frontend-left.png}
+      \caption{The left half of the page allows the user to provide the transition samples and the safety specification to verify.
       }
@@
       \centering
-    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
-    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
-    The right half of the screen shows the results produced by \lucid, including a plot of the computed barrier function, 
-    the numerical safety guarantee and , and detailed logs of the computations.
-    }
+      \includegraphics[trim={13.5cm 12.4cm 0 0},clip,width=.7\linewidth]{figures/frontend-right.png}
+      \caption{The right half of the page shows the results produced by \lucid, including a plot of the computed barrier function and detailed logs.}
       \label{fig:gui-right}
@@
 we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=5$ time steps.
+The kernel \hp set to be $\sigma_f=1$ and $\sigma_l=[1.0, 5.39334]$.
+Using a spectral basis of $M=15^2-1$ frequencies and a lattice density of $\hat{N} = 350^2$,
+we were able to generate a \gls{cbc} with $\eta \approx 5.032$, $\gamma = 100$, and $c \approx 3.926$ in $14.7$ minutes, achieving a lower bound on the safety probability of $P_{\text{safe}}(\S^\pi) \geq 75.34\%$.
+The result is shown in Figure~\ref{fig:CSBarr2}.
 The complete configuration for the \barrII benchmark is shown in Listing~\ref{lst:barrier2}.
@@
 we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=5$ time steps.
+The kernel \hp were set to $\sigma_f=1$ and $\sigma_l=[1.0, 1.0, 1.0]$.
+Hence, we need a rather high number of frequencies to achieve the required expressivity in the barrier.
+Using a spectral basis of $M=15^3-1$ frequencies and a lattice density of $\hat{N} = 30^2$,
+we were able to generate a \gls{cbc} with $\eta \approx 0.1$, $\gamma = 100$, and $c \approx 0.1$ in $XX:XX$ minutes, achieving a lower bound on the safety probability of $P_{\text{safe}}(\S^\pi) \geq XX\%$.
+The result is shown in Figure~\ref{fig:CSBarr3}.
 The complete configuration for the \barrIII benchmark is shown in Listing~\ref{lst:barrier3}.
@@
 We consider a scenario where an autonomous vehicle (AV) controlled by a \gls{nn} is overtaking another vehicle.
-The dynamics of the ego vehicle are given by Dubin's car model \EC{does it need a cit or is it just textbook} by adding the noise vector $w = \begin{bmatrix}w_t^1 & w_t^2 & w_t^3\end{bmatrix}$ where each component is drawn from a zero-mean Gaussian with standard deviation $0.01$, $0.01$, and $0.001$, respectively.
-The steering wheel angle is supplied by the \gls{nn} controller and we travel at a fixed velocity $v=1$.
+The dynamics of the ego vehicle are given by Dubin's car model by adding the noise vector $w = \begin{bmatrix}w_t^1 & w_t^2 & w_t^3\end{bmatrix}$ where each component is drawn from a zero-mean Gaussian with standard deviation $0.01$, $0.01$, and $0.001$, respectively.
+The steering wheel angle is supplied by the \gls{nn} controller and we travel at a fixed velocity.
 Given
@@
 \lstinputlisting[language=yaml,caption={Configuration for \overtaking},captionpos=b,label={lst:overtaking}]{code/overtaking.yaml}
+
+% Linear
+% Success: 93.74%, c 0.0032813476604243406, eta 0.013421457997340467, lambda 1e-05, num_frequencies 5, num_oversample 704, oversample_factor 2.0, sigma_l 0.034, sigma_f 18.0, T 15
+% \begin{tabular}{rlrrrrrrrrl}
+%   \toprule
+%   sigma_f   & sigma_l & lambda_  & num_frequencies & num_oversample & T  & gamma    & eta      & c        & percentage & time \\
+%   \midrule
+%   18.000000 & 0.034   & 0.000010 & 5               & 704            & 15 & 1.000000 & 0.013421 & 0.003281 & 93.735833  & 0:01 \\
+%   \bottomrule
+% \end{tabular}
+
+% Barrier 2
+% \begin{tabular}{rlrrrrrrrrl}
+%     \toprule
+%     sigma_f  & sigma_l           & lambda_  & num_frequencies & num_oversample & T & gamma      & eta      & c        & percentage & time  \\
+%     \midrule
+%     1.000000 & [2.50304 3.77779] & 0.000001 & 15              & 400            & 5 & 2.000000   & 0.155993 & 0.141315 & 56.871502  & 10:01 \\
+%     1.000000 & [2.50304 3.77779] & 0.000001 & 9               & 350            & 5 & 100.000000 & 8.116091 & 7.537732 & 54.195247  & 2:02  \\
+%     1.000000 & [2.50304 3.77779] & 0.000001 & 11              & 300            & 5 & 2.000000   & 0.183647 & 0.150238 & 53.258213  & 2:25  \\
+%     1.000000 & [2.50304 3.77779] & 0.000001 & 13              & 300            & 5 & 2.000000   & 0.182542 & 0.150821 & 53.167620  & 3:53  \\
+%     1.000000 & [2.50304 3.77779] & 0.000001 & 9               & 300            & 5 & 2.000000   & 0.176700 & 0.153188 & 52.868065  & 1:28  \\
+%     1.000000 & [2.50304 3.77779] & 0.000001 & 9               & 300            & 5 & 100.000000 & 8.835006 & 7.659386 & 52.868065  & 1:33  \\
+%     1.000000 & [2.50304 3.77779] & 0.000001 & 20              & 300            & 5 & 2.000000   & 0.223455 & 0.147586 & 51.930650  & 16:48 \\
+%     1.000000 & [2.50304 3.77779] & 0.000001 & 9               & 250            & 5 & 100.000000 & 9.875340 & 7.785029 & 51.199515  & 1:10  \\
+%     \bottomrule
+% \end{tabular}
+
+% Barrier3
+% Success: 42.25%, c 0.11928419647787443, eta 0.5584972599863635, lambda 1e-08, num_frequencies 15, num_oversample 800, oversample_factor 1.0, sigma_l [2.99266 4.62946], sigma_f 1.0, T 5
+% \begin{tabular}{rlrrrrrrrrl}
+%     \toprule
+%     sigma_f  & sigma_l           & lambda_  & num_frequencies & num_oversample & T & gamma    & eta      & c        & percentage & time  \\
+%     \midrule
+%     1.000000 & [2.99266 4.62946] & 0.000000 & 15              & 800            & 5 & 2.000000 & 0.558497 & 0.119284 & 42.254088  & 64:20 \\
+%     1.000000 & [2.99266 4.62946] & 0.000000 & 15              & 600            & 5 & 2.000000 & 0.598432 & 0.122033 & 39.570103  & 25:12 \\
+%     1.000000 & [2.99266 4.62946] & 0.000000 & 15              & 450            & 5 & 2.000000 & 0.638667 & 0.127644 & 36.155716  & 12:07 \\
+%     1.000000 & [2.99266 4.62946] & 0.000000 & 14              & 450            & 5 & 2.000000 & 0.638151 & 0.128054 & 36.078977  & 9:58  \\
+%     1.000000 & [2.99266 4.62946] & 0.000000 & 14              & 400            & 5 & 2.000000 & 0.651139 & 0.130655 & 34.779342  & 7:50  \\
+%     1.000000 & [2.99266 4.62946] & 0.000000 & 14              & 370            & 5 & 2.000000 & 0.662921 & 0.133060 & 33.589019  & 6:49  \\
+%     1.000000 & [2.99266 4.62946] & 0.000000 & 16              & 370            & 5 & 2.000000 & 0.646389 & 0.136513 & 33.552259  & 11:35 \\
+%     1.000000 & [2.99266 4.62946] & 0.000000 & 12              & 370            & 5 & 2.000000 & 0.710767 & 0.127533 & 32.578438  & 4:38  \\
+%     1.000000 & [2.99266 4.62946] & 0.000000 & 11              & 350            & 5 & 2.000000 & 0.755459 & 0.128623 & 30.071348  & 3:14  \\
+%     1.000000 & [2.99266 4.62946] & 0.000000 & 10              & 350            & 5 & 2.000000 & 0.812608 & 0.125781 & 27.924451  & 2:34  \\
+%     1.000000 & [2.99266 4.62946] & 0.000000 & 9               & 350            & 5 & 2.000000 & 0.836442 & 0.128851 & 25.965203  & 2:02  \\
+%     \bottomrule
+% \end{tabular}
+
+% Overtaking
+% Success: 30.32%, c 0.05031756638044985, eta 0.09681458793205037, lambda 1e-05, num_frequencies 5, num_oversample -1, oversample_factor 9.0, sigma_l [10.  7.  5.], sigma_f 7.0, T 5
+% \begin{tabular}{rlrrrrrrrrl}
+%     \toprule
+%     sigma_f  & sigma_l       & lambda_  & num_frequencies & num_oversample & T & gamma    & eta      & c        & percentage & time  \\
+%     \midrule
+%     7.000000 & [10.  7.  5.] & 0.000010 & 5               & 99             & 5 & 0.500000 & 0.096815 & 0.050318 & 30.319516  & 46:33 \\
+%     7.000000 & [10.  7.  5.] & 0.000010 & 5               & 100            & 5 & 0.500000 & 0.100419 & 0.050519 & 29.396944  & 49:21 \\
+%     7.000000 & [10.  7.  5.] & 0.000010 & 5               & 88             & 5 & 0.500000 & 0.093582 & 0.052546 & 28.737764  & 25:52 \\
+%     7.000000 & [10.  7.  5.] & 0.000010 & 5               & 77             & 5 & 0.500000 & 0.103997 & 0.054252 & 24.948829  & 13:49 \\
+%     7.000000 & [10.  7.  5.] & 0.000010 & 5               & 66             & 5 & 0.500000 & 0.124539 & 0.058476 & 16.616154  & 8:16  \\
+%     7.000000 & [10.  7.  5.] & 0.000010 & 4               & 90             & 5 & 0.500000 & 0.101765 & 0.067857 & 11.790251  & 11:21 \\
+%     7.000000 & [10.  7.  5.] & 0.000010 & 4               & 81             & 5 & 0.500000 & 0.109691 & 0.068535 & 9.527199   & 8:08  \\
+%     7.000000 & [10.  7.  5.] & 0.000010 & 5               & 55             & 5 & 0.500000 & 0.135738 & 0.063642 & 9.210252   & 4:15  \\
+%     7.000000 & [10.  7.  5.] & 0.000010 & 4               & 72             & 5 & 0.500000 & 0.109150 & 0.069704 & 8.465822   & 5:10  \\
+%     7.000000 & [10.  7.  5.] & 0.000010 & 5               & 44             & 5 & 0.500000 & 0.160935 & 0.062971 & 4.842390   & 2:06  \\
+%     7.000000 & [10.  7.  5.] & 0.000010 & 4               & 63             & 5 & 0.500000 & 0.120951 & 0.071611 & 4.198906   & 3:25  \\
+%     \bottomrule
+% \end{tabular}

### 2025-08-01 docs/paper/figures/architecture.tex
feat: move to appendix

@@
         % fit=(estimator)(feature)(optimizer)(verifier), label=above:{\textbf{Lucid}}] {};
-        fit=(estimator)(feature)(optimizer)(sets)(tuner), label=below:{\textbf{\lucid}}] {};
+        fit=(estimator)(feature)(optimizer)(sets)(tuner), label={[xshift=3cm]below:{\textbf{\lucid}}}] {};
 
@@
         \node[output-block, below=of optimizer] (output) {Barrier Certificate};
-        \node[output-block, below=.5cm of output] (prob) {Safety Probability};
+        \node[output-block, right=.5cm of output] (prob) {Safety Probability};
         \node[] at ($(output)!0.5!(prob)$) (plus) {$+$};

### 2025-08-01 docs/paper/main.tex
feat: move to appendix

@@
 
-\subsection{Data-Driven Dynamics Estimation via Conditional Mean Embeddings}
+\subsection{Data-Driven Dynamics Estimation via Conditional Mean Embeddings}\label{sec:dd_estimation_via_cme}
 To reason about the expected value of a random variable, embedding the variable into a (higher dimensional) space and forming a data-driven estimate is a well-established concept in machine learning \cite{scholkopf2002learning,Steinwart2008SVM}.
@@
 The same configuration values can also be given directly as command line arguments.
-For a list of all available options, run \lstinline|pylucid --help|.
+\pylucid also provides a browser-based \gls{gui} to aid in the configuration and execution of the tool.
 \Sadegh{space needs fixing before ".. to start ...".}
@@
 Different feature map implementations may yield different results.
-In our example, we truncate the Fourier expansion to $5$ frequency bands, including the constant term, and use $64$ times the Nyquist frequency of lattice points to build the constraints of the optimization problem, to avoid it being too conservative.\OS{Specifying it as a multiple of the Nyquist frequency will inevitably raise questions.
+In our example, we truncate the Fourier expansion to $5$ frequency bands, including the constant term, and use $704$ lattice points to build the constraints of the optimization problem, to avoid it being too conservative.\OS{Specifying it as a multiple of the Nyquist frequency will inevitably raise questions.
 Just say we generate $X$ lattice points?
-"lattice size"}
+"lattice size"}\EC{new}
 \begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
@@
 num_frequencies: 5
-oversample_factor: 64
+num_oversample: 704
 \end{lstlisting}
@@
     \centering
-    \resizebox{\columnwidth}{!}{\import{figures}{example.pgf}}
+    \begin{adjustbox}{max width=\columnwidth}
+        \input{figures/example.pgf}
+    \end{adjustbox}
+    %\resizebox{\columnwidth}{!}{\import{figures}{example.pgf}}
     \caption{Barrier certificate for the running example.
         The state space $\X$ is plotted in the X axis, while the value of the barrier $\B$ is plotted in the Y axis.
-        The green line represents the barrier value at time $t$ while the purple one represents the barrier value at time $t+1$.
-        The initial and unsafe sets are highlighted in blue and red respectively. \Sadegh{Figure not very readable.}}
+        The green line represents the barrier value at time $t$.
+        The initial and unsafe sets are highlighted in blue and red respectively. % \Sadegh{Figure not very readable.}
+        }
     \label{fig:example}
@@
 \end{lstlisting}
-Doing so confirms that $\B$ is indeed a valid \gls{cbc} for the system.
-
-\subsection{Graphical User Interface}
-
-\pylucid provides a \gls{gui} to guide the user in the creation of the scenario configuration and presenting the results in an intuitive way.
-Running \lstinline|pylucid-gui| will open a browser tab containing the interface shown in Figure~\ref{fig:gui}, while a local server will listen for requests coming from the \gls{gui}, computing and returning the results.
-\todo{Improve picture of the GUI}
-\begin{figure}
-    \centering
-    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
-    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
-    The left half of the screen, \Sadegh{as indicated in this picture,} allows the user to provide the transition samples and the safety specification to verify.
-    The results will be shown on the right half of the screen.
-    }
-    \label{fig:gui}
-\end{figure}
+Doing so confirms that $\B$ is indeed a valid \gls{cbc}.
 
@@
 
-To ascertain the performance of \lucid, we conduct a series of experiments, run on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, and 64 GB of RAM.
+To ascertain the performance of \lucid, we conduct a series of experiments, run on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, NVIDIA GeForce RTX 3090 GPU, and 64 GB of RAM.
 All runs had the random seed set to $42$ to ensure reproducibility.
-The results of all experimental results are summarized in Table~\ref{tbl:benchmarks_results}.
+
+We adapt the \barrII and \barrIII benchmarks from \cite{abate2021fossil}.
+Both are two-dimensional highly nonlinear systems to which we add the stochastic noise $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$.
+Given the initial set $\X_0$ and the unsafe set $\X_U$, we synthesize a barrier $\B$ that guarantees trajectories starting in $\X_0$ do not enter $\X_U$ within $T=5$ time steps.
+Note that we can only certify safety w.r.t. the empirical distribution, i.e., the \gls{cme} constructed from the observed data.
+\barrIII is particularly challenging due to the closeness between the initial set and the unsafe set.
+The synthesized barriers are shown in Figures~\ref{fig:CSBarr2}--\ref{fig:CSBarr3}.
+We also consider a scenario, we name \overtaking, where an autonomous vehicle (AV) controlled by a \gls{nn} is overtaking another vehicle.
+The dynamics of the ego vehicle are given by Dubin's car model with an added noise vector $w$ where each component is drawn from a zero-mean Gaussian with standard deviation $0.01$, $0.01$, and $0.001$ respectively.
+The steering wheel angle is supplied by the \gls{nn} controller and we travel at a fixed velocity.
+
+Table~\ref{tbl:benchmarks_results} summarizes the results of all the experiments presented.
+More details about the configurations and \hp used can be found in the Appendix.
+
+\begin{figure}[ht]
+    \begin{adjustbox}{clip,trim=0cm 1.7cm 0cm 2cm,max width=\columnwidth}
+        \input{figures/barrier2.pgf}
+    \end{adjustbox}
+    %\includegraphics[trim={5cm 3cm 2cm 4cm},clip,width=\linewidth]{barrier2.pgf}
+    \caption{\gls{cbc} synthesised for the \barrII benchmark.}
+    \label{fig:CSBarr2}
+\end{figure}
+
+\begin{figure}[ht]
+    \begin{adjustbox}{clip,trim=0cm 2cm 0cm 2cm,max width=\columnwidth}
+        \input{figures/barrier3.pgf}
+    \end{adjustbox}
+    %\resizebox{\columnwidth}{!}{\import{figures}{barrier3.pgf}}%
+    \caption{\gls{cbc} synthesised for the \barrIII benchmark.}
+    \label{fig:CSBarr3}
+\end{figure}
+
 \begin{table}[tb]
     \centering
-    \begin{tabular}{ccccc}
+    \begin{tabular}{cccccc}
         \toprule
-        \textbf{Benchmark} & \textbf{Dim} & \textbf{Lattice} & \textbf{Runtime} & \textbf{Safety} \\
-                           &              & \textbf{Size} & [mm:ss]          & \textbf{Probability}                  \\ % Units
+                    & \textbf{T} & \textbf{Freq} & \textbf{Lattice} & \textbf{Runtime} & \textbf{Safety} \\
+                    &            &               & \textbf{Size}    & [mm:ss]          & \textbf{Prob}   \\ % Units
         \midrule
-        Linear             & 1            & $?$              & 00:02            & 95.15\%                 \\
-        Barr2              & 2            & $350^2$           & 14:42            & 75.34\%                    \\
-        Barr3              & 2            & $30^2$           & XX:XX            & XX\%                    \\
-                           &              & $40^2$           & XX:XX            & XX\%                    \\
-                           &              & $?^2$            & XX:XX            & XX\%                    \\
-        Overtaking         & 3            & $?^3$            & XX:XX            & XX\%                    \\
-                           & 3            & $?^3$            & XX:XX            & XX\%                    \\
-                           & 3            & $?^3$            & XX:XX            & XX\%                    \\
-        anotherSimpleOne              & X            &                  & XX:XX            & XX\%                    \\
+        \linear     & 15         & 5             & $704$            & 00:02            & 93.74\%         \\
+        \barrII     & 5          & 15            & $350^2$          & 10:01            & 56.87\%         \\
+        \barrIII    & 5          & 15            & $800^2$          & 64:20            & 42.25\%         \\
+        \overtaking & 5          & 5             & $99^3$           & 46:33            & 30.32\%         \\
         \bottomrule
     \end{tabular}
-    \caption{Computational benchmarks: ...}
+    \caption{Computational benchmarks.
+        The lattice size indicates the number of points of the lattice as the resolution for each dimension raised to the number of dimensions.
+        $T$ is the number of time steps associated with the lower bound on the safety probability, displayed in the last column.
+    }
     \label{tbl:benchmarks_results}
@@
 
-\subsection{Barrier 2}
-
-The \barrII experiment is inspired by the one from \cite{abate2021fossil}, which we extend by adding stochastic noise $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$ to arrive at the two-dimensional nonlinear stochastic dynamics
-
-\begin{equation*}
-    \begin{bmatrix}
-        {x}_{1, t+1} \\
-        {x}_{2, t+1}
-    \end{bmatrix}
-    = \begin{bmatrix}
-        {x}_{1, t} \\
-        {x}_{2, t}
-    \end{bmatrix}+ h\begin{bmatrix}
-        {x}_{2, t} - 1 + e^{-x_{1, t}} \\
-        -\sin^2(x_{1, t})
-    \end{bmatrix} + w_t.
-\end{equation*}
-with {\color{red}$h:=0.01-0.0001$}.
-Given
-\begin{align*}
-    &\X = [ -2, 2 ] \times [ -2 , 2 ] \\
-    &\X_0 = \{ [x_1, x_2] : (x_1 + 0.5)^2 + (x_2 - 0.5)^2 \leq 0.4 \} \\
-    &\X_U = \{ [x_1, x_2] : (x_1 - 0.7)^2 + (x_2 + 0.7)^2 \leq 0.3 \}
-\end{align*}
-we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=5$ time steps.
-\EC{we can remove all the explicit set intervals}
-The results are shown in Figure~\ref{fig:CSBarr2}.
-The kernel \hp have been selected through offline tuning to be $\sigma_f=1$ and $\sigma_l=[1.0, 5.39334]$.
-Using a spectral basis of $M=15^2-1$ frequencies and a lattice density of $\hat{N} = 350^2$, 
-we were able to generate a \gls{cbc} with $\eta \approx 5.032$, $\gamma = 100$, and $c \approx 3.926$ in $14.7$ minutes, achieving a lower bound on the safety probability of $P_{\text{safe}}(\S^\pi) \geq 75.34\%$.
-% Knowing the system dynamics, we were also able to formally validate the barrier.
-
-\begin{figure}[ht]
-    %\resizebox{\columnwidth}{!}{\import{figures}{barrier2.pdf}}%
-    \includegraphics[trim={5cm 3cm 2cm 4cm},clip,width=\linewidth]{barrier2.pdf}
-    \caption{\gls{cbc} synthesis for the \barrII benchmark.
-        The blue circle represents the initial set $\X_0$, while the red one represents the unsafe set $\X_U$.
-    }
-    \label{fig:CSBarr2}
-\end{figure}
-
-\subsection{Barrier 3}
-
-Similarly, we also tested \lucid on the \barrIII benchmark adapted from \cite{abate2021fossil} with added stochastic noise.
-The resulting nonlinear stochastic dynamics are
-\begin{equation*}
-    \begin{bmatrix}
-        {x}_{1, t+1} \\
-        {x}_{2, t+1}
-    \end{bmatrix}
-    = \begin{bmatrix}
-        {x}_{1, t} \\
-        {x}_{2, t}
-    \end{bmatrix}+ h
-    \begin{bmatrix}
-        {x}_{2, t} \\
-        \frac{1}{3} {x}^3_{1, t} - {x}_{1,t} - {x}_{2,t}
-    \end{bmatrix} + w_t
-\end{equation*}
-with {\color{red}$h:=0.01-0.0001$}.
-Given
-\begin{align*}
-    &\X = [ -3, 2.5 ] \times [ -2 , 1 ] \\
-    &\X_0 = [ 1 , 2 ] \times [ -0.7 , 0.3 ] \cup [ -1.8 , -1.4 ] \times [ -0.1 , 0.1 ] \\
-    &\qquad \cup [-1.4, -1.2] \times [-0.5 , 0.1] \\
-    &\X_U = [ 0.4 , 0.6 ] \times [ 0.2 , 0.6 ] \cup [ 0.6 , 0.7 ] \times [ 0.2 , 0.4 ],
-\end{align*}
-we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=10$ time steps.
-\EC{we can remove all the explicit set intevals}
-This example is particularly challenging due to the closeness between the initial set and the unsafe set.
-Hence, we need a rather high number of frequencies to achieve the required expressivity in the barrier.
-The results are shown in Figure~\ref{fig:CSBarr3}.
-The kernel \hp have been selected through offline tuning to be $\sigma_f=X$ and $\sigma_l=[X, X]$.
-Using a spectral basis of $M=X^3-1$ frequencies and a lattice density of $\hat{N} = X^2$, 
-we were able to generate a \gls{cbc} with $\eta \approx X.X$, $\gamma \approx X.X$, and $c \approx X.X$ in $X$ minutes and $X$ seconds, achieving a safety probability of $P_{safe}(\S^\pi) \approx XX.X\%$.
-% Knowing the system dynamics, we were also able to formally validate the barrier.
-
-\begin{figure}[ht]
-    \resizebox{\columnwidth}{!}{\import{figures}{barrier3.pgf}}%
-    \caption{\gls{cbc} synthesis for the \barrIII benchmark.
-        The blue regions represent the initial set $\X_0$, while the red regions represent the unsafe set $\X_U$.
-        The pink surface indicates the value of $\gamma$.
-    }
-    \label{fig:CSBarr3}
-\end{figure}
-
-\subsection{Overtaking}
-
-We consider a scenario where an autonomous vehicle (AV) controlled by a \gls{nn} is overtaking another vehicle, as indicated in Figure~\ref{fig:safety_setup}. 
-The dynamics of the ego vehicle are given by Dubin's car model \EC{does it need a cit or is it just textbook} by adding the noise vector $w = \begin{bmatrix}w_t^1 & w_t^2 & w_t^3\end{bmatrix}$ where each component is drawn from a zero-mean Gaussian with standard deviation $0.01$, $0.01$, and $0.001$, respectively.
-The steering wheel angle is supplied by the \gls{nn} controller and we travel at a fixed velocity $v=1$.
-The goal is to certify that the controlled system remains safe by computing the probability that the system initialized in $[{x}_0,{y}_0,\phi_0]\T\in \X_0$ does not enter the unsafe region $\X_U$ within $T=50$ time steps.
-
-The \gls{lp} is generated based on a lattice of $\hat{N}=X^3$ equidistant points and a spectral basis of $M=4^3-1$ frequencies.
-The kernel \hp are selected to be $\sigma_f=X$ and $\sigma_l=[X, X, X]$.
-We obtained a barrier which certifies safety with a probability of at least $XX\%$ with $c=0$, $\gamma=X.X$ and $\eta=X.X$.
-Note that this is only certifying safety w.r.t. the empirical distribution, i.e., the \gls{cme} constructed from the observed data.
+% Linear
+% Success: 93.74%, c 0.0032813476604243406, eta 0.013421457997340467, lambda 1e-05, num_frequencies 5, num_oversample 704, oversample_factor 2.0, sigma_l 0.034, sigma_f 18.0, T 15
+% Barrier3
+% Success: 42.25%, c 0.11928419647787443, eta 0.5584972599863635, lambda 1e-08, num_frequencies 15, num_oversample 800, oversample_factor 1.0, sigma_l [2.99266 4.62946], sigma_f 1.0, T 5
+% Overtaking
+% Success: 30.32%, c 0.05031756638044985, eta 0.09681458793205037, lambda 1e-05, num_frequencies 5, num_oversample -1, oversample_factor 9.0, sigma_l [10.  7.  5.], sigma_f 7.0, T 5
 
@@
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\linewidth]{placeholder.jpeg}
-    \caption{Barrier}
-    \label{fig:barr3_barrier}
-\end{figure}
-
 %\Sadegh{Are we comparing with alternative approaches in the literature?
@@
 \section{Conclusion and Future Extensions}\label{sec:conclusion_and_future_extensions}
-\Sadegh{we should combine Conclusion and Future extensions into one section and keep it in the main body. We should also mention sparse CME as a way of improving scalability...}
+\new{This paper introduces \lucid, a novel tool capable of quantifying safety guarantees for black-box systems with complex stochastic dynamics and deep learning components in the loop.
+As such, \lucid fills a gap currently unaddressed by preexisting tools.
+To achieve this, \lucid, leverages Conditional Mean Embeddings (CME) to learn control barrier certificates from data, and recasts the problem into a tractable linear form via a spectral abstraction.}
 
-\new{This paper introduces \lucid, a novel }
-
-The form of data \eqref{eq:data} considered here assumes access to full state measurements, as it is the case when working with simulated systems.
-Extending this to partially observed settings adds another level of complexity.
-Extending \lucid to such settings is on our agenda and builds on top of the results presented in this paper.
-
-\OS{As the GaussianKernel and KernelRidgeRegressor are the only options we currently provide, is specifying them explicitly necessary?
-Maybe we could also add a sentence about the fact that they are currently the only option, but that in the future we plan to extend this to to allow to include prior knowledge about the system dynamics (in the spirit of physics-informed approaches).}
-
-\OS{Mention robustness radius}
-
-\section{Conclusion}\label{sec:conclusion}
-...
+\new{
+    \lucid is built for extensibility.
+In its current form, it assumes access to full state measurements (cf.~\eqref{eq:data}), as is the case when working with simulated systems, and focuses on verification, i.e., when a policy is given.
+    Extending \lucid to partially observed settings and safe controller synthesis
+    % adds another level of complexity and 
+    is on our agenda and builds on top of the results presented in this paper.
+    \lucid derives barriers based on the empirical CME, which can be robustified against out-of-sample system behavior by tightening the barrier constraint (c) (cf.~Sections~\ref{sec:dd_estimation_via_cme}--\ref{sec:ddbarriers}).
+    The scalability of \lucid can be improved by performing sparse CME computations or specializing the estimator's \texttt{Kernel} to embed prior knowledge about the system dynamics.
+}
 

### 2025-08-01 bindings/pylucid/model.cpp
feat: support default KernelRidgeRegressor fro pylucid

@@ -485,6 +485,10 @@ void init_model(py::module_ &m) {
       .def("__call__", py::overload_cast<ConstMatrixRef>(&Estimator::operator(), py::const_), ARG_NONCONVERT("x"))
       .def("__str__", STRING_LAMBDA(Estimator));
   py::class_<KernelRidgeRegressor, Estimator>(m, "KernelRidgeRegressor")
+      .def(py::init([](double regularization_constant, const std::shared_ptr<Tuner> &tuner) {
+             return KernelRidgeRegressor{std::make_unique<GaussianKernel>(), regularization_constant, tuner};
+           }),
+           py::arg("regularization_constant") = 1.0, py::arg("tuner") = nullptr)
       .def(py::init<const Kernel &, double, const std::shared_ptr<Tuner> &>(), py::arg("kernel"),
            py::arg("regularization_constant") = 1.0, py::arg("tuner") = nullptr)
       .def(

### 2025-08-01 tests/bindings/pylucid/TestEstimator.py

@@ -19,8 +19,19 @@ except ImportError:
 class TestRegression:
     class TestGaussianKernelRidgeRegressor:
 
+        def test_init_default(self):
+            o = KernelRidgeRegressor()
+            assert o is not None
+            assert isinstance(o, Estimator)
+            assert isinstance(o.kernel, GaussianKernel)
+            assert o.training_inputs.size == 0
+            assert o.coefficients.size == 0
+            assert o.get(Parameter.REGULARIZATION_CONSTANT) == o.regularization_constant == 1
+            assert np.allclose(o.get(Parameter.SIGMA_L), o.kernel.sigma_l)
+            assert o.get(Parameter.SIGMA_F) == o.kernel.sigma_f == 1
+
         def test_init(self):
-            k = GaussianKernel(sigma_f=2, sigma_l=[3, 4, 5])
+            k = GaussianKernel(sigma_f=2, sigma_l=np.array([3.0, 4.0, 5.0]))
             o = KernelRidgeRegressor(kernel=k, regularization_constant=11)
             assert o is not None
             assert isinstance(o, Estimator)
@@ -97,7 +108,7 @@ class TestRegression:
 
             # Solving (K + λI) * x = y
             # K = sigma_f^2 * exp(-γ||x_i - x_j||^2)
-            kr = KernelRidge(kernel="rbf", gamma=0.5 * sigma_l**-2, alpha=reg_coeff * 2)
+            kr = KernelRidge(kernel="rbf", gamma=0.5 * sigma_l ** -2, alpha=reg_coeff * 2)
 
             training_inputs = np.array([[1.0, 2.0, 3.0], [4.0, 5.0, 6.0]])
             training_outputs = np.array([[1.0, 2.0], [5.0, 3.0]])

### 2025-08-01 benchmarks/integration/collect_results.py
feat: improve data collection

@@ -26,6 +26,8 @@ class Args(argparse.Namespace):
 
 def plot_solution(args: Args, data: pd.DataFrame):
     config = base_load_configuration(f"benchmarks/integration/{args.experiment.lower()}.yaml")
+    if isinstance(data, tuple):
+        data = pd.DataFrame([data._asdict()])
     for run in data.itertuples():
         feature_map = config.feature_map(
             num_frequencies=run.num_frequencies,
@@ -70,39 +72,67 @@ def main(args: Args):
     runs = client.search_runs(
         experiment_ids=[e.experiment_id for e in experiments],
         filter_string=FILTER,
-        order_by=["metrics.run.obj_val desc"],
+        order_by=["metrics.run.obj_val asc"],
     )
     print(f"Found {len(runs)} runs in experiment '{args.experiment}'.")
     data = pd.DataFrame(
         {
+            # Params
+            "sigma_f": float(run.data.params["sigma_f"]),
+            "sigma_l": np.array(eval(run.data.params["sigma_l"])),
+            "oversample_factor": float(run.data.params["oversample_factor"]),
+            "lambda_": float(run.data.params["lambda_"]),
+            "num_frequencies": int(run.data.params["num_frequencies"]),
+            "num_oversample": int(
+                (
+                    run.data.params["num_oversample"]
+                    if run.data.params["num_oversample"] != "-1"
+                    else np.ceil(
+                        (2 * int(run.data.params["num_frequencies"]) + 1) * float(run.data.params["oversample_factor"])
+                    )
+                ),
+            ),
+            "T": int(run.data.params["time_horizon"]),
+            "gamma": float(run.data.params["gamma"]),
+            "noise_scale": float(run.data.params["noise_scale"]),
+            "oversample_factor": float(run.data.params["oversample_factor"]),
             # Metrics
-            "c": float(run.data.metrics["run.c"]),
             "eta": float(run.data.metrics["run.eta"]),
+            "c": float(run.data.metrics["run.c"]),
             "norm": float(run.data.metrics["run.norm"]),
             "obj_val": float(run.data.metrics["run.obj_val"]),
             "percentage": (1 - float(run.data.metrics["run.obj_val"])) * 100,
-            # Params
-            "lambda_": float(run.data.params["lambda_"]),
-            "noise_scale": float(run.data.params["noise_scale"]),
-            "num_frequencies": int(run.data.params["num_frequencies"]),
[…]

### 2025-08-01 benchmarks/integration/plot_solution.py

@@ -15,10 +15,6 @@ except ImportError:
 from pylucid import random
 import matplotlib.pyplot as plt
 
-plt.rcParams.update({
-    'text.latex.preamble': r'\usepackage{amsfonts}'
-})
-
 def plot_solution_matplotlib(
     args: "argparse.Namespace",
     X_bounds: "RectSet",
@@ -75,21 +71,21 @@ def plot_solution_1d_matplotlib(
     # Draw the initial and unsafe sets
     def plot_rect_1d(s, color, label=None):
         if isinstance(s, RectSet):
-            ax.plot([s.lower_bound[0], s.upper_bound[0]], [-0.005, -0.005], color=color, linewidth=4, label=label)
+            ax.plot([s.lower_bound[0], s.upper_bound[0]], [-0.005, -0.005], color=color, linewidth=3, label=label)
         elif isinstance(s, MultiSet):
             for i, rect in enumerate(s):
                 ax.plot(
                     [rect.lower_bound[0], rect.upper_bound[0]],
                     [-0.005, -0.005],
                     color=color,
-                    linewidth=4,
+                    linewidth=3,
                     label=label if i == 0 else None,
                 )
 
     if X_init is not None:
-        plot_rect_1d(X_init, "blue", label=r"$\mathbb{X}_0$")
+        plot_rect_1d(X_init, "blue", label=r"$X_0$")
     if X_unsafe is not None:
-        plot_rect_1d(X_unsafe, "red", label=r"$\mathbb{X}_U$")
+        plot_rect_1d(X_unsafe, "red", label=r"$X_U$")
 
     if eta is not None:
         ax.axhline(eta, linestyle="dotted", color="green", label=r"$\eta$")
@@ -99,16 +95,16 @@ def plot_solution_1d_matplotlib(
     if feature_map is not None and sol is not None:
         x_lattice = X_bounds.lattice(num_samples or 200, True)
         values = feature_map(x_lattice) @ sol.T
-        ax.plot(x_lattice.flatten(), values.flatten(), color="green", label=r"$\boldsymbol{B}(x)$")
+        ax.plot(x_lattice.flatten(), values.flatten(), color="green", label=r"$B(x)$")
         # ax.fill_between(x_lattice.flatten(), values, (values + c + 1e-8).flatten(), alpha=0.3, color="lightgreen", label="Barrier region")
 
         if f is not None and args.plot_bxp:
[…]

### 2025-08-01 benchmarks/integration/Barrier2.py
chore: finalize benchmarks

@@ -59,6 +59,7 @@ def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) ->
         config=config,
     )
 
+
 if __name__ == "__main__":
     # ################################## #
     # Lucid
@@ -67,12 +68,13 @@ if __name__ == "__main__":
     start = time.time()
 
     grid = {
+        "c_coefficient": [1.0],
         # "num_frequencies": [9, 12, 13, 16, 17],
-        "num_frequencies": [20],
+        # "num_frequencies": [15],
         # "num_frequencies": [4],
-        "time_horizon": [5],
+        # "time_horizon": [5],
         # "oversample_factor": [10.0, 20.0, 30.0],
-        "num_oversample": [300],
+        # "num_oversample": [400],
         # "oversample_factor": [10.0],
     }
 
@@ -83,10 +85,10 @@ if __name__ == "__main__":
     args_list = [(grid_keys, param_combination) for param_combination in param_combinations]
 
     # Run benchmarks in parallel using multiprocessing
-    MAX_PARALLEL = multiprocessing.cpu_count() // 2
-    MAX_PARALLEL = 1
+    MAX_PARALLEL = multiprocessing.cpu_count() // 3
     with multiprocessing.Pool(processes=max(1, MAX_PARALLEL)) as pool:
         pool.starmap(scenario_config, args_list)
+    # scenario_config(*args_list[0])  # Run only one configuration for testing
 
     end = time.time()
     log.info(f"Elapsed time: {end - start}")

### 2025-08-01 benchmarks/integration/Barrier3.py

@@ -4,11 +4,10 @@ import multiprocessing
 import time
 
 import numpy as np
-from benchmark import grid_to_config, single_benchmark
+from benchmark import single_benchmark
 
 from pylucid import *
 from pylucid import __version__
-from pylucid.plot import plot_function, plot_data
 
 
 def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) -> Configuration:
@@ -50,6 +49,7 @@ def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) ->
         config=config,
     )
 
+
 if __name__ == "__main__":
     # ################################## #
     # Lucid
@@ -58,11 +58,12 @@ if __name__ == "__main__":
     start = time.time()
 
     grid = {
+        "c_coefficient": [1.0],
         # "num_frequencies": [9, 12, 13, 16, 17],
-        "num_frequencies": [12, 14, 16],
+        "num_frequencies": [16],
         # "num_frequencies": [4],
-        "time_horizon": [5],
-        "num_oversample": [370],
+        # "time_horizon": [5],
+        "num_oversample": [800],  #  , 20.0 , 30.0
         # "oversample_factor": [10.0],
     }
 
@@ -73,10 +74,10 @@ if __name__ == "__main__":
     args_list = [(grid_keys, param_combination) for param_combination in param_combinations]
 
     # Run benchmarks in parallel using multiprocessing
-    MAX_PARALLEL = multiprocessing.cpu_count() // 2
-    MAX_PARALLEL = 1
+    MAX_PARALLEL = multiprocessing.cpu_count() // 3
     with multiprocessing.Pool(processes=max(1, MAX_PARALLEL)) as pool:
         pool.starmap(scenario_config, args_list)
+    # scenario_config(*args_list[0])  # Run only one configuration for testing
 
     end = time.time()
     log.info(f"Elapsed time: {end - start}")

### 2025-08-01 benchmarks/integration/Linear.py

@@ -20,7 +20,7 @@ def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) ->
     # Algorithm parameters
     config = Configuration()
     action = ConfigAction(option_strings=None, dest="input")
-    action(None, config, Path("examples/linear.yaml"), None)
+    action(None, config, Path("benchmarks/integration/linear.yaml"), None)
 
     # Add process noise
     if config.seed >= 0:
@@ -52,9 +52,7 @@ if __name__ == "__main__":
     start = time.time()
 
     grid = {
-        "c_coefficient": [1.0],
-        "time_horizon": [5, 10],
-        "oversample_factor": [20.0, 40.0, 60.0],
+        "num_oversample": [704],
     }
 
     param_combinations = list(itertools.product(*grid.values()))
@@ -64,8 +62,10 @@ if __name__ == "__main__":
     args_list = [(grid_keys, param_combination) for param_combination in param_combinations]
 
     # Run benchmarks in parallel using multiprocessing
-    with multiprocessing.Pool(processes=max(1, multiprocessing.cpu_count() - 2)) as pool:
+    MAX_PARALLEL = multiprocessing.cpu_count() // 3
+    with multiprocessing.Pool(processes=max(1, MAX_PARALLEL)) as pool:
         pool.starmap(scenario_config, args_list)
+    # scenario_config(*args_list[0])  # Run only one configuration for testing
 
     end = time.time()
     log.info(f"Elapsed time: {end - start}")

### 2025-08-01 benchmarks/integration/Overtaking.py

@@ -48,7 +48,7 @@ if __name__ == "__main__":
 
     grid = {
         # "num_frequencies": [9, 12, 13, 16, 17],
-        "num_frequencies": [5, 6], # [6, 7], 
+        "num_frequencies": [5, 6],  # [6, 7],
         # "num_frequencies": [4],
         "c_coefficient": [1.0],
         "time_horizon": [5],
@@ -63,10 +63,10 @@ if __name__ == "__main__":
     args_list = [(grid_keys, param_combination) for param_combination in param_combinations]
 
     # Run benchmarks in parallel using multiprocessing
-    MAX_PARALLEL = multiprocessing.cpu_count() // 2
-    MAX_PARALLEL = 1
+    MAX_PARALLEL = multiprocessing.cpu_count() // 3
     with multiprocessing.Pool(processes=max(1, MAX_PARALLEL)) as pool:
         pool.starmap(scenario_config, args_list)
+    # scenario_config(*args_list[0])  # Run only one configuration for testing
 
     end = time.time()
     log.info(f"Elapsed time: {end - start}")

### 2025-08-01 benchmarks/integration/TuneBarrier2.py

@@ -1,8 +1,9 @@
 #!/usr/bin/env python3
-from pylucid import *
-from hp_tuning import hp_tuning
 import itertools
 
+from hp_tuning import hp_tuning
+
+from pylucid import *
 
 if __name__ == "__main__":
     val = np.logspace(-5, 5, num=10, endpoint=True, dtype=float)

### 2025-08-01 benchmarks/integration/TuneBarrier3.py

@@ -1,8 +1,9 @@
 #!/usr/bin/env python3
-from pylucid import *
-from hp_tuning import hp_tuning
 import itertools
 
+from hp_tuning import hp_tuning
+
+from pylucid import *
 
 if __name__ == "__main__":
     val = np.logspace(-35, 5, num=10, endpoint=True, dtype=float)

### 2025-08-01 benchmarks/integration/TuneDcMotor.py

@@ -1,15 +1,0 @@
-from hp_tuning import hp_tuning, Parameter
-import numpy as np
-import itertools
-
-if __name__ == "__main__":
-    # Define the grid for tuning parameters
-    val = np.logspace(-5, 1, num=100, endpoint=True, dtype=float)
-    grid = {
-        Parameter.REGULARIZATION_CONSTANT: [1e-3, 1e-4, 1e-5, 1e-6, 1e-7, 1e-8],
-        Parameter.SIGMA_F: [1.0],
-        Parameter.SIGMA_L: [np.array(vs) for vs in itertools.product(val, val)],
-    }
-
-    # Call the scenario tuner with the path to the configuration file and the grid
-    scenario_tuner("benchmarks/integration/dc_motor.yaml", grid)

### 2025-08-01 benchmarks/integration/TuneOvertaking.py

@@ -1,8 +1,9 @@
 #!/usr/bin/env python3
-from pylucid import *
-from hp_tuning import hp_tuning
 import itertools
 
+from hp_tuning import hp_tuning
+
+from pylucid import *
 
 if __name__ == "__main__":
     val = np.logspace(-3, 2, num=10, endpoint=True, dtype=float)

### 2025-08-01 benchmarks/integration/benchmark.py

@@ -63,10 +63,12 @@ def benchmark(name: str, config: Configuration, grid: dict[str, list[Any]]):
 def single_benchmark(name: str, config: Configuration):
     """Run the benchmark scenario."""
     logs: list[str] = []
+
     def handle_log(message: str):
         logs.append(message)
         if "C:" in message:
             print(message)
+
     log.set_sink(handle_log)
     log.set_verbosity(log.LOG_DEBUG)
 

### 2025-08-01 benchmarks/integration/collect_results.py

@@ -1,11 +1,12 @@
-from mlflow import MlflowClient, artifacts
-from mlflow.entities import Run
+import argparse
+from dataclasses import dataclass
+
+import numpy as np
 import pandas as pd
 import requests
-import numpy as np
-from plot_solution import plot_solution_matplotlib, base_load_configuration
-from dataclasses import dataclass
-import argparse
+from mlflow import MlflowClient, artifacts
+from mlflow.entities import Run
+from plot_solution import base_load_configuration, plot_solution_matplotlib
 
 FILTER = 'params.c_coefficient = "1.0" and metrics.run.obj_val > 0 and metrics.run.obj_val < 1 and params.constant_lattice_points = "False" and metrics.run.success = 1'
 

### 2025-08-01 benchmarks/integration/hp_tuning.py

@@ -1,7 +1,8 @@
 #!/usr/bin/env python3
+from typing import TYPE_CHECKING
+
 from pylucid import *
 from pylucid import __version__
-from typing import TYPE_CHECKING
 
 if TYPE_CHECKING:
     from pylucid._pylucid import ParameterValuesType

### 2025-08-01 benchmarks/integration/plot_solution.py

@@ -1,6 +1,7 @@
 import json
-import numpy as np
 from pathlib import Path
+
+import numpy as np
 
 from pylucid import *
 
@@ -12,8 +13,10 @@ except ImportError:
         pass
 
 
-from pylucid import random
 import matplotlib.pyplot as plt
+
+from pylucid import random
+
 
 def plot_solution_matplotlib(
     args: "argparse.Namespace",
@@ -124,7 +127,6 @@ def plot_solution_1d_matplotlib(
     ax.legend(loc="center", ncol=2, fontsize=16, frameon=True)
     fig.tight_layout()
     fig.savefig(f"benchmarks/integration/{args.experiment.lower()}.pgf", bbox_inches="tight", dpi=300)
-
 
     if show:
         plt.show()

### 2025-08-01 bindings/pylucid/dreal.py

@@ -6,11 +6,11 @@ import numpy as np
 from ._pylucid import (
     Estimator,
     MultiSet,
+    PolytopeSet,
     RectSet,
     SphereSet,
     TruncatedFourierFeatureMap,
     log,
-    PolytopeSet,
 )
 
 if TYPE_CHECKING:
@@ -19,12 +19,11 @@ if TYPE_CHECKING:
     from ._pylucid import NMatrix, NVector, Set
 
 try:
-    from dreal import And, CheckSatisfiability, Implies, Not, Or
+    from dreal import And, CheckSatisfiability, Expression, Implies, Not, Or
     from dreal import Variable as Real
     from dreal import cos as Cosine
-    from dreal import sin as Sine
     from dreal import exp as Exp
-    from dreal import Expression
+    from dreal import sin as Sine
 except ImportError as e:
     log.warn("Could not import dreal. Make sure it is installed with 'pip install dreal'")
     raise e
@@ -42,6 +41,7 @@ math_exp = math.exp
 math.cos = lambda x: Cosine(x) if isinstance(x, (Real, Expression)) else math_original_cos(x)
 math.sin = lambda x: Sine(x) if isinstance(x, (Real, Expression)) else math_original_sin(x)
 math.exp = lambda x: Exp(x) if isinstance(x, (Real, Expression)) else math_exp(x)
+
 
 def build_set_constraint(xs: "list", X_set: "Set"):
     """

### 2025-08-01 bindings/pylucid/pipeline.py

@@ -157,7 +157,6 @@ def pipeline(
     u_f_xp_lattice_via_regressor[:, 0] = feature_map.weights[0] * args.sigma_f
     log.debug(f"x_lattice: {x_lattice.shape}, u_f_x_lattice: {u_f_x_lattice.shape}")
 
-
     if args.constant_lattice_points:
         x0_lattice = args.X_init.lattice(num_oversample, True)
         xu_lattice = args.X_unsafe.lattice(num_oversample, True)

### 2025-08-01 tests/bindings/pylucid/TestEstimator.py

@@ -108,7 +108,7 @@ class TestRegression:
 
             # Solving (K + λI) * x = y
             # K = sigma_f^2 * exp(-γ||x_i - x_j||^2)
-            kr = KernelRidge(kernel="rbf", gamma=0.5 * sigma_l ** -2, alpha=reg_coeff * 2)
+            kr = KernelRidge(kernel="rbf", gamma=0.5 * sigma_l**-2, alpha=reg_coeff * 2)
 
             training_inputs = np.array([[1.0, 2.0, 3.0], [4.0, 5.0, 6.0]])
             training_outputs = np.array([[1.0, 2.0], [5.0, 3.0]])

### 2025-08-01 docs/paper/main.tex
feat: update linear results

@@
         \midrule
-        \textbf{\lucid}                                  & \cmark                                          & \cmark                      & \cmark                           & \cmark                         & \cmark                         & \cmark                      \\
+        \textbf{\lucid} (this work)                      & \cmark                                          & \cmark                      & \cmark                           & \cmark                         & \cmark                         & \cmark                      \\
         \trust~\shortcite{gardner2025trust}              & \cmark                                          & \cmark                      & \xmarkred                        & \xmarkred                      & \cmark\footnotemark[1]         & \cmark                      \\
@@
     \item We introduce \lucid, a novel verification engine that learns control barrier certificates from data using kernel-based \glspl{cme}.
-\lucid uses a tractable reformulation of the verification problem via a finite Fourier expansion, enabling efficient barrier synthesis based on a linear program.
+\lucid uses a tractable reformulation of the problem via a finite Fourier expansion, enabling efficient barrier synthesis based on a linear program.
     \item A robust and extensible software implementation, with both C++ and Python interfaces, supporting configuration via YAML, JSON, or Python scripts, and offering both a \gls{cli} and a \gls{gui}.
@@
 
-Although there exist model-\emph{based} efficient solutions to this problem for linear and control affine systems, especially for complex systems this is generally a semi-infinite problem, demanding a data-driven solution.
+Although there exist model-\emph{based} efficient solutions to this problem for linear and control affine systems, this is generally a semi-infinite problem, demanding a data-driven solution.
 Furthermore, for the data-driven case, establishing constraint (c) rigorously without relying on impractical assumptions is extremely challenging.
@@
 We suggest defining it as a \yaml or equivalent \json file.%
-\footnote[4]{The Json schema for \yaml and \json files can be found at \url{https://lucidtoolsource.gitlab.io/lucid/configuration_schema.json}}
+%\footnote[4]{The Json schema for \yaml and \json files can be found at \url{https://lucidtoolsource.gitlab.io/lucid/configuration_schema.json}}
 % \OS{I would personally avoid the word "scenario", as it could be misunderstood with an actual run of the system.}
@@
 \end{lstlisting}
-Alternatively, the samples can either be generated programmatically in the user-provided Python configuration script, or be stored in a separate file.
+Alternatively, the samples can either be generated by the Python configuration script, or be stored in a separate file.
 % Refer to the documentation for more details.
@@
 \begin{itemize}
-    \item \texttt{MedianHeuristicTuner} uses the \emph{median heuristic} \cite{garreau2018largesampleanalysismedian} to produce rule-of-thumb-type estimates for the hyperparameters $\sigma_f$ and $\sigma_l$ of, e.g., the Gaussian kernel \eqref{eq:gaussian_kernel}, via closed-form expressions.
-          This can offer a cheap starting point for successive fine-tuning.
+    \item \texttt{MedianHeuristicTuner} uses the \emph{median heuristic} \cite{garreau2018largesampleanalysismedian} to produce rule-of-thumb-type estimates for the \hp $\sigma_f$ and $\sigma_l$ of, e.g., the Gaussian kernel \eqref{eq:gaussian_kernel}, via closed-form expressions.
+          It can be useful as a starting point for subsequent improvements.
     \item \texttt{LbfgsTuner} finds the \hp that maximize the \emph{log marginal likelihood}~\cite{rasmussen2006gaussian}, defined as
@@
           where $\theta:=(\sigma_f,\sigma_l,\lambda)$ is the hyperparameter being optimized.
-          The \texttt{LbfgsTuner} uses the L-BFGS or L-BFGS-B quasi-Newton optimization algorithms~\cite{book:nonlinear-programming},
-          implemented in the \texttt{LBFGS++} library.\footnote{https://github.com/yixuan/LBFGSpp}
+          We use the L-BFGS or L-BFGS-B quasi-Newton optimization algorithms~\cite{book:nonlinear-programming},
+          implemented in the \texttt{LBFGS++} library~\cite{LBFGSpp}.
+          %          \footnote{https://github.com/yixuan/LBFGSpp}
     \item \texttt{GridSearchTuner} implements the grid search method, exploring the space of possible \hp values to find the one that maximizes the \estimator's $R^2$ score, defined as $$R^2 = 1 - (\sum_{i=1}^M (y_i - \hat{y}_i)^2/\sum_{i=1}^M (y_i - \bar{y})^2).$$
@@
 def scenario_config(c: Configuration):
-    ...
     t = LbfgsTuner(lb=[1e-5], ub=[1e5])
-    c.estimator = KernelRidgeRegressor(
-        kernel=GaussianKernel(),
-    )
+    c.estimator = KernelRidgeRegressor()
     c.estimator.fit(c.x_samples, c.xp_samples, tuner=t)
@@
 \end{lstlisting}
-For the running example, we set the hyperparameters explicitly:
+In this example, we set the \hp explicitly:
 \begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
 sigma_f: 15
-sigma_l: [1.76]
+sigma_l: [1.2]
 lambda: 1.0e-5
@@
 \lucid will parse the configuration, synthesize a barrier certificate and plot the result.
-For the running example, we obtain the barrier certificate shown in Figure~\ref{fig:example} for a time horizon of $T = 15$ certifying safety of the system in \eqref{eq:linear-system} with a probability of at least $93.73\%$ ($\eta = 0.013, \gamma=1.0, c = 0.003$).
+For the running example, we obtain the barrier certificate shown in Figure~\ref{fig:example} for a time horizon of $T = 15$ certifying safety of the system in \eqref{eq:linear-system} with a probability of at least $95.12\%$ ($\eta = 0.03, \gamma=1.0, c = 0.001$).
 %\|B\| = 1.72
@@
     %\resizebox{\columnwidth}{!}{\import{figures}{example.pgf}}
-    \caption{Barrier certificate for the running example.
-        The state space $\X$ is plotted in the X axis, while the value of the barrier $\B$ is plotted in the Y axis.
-        The green line represents the barrier value at time $t$.
+    \caption{Barrier certificate for the example.
+        The value of the barrier $\B$ is plotted against the state space $\X$.
+        The green line represents the barrier value.
         The initial and unsafe sets are highlighted in blue and red respectively. % \Sadegh{Figure not very readable.}
@@
 
-To ascertain the performance of \lucid, we conduct a series of experiments, run on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, NVIDIA GeForce RTX 3090 GPU, and 64 GB of RAM.
+To ascertain the performance of \lucid, we conduct a series of experiments on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, NVIDIA GeForce RTX 3090 GPU, and 64 GB of RAM.
 All runs had the random seed set to $42$ to ensure reproducibility.
@@
 Table~\ref{tbl:benchmarks_results} summarizes the results of all the experiments presented.
-More details about the configurations and \hp used can be found in the Appendix.
+More details about the dynamics, configurations and \hp used can be found in the Appendix.
 
@@
     %\includegraphics[trim={5cm 3cm 2cm 4cm},clip,width=\linewidth]{barrier2.pgf}
-    \caption{\gls{cbc} synthesised for the \barrII benchmark.}
+    \caption{\gls{cbc} synthesized for the \barrII benchmark.}
     \label{fig:CSBarr2}
@@
     %\resizebox{\columnwidth}{!}{\import{figures}{barrier3.pgf}}%
-    \caption{\gls{cbc} synthesised for the \barrIII benchmark.}
+    \caption{\gls{cbc} synthesized for the \barrIII benchmark.}
     \label{fig:CSBarr3}
@@
         \toprule
-                    & \textbf{T} & \textbf{Freq} & \textbf{Lattice} & \textbf{Runtime} & \textbf{Safety} \\
-                    &            &               & \textbf{Size}    & [mm:ss]          & \textbf{Prob}   \\ % Units
+                    & \textbf{T} & \textbf{Freq.} & \textbf{Lattice} & \textbf{Runtime} & \textbf{Safety} \\
+                    &            &                & \textbf{Size}    & [mm:ss]          & \textbf{Prob.}  \\ % Units
         \midrule
-        \linear     & 15         & 5             & $704$            & 00:02            & 93.74\%         \\
+        \linear     & 15         & 5              & $704$            & 00:02            & 95.12\%         \\
         \barrII     & 5          & 15             & $350^2$          & 10:01            & 56.87\%         \\
@@
         The lattice size indicates the number of points of the lattice as the resolution for each dimension raised to the number of dimensions.
-        $T$ is the number of time steps associated with the lower bound on the safety probability, displayed in the last column.
+        $T$ is the time horizon associated with the lower bound on the safety probability, displayed in the last column.
     }

### 2025-08-01 benchmarks/integration/Barrier2.py
chore: clean up benchmarks

@@ -10,10 +10,7 @@ from pylucid import *
 from pylucid import __version__
 
 
-def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) -> Configuration:
-    """Benchmark scenario taken from
-    https://github.com/oxford-oxcav/fossil/blob/10f1f071784d16b2a5ee5da2f51ff2a81d753e2e/experiments/benchmarks/models.py#L350C1-L360C1
-    """
+def scenario_config(param_name: "tuple[str]", param_combinations: "tuple[tuple]") -> Configuration:
     # ################################## #
     # System dynamics
     # ################################## #
@@ -36,21 +33,6 @@ def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) ->
     config.x_samples = config.X_bounds.sample(config.num_samples)
     config.xp_samples = f(config.x_samples)
 
-    # feature_map = config.feature_map(
-    #     num_frequencies=config.num_frequencies,
-    #     sigma_l=config.sigma_l,
-    #     sigma_f=config.sigma_f,
-    #     x_limits=config.X_bounds,
-    # )
-    # config.estimator = ModelEstimator(
-    #     lambda x: feature_map(f(x)),
-    #     {
-    #         Parameter.SIGMA_F: config.sigma_f,
-    #         Parameter.SIGMA_L: config.sigma_l,
-    #         Parameter.REGULARIZATION_CONSTANT: config.lambda_,
-    #     },
-    # )
-
     # ################################## #
     # Running the pipeline
     # ################################## #
@@ -68,14 +50,8 @@ if __name__ == "__main__":
     start = time.time()
 
     grid = {
-        "c_coefficient": [1.0],
-        # "num_frequencies": [9, 12, 13, 16, 17],
-        # "num_frequencies": [15],
-        # "num_frequencies": [4],
-        # "time_horizon": [5],
-        # "oversample_factor": [10.0, 20.0, 30.0],
-        # "num_oversample": [400],
-        # "oversample_factor": [10.0],
+        "num_frequencies": [9, 12, 13, 16, 17],
+        "num_oversample": [400, 500, 600, 700, 800],
     }
 
     param_combinations = list(itertools.product(*grid.values()))

### 2025-08-01 benchmarks/integration/Barrier3.py

@@ -11,9 +11,6 @@ from pylucid import __version__
 
 
 def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) -> Configuration:
-    """Benchmark scenario taken from
-    https://github.com/oxford-oxcav/fossil/blob/10f1f071784d16b2a5ee5da2f51ff2a81d753e2e/experiments/benchmarks/models.py#L350C1-L360C1
-    """
     # ################################## #
     # System dynamics
     # ################################## #
@@ -39,11 +36,6 @@ def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) ->
     # ################################## #
     # Running the pipeline
     # ################################## #
-
-    if config.num_frequencies >= 12 and config.oversample_factor > 20.0:
-        log.warn("The number of frequencies and oversampling factor too high.")
-        return
-
     single_benchmark(
         name="Barrier3",
         config=config,
@@ -58,13 +50,8 @@ if __name__ == "__main__":
     start = time.time()
 
     grid = {
-        "c_coefficient": [1.0],
-        # "num_frequencies": [9, 12, 13, 16, 17],
-        "num_frequencies": [16],
-        # "num_frequencies": [4],
-        # "time_horizon": [5],
-        "num_oversample": [800],  #  , 20.0 , 30.0
-        # "oversample_factor": [10.0],
+        "num_frequencies": [9, 12, 13, 16, 17],
+        "num_oversample": [400, 500, 600, 700, 800],
     }
 
     param_combinations = list(itertools.product(*grid.values()))

### 2025-08-01 benchmarks/integration/Barrier3_orig.py

@@ -11,9 +11,6 @@ from pylucid import __version__
 
 
 def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) -> Configuration:
-    """Benchmark scenario taken from
-    https://github.com/oxford-oxcav/fossil/blob/10f1f071784d16b2a5ee5da2f51ff2a81d753e2e/experiments/benchmarks/models.py#L350C1-L360C1
-    """
     # ################################## #
     # System dynamics
     # ################################## #
@@ -39,11 +36,6 @@ def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) ->
     # ################################## #
     # Running the pipeline
     # ################################## #
-
-    if config.num_frequencies >= 12 and config.oversample_factor > 20.0:
-        log.warn("The number of frequencies and oversampling factor too high.")
-        return
-
     single_benchmark(
         name="Barrier3_orig",
         config=config,

### 2025-08-01 benchmarks/integration/Linear.py

@@ -11,13 +11,9 @@ from pylucid import __version__
 
 
 def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) -> Configuration:
-    """Benchmark scenario taken from
-    https://github.com/oxford-oxcav/fossil/blob/10f1f071784d16b2a5ee5da2f51ff2a81d753e2e/experiments/benchmarks/models.py#L350C1-L360C1
-    """
     # ################################## #
     # System dynamics
     # ################################## #
-    # Algorithm parameters
     config = Configuration()
     action = ConfigAction(option_strings=None, dest="input")
     action(None, config, Path("benchmarks/integration/linear.yaml"), None)

### 2025-08-01 benchmarks/integration/Overtaking.py

@@ -7,7 +7,6 @@ from benchmark import single_benchmark
 
 from pylucid import *
 from pylucid import __version__
-from pylucid.cli import ConfigAction
 
 
 def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) -> Configuration:
@@ -21,18 +20,9 @@ def scenario_config(param_name: tuple[str], param_combinations: tuple[tuple]) ->
     for key, value in zip(param_name, param_combinations):
         setattr(config, key, value)
 
-    # plot_data(
-    #     config.x_samples,
-    #     config.xp_samples,
-    #     X_bounds=config.X_bounds,
-    #     X_init=config.X_init,
-    #     X_unsafe=config.X_unsafe,
-    # )
-
     # ################################## #
     # Running the pipeline
     # ################################## #
-
     single_benchmark(
         name="Overtaking",
         config=config,
@@ -47,13 +37,8 @@ if __name__ == "__main__":
     start = time.time()
 
     grid = {
-        # "num_frequencies": [9, 12, 13, 16, 17],
-        "num_frequencies": [5, 6],  # [6, 7],
-        # "num_frequencies": [4],
-        "c_coefficient": [1.0],
-        "time_horizon": [5],
-        "num_oversample": [100, 110],  #  , 20.0 , 30.0
-        # "oversample_factor": [10.0],
+        "num_frequencies": [5, 6],
+        "num_oversample": [100, 110],
     }
 
     param_combinations = list(itertools.product(*grid.values()))

### 2025-08-11 docs/paper/appendix.tex
feat: update linear results
feat: submitted

--- 2025-07-30 docs/paper/appendix.tex
@@
 \appendix
+\onecolumn
 
@@
 The finitely-constrained LP discussed in Section~\ref{sec:ddbarriers} is presented.
-For this, the lattices $X_{{N}}\subset\X$, $\smash{\{ x_0^{1}, \ldots, x_0^{{N}_0} \}} \subset \X_0$, and $\smash{\{ x_u^{1}, \ldots, x_u^{{N}_u} \}} \subset \X_u$ of cardinality ${N}_0\in\N$ and ${N}_u\in\N$, respectively, are formed.
+For this, the lattices $\smash{\{ x^{1}, \ldots, x^{{N}} \}}\subset\X$, $\smash{\{ x_0^{1}, \ldots, x_0^{{N}_0} \}} \subset \X_0$, and $\smash{\{ x_U^{1}, \ldots, x_U^{N_U} \}} \subset \X_U$ of cardinality $N\in\N$, ${N}_0\in\N$, and $N_U\in\N$, respectively, are formed.
 %
@@
       \begin{alignedat}{3}
-                  & \min_{\stackrel{b, c, \eta}{\Bmin_{{N}}^{\X_0}, \Bmax_{{N}}^{\X_u},\Bmax_{{N}}^\X,\Bmin_\Delta}}\hspace{-1.5em} &                                          & \eta + cT,                                    &                   &
+            & \min_{\stackrel{b, c, \eta}{\Bmin_{{N}}^{\X_0}, \Bmax_{{N}}^{\X_U},\Bmax_{{N}}^\X,\Bmin_\Delta}} &                                          & \eta + cT,                                    &                   &
             %\label{eq:blackbox:linear_prog_objective}
@@
             \\
-                  &                                                                                                                 &                                          & \phi_M(x_u^{i})\T b\geq\hat{\gamma},
-            \quad &                                                                                                                 & i=1,\ldots,{N}_u,
+            &                                                                                                  &                                          & \phi_M(x_U^{i})\T b\geq\hat{\gamma},
+            \quad &                                                                                                  & i=1,\ldots,N_U,
             %\label{eq:blackbox:linear_prog_unsafe}
@@
             \quad &                                                                                                  & i=1,\ldots,{N}_0,                                                                                              \\
-                  &                                                                                                                 &                                          & \Bmax_{{N}}^{\X_u}\geq\phi_M(x_u^{i})\T b,
-            \quad &                                                                                                                 & i=1,\ldots,{N}_u,                                                                                              \\
+            &                                                                                                  &                                          & \Bmax_{{N}}^{\X_U}\geq\phi_M(x_U^{i})\T b,
+            \quad &                                                                                                  & i=1,\ldots,N_U,                                                                                              \\
             &                                                                                                  &                                          & \Bmax_{{N}}^\X\geq\phi_M(x^{i})\T b,
@@
       \hat{\eta}   & := \frac{2}{C_{{N}}+1}\eta + \frac{C_{{N}}-1}{C_{{N}}+1}\Bmin_{{N}}^{\X_0},
-      \\                                                                                                                                    & \hat{\gamma} := \frac{2}{C_{{N}}+1}\gamma + \frac{C_{{N}}-1}{C_{{N}}+1}\Bmax_{{N}}^{\X_u}, \\
+                   &                                                                                                                             & \hat{\gamma} := \frac{2}{C_{{N}}+1}\gamma + \frac{C_{{N}}-1}{C_{{N}}+1}\Bmax_{{N}}^{\X_U}, \\
       \hat{\Delta} & := \frac{2}{C_{{N}}+1}\left(c - \mathcal{R}\overline{\B}\overline{\kappa}\right) + \frac{C_{{N}}-1}{C_{{N}}+1}\Bmin_\Delta,
-      \\                                                                                                                                     & \hat{\xi} := \frac{C_{{N}}-1}{C_{{N}}+1}\Bmax_{{N}}^\X.
+                   &                                                                                                                             & \hat{\xi} := \frac{C_{{N}}-1}{C_{{N}}+1}\Bmax_{{N}}^\X.
 \end{align*}
@@
 
-\section{Tool technical details}
+\section{Tool Technical Details}
 
 \subsection{Installation}
-\OS{Ernesto, can we organise this in a better order?}
 The recommended way to install \pylucid is via the \texttt{pip} package manager, using one of the pre-built wheels,
 hence avoiding the time-consuming need to compile the code from source.
-Provided \texttt{Python>=3.8} is already present, installing \pylucid requires only the command
-\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
-pip install pylucid[gui,plot] --index-url \
-  https://gitlab.com/api/v4/projects/71977529/packages/pypi/simple
+Provided \texttt{Python>=3.8} is already present on the system, \pylucid is installed using a single command:
+%
+\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em,backgroundcolor=\color{ipython_bg}]
+pip install "pylucid[gui,plot]" --index-url https://gitlab.com/api/v4/projects/71977529/packages/pypi/simple
 \end{lstlisting}
-If the desired platform's wheel is not available, \pylucid can be installed from source by cloning the repository and running
-\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em]
-pip install .[gui,plot]
+%
+Note that installing \pylucid this way requires \gurobi to be installed beforehand, which can be obtained for free from the official website.
+A valid license is not required unless the \gurobi solver is used.
+If no wheel is available for the desired platform, \pylucid can be installed from source by running the following commands:
+%
+\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em,backgroundcolor=\color{ipython_bg}]
+git clone https://gitlab.com/lucidtoolsource/lucid.git
+cd lucid
+pip install ".[gui,plot]"
 \end{lstlisting}
+%
 Note that this requires \texttt{Python>=3.8} and \texttt{Bazel>=8.0} to be installed on the system.
@@
 
-\subsection{Platform support}
-Some dependencies \pylucid includes do not support all platforms, which may preclude the ability of using certain features.
-Formal verification of the barrier requires the \dreal SMT solver, which can be installed with \lstinline|pip install dreal|, but only supports Linux and non-ARM macOS.
+\subsection{Containerized Installation}
+
+We also provide a pre-built Docker image that can be used to run \pylucid in a containerized environment, making Docker the only dependency.
+To run the image with the desired configuration, the following command can be used:
+\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em,backgroundcolor=\color{ipython_bg}]
+docker run --name lucid -it --rm \
+  -v/path/to/conf.py:/config \
+  registry.gitlab.com/lucidtoolsource/lucid:latest /config/conf.py
+\end{lstlisting}
+Alternatively, the container can also run the GUI by changing the command to
+\begin{lstlisting}[language=bash,numbers=none,xleftmargin=0em,backgroundcolor=\color{ipython_bg}]
+docker run --name lucid -it --rm \
+  -p 3661:3661 --entrypoint pylucid-gui \
+  registry.gitlab.com/lucidtoolsource/lucid:latest
+\end{lstlisting}
+The GUI will be accessible at \url{http://localhost:3661}.
+In both cases, to use the \gurobi solver, a \gurobi Web License Service (WLS) license\footnote{See \url{https://www.gurobi.com/features/web-license-service/}} will have to be mounted in the container.
+
+\subsection{Platform Support}
+Some of \pylucid's dependencies are not supported on all platforms, which may preclude the ability of using certain features.
+For instance, optional formal verification of the barrier requires the \dreal SMT solver, which can be installed only on Linux and non-ARM macOS.
 The \highs \gls{lp} solver cannot be used on Windows at the moment.
-The \gurobi solver must be installed separately beforehand and requires a licence.
+The \gurobi solver must be installed separately beforehand and requires a licence, which is free for academic use.
+Using the Docker container sidesteps most of these issues, with the only requirement being a CPU with x86-64 architecture.
 
-\subsection{Configuration formats}
-\pylucid provides extensive support for configuration, which can be specified as a \texttt{.yaml} file (recommended), \texttt{.json} file,
-with a \texttt{.py} file returning a \texttt{Configuration} object, or directly via command line arguments.
-Moreover, sampled transitions can be embedded in the configuration file, or be provided separately with \texttt{.csv}, \texttt{.mat}, \texttt{.npy}, or \texttt{.npz} file.
-For example, following configurations will be equivalent:
-\lstinputlisting[language=yaml,caption={Yaml configuration.},captionpos=b,label={lst:configuration.yaml}]{code/configuration.yaml}
-\lstinputlisting[language=json,caption={Json configuration.},captionpos=b,label={lst:configuration.json}]{code/configuration.json}
-\lstinputlisting[language=iPython,style={nonumbers},caption={Python configuration.},captionpos=b,label={lst:configuration.py}]{code/configuration.py}
-\lstinputlisting[language=bash,style={nonumbers},caption={Command line configuration.
-Assumes that the transition samples have been stored as \texttt{.csv} files.},captionpos=b,label={lst:configuration.sh}]{code/configuration.sh}
+\subsection{Configuration Formats}
+\pylucid provides extensive support for various ways of specifying configurations, which can be defined as a \texttt{.yaml} file (recommended), \texttt{.json} file,
+generated via a \texttt{.py} file returning a \texttt{Configuration} object, or provided directly via command line arguments.
+Moreover, system transition data can be either embedded directly in the configuration file or provided separately in the form of \texttt{.csv}, \texttt{.mat}, \texttt{.npy}, or \texttt{.npz} files.
+For example, the following configurations are equivalent:
+
+\begin{minipage}{.45\columnwidth}
+      \lstinputlisting[language=yaml,style={bgnonumbers},caption={YAML configuration.},captionpos=b,label={lst:configuration.yaml},backgroundcolor=\color{ipython_bg}]{code/configuration.yaml}
+\end{minipage}\hfill
+\begin{minipage}{.45\columnwidth}
+      \lstinputlisting[language=json,style={bgnonumbers},caption={JSON configuration.},captionpos=b,label={lst:configuration.json}]{code/configuration.json}
+\end{minipage}
+\begin{minipage}{.45\columnwidth}
+      \lstinputlisting[language=iPython,style={bgnonumbers},caption={Python configuration.},captionpos=b,label={lst:configuration.py}]{code/configuration.py}
+\end{minipage}\hfill
+\begin{minipage}{.45\columnwidth}
+      \lstinputlisting[language=bash,style={bgnonumbers},caption={Command line configuration assuming that the transition samples have been stored as \texttt{.csv} files.},captionpos=b,label={lst:configuration.sh}]{code/configuration.sh}
+\end{minipage}
 
@@
 
-\pylucid provides a \gls{gui} to guide the user in the creation of the scenario configuration and presenting the results in an intuitive way.
-Running \lstinline|pylucid-gui| will open a browser tab containing the interface shown in Figures~[\ref{fig:gui-left},\ref{fig:gui-right}], while a local server will listen for requests coming from the \gls{gui}, computing and returning the results.
+\pylucid provides a \gls{gui} to guide the user in the creation of the scenario configuration and presenting the results in an intuitive format.
+Running \lstinline|pylucid-gui| will open a browser tab with the interface shown in
+%Figures~\ref{fig:gui-left}--\ref{fig:gui-right}, 
+Figure~\ref{fig:gui-full},
+while a local server will listen for requests coming from the \gls{gui}, computing and returning the results.
+Following the same enumeration as the arrows in the figure, we provide a list of the main components of the \gls{gui}:
+
 \begin{figure}
       \centering
-    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
-    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
-    The left half of the screen allows the user to provide the transition samples and the safety specification to verify.
-    }
-    \label{fig:gui-left}
+      \shadowimage[width=16.5cm]{figures/frontend-highlight.png}
+      \caption{
+            \pylucid's \gls{gui} as presented in the browser.
+            The left half of the page allows the user to provide the transition samples and the safety specification to verify.
+            The right half of the page shows the results produced by \lucid, including a plot of the computed barrier function and detailed logs.}
+      \label{fig:gui-full}
 \end{figure}
-\begin{figure}
-    \centering
-    \includegraphics[trim={0 12.4cm 15cm 0},clip,width=.7\linewidth]{figures/frontend.png}
-    \caption{\lucid's \gls{gui} can be accessed via any web browser. 
-    The right half of the screen shows the results produced by \lucid, including a plot of the computed barrier function, 
-    the numerical safety guarantee and , and detailed logs of the computations.
-    }
-    \label{fig:gui-right}
-\end{figure}
+
+\begin{enumerate}
+      \item It is easy to import or export configurations in JSON format.
+            In the \textit{Import} menu, the user can paste the configuration or load it from a file.
+            The experiments discussed in this paper are also available and can be selected from a dropdown list.
+            The \textit{Export} menu can be used to copy the current configuration to the clipboard or download it locally.
+      \item The dimension $n$ of the system is specified. Here, $n=1$.
+      \item  The user can provide transition samples directly by copy--pasting them into the text fields in the Data tab.
+            Alternatively, if a model describing the system’s expected behavior is available, the user can specify it in the Model tab.
+            Lucid will then automatically generate a set of transitions from the model to be used in the computation of the barrier function.
+            Note that this model-based generation is mainly intended for reference and convenience.
+      \item The $x^1,\ldots,x^N$ samples are specified in CSV format. They can be edited manually or loaded from a file.
+      \item The $x^1_+,\ldots,x^N_+$ samples are specified analogously.
+      \item The state space $\X$ is defined by a \texttt{RectSet}. Here, $\X=[-1,1]$.
+      \item The initial set $\X_0$ is defined from one of the available type options. A \texttt{MultiSet} can be defined via the \textit{+} button. Here, $\X_0=[-0.5,0.5]$.
+      \item The unsafe set $\X_U$ is defined analogously. Here, $\X_U=[-1, -0.9] \cup [0.9, 1]$.
+      \item The \textit{Preview} button visualizes the expected stochastic behavior of the black-box system, predicted from the transition samples or alternatively as specified in the \textit{Model} tab,
+            alongside the bounding boxes of the state space $\X$, the initial set $\X_0$, and the unsafe set $\X_U$.
+      \item The \textit{Submit} button starts the computation of the barrier function with the current configuration.
+      \item The plot of the transition function or the computed barrier function.
+      \item The numerical results of the computation, including the lower bound on the safety probability, values of $\eta$ and $c$, and the computation time.
+            If a model of the expected system behavior is provided, it is also possible to formally verify the computed barrier function via \dreal.
+      \item The logs provide information on the progress of the computation, updated in real-time.
+            The verbosity of the logs can be adjusted in the \textit{Advanced} options.
+      \item The main \gls{gui} displays the most important configuration options.
+            More advanced options can be accessed via the \textit{Advanced} button.
+            This includes the kernel \hp, time horizon, number of frequencies and lattice size, \gls{lp} solver selection, etc.
+\end{enumerate}
 
@@
 \label{app:benchmarks}
-Complete list of results for the benchmarks presented in Section~\ref{sec:experiments}.
-The legend is as follows:
-\textit{Output} indicates the result produced by the solver (i.e., optimal, unbounded, infeasible or unspecified),
-\textit{Prec} indicates the number of bits used in the last floating-point number representation,
-\textit{Ref} indicates the number of refinements,
-and \textit{time} is the time in seconds.
-
-All benchmarks were run on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, and 64 GB of RAM, and all runs had the random seed set to $42$ to ensure reproducibility.
-The scripts responsible for running the benchmarks and \hp tuning are available in the \texttt{benchmarks/integration} folder of the repository.
-Note that a version of \texttt{Python>=3.9} is required to run the scripts, as some dependencies used to track the benchmarks' metrics across multiple runs are not compatible with \texttt{Python 3.8}.
-The \hp tuning of the \estimator was performed with the \texttt{LbfgsTuner}, bounding the value of $\sigma_l$ between $[10^{-5}, 10^5]$, and refined with the \texttt{GridSearchTuner}.
-The implementation can be found in the \texttt{benchmarks/integration/hp\_tuning.py} script.
-Note that we used the \gurobi optimiser.
+We provide a more detailed description of the benchmarks presented in Section~\ref{sec:experiments}, including the corresponding configuration files and an extended list of experiments.
+All benchmarks were run on a Windows 10 machine with an AMD Ryzen 9 5950X 16-Core Processor @ 3.40 GHz, NVIDIA GeForce RTX 3090 GPU, and 64 GB of RAM.
+To ensure reproducibility, all runs had the random seed set to $42$.
+We ascertained that the variance of the safety probability is low across different seeds, and can be reduced further by increasing the number of samples used to fit the \estimator.
+The scripts for running the benchmarks and tuning the \hp are available in the \texttt{benchmarks/integration/} folder of the repository.
+Note that \texttt{Python>=3.9} is required to run the scripts, as some dependencies used to track the benchmarks' metrics across multiple runs are not compatible with Python 3.8.
+The hyperparameter tuning of the \estimator was performed with the \texttt{LbfgsTuner}, bounding the value of $\sigma_l$ between $[10^{-5}, 10^5]$, and refined with the \texttt{GridSearchTuner}.
+We use $N=1000$ sample transitions and the \gurobi solver for all experiments;
 Other optimizers, such as \alglib or \highs, can be used instead, but may yield different results, especially in terms of performance.
@@
 
-We consider the following system:
+We consider a black-box system with the following dynamics:
 \begin{equation*}
-      \begin{bmatrix}
-            {x}_{t+1}
-      \end{bmatrix}
-      = \begin{bmatrix}
-            0.5 {x}_{t}
-      \end{bmatrix} + w_t,
+      {x}_{t+1} = 0.5 {x}_{t} + w_t,
 \end{equation*}
 where $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_1)$.
-Given
-\begin{align*}
-       & \X = [-1, 1]                     \\
-       & \X_0 = [-0.5, 0.5]               \\
-       & \X_U = [-1, -0.9] \cup [0.9, 1],
-\end{align*}
+The data sampled from this black-box system is used as input for \lucid.
+Given $\X = [-1, 1]$, $\X_0 = [-0.5, 0.5]$, and $\X_U = [-1, -0.9] \cup [0.9, 1]$,
 we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=15$ time steps.
-The complete configuration for the linear example benchmark is shown in Listing~\ref{lst:linear}.
-\lstinputlisting[language=yaml,caption={Configuration for linear example},captionpos=b,label={lst:linear}]{code/linear.yaml}
+We set the kernel \hp to $\sigma_f=15$, $\sigma_l=1.2$, and $\lambda=0.00001$.
+The complete configuration for the linear example benchmark is shown in Listing~\ref{lst:linear}, with a satisfying barrier plotted in Figure~\ref{fig:example}.
+\lstinputlisting[language=yaml,style={bgnonumbers},caption={Configuration for the linear example.},captionpos=b,label={lst:linear},backgroundcolor=\color{ipython_bg}]{code/linear.yaml}
 
@@
 
-We consider the following system:
+We consider a black-box system with the following nonlinear dynamics:
 \begin{equation*}
@@
       = \begin{bmatrix}
+            {x}_{1, t} \\
+            {x}_{2, t}
+      \end{bmatrix} + 0.1 \begin{bmatrix}
             {x}_{2, t} - 1 + e^{-x_{1, t}} \\
@@
 where $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$.
+The data sampled from this black-box system is used as input for \lucid.
 Given
 \begin{align*}
-       & \X = [ -2, 2 ] \times [ -2 , 2 ]                                  \\
-       & \X_0 = \{ [x_1, x_2] : (x_1 + 0.5)^2 + (x_2 - 0.5)^2 \leq 0.4 \}  \\
+       & \X = [ -2, 2 ] \times [ -2 , 2 ]   ,                              \\
+       & \X_0 = \{ [x_1, x_2] : (x_1 + 0.5)^2 + (x_2 - 0.5)^2 \leq 0.4 \}, \\
        & \X_U = \{ [x_1, x_2] : (x_1 - 0.7)^2 + (x_2 + 0.7)^2 \leq 0.3 \},
@@
 we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=5$ time steps.
-The complete configuration for the \barrII benchmark is shown in Listing~\ref{lst:barrier2}.
-\lstinputlisting[language=yaml,caption={Configuration for \barrII},captionpos=b,label={lst:barrier2}]{code/barrier2.yaml}
+The system dynamics and safety specification are visualized in Figure~\ref{fig:model-barrier2}.
+The kernel \hp are set to $\sigma_f=1$, $\sigma_l=[2.50, 3.78]$, and $\lambda=\smash{10^{-6}}$.
+The complete configuration for the \barrII benchmark is shown in Listing~\ref{lst:barrier2}, with a satisfying barrier is plotted in Figure~\ref{fig:CSBarr2}.
+A list of experiments using different combinations of frequencies and lattice sizes, showing their impact on performance and final result, is presented in Table~\ref{tab:results-barrier2}.
+\lstinputlisting[language=yaml,style={bgnonumbers},caption={Configuration for \barrII.},captionpos=b,label={lst:barrier2}]{code/barrier2.yaml}
+
+\begin{figure}[ht]
+      \centering
+      \input{figures/model-barrier2-noise.pgf}
+      \caption{Visualization of the stochastic system behavior (based on 10 random transitions from an $100\times 100$ grid of initial states) and safety specification for the \barrII benchmark.}
+      \label{fig:model-barrier2}
+\end{figure}
+
+\begin{table}[tb]
+      \centering
+      \begin{tabular}{ccccccc}
+            \toprule
+            \textbf{Freq.} & \textbf{Lattice} & $\eta$ & $\gamma$ & $c$  & \textbf{Runtime} & \textbf{Safety} \\
+                           & \textbf{Size}    &        &          &      & [mm:ss]          & \textbf{Prob.}  \\ % Units
+            \midrule
+            17             & $700^2$          & 0.11   & 2        & 0.12 & 85:50            & 63.46\%         \\
+            16             & $700^2$          & 0.11   & 2        & 0.12 & 57:15            & 63.24\%         \\
+            18             & $600^2$          & 0.13   & 2        & 0.12 & 59:23            & 62.17\%         \\
+            17             & $600^2$          & 0.13   & 2        & 0.12 & 43:53            & 61.93\%         \\
+            16             & $600^2$          & 0.12   & 2        & 0.12 & 33:25            & 61.78\%         \\
+            10             & $800^2$          & 0.11   & 2        & 0.13 & 15:27            & 60.57\%         \\
+            18             & $500^2$          & 0.14   & 2        & 0.13 & 33:56            & 60.12\%         \\
+            17             & $500^2$          & 0.14   & 2        & 0.13 & 24:10            & 59.95\%         \\
+            16             & $500^2$          & 0.14   & 2        & 0.13 & 20:44            & 59.90\%         \\
+            10             & $700^2$          & 0.11   & 2        & 0.13 & 10:47            & 59.80\%         \\
+            9              & $800^2$          & 0.11   & 2        & 0.13 & 10:39            & 59.59\%         \\
+            9              & $700^2$          & 0.12   & 2        & 0.13 & 7:14             & 58.89\%         \\
+            10             & $600^2$          & 0.12   & 2        & 0.13 & 7:20             & 58.80\%         \\
+            9              & $600^2$          & 0.12   & 2        & 0.14 & 5:22             & 57.98\%         \\
+            10             & $500^2$          & 0.13   & 2        & 0.14 & 5:05             & 57.53\%         \\
+            18             & $400^2$          & 0.17   & 2        & 0.13 & 19:09            & 57.16\%         \\
+            15             & $400^2$          & 0.15   & 2        & 0.14 & 10:01            & 56.87\%         \\
+            9              & $500^2$          & 0.13   & 2        & 0.14 & 3:40             & 56.82\%         \\
+            10             & $400^2$          & 0.15   & 2        & 0.14 & 3:22             & 55.78\%         \\
+            9              & $400^2$          & 0.15   & 2        & 0.14 & 2:20             & 55.25\%         \\
+            11             & $300^2$          & 0.18   & 2        & 0.15 & 2:25             & 53.25\%         \\
+            13             & $300^2$          & 0.18   & 2        & 0.15 & 3:53             & 53.16\%         \\
+            10             & $300^2$          & 0.17   & 2        & 0.15 & 1:54             & 53.13\%         \\
+            9              & $300^2$          & 0.17   & 2        & 0.15 & 1:25             & 52.86\%         \\
+            18             & $300^2$          & 0.20   & 2        & 0.14 & 12:04            & 52.58\%         \\
+            20             & $300^2$          & 0.22   & 2        & 0.14 & 16:48            & 51.93\%         \\
+            \bottomrule
+      \end{tabular}
+      \caption{
+            \barrII results, sorted by the last column.
+For each combination of number of frequencies, $M$, and lattice size (i.e., number of lattice points per dimension), we report the values of $c$, $\gamma$, $\lambda$, the runtime, and the achieved lower bound on the safety probability.}
+      \label{tab:results-barrier2}
+\end{table}
 
@@
 
-We consider the following system:
+We consider a black-box system that has the following dynamics:
 \begin{equation*}
@@
       = \begin{bmatrix}
+            {x}_{1, t} \\
+            {x}_{2, t}
+      \end{bmatrix} + 0.1 \begin{bmatrix}
             {x}_{2, t} \\
@@
 where $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$.
+The data sampled from this black-box system is used as input for \lucid.
 Given
@@
 we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=5$ time steps.
-The complete configuration for the \barrIII benchmark is shown in Listing~\ref{lst:barrier3}.
-\lstinputlisting[language=yaml,caption={Configuration for \barrIII},captionpos=b,label={lst:barrier3}]{code/barrier3.yaml}
+The system dynamics and safety specification can be visualized in Figure~\ref{fig:model-barrier3}.
+The kernel \hp were set to $\sigma_f=1$, $\sigma_l=[2.99, 4.63]$, and $\lambda=10^{-8}$.
+The complete configuration for the \barrIII benchmark is shown in Listing~\ref{lst:barrier3}, while the barrier function is plotted in Figure~\ref{fig:CSBarr3}.
+A list of experiments using different combinations of frequencies and lattice sizes, showing their impact on performance and final result, is presented in Table~\ref{tab:results-barrier3}.
+\lstinputlisting[language=yaml,style={bgnonumbers},caption={Configuration for \barrIII.},captionpos=b,label={lst:barrier3}]{code/barrier3.yaml}
+
+\begin{figure}[ht]
+      \centering
+      \input{figures/model-barrier3-noise.pgf}
+      \caption{Visualization of the stochastic system behavior (based on 10 random transitions from an $100\times 100$ grid of initial states) and safety specification for the \barrIII benchmark.}
+      \label{fig:model-barrier3}
+\end{figure}
+
+\begin{table}[tb]
+      \centering
+      \begin{tabular}{cccccccc}
+            \toprule
+            \textbf{Freq.} & \textbf{Lattice} & $\eta$ & $\gamma$ & $c$  & \textbf{Runtime} & \textbf{Runtime Mac} & \textbf{Safety} \\
+                           & \textbf{Size}    &        &          &      & [mm:ss]          & [mm:ss]              & \textbf{Prob.}  \\ % Units
+            \midrule
+            15             & $800^2$          & 0.55   & 2        & 0.11 & 66:56            &                      & 42.25\%         \\
+            16             & $700^2$          & 0.53   & 2        & 0.12 & 52:51            &                      & 41.98\%         \\
+            14             & $800^2$          & 0.58   & 2        & 0.11 & 45:44            &                      & 41.66\%         \\
+            13             & $800^2$          & 0.57   & 2        & 0.12 & 35:51            &                      & 40.72\%         \\
+            14             & $700^2$          & 0.59   & 2        & 0.11 & 32:42            &                      & 40.57\%         \\
+            13             & $700^2$          & 0.60   & 2        & 0.12 & 25:40            &                      & 39.69\%         \\
+            15             & $600^2$          & 0.59   & 2        & 0.12 & 25:12            &                      & 39.57\%         \\
+            12             & $800^2$          & 0.61   & 2        & 0.11 & 27:38            &                      & 39.40\%         \\
+            14             & $600^2$          & 0.60   & 2        & 0.12 & 20:29            &                      & 39.24\%         \\
+            13             & $600^2$          & 0.61   & 2        & 0.12 & 16:39            &                      & 38.50\%         \\
+            12             & $700^2$          & 0.63   & 2        & 0.12 & 19:10            &                      & 38.43\%         \\
+            12             & $600^2$          & 0.64   & 2        & 0.12 & 11:53            &                      & 37.38\%         \\
+            15             & $450^2$          & 0.63   & 2        & 0.12 & 12:07            &                      & 36.15\%         \\
+            14             & $450^2$          & 0.63   & 2        & 0.12 & 9:58             &                      & 36.07\%         \\
+            14             & $400^2$          & 0.65   & 2        & 0.13 & 7:50             &                      & 34.77\%         \\
+            14             & $370^2$          & 0.66   & 2        & 0.13 & 6:49             & 149:48               & 33.58\%         \\
+            16             & $370^2$          & 0.64   & 2        & 0.13 & 11:35            &                      & 33.55\%         \\
+            12             & $370^2$          & 0.71   & 2        & 0.12 & 4:38             &                      & 32.57\%         \\
+            10             & $600^2$          & 0.73   & 2        & 0.12 & 46:40            &                      & 32.46\%         \\
+            9              & $800^2$          & 0.74   & 2        & 0.12 & 53:07            &                      & 31.45\%         \\
+            10             & $500^2$          & 0.76   & 2        & 0.12 & 45:03            &                      & 31.07\%         \\
+            9              & $700^2$          & 0.75   & 2        & 0.12 & 56:43            &                      & 30.78\%         \\
+            11             & $350^2$          & 0.75   & 2        & 0.12 & 3:14             &                      & 30.07\%         \\
+            9              & $600^2$          & 0.77   & 2        & 0.12 & 33:57            &                      & 29.91\%         \\
+            10             & $400^2$          & 0.79   & 2        & 0.12 & 34:09            &                      & 29.37\%         \\
+            9              & $500^2$          & 0.79   & 2        & 0.12 & 33:40            &                      & 28.74\%         \\
+            10             & $350^2$          & 0.81   & 2        & 0.12 & 2:34             &                      & 27.92\%         \\
+            9              & $400^2$          & 0.80   & 2        & 0.12 & 13:07            &                      & 27.29\%         \\
+            10             & $300^2$          & 0.84   & 2        & 0.12 & 8:18             &                      & 26.26\%         \\
+            9              & $350^2$          & 0.83   & 2        & 0.12 & 2:02             &                      & 25.96\%         \\
+            9              & $300^2$          & 0.85   & 2        & 0.13 & 6:35             & 1:21                 & 24.54\%         \\
+            \bottomrule
+      \end{tabular}
+      \caption{\barrIII results, sorted by the last column.
+For each combination of number of frequencies $M$ and lattice size (i.e., number of lattice points per dimension), we report the values of $c$, $\gamma$, $\lambda$, the runtime, and the achieved lower bound on the safety probability.}
+      \label{tab:results-barrier3}
+\end{table}
 
@@
 
-We consider a scenario where an autonomous vehicle (AV) controlled by a \gls{nn} is overtaking another vehicle.
-The dynamics of the ego vehicle are given by Dubin's car model \EC{does it need a cit or is it just textbook} by adding the noise vector $w = \begin{bmatrix}w_t^1 & w_t^2 & w_t^3\end{bmatrix}$ where each component is drawn from a zero-mean Gaussian with standard deviation $0.01$, $0.01$, and $0.001$, respectively.
-The steering wheel angle is supplied by the \gls{nn} controller and we travel at a fixed velocity $v=1$.
-Given
+We consider a scenario where an autonomous vehicle controlled by a \gls{nn} is overtaking another vehicle.
+The dynamics of the ego vehicle are given by Dubin's car model with additive noise $w = \smash{\begin{bmatrix}w_t^1 & w_t^2 & w_t^3\end{bmatrix}\T}$ where each component $w_t^i$ is drawn from a zero-mean Gaussian with standard deviation $0.01$, $0.01$, and $0.001$, respectively.
+The steering wheel angle is supplied by the \gls{nn} controller and we travel at a fixed velocity.
+Given $N=1000$ sample transitions and the sets
 \begin{align*}
-       & \X = [ 1, 90 ] \times [ -7, 19 ] \times [ -\pi, \pi ]         \\
-       & \X_0 = [ 1, 3 ] \times [ -1, 1 ] \times [ -0.5, 0.5 ]         \\
-       & \X_U = [ 1, 90 ] \times [ -7, -6 ] \times [ -\pi, \pi ]       \\
-       & \qquad \cup [ 1, 90 ] \times [ 18, 19 ] \times [ -\pi, \pi ]  \\
-       & \qquad \cup [ 40, 45 ] \times [ -6, 6 ] \times [ -\pi, \pi ],
+       & \X = [ 1, 90 ] \times [ -7, 19 ] \times [ -\pi, \pi ],
+       &                                                        & \X_0 = [ 1, 3 ] \times [ -1, 1 ] \times [ -0.5, 0.5 ],
+       &                                                        & \X_U = [ 1, 90 ] \times [ -7, -6 ] \times [ -\pi, \pi ]                                                                       \\
+       &                                                        &                                                         &  &  & \qquad \cup [ 1, 90 ] \times [ 18, 19 ] \times [ -\pi, \pi ]  \\
+       &                                                        &                                                         &  &  & \qquad \cup [ 40, 45 ] \times [ -6, 6 ] \times [ -\pi, \pi ],
 \end{align*}
 we want to ensure that the system, starting in $\X_0$, does not enter the unsafe regions $\X_U$ within $T=5$ time steps.
+The sampled transitions and safety specification are visualized in Figure~\ref{fig:model-overtaking}.
+The kernel \hp are set to $\sigma_f=7$, $\sigma_l=[10, 7, 5]$, and $\lambda=10^{-5}$.
+The complete configuration for the \overtaking benchmark is shown in Listing~\ref{lst:overtaking}.
+A list of experiments using different combinations of frequencies and lattice sizes, showing their impact on performance and final result, is presented in Table~\ref{tab:results-overtaking}.
+\lstinputlisting[language=yaml,style={bgnonumbers},caption={Configuration for \overtaking.
+The transition samples were generated by a separate script and appended to the configuration, abbreviated here for conciseness.},captionpos=b,label={lst:overtaking}]{code/overtaking.yaml}
 
-The complete configuration for the \overtaking benchmark is shown in Listing~\ref{lst:overtaking}.
-\lstinputlisting[language=yaml,caption={Configuration for \overtaking},captionpos=b,label={lst:overtaking}]{code/overtaking.yaml}
+\begin{figure}[ht]
+      \centering
+      \input{figures/model-overtaking.pgf}
+      \caption{Visualization of $N=200$ sample transitions and safety specification for the \overtaking benchmark.}
+      \label{fig:model-overtaking}
+\end{figure}
+
+\begin{table}[tb]
+      \centering
+      \begin{tabular}{ccccccc}
+            \toprule
+            \textbf{Freq.} & \textbf{Lattice} & $\eta$ & $\gamma$ & $c$  & \textbf{Runtime} & \textbf{Safety} \\
+                           & \textbf{Size}    &        &          &      & [mm:ss]          & \textbf{Prob.}  \\ % Units
+            \midrule
+            5              & $99^3$           & 0.09   & 0.5      & 0.05 & 46:33            & 30.31\%         \\
+            5              & $100^3$          & 0.10   & 0.5      & 0.05 & 49:21            & 29.39\%         \\
+            5              & $88^3$           & 0.09   & 0.5      & 0.05 & 25:52            & 28.73\%         \\
+            5              & $77^3$           & 0.10   & 0.5      & 0.05 & 13:49            & 24.94\%         \\
+            5              & $66^3$           & 0.12   & 0.5      & 0.05 & 8:16             & 16.61\%         \\
+            4              & $90^3$           & 0.10   & 0.5      & 0.06 & 11:21            & 11.79\%         \\
+            4              & $81^3$           & 0.11   & 0.5      & 0.06 & 8:08             & 9.52\%          \\
+            5              & $55^3$           & 0.13   & 0.5      & 0.06 & 4:15             & 9.21\%          \\
+            4              & $72^3$           & 0.10   & 0.5      & 0.06 & 5:10             & 8.46\%          \\
+            5              & $44^3$           & 0.16   & 0.5      & 0.06 & 2:06             & 4.84\%          \\
+            4              & $63^3$           & 0.12   & 0.5      & 0.07 & 3:25             & 4.19\%          \\
+            \bottomrule
+      \end{tabular}
+      \caption{\overtaking results, sorted by the last column.
+For each combination of number of frequencies $M$ and lattice size (i.e., number of lattice points per dimension), we report the values of $c$, $\gamma$, $\lambda$, the runtime, and the achieved lower bound on the safety probability.}
+      \label{tab:results-overtaking}
+\end{table}
+
+\begin{figure}[ht]
+      \centering
+      \input{figures/contour-overtaking.pgf}
+      \caption{Contour plot of the lower bound on the safety probability with respect to the number of frequencies $M$ and the lattice size per dimension for the \overtaking benchmark.}
+      \label{fig:contour-overtaking}
+\end{figure}

### 2025-08-11 docs/paper/figures/steps.tex
feat: update paper
feat: submitted

@@
     \centering
-    \begin{tikzpicture}[node distance=0.6cm and 0.9cm,
-            input-block/.style={rectangle, draw, fill=white, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
-            output-block/.style={rectangle, draw, fill=green!20, text width=3.5cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
+    \begin{tikzpicture}[node distance=0.4cm and 0.9cm,
+            input-block/.style={rectangle, draw, fill=white, text width=2.9cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
+            output-block/.style={rectangle, draw, fill=green!20, text width=2.9cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
             block/.style={rectangle, draw, fill=accent!20, text width=3.7cm, minimum height=1.0cm, align=center, rounded corners, drop shadow=gray!50},
@@
         \node[block, below=of estimator] (feature) {Construct the feature map $\phi_M\colon \X \to \mathbb{R}^{2M+1}$};
-        \node[block, below=of feature] (lattice) {Construct lattices on $\X, \X_0, \X_u$};
+        \node[block, below=of feature] (lattice) {Construct lattices on $\X, \X_0, \X_U$};
         \node[block, below=of lattice] (apply-lattice) {Apply the feature map to the lattice points};
@@
 
-        \node[input-block, left=of lattice] (specification) {Specify $\X, \X_0, \X_u$};
+        \node[input-block, left=of lattice] (specification) {Specify $\X, \X_0, \X_U$};
 
@@
     \caption{Sequence of steps \lucid goes through to generate a barrier certificate.}
+    \vspace{-0.5cm}
     \label{fig:steps}

### 2025-08-11 docs/paper/main.tex
feat: submitted

@@
 % directly follow a colon or long dash
-\title{LUCID: Learning-Enabled Uncertainty-Aware Certification of Stochastic Dynamical Systems}
+\title{
+Supplementary Material for
+``LUCID: Learning-Enabled Uncertainty-Aware Certification of Stochastic Dynamical Systems''}
 %\title{LUCID -- ???}
@@
 \end{equation}
-where $f\colon\X\times\A\times\W\rightarrow\X$ is a continuous vector field describing the evolution of the system state $x_t\in\X\subset\R^n$ over time $t\in\N_{\geq0}$, driven by control actions $a_t\in\A\subset\R^m$ and process noise $w_t\in\W\subset\R^l$.
+where $f\colon\X\times\A\times\W\rightarrow\X$ is a continuous vector field describing the evolution of the system state $x_t\in\X\subset\R^n$ over time $t\in\smash{\N_{\geq0}}$, driven by control actions $a_t\in\A\subset\R^m$ and process noise $w_t\in\W\subset\R^l$.
 The noise is assumed to be drawn from a stochastic distribution $p_w$ in an independent and identically distributed (i.i.d.) manner.
@@
 Furthermore, for unbounded stochasticity $w_t\sim p_w$, there is generally no yes/no answer to safety, but a safety probability $P_{\text{safe}}(\S^\pi)\in[0,1)$. 
-Thus the goal is generally to estimate a \emph{lower bound} on the true safety probability $P_{\text{safe}}(\S^\pi)$.
+Note that given a policy $\pi$, for every initial state $x_0\in\X_0$ there is an associated safety probability.
+Our goal is to estimate a \emph{lower bound} on the infimum of such probabilities across all initial states in $\X_0$.
+% Thus the goal is generally to estimate a \emph{lower bound} on the true safety probability $P_{\text{safe}}(\S^\pi)$.
+\textcolor{blue}{[Paolo] I think this needs clarification: given a policy $\pi$, for every initial state there is a safety probability.
+With Lucid we aim at computing a lower bound on the inf of such probabilities across all initial states.
+Did I understand correctly?}
 
@@
 
-\medskip
+\smallskip
 
-\lucid provides a solution to this problem by automating the steps in Figure~\ref{fig:steps}, outlined in the next sections.
+Available sampling-based methods such as Monte Carlo simulation are unfit to solve this problem, as they compute guarantees for fixed initial conditions $x_0\in\X$.
+\lucid provides a solution for continuous sets $\X_0$ by automating the steps in Figure~\ref{fig:steps}, outlined in the next sections.
 
@@
 Following the same reasoning, the \emph{kernel mean embedding} represents the projection of a probability measure into a \gls{rkhs} via a feature map $\phi$ associated with a positive definite kernel $k$~\cite{Smola2007EmbedDistrb,muandet2017kernel}.
-For conditional probability distributions a similar concept exists: \glspl{cme} can be used to model the expected value of any \gls{rkhs} function $\new{g}\colon\X\rightarrow\R$ under a stochastic process such as $\S$~\cite{park2020measuretheoretic,muandet2017kernel}.
+For conditional probability distributions a similar concept exists: \glspl{cme} can be used to model the expected value of any \gls{rkhs} function $g\colon\X\rightarrow\R$ under a stochastic process such as $\S$~\cite{park2020measuretheoretic,muandet2017kernel}.
 For the Gaussian kernel,
@@
 \end{equation}
-where $\Sigma:=\diag(\sigma_l)^{-2}$, with hyperparameters $\sigma_f,\sigma_l\in\R$, \new{the associated RKHS encompasses all smooth functions $g$}.
+where $\Sigma:=\diag(\sigma_l)^{-2}$, with hyperparameters $\sigma_f,\sigma_l\in\R$, the associated RKHS encompasses all smooth functions $g$.
 A data-driven estimate can then be obtained in closed form from a finite amount of data $\data_N$:
@@
 with the zero-mean Gaussian distribution $\smash{\mathcal{N}(d\omega\mid0,\Sigma)}$ with covariance $\Sigma$, the imaginary unit $\mathbf{i}:=\smash{\sqrt{-1}}$, and where the projection $x \mapsto P(x)$ maps the domain $\X$ into the unit hypercube $[0,1]^{n}$.
-Partitioning the space of spatial frequencies $\omega\in\R^n$ into a set of discrete frequency bands (see Figure~\ref{fig:spectral_barrier}) yields a spectral abstraction of the associated \gls{rkhs}, i.e., characterizing learnable functions $B$ in the form of Fourier series.
+Partitioning the space of spatial frequencies $\omega\in\R^n$ into a set of discrete frequency bands (see Figure~\ref{fig:spectral_barrier}) yields a spectral abstraction of the associated \gls{rkhs}, i.e., characterizing learnable functions $\B$ in the form of Fourier series.
 By truncating the series to a finite number, $M$, of fixed frequency bands $\omega_j\in\R^{n}$, $j\in\{0,\ldots,M\}$, the resulting barriers are of the form
@@
 \end{align*}
-Notably, $\B$ admits the linear form \new{$B(x)=\phi_M(x)\T b$}, with a truncated Fourier feature map $\phi_M\colon\X\rightarrow\R^{2M+1}$, parametrized by learnable spectral amplitudes
+Notably, $\B$ admits the linear form $\B(x)=\phi_M(x)\T b$, with a truncated Fourier feature map $\phi_M\colon\X\rightarrow\R^{2M+1}$, parametrized by learnable spectral amplitudes
 \begin{figure}
     \centering
-    \includegraphics[width=\linewidth]{fourier_series.pdf}
-    \caption{Spectral barrier certificate \new{$B(x)=\phi_M(x)\T b$}.}
+    \includegraphics[width=0.9\linewidth]{fourier_series.pdf}
+    \caption{Spectral barrier certificate $\B(x)=\phi_M(x)\T b$.}
+    \vspace{-0.3cm}
     \label{fig:spectral_barrier}
@@
     \approx
-    \new{\varphi_M(x,a)}\T H,
+    \varphi_M(x,a)\T H,
 \end{equation*}
-where $\Phi_{M,+}^N:=[\phi_M(x_+^i)\T]_{i=1}^N$, \new{$\varphi_M(x,a)\colon\X\times\A\rightarrow\smash{\R^{2M+1}}$ a feature map augmenting $\phi_M(x)$}, and
+where $\Phi_{M,+}^N:=[\phi_M(x_+^i)\T]_{i=1}^N$, $\varphi_M(x,a)\colon\X\times\A\rightarrow\smash{\R^{2M+1}}$ a feature map augmenting $\phi_M(x)$, and
 with an approximation error decreasing exponentially with $M$~\cite{rahimi2007random}.
@@
     \item[(b)] $\forall x_U\in \X_U\colon\,\phi_M(x_U)\T b\geq\gamma$; and
-    \item[(c)] $\forall x\in\X,\,\exists a\in\A\colon\,\new{\varphi_M(x,a)}\T (Hb -b) \leq  c.$
+    \item[(c)] $\forall x\in\X,\,\exists a\in\A\colon\,\varphi_M(x,a)\T (Hb -b) \leq  c.$
 \end{itemize}
-\new{For the case where $a$ is provided by a given fixed policy $\pi$, $\varphi_M(x,a)$ reduces to $\phi_M(x)$.}
+For the case where $a$ is provided by a given fixed policy $\pi$, $\varphi_M(x,a)$ reduces to $\phi_M(x)$.
 % \OS{Importantly, the closed-form estimator in \eqref{eq:empiricalEstimate} does not depend on the choice of features and only through the spectral abstraction is the feature map introduced directly.}
@@
     \caption{Abstraction of a 1-dim. Gaussian spectral measure of the Gaussian kernel, shown in \eqref{eq:sqexp_kernel_fourier}.}
+    \vspace{-0.5cm}
     \label{fig:spectral_measure_abstraction}
@@
 Selecting lattices with a sampling density meeting the Nyquist-Shannon sampling theorem with respect to the highest frequency $\omega_M$ appearing in the barrier and truncated estimator, the relaxation retains all guarantees.
-As a result, the semi-infinite problem is relaxed to a finitely-constrained \gls{lp}, provided in full in {\color{red}the appendix}.
+As a result, the semi-infinite problem is relaxed to a finitely-constrained \gls{lp}, provided in full in the supplementary material.
 Recall that given an appropriate robustness radius, the barriers produced by \lucid based on data $\data_N$ are statistically correct with respect to the unknown true system $\S$, and a lower bound for the safety probability is computed according to \eqref{eq:safety_prob_lb}.
@@
 Hence, for the rest of the paper, we will focus on \pylucid when describing the user interfaces.
-    {\color{red}Further information about \pylucid are deferred to the appendix.}
+Further information about \pylucid are deferred to the supplementary material.
 
@@
 To certify safety of a system, \lucid accepts a configuration comprising data from the system and the safety specification.
-We suggest defining it as a \yaml or equivalent \json file.%
+We suggest defining it as a \yaml or equivalent \json file.
 %\footnote[4]{The Json schema for \yaml and \json files can be found at \url{https://lucidtoolsource.gitlab.io/lucid/configuration_schema.json}}
@@
 \pylucid also provides a browser-based \gls{gui} to aid in the configuration and execution of the tool.
-\Sadegh{space needs fixing before ".. to start ...".}
 
 In its current form, \lucid implements all the functionalities needed to certify safety of a closed-loop system with a given control policy $\pi$.
-\OS{Thus the action $a$ in the previous section is replaced with the policy $\pi(x)$.}
+Thus the action $a$ in the previous section is replaced with the policy $\pi(x)$.
 Future releases will expand this core functionality to
@@
           %          \footnote{https://github.com/yixuan/LBFGSpp}
-    \item \texttt{GridSearchTuner} implements the grid search method, exploring the space of possible \hp values to find the one that maximizes the \estimator's $R^2$ score, defined as $$R^2 = 1 - (\sum_{i=1}^M (y_i - \hat{y}_i)^2/\sum_{i=1}^M (y_i - \bar{y})^2).$$
+    \item \texttt{GridSearchTuner} implements the grid search method, exploring the space of possible \hp values to find the one that maximizes the \estimator's $R^2$ score, defined as $$R^2 = 1 - \textstyle\left(\sum_{i=1}^M (y_i - \hat{y}_i)^2/\sum_{i=1}^M (y_i - \bar{y})^2\right),$$ with $\hat{y}_i$ and $\bar{y}:=(\sum_{i=1}^N y_i)/N$ being the $i^{\text{th}}$ predicted and mean observed outputs, respectively.
 \end{itemize}
@@
 \paragraph{\Circled{4}~Feature Map}
-We exploit the truncated spectral kernel expansion in \eqref{eq:sqexp_kernel_fourier} by building an explicit approximated feature map, composed of a linear sum of trigonometric functions with increasing frequencies (see Figure~\ref{fig:spectral_barrier}).
+We exploit the spectral kernel expansion in \eqref{eq:sqexp_kernel_fourier} by building an explicit approximated feature map, composed of a linear sum of trigonometric functions with increasing frequencies (see Figure~\ref{fig:spectral_barrier}).
 The underlying kernel expansion, visualized in Figure~\ref{fig:spectral_measure_abstraction}, can be controlled to trade-off efficiency and accuracy/conserativeness.
@@
 Different feature map implementations may yield different results.
-In our example, we truncate the Fourier expansion to $5$ frequency bands, including the constant term, and use $704$ lattice points to build the constraints of the optimization problem, to avoid it being too conservative.\OS{Specifying it as a multiple of the Nyquist frequency will inevitably raise questions.
-Just say we generate $X$ lattice points?
-"lattice size"}\EC{new}
+In our example, we truncate the Fourier expansion to $5$ frequency bands, including the constant term, and use $704$ lattice points to build the constraints of the optimization problem, to avoid it being too conservative.
 \begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
@@
 % or adjust the coefficient $C_{\hat{N}}$, improving performance at the cost of loosening the guarantees.
-For solving the \gls{lp}, \lucid can interface with different linear optimizers: \gurobi, \alglib or \highs. Here, we use \gurobi:
+For solving the \gls{lp}, \lucid can interface with different linear optimizers: \gurobi, \alglib, or \highs. Here, we use \gurobi:
 \begin{lstlisting}[language=yaml,backgroundcolor=\color{ipython_bg}]
@@
 Both are two-dimensional highly nonlinear systems to which we add the stochastic noise $w_t\sim\mathcal{N}(\cdotx\vert 0,0.01I_2)$.
-Given the initial set $\X_0$ and the unsafe set $\X_U$, we synthesize a barrier $\B$ that guarantees trajectories starting in $\X_0$ do not enter $\X_U$ within $T=5$ time steps.
+Given $N=1000$ samples, initial set $\X_0$, and unsafe set $\X_U$, we synthesize a barrier $\B$ that guarantees trajectories starting in $\X_0$ do not enter $\X_U$ within $T=5$ time steps.
 Note that we can only certify safety w.r.t. the empirical distribution, i.e., the \gls{cme} constructed from the observed data.
@@
 The synthesized barriers are shown in Figures~\ref{fig:CSBarr2}--\ref{fig:CSBarr3}.
-We also consider a scenario, we name \overtaking, where an autonomous vehicle (AV) controlled by a \gls{nn} is overtaking another vehicle.
+We also consider a scenario, we name \overtaking, where an autonomous vehicle controlled by a \gls{nn} is overtaking another vehicle.
 The dynamics of the ego vehicle are given by Dubin's car model with an added noise vector $w$ where each component is drawn from a zero-mean Gaussian with standard deviation $0.01$, $0.01$, and $0.001$ respectively.
@@
 Table~\ref{tbl:benchmarks_results} summarizes the results of all the experiments presented.
-More details about the dynamics, configurations and \hp used can be found in the Appendix.
+Further results and details on the dynamics, configurations, and \hp can be found in the supplementary material.
 
 \begin{figure}[ht]
-    \begin{adjustbox}{clip,trim=0cm 1.7cm 0cm 2cm,max width=\columnwidth}
+    \begin{adjustbox}{clip,trim=0cm 1.5cm 0cm 2cm,max width=\columnwidth}
         \input{figures/barrier2.pgf}
@@
     \label{tbl:benchmarks_results}
+    \vspace{-0.5cm}
 \end{table}
@@
 \section{Conclusion and Future Extensions}\label{sec:conclusion_and_future_extensions}
-\new{This paper introduces \lucid, a novel tool capable of quantifying safety guarantees for black-box systems with complex stochastic dynamics and deep learning components in the loop.
+This paper introduces \lucid, a novel tool capable of quantifying safety guarantees for black-box systems with complex stochastic dynamics and deep learning components in the loop.
 As such, \lucid fills a gap currently unaddressed by preexisting tools.
-To achieve this, \lucid, leverages Conditional Mean Embeddings (CME) to learn control barrier certificates from data, and recasts the problem into a tractable linear form via a spectral abstraction.}
+To achieve this, \lucid leverages Conditional Mean Embeddings (CME) to learn control barrier certificates from data, and recasts the problem into a tractable linear form via a spectral abstraction.
 
-\new{
 \lucid is built for extensibility.
@@
 The scalability of \lucid can be improved by performing sparse CME computations or specializing the estimator's \texttt{Kernel} to embed prior knowledge about the system dynamics.
-}
 
@@
 % \def\isChecklistMainFile{\FALSE}
-\input{reproducibility checklist/ReproducibilityChecklist}
+% \input{reproducibility checklist/ReproducibilityChecklist}
 

### 2025-08-11 docs/paper/reproducibility checklist/ReproducibilityChecklist.tex
feat: submitted

@@
 	\question{This paper states the number and range of values tried per (hyper-) parameter during development of the paper, along with the criterion used for selecting the final parameter setting}{(yes/partial/no/NA)}
-	Type your response here
+	yes
 
 	\question{Any code required for pre-processing data is included in the appendix}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{All source code required for conducting and analyzing the experiments is included in a code appendix}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{All source code required for conducting and analyzing the experiments will be made publicly available upon publication of the paper with a license that allows free usage for research purposes}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{All source code implementing new methods have comments detailing the implementation, with references to the paper where each step comes from}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{If an algorithm depends on randomness, then the method used for setting seeds is described in a way sufficient to allow replication of results}{(yes/partial/no/NA)}
-	Type your response here
+	yes
 
 	\question{This paper specifies the computing infrastructure used for running experiments (hardware and software), including GPU/CPU models; amount of memory; operating system; names and versions of relevant software libraries and frameworks}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{This paper formally describes evaluation metrics used and explains the motivation for choosing these metrics}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{This paper states the number of algorithm runs used to compute each reported result}{(yes/no)}
-	Type your response here
+	yes
 
 	\question{Analysis of experiments goes beyond single-dimensional summaries of performance (e.g., average; median) to include measures of variation, confidence, or other distributional information}{(yes/no)}
-	Type your response here
+	yes
 
 	\question{The significance of any improvement or decrease in performance is judged using appropriate statistical tests (e.g., Wilcoxon signed-rank)}{(yes/partial/no)}
-	Type your response here
+	yes
 
 	\question{This paper lists all final (hyper-)parameters used for each model/algorithm in the paper’s experiments}{(yes/partial/no/NA)}
-	Type your response here
+	yes
 

### 2025-08-11 docs/paper/shader.tex
feat: submitted

\usepackage{tikz}
\usetikzlibrary{shadows,calc}

% code adapted from https://tex.stackexchange.com/a/11483/3954

% some parameters for customization
\def\shadowshift{3pt,-3pt}
\def\shadowradius{0pt}

\colorlet{innercolor}{black!10}
\colorlet{outercolor}{gray!0}

% this draws a shadow under a rectangle node
\newcommand\drawshadow[1]{
    \begin{pgfonlayer}{shadow}
        \shade[outercolor,inner color=innercolor,outer color=outercolor] ($(#1.south west)+(\shadowshift)+(\shadowradius/2,\shadowradius/2)$) circle (\shadowradius);
        \shade[outercolor,inner color=innercolor,outer color=outercolor] ($(#1.north west)+(\shadowshift)+(\shadowradius/2,-\shadowradius/2)$) circle (\shadowradius);
        \shade[outercolor,inner color=innercolor,outer color=outercolor] ($(#1.south east)+(\shadowshift)+(-\shadowradius/2,\shadowradius/2)$) circle (\shadowradius);
        \shade[outercolor,inner color=innercolor,outer color=outercolor] ($(#1.north east)+(\shadowshift)+(-\shadowradius/2,-\shadowradius/2)$) circle (\shadowradius);
        \shade[top color=innercolor,bottom color=outercolor] ($(#1.south west)+(\shadowshift)+(\shadowradius/2,-\shadowradius/2)$) rectangle ($(#1.south east)+(\shadowshift)+(-\shadowradius/2,\shadowradius/2)$);
        \shade[left color=innercolor,right color=outercolor] ($(#1.south east)+(\shadowshift)+(-\shadowradius/2,\shadowradius/2)$) rectangle ($(#1.north east)+(\shadowshift)+(\shadowradius/2,-\shadowradius/2)$);
        \shade[bottom color=innercolor,top color=outercolor] ($(#1.north west)+(\shadowshift)+(\shadowradius/2,-\shadowradius/2)$) rectangle ($(#1.north east)+(\shadowshift)+(-\shadowradius/2,\shadowradius/2)$);
        \shade[outercolor,right color=innercolor,left color=outercolor] ($(#1.south west)+(\shadowshift)+(-\shadowradius/2,\shadowradius/2)$) rectangle ($(#1.north west)+(\shadowshift)+(\shadowradius/2,-\shadowradius/2)$);
        \filldraw ($(#1.south west)+(\shadowshift)+(\shadowradius/2,\shadowradius/2)$) rectangle ($(#1.north east)+(\shadowshift)-(\shadowradius/2,\shadowradius/2)$);
        % \shade[outercolor,right color=black!40,left color=black!40] ($(#1.north west)+(-\shadowradius/12,\shadowradius/12)$) rectangle ($(#1.south east)+(\shadowradius/12,-\shadowradius/12)$);%Frame
    \end{pgfonlayer}
}

% create a shadow layer, so that we don't need to worry about overdrawing other things
\pgfdeclarelayer{shadow} 
\pgfsetlayers{shadow,main}

\newsavebox\mybox
\newlength\mylen

\newcommand\shadowimage[2][]{
\setbox0=\hbox{\includegraphics[#1]{#2}}
\setlength\mylen{\wd0}
\ifnum\mylen<\ht0
\setlength\mylen{\ht0}
\fi
\divide \mylen by 50
\def\shadowshift{0,0}
\def\shadowradius{\the\dimexpr\mylen+\mylen+\mylen\relax}
\begin{tikzpicture}
\begin{scope}
    \clip [rounded corners=\shadowradius * 0.2] (0,0) rectangle coordinate (centerpoint) (\the\wd0, \the\ht0);
    \node[anchor=south west,inner sep=0] (image) at (0,0) {\includegraphics[#1]{#2}};
\end{scope}
\drawshadow{image}
\end{tikzpicture}
}

### 2025-08-11 docs/paper/code/configuration.py

@@ -8,7 +8,10 @@ def scenario_config() -> Configuration:
     c.seed = 42
     c.X_bounds = RectSet([(-1, 1)])
     c.X_init = RectSet([(-0.5, 0.5)])
-    c.X_unsafe = MultiSet(RectSet([(-1, -0.9)]), RectSet([(0.9, 1)]))
+    c.X_unsafe = MultiSet(
+        RectSet([(-1, -0.9)]), 
+        RectSet([(0.9, 1)]),
+    )
     c.x_samples = np.array([[1.0], [-1.0]])
     c.xp_samples = np.array([[0.5], [-0.5]])
     c.lambda_ = 1.0e-5
@@ -16,5 +19,5 @@ def scenario_config() -> Configuration:
     c.sigma_f = 18.0
     c.sigma_l = 0.034
     c.num_frequencies = 5
-    c.oversample_factor = 64.0
+    c.num_oversample = 700
     return c

### 2025-08-11 docs/paper/code/configuration.sh

@@ -2,12 +2,13 @@ pylucid \
   --seed 42 \
   --X_bounds "RectSet([-1], [1])" \
   --X_init "RectSet([-0.5], [0.5])" \
-  --X_unsafe "MultiSet([RectSet([-1], [-0.9]), RectSet([0.9], [1])])" \
+  --X_unsafe "MultiSet([RectSet([-1], [-0.9]),
+  RectSet([0.9], [1])])" \
   --lambda "1.0e-5" \
   --time_horizon 15 \
   --sigma_f 18.0 \
   --sigma_l 0.034 \
   --num_frequencies 5 \
-  --oversample_factor 64.0 \
+  --num_oversample 700 \
   -i x_samples.csv \
   -o xp_samples.csv

### 2025-08-11 frontend/src/utils/constants.ts
fix: the default examples in the GUI have been updated to match the ones in the paper

@@ -101,12 +101,12 @@ const Barrier2: Partial<Configuration> = {
   c_coefficient: 1,
   estimator: "KernelRidgeRegressor",
   feature_map: "LinearTruncatedFourierFeatureMap",
-  gamma: 100,
+  gamma: 2,
   kernel: "GaussianKernel",
   lambda: 0.000001,
   noise_scale: 0.01,
-  num_frequencies: 15,
-  num_oversample: 350,
+  num_frequencies: 17,
+  num_oversample: 700,
   num_samples: 1000,
   optimiser: "GurobiOptimiser",
   oversample_factor: 1,
@@ -114,8 +114,11 @@ const Barrier2: Partial<Configuration> = {
   seed: 42,
   dimension: 2,
   sigma_f: 1,
-  sigma_l: [2.50, 3.78],
-  system_dynamics: ["x2 - 1 + exp(-x1)", "-sin(x1)**2"],
+  sigma_l: [2.50304, 3.77779],
+  system_dynamics: [
+    "x1 + 0.1 * (x2 - 1 + exp(-x1))",
+    "x2 + 0.1 * (-sin(x1)**2)",
+  ],
   time_horizon: 5,
   verbose: 3,
   verify: false,
@@ -125,7 +128,7 @@ const Barrier3: Partial<Configuration> = {
   verbose: 3,
   seed: 42,
   dimension: 2,
-  system_dynamics: ["x2", "-x1 - x2 + 1 / 3 * x1 ** 3"],
+  system_dynamics: ["x1 + 0.1 * x2", "x2 + 0.1 * (-x1 - x2 + 1 / 3 * x1 ** 3)"],
   x_samples: [],
   xp_samples: [],
   X_bounds: [
@@ -172,17 +175,16 @@ const Barrier3: Partial<Configuration> = {
   ],
   gamma: 2,
   c_coefficient: 1,
-  lambda: 0.000001,
+  lambda: 1e-08,
   num_samples: 1000,
   time_horizon: 5,
   sigma_f: 1.0,
   sigma_l: [2.99266, 4.62946],
-  num_frequencies: 4,
-  oversample_factor: 32,
-  num_oversample: -1,
+  num_frequencies: 15,
+  num_oversample: 800,
   noise_scale: 0.01,
   plot: true,
-  verify: true,
+  verify: false,
   estimator: "KernelRidgeRegressor",
   feature_map: "LinearTruncatedFourierFeatureMap",
   optimiser: "GurobiOptimiser",
[…]

### 2025-08-11 frontend/src/utils/constants.ts
fix: plot and verify will require both capabilities and config

@@ -192,7 +192,7 @@ const Barrier3: Partial<Configuration> = {
 };
 
 const Overtaking: Partial<Configuration> = {
-  verbose: 4,
+  verbose: 3,
   seed: 42,
   dimension: 3,
   X_bounds: [

### 2025-08-11 frontend/src/utils/utils.ts

@@ -50,8 +50,8 @@ export function capableConfiguration<T extends Partial<Configuration>>(
       : capabilities.ALGLIB
       ? "AlglibOptimiser"
       : "HighsOptimiser",
-    plot: capabilities.PLOT,
-    verify: capabilities.VERIFICATION,
+    plot: capabilities.PLOT && config.plot,
+    verify: capabilities.VERIFICATION && config.verify,
   };
 }
 
